### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
added poster so far

\documentclass[final]{beamer}
%Poster Packages: 
\usepackage[orientation=lanscape,size=a0]{beamerposter}
%General Packages:
\usepackage{amsmath,amsthm, amssymb, latexsym}
%TikZ:
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\input{arrowsnew}

%Theme:
\mode<presentation>{\usetheme{I6pd2}}

\graphicspath{{figures/}}

\newlength{\columnheight}
\setlength{\columnheight}{105cm}

\title{\huge Modeling Intervention Strategies for TB Control in the United States}
\author{Jessica Ginepro, Emma Hartman, Ryo Kimura, Matthew McDermott, Colin
        Pawlowski, \& Dylan Shepardson}
\institute[MHC]{Mathematical Modeling Group, Mount Holyoke College, South
                Hadley, MA, USA}
\date[July 31, 2013]{July 31, 2013}
\begin{document}
%For the compartmental models:
\tikzstyle{compartment} = [rectangle, draw, fill=blue!20, text badly centered,
  node distance=3.8em, inner sep=0.4em, rounded corners]
\tikzstyle{compartment rate} = [right of=start, color=black, node distance=2.2em,
text width=3em]
%TODO: Increase arrow head size
\tikzstyle{line} = [draw, -latexnew, arrowhead = 7mm]

\begin{frame}
  \begin{columns}
    \begin{column}{.3\textwidth}
      \begin{block}{Introduction}
        Compartmental models are often used to model disease spread in the
        population. The canonical example of such a model is the SIR model,
        which has three compartments: Susceptible, Infected, and Recovered. The
        dynamics of a population modeled by this framework are shown in
        figure~\ref{fig:SIRFlowchart}, with associated system of
        differential equations~\ref{eq:SIRdes}.
        %TODO equalize figure heights
        \begin{block}{}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{center}
                \begin{tikzpicture}
                  \node [compartment] (S) {Susceptible (S)};
                  \node [compartment, below of=S] (I) {Infected (I)};
                  \node [compartment, below of=I] (R) {Recovered (R)};
                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
                \end{tikzpicture}
              \end{center}
              \caption{This flowchart depicts the standard SIR epidemiological
                       model. It is accomponanied by the system of differential
                       equations~\ref{eq:SIRdes}.}
              \label{fig:SIRFlowchart}
            \end{figure}
          \end{column}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{align*}
                \frac{dS}{dt} &= -\beta S(t)I(t) \\
                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
                \frac{dR}{dt} &= \gamma I(t)\\
              \end{align*}
              \caption{The system of differential equations governing the SIR
                       model.}
              \label{eq:SIRdes}
            \end{figure}
          \end{column}
        \end{block}
      \end{block}
    \end{column}
    \begin{column}{.3\textwidth}
      \begin{block}{Intervention Analysis}
        Intervention Analysis
      \end{block}
    \end{column}
    \begin{column}{.3\textwidth}
      \begin{block}{An Agent Based Implementation}
        Implementing an Agent Based Framework
      \end{block}
    \end{column}
  \end{columns}
\end{frame}
\end{document}

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex

@@
       \begin{block}{Introduction}
-        Compartmental models are often used to model disease spread in the
-        population. The canonical example of such a model is the SIR model,
-        which has three compartments: Susceptible, Infected, and Recovered. The
-        dynamics of a population modeled by this framework are shown in
-        figure~\ref{fig:SIRFlowchart}, with associated system of
+        The most common epidemiological models are compartmental models, in
+        which a system of differential equations describes how parts of the
+        population move between different disease states, or
+        \emph{compartments}. The canonical example of such a model is the SIR
+        model, which has three compartments: Susceptible, Infected, and
+        Recovered. The dynamics of a population modeled by this framework are
+        shown in figure~\ref{fig:SIRFlowchart}, with associated system of
         differential equations~\ref{eq:SIRdes}.
@@
         \end{block}
+        The SIR system, though very informative about basic disease dynamics,
+        fails to capture the intricacies of more complicated diseases. This
+        project examines the spread of tuberculosis (TB) in the United States
+        (US) via compartmental models and stochastic, agent-based models. These
+        explorations allow one to explore the impact, both epidemiological and
+        economic, of various intervention strategies. These models are based on
+        a 2012 compartmental model of TB in the US created by A. N. Hill, J. E.
+        Becerra, and K. G. Castro.
+      \end{block}
+      \begin{block}{The Basic Hill Model}
       \end{block}

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
added hill flow chart
added Hill explanation

--- 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
@@
         \end{block}
+        The SIR system, though very informative about basic disease dynamics,
+        fails to capture the intricacies of more complicated diseases. This
+        project examines the spread of tuberculosis (TB) in the United States
+        (US) via compartmental models and stochastic, agent-based models. These
+        explorations allow one to explore the impact, both epidemiological and
+        economic, of various intervention strategies. These models are based on
+        a 2012 compartmental model of TB in the US created by A. N. Hill, J. E.
+        Becerra, and K. G. Castro.
+      \end{block}
+      \begin{block}{The Basic Hill Model}
+        The Hill model is another compartmental model, illustrated in
+        figure~\ref{fig:hillFlow}.
+        \begin{block}{}
+          \begin{column}{.39\textwidth}
+            \begin{figure}[h]
+              \begin{center}
+                \includegraphics[scale=.25]{HillModelFlowChart}
+              \end{center}
+              \caption{The Hill Model}
+              \label{fig:hillFlow}
+            \end{figure}
+          \end{column}
+          \begin{column}{.39\textwidth}
+            The illustration of this model is not full, as there are two
+            subpopulations in the Hill Model. TB dynamics in the US differ
+            radically between US born (USB) individuals and foreign born (FB)
+            individuals,  so this model maintains two distinct populations in
+            which the disease can spread. There is a near identical diagram to
+            describe the dynamics of the model for the FB population. 
+          \end{column}
+        \end{block}
       \end{block}

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
still working on poster

@@
         %TODO equalize figure heights
+        \vspace{-3em}
         \begin{block}{}
@@
                 \frac{dR}{dt} &= \gamma I(t)\\
+                N             &= S(t) + I(t) + R(t)\\
               \end{align*}
@@
         figure~\ref{fig:hillFlow}.
+        \vspace{-2em}
         \begin{block}{}
-          \begin{column}{.39\textwidth}
+          \begin{column}{.2\textwidth}
             \begin{figure}[h]
@@
               \end{center}
-              \caption{The Hill Model}
+              \caption{A flow chart representing the compartments of the Hill
+                       Model.}
               \label{fig:hillFlow}
@@
           \end{column}
-          \begin{column}{.39\textwidth}
+          \begin{column}{.6\textwidth}
             The illustration of this model is not full, as there are two
@@
             which the disease can spread. There is a near identical diagram to
-            describe the dynamics of the model for the FB population. 
+            describe the dynamics of the model for the FB population. Further,
+            each compartment in this model also loses people to do natural
+            death. The system of differential equations for this model is
+            naturally more complex and is provided in an appendix. In order to
+            implement this model, Hill, Becerra, and Castro used the \texttt{R}
+            programming language, with the \texttt{lsoda} routine to numerically
+            solve the differential equations. 
           \end{column}
         \end{block}
+        For this implementation, various numerical solvers were implemented,
+        including an Eulerian Method, a Quadratic Method, a Fourth-order runge
+        kutta method, and the $\texttt{lsoda}$ routine. Once the basic Hill
+        model was implemented, further tracking capabilities were added as well
+        as economic modeling. This implementation tracks total active TB cases,
+        entering cases of LTBI, and treatment costs for active and latent disease
+        for all populations. Tracking was used to evaluate various interventions
+        explored in Hill, Becerra, and Castro's work, as well as interventions
+        exploring the possibility of treating incoming LTBI cases.
       \end{block}

### 2013-07-26 in_progress/models/costBenefitAnalysis/interventionGroupsPresenter.R
working on groupspresenter

@@ -57,16 +57,16 @@ for (interventionName in redEnLTBI_Interventions) {
   #Implementation cost of intervention
   costOfInter[[y]] <- (interventionData$interventionCost)/1e9
   #Savings from intervention
-  saveOfInter[[y]] <- baseHCSCost - interHCSCost
+  saveOfInter[[y]] <- baseHCSCost - interHCSCost[[y]]
   #Total US HCS cost due to intervention
-  interTot[[y]] <- interHCSCost + costOfInter
+  interTot[[y]] <- interHCSCost[[y]] + costOfInter[[y]]
   #Total additional spent by US HCS due to intervention
-  totSpent[[y]]  <- interTot - baseHCSCost 
+  totSpent[[y]]  <- interTot[[y]] - baseHCSCost 
   
   #Cost per cases averted
   intCasesD         <- 1e6*(interventionData$progTotalD0 + interventionData$progTotalD1)
   casesAvertedD     <- baseCasesD - intCasesD
-  cpcaDataD <- 1e9*totSpent/casesAvertedD
+  cpcaDataD <- 1e9*totSpent[[y]]/casesAvertedD
   
   y <- y + 1
 }
@@ -99,15 +99,14 @@ x <- ggplot(redEnLTBI,aes(x=year)) +
        labs(x="Years", y="Billions of USD") +
        scale_y_continuous(breaks=yrange) + 
        plotTitle("Costs, Savings, and Net Costs for 
-                  100%, 75%, and 50% LTBI reduction") + 
+                  100%, 75%, and 50% LTBI reduction","") + 
        geom_line(aes(y=redEnLTBI100_costs, color=costsC)) +
        geom_line(aes(y=redEnLTBI75_costs, color=costsC)) +
        geom_line(aes(y=redEnLTBI50_costs, color=costsC)) +
-       geom_line(aes(y=redEnLTBI100_savings, color=savingsC) +
-       geom_line(aes(y=redEnLTBI75_savings, color=savingsC) +
-       geom_line(aes(y=redEnLTBI50_savings, color=savingsC) +
+       geom_line(aes(y=redEnLTBI100_savings, color=savingsC)) +
+       geom_line(aes(y=redEnLTBI75_savings, color=savingsC)) +
+       geom_line(aes(y=redEnLTBI50_savings, color=savingsC)) +
        geom_line(aes(y=redEnLTBI100_totCost, color='black')) +
[…]

### 2013-07-26 in_progress/models/agentHillModel/cppStrictHill/agentbasedStrictHill.cpp
removed fast vs. chronic separate compartments within the model, but updatePop still keeps them as two compartments for the purpose of graphing

@@ -9,6 +9,7 @@
 #include <stdlib.h>
 #include <stdio.h>
 #include <sstream>
+#include <time.h>
 #include "turtleStrictHill.hpp"
 using namespace std;
 
@@ -30,6 +31,7 @@ const int    totT     = (int) (finalYr/DELTA_T);
 const int newCases0 = 8714; //US-born
 const int newCases1 = 7554; //Foreign-born
 
+int chron = 0;
 
 turtleList population;
 
@@ -47,23 +49,32 @@ int I1[totT];
 int J1[totT];
 double cost[totT];
 
+  /*time_t start = time(NULL);
+  time_t stop = time(NULL);
+  double runtime = difftime(stop,start);*/
+
+
+
 /* 
  * void updatePop(...)
  *
  * This functions updates the population lists given the number of turtles of 
  * the given states. It returns nothing, as it is a state updating function.
  */
-void updatePop(const turtle::State &turtState, const turtle::COB &cob, int timeStep, 
+void updatePop(const turtle::State &turtState, const turtle::COB &cob, int timeStep, int timeinfec,
                int numTurtles = 1)
 {
   switch(cob) {
     case turtle::USA:
       switch(turtState) {
-        case turtle::CHRONIC_LTBI:
-          L0[timeStep] += numTurtles;
-          break;
-        case turtle::ACUTE_LTBI:
-          F0[timeStep] += numTurtles;
+        case turtle::LATENT:
+          if (timeinfec < 40)
+          {
+            F0[timeStep] += numTurtles;
+          }
+          else{
+            L0[timeStep] += numTurtles;
+          }
           break;
         case turtle::INFECTIOUS_TB:
           I0[timeStep] += numTurtles;
@@ -82,11 +93,14 @@ void updatePop(const turtle::State &turtState, const turtle::COB &cob, int timeS
       break;
     case turtle::OTHER:
       switch(turtState) {
-        case turtle::CHRONIC_LTBI:
-          L1[timeStep] += numTurtles;
-          break;
-        case turtle::ACUTE_LTBI:
-          F1[timeStep] += numTurtles;
+        case turtle::LATENT:
+          if (timeinfec < 40)
+          {
[…]

### 2013-07-26 in_progress/models/agentHillModel/cppStrictHill/plotData.R

@@ -4,6 +4,7 @@ vL1 <- 0.0010     #Progression rate for reactivation (chronic LTBI) in the FB po
 popConst <- 1000
 
 generateIncidence <- function(dataSet) {
+  
   IN0   <- 1e6 * (vF*dataSet$F0 + vL0*dataSet$L0)/dataSet$N0
   IN1   <- 1e6 * (vF*dataSet$F1 + vL1*dataSet$L1)/dataSet$N1
   INall <- 1e6 * (vF*(dataSet$F0 + dataSet$F1) + vL0*dataSet$L0 + vL1*dataSet$L1)/(dataSet$N0 + dataSet$N1)

### 2013-07-26 in_progress/models/agentHillModel/cppStrictHill/turtleStrictHill.cpp

@@ -10,22 +10,27 @@ using namespace std;
 
 
 const char* countryNames[2] = {"USA", "Other"};
-const char* stateNames[7] = {"Acute Latent (F)", "Chronic Latent (L)", "Infectious TB (I)",
-							"Non-Infectious TB (J)", "Susceptible (S)", "TB Death", "Natural Death"};
+const char* stateNames[6] = {"Infectious TB (I)",
+							"Non-Infectious TB (J)", "Susceptible (S)", "TB Death", "Natural Death", "Latent (L)"};
 
 //Implementation
 //Constructor
-turtle::turtle(const COB &c, const State &s)
-  : country(c), state(s)
+turtle::turtle(const COB &c, const State &s, int timeinfec)
+  : country(c), state(s), timeinfec(timeinfec)
 {}
 
 bool turtle::dead() {
   return (state == NATURAL_DEATH || state == TB_DEATH);
 }
 
+int turtle::InfecChange(){
+  return timeinfec - prevtime;
+}
+
 //Updates turtle state
 void turtle::updateState(){
   //Initializations
+  prevtime = timeinfec;
   double r  = (double)rand()/RAND_MAX; //random number from (0,1]
   if(country == USA){
     if (r < MU0) {  //Natural death rate (USB)
@@ -35,29 +40,32 @@ void turtle::updateState(){
     r -= MU0;  //Natural death rate probability accounted for
 
     //Disease progression and self-cure
-    if (state == CHRONIC_LTBI) {
-      if (r < PROB_CHRONIC_PROGRESSION_0) {  //Disease progression from Chronic Latent to Active TB (USB)
-        if (r < q*PROB_CHRONIC_PROGRESSION_0) {
-          state = INFECTIOUS_TB;
-        } else {
-          state = NONINFECTIOUS_TB;
+    if (state == LATENT) {
+      timeinfec++;
+      if (timeinfec < 2/DELTA_T) {
+        if(r < PROB_ACUTE_PROGRESSION){  //Disease progression from Acute Latent to Active TB
+          if(r < q*PROB_ACUTE_PROGRESSION) {
+            state = INFECTIOUS_TB;
+          } else {
+            state = NONINFECTIOUS_TB;
+          }
+          return;
+        } else if (r - PROB_ACUTE_PROGRESSION < PROB_ACUTE_LATENT_CURE_0) {
+          state = SUSCEPTIBLE;
+          return;
[…]

### 2013-07-26 in_progress/models/agentHillModel/cppStrictHill/turtleStrictHill.hpp

@@ -57,28 +57,33 @@ public:
     OTHER = 1
   };
   enum State {  // Health state
-    ACUTE_LTBI       = 0,
-    CHRONIC_LTBI     = 1,
+    //ACUTE_LTBI       = 0,
+    //CHRONIC_LTBI     = 1,
     INFECTIOUS_TB    = 2,
     NONINFECTIOUS_TB = 3,
     SUSCEPTIBLE      = 4,
     TB_DEATH         = 5,
-    NATURAL_DEATH    = 6
+    NATURAL_DEATH    = 6,
+    LATENT           = 7
   };
-  turtle(const COB &c, const State &s);
+  turtle(const COB &c, const State &s, int timeinfec);
   bool dead();
   void updateState();
   void display();
   COB getCountry();
   State getState();
   void reinfect();
+  int InfectionTime();
+  int InfecChange();
 
 private:
   COB country;
   State state;
+  int prevtime;
+  int timeinfec;
 };
 
 extern const char* countryNames[2];
-extern const char* stateNames[7];
+extern const char* stateNames[6];
 
 #endif /* defined(____turtle__) */

### 2013-07-26 in_progress/models/agentHillModel/cppStrictHill/agentbasedStrictHill.cpp
cleaned up cppStrictHill

@@ -49,11 +49,6 @@ int I1[totT];
 int J1[totT];
 double cost[totT];
 
-  /*time_t start = time(NULL);
-  time_t stop = time(NULL);
-  double runtime = difftime(stop,start);*/
-
-
 
 /* 
  * void updatePop(...)
@@ -163,12 +158,7 @@ int run(string rfname)
 
   N0[0] = initUSP;
   N1[0] = initFBP;
-  //Acute (Fast) LTBI, new cases
-  // createTurtles(turtle::ACUTE_LTBI, turtle::USA, 0, initF0);
-  // createTurtles(turtle::ACUTE_LTBI, turtle::OTHER, 0, initF1);
-  //Chronic (Long) LTBI
-  // createTurtles(turtle::CHRONIC_LTBI, turtle::USA, 0, initL0);
-  // createTurtles(turtle::CHRONIC_LTBI, turtle::OTHER, 0, initL1);
+
   //LATENT LTBI
   createTurtles(turtle::LATENT, turtle::USA, 0, initF0, 1);
   createTurtles(turtle::LATENT, turtle::OTHER, 0, initF1, 1);
@@ -213,11 +203,10 @@ int run(string rfname)
 			turtleIter != population.end(); ++turtleIter)
 		{
 		  turtle &t = *turtleIter;
-      //cout<<t.InfectionTime()<<endl;
   
       //Update the turtle's state
       t.updateState();
-      //time_t start = time(NULL);
+
       if (t.dead())
       {
         turtleList::iterator newIter = population.erase(turtleIter);
@@ -243,7 +232,7 @@ int run(string rfname)
         }
       }
     }
-    //time_t startfor = time(NULL);
+
     // Agent independent Population Changes during this time step: 
     // Note that these did not affect infection likelihood during
     // this time step.
@@ -285,9 +274,6 @@ int run(string rfname)
     N0[i]    = S0[i] + L0[i] + F0[i] + I0[i] + J0[i];
     N1[i]    = S1[i] + L1[i] + F1[i] + I1[i] + J1[i];
     cost[i] += cost[i-1];
-    //time_t stopfor = time(NULL);
-    //double forruntime = difftime(stopfor,startfor);
-    //cout<<"For runtime: "<<forruntime<<endl;
   }
   // write data to file
   exportData(rfname);
@@ -299,9 +285,6 @@ int main(int argc, char const *argv[])
   vector<string> args(argv + 1, argv + argc);
   int numruns;
   int runnumber;
-  // Loop over command-line args
[…]

### 2013-07-26 in_progress/models/agentHillModel/cppStrictHill/agentbasedStrictHill.cpp
cleaned up cppStrictHill more

@@ -9,7 +9,6 @@
 #include <stdlib.h>
 #include <stdio.h>
 #include <sstream>
-#include <time.h>
 #include "turtleStrictHill.hpp"
 using namespace std;
 
@@ -30,8 +29,6 @@ const int    totT     = (int) (finalYr/DELTA_T);
 //TODO upon moving over constants, fix them here.
 const int newCases0 = 8714; //US-born
 const int newCases1 = 7554; //Foreign-born
-
-int chron = 0;
 
 turtleList population;
 
@@ -63,7 +60,7 @@ void updatePop(const turtle::State &turtState, const turtle::COB &cob, int timeS
     case turtle::USA:
       switch(turtState) {
         case turtle::LATENT:
-          if (timeinfec < 40)
+          if (timeinfec <= 2/DELTA_T)
           {
             F0[timeStep] += numTurtles;
           }
@@ -89,7 +86,7 @@ void updatePop(const turtle::State &turtState, const turtle::COB &cob, int timeS
     case turtle::OTHER:
       switch(turtState) {
         case turtle::LATENT:
-          if (timeinfec < 40)
+          if (timeinfec <= 2/DELTA_T)
           {
             F1[timeStep] += numTurtles;
           }

### 2013-07-26 in_progress/models/agentHillModel/cppStrictHill/turtleStrictHill.cpp

@@ -42,7 +42,7 @@ void turtle::updateState(){
     //Disease progression and self-cure
     if (state == LATENT) {
       timeinfec++;
-      if (timeinfec < 2/DELTA_T) {
+      if (timeinfec <= 2/DELTA_T) {
         if(r < PROB_ACUTE_PROGRESSION){  //Disease progression from Acute Latent to Active TB
           if(r < q*PROB_ACUTE_PROGRESSION) {
             state = INFECTIOUS_TB;
@@ -88,7 +88,7 @@ void turtle::updateState(){
     //Disease progression and self-cure
     if (state == LATENT) {
       timeinfec++;
-      if (timeinfec < 2/DELTA_T) {
+      if (timeinfec <= 2/DELTA_T) {
         if(r < PROB_ACUTE_PROGRESSION){  //Disease progression from Acute Latent to Active TB
           if(r < q*PROB_ACUTE_PROGRESSION) {
             state = INFECTIOUS_TB;

### 2013-07-26 in_progress/models/costBenefitAnalysis/interventionGroupsPresenter.R
updated popConst in NetLogo model to match C++ def

@@ -2,6 +2,15 @@ library(ggplot2)
 source('interventionGroups.R')
 source('deSolConstants.R')
 
+#Title Generation:
+plotTitle <- function(base,interventionName,final="") {
+  if (final != "") {
+    return(ggtitle(paste(c(base,interventionName,final),collapse=" ")))
+  } else {
+    return(ggtitle(paste(c(base,interventionName),collapse=" ")))
+  }
+}
+
 baseData <- read.csv(baseFile)
 #Base Incidence
 baseInc <- generateIncidence(baseData)

### 2013-07-26 in_progress/models/costBenefitAnalysis/interventionGroupsPresenter.R
adding pdfs for the poster

@@ -2,6 +2,15 @@ library(ggplot2)
 source('interventionGroups.R')
 source('deSolConstants.R')
 
+#Title Generation:
+plotTitle <- function(base,interventionName,final="") {
+  if (final != "") {
+    return(ggtitle(paste(c(base,interventionName,final),collapse=" ")))
+  } else {
+    return(ggtitle(paste(c(base,interventionName),collapse=" ")))
+  }
+}
+
 baseData <- read.csv(baseFile)
 #Base Incidence
 baseInc <- generateIncidence(baseData)
@@ -9,6 +18,20 @@ baseInc <- generateIncidence(baseData)
 baseHCSCost <- (baseData$cN0 + baseData$cN1)/1e9
 baseCasesD <- 1e6*(baseData$progTotalD0 + baseData$progTotalD1)
 
+#Data Labels
+USB             <- rep("USB",                 totT)
+FB              <- rep("FB",                  totT)
+all             <- rep("All",                 totT)
+noInt           <- rep("No Intervention",     totT)
+int             <- rep("Intervention",        totT)
+savings         <- rep("Savings",             totT)
+costs           <- rep("Implementation Cost", totT)
+totalCosts      <- rep("US HCS Cost",         totT)
+averted         <- rep("Cases Averted",       totT)
+TBdeathsAverted <- rep("TB Deaths Averted",   totT)
+redEnLTBI100L   <- rep("100% reduction",      totT)
+redEnLTBI75L    <- rep("75% reduction",       totT)
+redEnLTBI50L    <- rep("50% reduction",       totT)
 # #Tables
 # redEnLTBIcostTable <- matrix(nrow=5,ncol=30)
 # redEnLTBIcpcaDTable <- matrix(nrow=5,ncol=30)
@@ -88,25 +111,27 @@ redEnLTBI <- data.frame(year = years,
                         redEnLTBI100_costs   = costOfInter[[1]], 
                         redEnLTBI75_costs    = costOfInter[[2]], 
                         redEnLTBI50_costs    = costOfInter[[3]],
-                        redEnLTBI100_savings = saveOfInter[[1]], 
-                        redEnLTBI75_savings  = saveOfInter[[2]], 
-                        redEnLTBI50_savings  = saveOfInter[[3]],
+                        redEnLTBI100_savings = -1*saveOfInter[[1]], 
[…]

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
Added economic modeling description to beamer poster

@@
     \begin{column}{.3\textwidth}
+      \begin{block}{Economic Modeling}
+        We extended our basic implementation of the Hill model to incorporate
+        economic data of treatment costs for Active and Latent Tuberculosis.  
+        In our model, we estimate the average heath care costs to be \$14,014.90
+        and \$403.45 to treat a single case of Active or Latent TB respectively.  
+        Given these costs and the average treatment rates for Active and Latent
+        TB in the USA, we modeled the expected economic burden of Tuberculosis
+        projected over the next hundred years.        
+      \end{block}
       \begin{block}{Intervention Analysis}

### 2013-07-26 in_progress/models/costBenefitAnalysis/helpers.R
added some helper functions I made, and some more graphs for the poster

@@ -1,0 +1,76 @@
+acuteLatentFBL    <- rep("Acute Latent (FB)",totT)
+chronicLatentFBL  <- rep("Chronic Latent (FB)", totT)
+acuteLatentUSBL   <- rep("Acute Latent (USB)",totT)
+chronicLatentUSBL <- rep("Chronic Latent (USB)", totT)
+activeInfecFBL    <- rep("Active Infectious TB (FB)",totT)
+activeNoInfecFBL  <- rep("Active Non-infectious TB (FB)", totT)
+activeInfecUSBL   <- rep("Active Infectious TB (USB)",totT)
+activeNoInfecUSBL <- rep("Active Non-infectious TB (USB)", totT)
+
+generateSourcedIncidence <- function(dataSet) {
+  with(as.list(parms), {
+    IdF0  <- 1e6 * vF  * dataSet$F0
+    IdF1  <- 1e6 * vF  * dataSet$F1
+    IdL0  <- 1e6 * vL0 * dataSet$L0
+    IdL1  <- 1e6 * vL1 * dataSet$L1
+	  return(data.frame(IdF0,IdF1,IdL0,IdL1))
+  })
+}
+
+baseSourcedInc <- generateSourcedIncidence(baseData)
+IdL1c <- baseSourcedInc$IdL1
+IdF1c <- IdL1c + baseSourcedInc$IdF1
+IdL0c <- IdF1c + baseSourcedInc$IdL0
+IdF0c <- IdL0c + baseSourcedInc$IdF0
+baseCumulativeSourcedInc <- data.frame(year=years,IdL1c,IdF1c,IdL0c,IdF0c)
+incPlotSourced <- ggplot(baseCumulativeSourcedInc, aes(x=year)) + 
+           labs(x="Years", y="Incidence", fill="Population and Health State") + 
+           plotTitle("Incidence Levels due to Various 
+Populations With No Intervention","") +
+           geom_ribbon(aes(ymin=0,    ymax=IdL1c,fill=chronicLatentFBL))  + 
+           geom_ribbon(aes(ymin=IdL1c,ymax=IdF1c,fill=acuteLatentFBL))    + 
+           geom_ribbon(aes(ymin=IdF1c,ymax=IdL0c,fill=chronicLatentUSBL)) + 
+           geom_ribbon(aes(ymin=IdL0c,ymax=IdF0c,fill=acuteLatentUSBL))
+
+
[…]

### 2013-07-26 in_progress/models/costBenefitAnalysis/hillFunctions.R

@@ -183,3 +183,41 @@ generateIncidence <- function(dataSet) {
 	  return(data.frame(IN0,IN1,INall))
   })
 }
+
+generateTotalIncidence <- function(dataSet,incLTBI=1,transmission=1,f=fBase) {
+  with(as.list(parms), {
+    #proportion of contacts made with FB individuals  (USB)
+    c01          <- (1-e0)*((1-e1)*dataSet$N1)/((1-e0)*dataSet$N0 + 
+                    (1-e1)*dataSet$N1)
+    #proportion of contacts made with USB individuals (USB)
+    c00          <- 1 - c01
+    c10          <- (1-e1)*((1-e0)*dataSet$N0)/((1-e0)*dataSet$N0 + 
+                    (1-e1)*dataSet$N1)
+    #proportion of contacts made with USB individuals (FB)
+    c11          <- 1 - c10
+    #proportion of contacts made with FB individuals  (FB)
+    #Forces of Infection (USB)
+    lambda0      <- transmission*(beta*(c00*(dataSet$I0/dataSet$N0) + 
+                                        c01*(dataSet$I1/dataSet$N1)))
+    #Forces of Infection (FB)
+    lambda1      <- transmission*(beta*(c10*(dataSet$I0/dataSet$N0) + 
+                                        c11*(dataSet$I1/dataSet$N1)))
+
+
+    IN0   <- 1e6 * (vF*dataSet$F0 + vL0*dataSet$L0)/dataSet$N0
+    IN1   <- 1e6 * (vF*dataSet$F1 + vL1*dataSet$L1)/dataSet$N1
+    INall <- 1e6 * (vF*(dataSet$F0 + dataSet$F1) + vL0*dataSet$L0 + 
+                    vL1*dataSet$L1)/(dataSet$N0 + dataSet$N1)
+    IL0   <- 1e6 * ((1-p) * lambda0 * dataSet$S0)
+    IL1   <- 1e6 * ((1-p) * lambda1 * dataSet$S1 + (1-g*p) * f * alpha * incLTBI
+                    * (dataSet$N0 + dataSet$N1))
+    IF0   <- 1e6 * (p     * lambda0 * dataSet$S0 + x * p * lambda0 * L0)
[…]

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
added a caption to net costs, savings graph on poster

@@
     \begin{column}{.3\textwidth}
+      \begin{block}{TB Reduction Strategies for the United States}
+        From the Hill model, we 
+      \end{block}
+      \begin{block}{Intervention Analysis}
+        Intervention Analysis
+        \begin{figure}[h]
+          \begin{center}
+            \includegraphics[scale=1]{incidencePlotRedEnLTBI.pdf}
+          \end{center}
+          \caption{caption here!}
+          \label{fig:redEnLTBI_costs}
+        \end{figure}
+      \end{block}
       \begin{block}{Economic Modeling}
@@
         projected over the next hundred years.
-      \end{block}
-      \begin{block}{Intervention Analysis}
-        Intervention Analysis
+
+        \begin{figure}[h]
+          \begin{center}
+            \includegraphics[scale=1]{EnLTBIRedGroupCost.pdf}
+          \end{center}
+          \caption{A graph of the cumulative implementation costs, savings, and 
+                       net US health care system costs of reducing rates of LTBI in
+                       Foreign-born arrivals by 50\%, 75\%, and 100\%.  To determine the 
+                       implementation cost for each intervention, the average cost
+                       to identify and treat entering Foreign-born individuals with LTBI
+                       was set to be \$600, \$800, and \$1000 for the 50\%, 75\%, 
+                       and 100\% reduction strategies respectively.}
+          \label{fig:redEnLTBI_costs}
+        \end{figure}
       \end{block}

### 2013-07-26 in_progress/models/costBenefitAnalysis/helpers.R
still working

@@ -55,6 +55,40 @@ incPlotTotalAll <- ggplot(baseCumulativeInc, aes(x=year)) +
            geom_ribbon(aes(ymin=IL0c,ymax=II0c,fill=activeInfecUSBL))   + 
            geom_ribbon(aes(ymin=II0c,ymax=IJ0c,fill=activeNoInfecUSBL))
 
+interventionTypes <- list('redEnLTBI','redImm','incLTBItrmt')
+interventionMags <- list(redEnLTBI=list(50,75,100),redImm=list(50,75),
+                         incLTBItrmt=list(100,300))
+incDataTypeGrouped <- list()
+for (interventionType in interventionTypes) {
+  dataL = list()
+  incDataTypeGrouped[[interventionType]] = dataL
+}
+
+incPlotTypeGroupedG <- function(incDataTypeGrouped, type) {
+  data <- incDataTypeGrouped[[type]]
+  return(
+  ggplot(data.frame(year=years, baseInc), aes(x=year)) + 
+         scale_y_log10(breaks=c(1,2,5,10,25,50,100,200),
+                       labels=c("Elimination (1)",2,5,10,25,50,100,200),
+                       limits=c(0.5,250)) + 
+         labs(x="Years", y="Incidence/million", color="Population", 
+                linetype="Intervention Status") + 
+         plotTitle("Incidence Levels for Various Reductions of Entering LTBI","") +
+         geom_line(aes(y=IN0,   color=USB, linetype=noInt))  + 
+         geom_line(aes(y=IN1,   color=FB,  linetype=noInt))  + 
+         geom_line(aes(y=INall, color=all, linetype=noInt))  + 
+         geom_line(aes(y=redEnLTBI100USB, color=USB, linetype=redEnLTBI100L))  + 
+         geom_line(aes(y=redEnLTBI100FB, color=FB, linetype=redEnLTBI100L))  + 
+         geom_line(aes(y=redEnLTBI100All, color=all, linetype=redEnLTBI100L))  + 
+         geom_line(aes(y=redEnLTBI75USB, color=USB, linetype=redEnLTBI75L))  + 
+         geom_line(aes(y=redEnLTBI75FB, color=FB, linetype=redEnLTBI75L))  + 
+         geom_line(aes(y=redEnLTBI75All, color=all, linetype=redEnLTBI75L))  + 
[…]

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
added caption for Incidence plot in beamer poster
added agentbased section to poster

@@
           \end{center}
-          \caption{caption here!}
+          \caption{A graph of the projected incidence levels per million in
+                       the US-born, Foreign-born, and Total US population, given
+                       that LTBI rates in Foreign-born arrivals are reduced by 
+                       0\%, 50\%, 75\%, and 100\%.}
           \label{fig:redEnLTBI_costs}
@@
       \begin{block}{An Agent Based Implementation}
-        Implementing an Agent Based Framework
+        In addition to the extended Hill model (implemented in R), we also
+        created a stochastic agent-based counterpart in both NetLogo and C++.
+        Stochastic models add notions of uncertainty into the model structure,
+        while agent-based models simulate global behavior of the system by
+        describing local behavior of individual agents in the population.
+
+        Figure~\ref{fig:NLHMinc} shows the incidence rate over time for both
+        the R and NetLogo models. Although the NetLogo model is stochastic, its
+        incidence rates roughly coincide with those given by the R model. With the
+        C++ model (figure~\ref{fig:finalRun}), we obtain even better convergence.
+        \begin{block}{}
+          \begin{column}{.45\textwidth}
+            \begin{figure}[h]
+              \begin{center}
+                \includegraphics[width=\textwidth]{NLHMinc}
+              \end{center}
+              \caption{Incidence per million for R and NetLogo models (12 runs)}
+              \label{fig:NLHMinc}
+            \end{figure}
+          \end{column}
+          \begin{column}{.45\textwidth}
+            \begin{figure}[h]
+              \begin{center}
+                \includegraphics[width=\textwidth]{finalRunSmall}
+              \end{center}
+              \caption{Incidence per million for R and C++ models (2100 runs)}
+              \label{fig:finalRun}
+            \end{figure}
+          \end{column}
+        \end{block}
       \end{block}

### 2013-07-26 in_progress/models/costBenefitAnalysis/helpers.R
some helper functions in helpers.R now produce plots of grouped incidence for all intervention types, and specifiable intervention magnitudes. Hopefully adaptable to groups of interventions as well

@@ -55,38 +55,59 @@ incPlotTotalAll <- ggplot(baseCumulativeInc, aes(x=year)) +
            geom_ribbon(aes(ymin=IL0c,ymax=II0c,fill=activeInfecUSBL))   + 
            geom_ribbon(aes(ymin=II0c,ymax=IJ0c,fill=activeNoInfecUSBL))
 
-interventionTypes <- list('redEnLTBI','redImm','incLTBItrmt')
+
+intLabels <- function(type,magnitude) {
+  redEnLTBI100L   <- rep("100% Reduction in Entering LTBI", totT)
+  redEnLTBI75L    <- rep("75% Reduction in Entering LTBI",  totT)
+  redEnLTBI50L    <- rep("50% Reduction in Entering LTBI",  totT)
+  redImm50L       <- rep("50% Reduction in Immigration",    totT)
+  redImm75L       <- rep("75% Reduction in Immigration",    totT)
+  incLTBItrmt100L <- rep("100% Increase in Immigration",    totT)
+  incLTBItrmt300L <- rep("300% Increase in Immigration",    totT)
+  redTrans100L    <- rep("100% Reduction in Transmission",  totT)
+  #TODO: This is not the best way to do this
+  return(eval(as.name(paste(c(type,magnitude,'L'),collapse=""))))
+}
+
+interventionTypes <- list('redEnLTBI','redImm','incLTBItrmt','redTrans')
 interventionMags <- list(redEnLTBI=list(50,75,100),redImm=list(50,75),
-                         incLTBItrmt=list(100,300))
+                         incLTBItrmt=list(100,300),redTrans=list(100))
 incDataTypeGrouped <- list()
 for (interventionType in interventionTypes) {
   dataL = list()
+  mags  = interventionMags[[interventionType]]
+  for (mag in mags) {
+    magnitude = as.character(mag)
+    dataName  = paste(c(interventionType,magnitude),collapse="")
+    dataL[[magnitude]] = incDataList[[dataName]]
+  }
   incDataTypeGrouped[[interventionType]] = dataL
 }
 
-incPlotTypeGroupedG <- function(incDataTypeGrouped, type) {
+incPlotTypeGroupedG <- function(type, incDataTypeGrouped=incDataTypeGrouped) {
   data <- incDataTypeGrouped[[type]]
-  return(
-  ggplot(data.frame(year=years, baseInc), aes(x=year)) + 
-         scale_y_log10(breaks=c(1,2,5,10,25,50,100,200),
[…]

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
formatting poster 1

@@
 %Poster Packages: 
-\usepackage[orientation=lanscape,size=a0]{beamerposter}
+%\usepackage[orientation=lanscape,size=a0]{beamerposter}
+%dimensions are in cm, scale is for font size
+\usepackage[size=custom,height=91.4,width=121.9,scale=1.8]{beamerposter}
 %General Packages:
@@
     \begin{column}{.3\textwidth}
-      \begin{block}{Introduction}
-        The most common epidemiological models are compartmental models, in
-        which a system of differential equations describes how parts of the
-        population move between different disease states, or
-        \emph{compartments}. The canonical example of such a model is the SIR
-        model, which has three compartments: Susceptible, Infected, and
-        Recovered. The dynamics of a population modeled by this framework are
-        shown in figure~\ref{fig:SIRFlowchart}, with associated system of
-        differential equations~\ref{eq:SIRdes}.
+%      \begin{block}{Introduction}
+%        The most common epidemiological models are compartmental models, in
+%        which a system of differential equations describes how parts of the
+%        population move between different disease states, or
+%        \emph{compartments}. The canonical example of such a model is the SIR
+%        model, which has three compartments: Susceptible, Infected, and
+%        Recovered. The dynamics of a population modeled by this framework are
+%        shown in figure~\ref{fig:SIRFlowchart}, with associated system of
+%        differential equations~\ref{eq:SIRdes}.
         %TODO equalize figure heights
-        \vspace{-3em}
+%        \vspace{-3em}
+%        \begin{block}{}
+%          \begin{column}{.39\textwidth}
+%            \begin{figure}[h]
+%              \begin{center}
+%                \begin{tikzpicture}
+%                  \node [compartment] (S) {Susceptible (S)};
+%                  \node [compartment, below of=S] (I) {Infected (I)};
+%                  \node [compartment, below of=I] (R) {Recovered (R)};
+%                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
+%                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
+%                \end{tikzpicture}
+%              \end{center}
+%              \caption{This flowchart depicts the standard SIR epidemiological
+%                       model. It is accomponanied by the system of differential
+%                       equations~\ref{eq:SIRdes}.}
+%              \label{fig:SIRFlowchart}
+%            \end{figure}
+%          \end{column}
+%          \begin{column}{.39\textwidth}
+%            \begin{figure}[h]
+%              \begin{align*}
+%                \frac{dS}{dt} &= -\beta S(t)I(t) \\
+%                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
+%                \frac{dR}{dt} &= \gamma I(t)\\
+%                N             &= S(t) + I(t) + R(t)\\
+%              \end{align*}
+%              \caption{The system of differential equations governing the SIR
+%                       model.}
+%              \label{eq:SIRdes}
+%            \end{figure}
+%          \end{column}
+%        \end{block}
+%        The SIR system, though very informative about basic disease dynamics,
+%        fails to capture the intricacies of more complicated diseases. This
+%        project examines the spread of tuberculosis (TB) in the United States
+%        (US) via compartmental models and stochastic, agent-based models. These
+%        explorations allow one to explore the impact, both epidemiological and
+%        economic, of various intervention strategies. These models are based on
+%        a 2012 compartmental model of TB in the US created by A. N. Hill, J. E.
+%        Becerra, and K. G. Castro.
+%      \end{block}
+
+      \begin{block}{The Basic Hill Model}
         \begin{block}{}
-          \begin{column}{.39\textwidth}
             \begin{figure}[h]
               \begin{center}
-                \begin{tikzpicture}
-                  \node [compartment] (S) {Susceptible (S)};
-                  \node [compartment, below of=S] (I) {Infected (I)};
-                  \node [compartment, below of=I] (R) {Recovered (R)};
-                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
-                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
-                \end{tikzpicture}
-              \end{center}
-              \caption{This flowchart depicts the standard SIR epidemiological
-                       model. It is accomponanied by the system of differential
-                       equations~\ref{eq:SIRdes}.}
-              \label{fig:SIRFlowchart}
-            \end{figure}
-          \end{column}
-          \begin{column}{.39\textwidth}
-            \begin{figure}[h]
-              \begin{align*}
-                \frac{dS}{dt} &= -\beta S(t)I(t) \\
-                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
-                \frac{dR}{dt} &= \gamma I(t)\\
-                N             &= S(t) + I(t) + R(t)\\
-              \end{align*}
-              \caption{The system of differential equations governing the SIR
-                       model.}
-              \label{eq:SIRdes}
-            \end{figure}
-          \end{column}
-        \end{block}
-        The SIR system, though very informative about basic disease dynamics,
-        fails to capture the intricacies of more complicated diseases. This
-        project examines the spread of tuberculosis (TB) in the United States
-        (US) via compartmental models and stochastic, agent-based models. These
-        explorations allow one to explore the impact, both epidemiological and
-        economic, of various intervention strategies. These models are based on
-        a 2012 compartmental model of TB in the US created by A. N. Hill, J. E.
-        Becerra, and K. G. Castro.
-      \end{block}
-      \begin{block}{The Basic Hill Model}
-        The Hill model is another compartmental model, illustrated in
-        figure~\ref{fig:hillFlow}.
-        \vspace{-2em}
-        \begin{block}{}
-          \begin{column}{.2\textwidth}
-            \begin{figure}[h]
-              \begin{center}
-                \includegraphics[scale=.25]{HillModelFlowChart}
+                \includegraphics[scale=.75]{HillModelFlowChart}
               \end{center}
@@
             \end{figure}
-          \end{column}
-          \begin{column}{.6\textwidth}
-            The illustration of this model is not full, as there are two
-            subpopulations in the Hill Model. TB dynamics in the US differ
-            radically between US born (USB) individuals and foreign born (FB)
-            individuals,  so this model maintains two distinct populations in
-            which the disease can spread. There is a near identical diagram to
-            describe the dynamics of the model for the FB population. Further,
-            each compartment in this model also loses people to do natural
-            death. The system of differential equations for this model is
-            naturally more complex and is provided in an appendix. In order to
-            implement this model, Hill, Becerra, and Castro used the \texttt{R}
-            programming language, with the \texttt{lsoda} routine to numerically
-            solve the differential equations. 
-          \end{column}
         \end{block}
+%            The illustration of this model is not full, as there are two
+%            subpopulations in the Hill Model. TB dynamics in the US differ
+%            radically between US born (USB) individuals and foreign born (FB)
+%            individuals,  so this model maintains two distinct populations in
+%            which the disease can spread. There is a near identical diagram to
+%            describe the dynamics of the model for the FB population. Further,
+%            each compartment in this model also loses people to do natural
+%            death. The system of differential equations for this model is
+%            naturally more complex and is provided in an appendix. In order to
+%            implement this model, Hill, Becerra, and Castro used the \texttt{R}
+%            programming language, with the \texttt{lsoda} routine to numerically
+%            solve the differential equations.
+
         For this implementation, various numerical solvers were implemented,
@@
     \end{column}
+
     \begin{column}{.3\textwidth}
@@
                        0\%, 50\%, 75\%, and 100\%.}
-          \label{fig:redEnLTBI_costs}
+          \label{fig:redEnLTBI_incidence}
         \end{figure}
@@
         describing local behavior of individual agents in the population.
-
-        Figure~\ref{fig:NLHMinc} shows the incidence rate over time for both
-        the R and NetLogo models. Although the NetLogo model is stochastic, its
-        incidence rates roughly coincide with those given by the R model. With the
-        C++ model (figure~\ref{fig:finalRun}), we obtain even better convergence.
         \begin{block}{}
@@
       \end{block}
+
+      \begin{block}{Stochastic Models as a Measure of Variability}
+      \end{block}
+
+      \begin{block}{Future Extensions}
+      \end{block}
+
     \end{column}

### 2013-07-26 in_progress/models/agentHillModel/cppCostStrict/agentbasedCostHill.cpp
incorporated cost structure into cpp, running well

@@ -1,0 +1,343 @@
+//  agentbasedCostHill.cpp
+
+#include <iostream>
+#include <fstream>
+#include <list>
+#include <random>
+#include <chrono>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <sstream>
+#include "turtleCostHill.hpp"
+using namespace std;
+
+const bool debug = false;
+
+typedef list<turtle> turtleList;
+
+double lambda0;
+double lambda1;
+
+const double discRate = 1.03;
+double popConst; //For now
+const int    finalYr  = 100;
+const int    totT     = (int) (finalYr/DELTA_T);
+
+//2010 New Cases in Population
+//source: http://www.cdc.gov/mmwr/preview/mmwrhtml/mm5105a3.htm
+//TODO upon moving over constants, fix them here.
+const int newCases0 = 8714; //US-born
+const int newCases1 = 7554; //Foreign-born
+
+turtleList population;
+
+int N0[totT];
+int S0[totT];
+int L0[totT];
+int F0[totT];
+int J0[totT];
+int I0[totT];
+int N1[totT];
+int S1[totT];
+int L1[totT];
+int F1[totT];
+int I1[totT];
+int J1[totT];
+double cost[totT];
+
+
+
+/* 
+ * void updatePop(...)
+ *
+ * This functions updates the population lists given the number of turtles of 
+ * the given states. It returns nothing, as it is a state updating function.
+ */
+void updatePop(const turtle::State &turtState, const turtle::COB &cob, int timeStep, int timeinfec,
+               int numTurtles = 1, bool discount = true)
+{ double discV = 1/(pow(1.03,timeStep*DELTA_T));
+  if (discount == false)
+  {
+    discV=1;
+  }
+  switch(cob) {
+    case turtle::USA:
+      switch(turtState) {
+        case turtle::LATENT:
+          if (timeinfec <= 2/DELTA_T)
+          {
+            F0[timeStep] += numTurtles;
+          }
+          else{
+            L0[timeStep] += numTurtles;
+          }
+          break;
+        case turtle::INFECTIOUS_TB:
+          I0[timeStep] += discV*numTurtles;
+          break;
+        case turtle::NONINFECTIOUS_TB:
+          J0[timeStep] += discV*numTurtles;
+          break;
[…]

### 2013-07-26 in_progress/models/agentHillModel/cppCostStrict/plotData.R

@@ -1,0 +1,95 @@
+vF <- 1.5         #Progression rate of acute infection per year
+vL0 <- 0.0014     #Progression rate for reactivation (chronic LTBI) in the USB population per year
+vL1 <- 0.0010     #Progression rate for reactivation (chronic LTBI) in the FB population per year
+popConst <- 1000
+
+generateIncidence <- function(dataSet) {
+  
+  IN0   <- 1e6 * (vF*dataSet$F0 + vL0*dataSet$L0)/dataSet$N0
+  IN1   <- 1e6 * (vF*dataSet$F1 + vL1*dataSet$L1)/dataSet$N1
+  INall <- 1e6 * (vF*(dataSet$F0 + dataSet$F1) + vL0*dataSet$L0 + vL1*dataSet$L1)/(dataSet$N0 + dataSet$N1)
+  #IN0   <- 1e6 * (dataSet$newI0 + dataSet$newJ0)/dataSet$N0
+  #IN1   <- 1e6 * (dataSet$newI1 + dataSet$newJ1)/dataSet$N1
+  #INall <- 1e6 * (dataSet$newI0 + dataSet$newI1 + dataSet$newJ0 + dataSet$newJ1)/(dataSet$N0 + dataSet$N1)
+  frame <- data.frame(IN0,IN1,INall)
+  write.table(frame, file="incData.csv", sep=",")
+  return(frame)
+}
+
+
+
+args <- commandArgs(trailingOnly = T)
+if (length(args) > 0) {
+  firstDataSet <- read.csv('modelDataRun1.csv')
+  deltaT  <- as.numeric(args[1])
+  print(deltaT)
+  if (length(args) > 2) {
+    initialYr <- as.integer(args[2])
+    finalYr   <- as.integer(args[3])
+  } else {
+    # Defaults:
+    initialYr <- 2000
+    finalYr   <- 2100
+  }
+} else if (!exists('noImport')) {
+  firstDataSet   <- read.csv('modelDataRun1.csv')
+  deltaT    <- .05
+  initialYr <- 2000
+  finalYr   <- 2100
+} else if (!exists('dataSet')) {
+  print('No Data to Plot! Either list the import file as a cmd argument, or define it in the calling script')
+  stop()
+} 
+if (Sys.info()['sysname'] == "Linux") {
+  #Making it plot on linux
+  X11.options(type='nbcairo')
+}
+
+yrs <- seq(initialYr, finalYr - deltaT, deltaT)
[…]

### 2013-07-26 in_progress/models/agentHillModel/cppCostStrict/turtleCostHill.cpp

@@ -1,0 +1,220 @@
+//  turtleCostHill.cpp
+
+#include <iostream>
+#include <math.h>
+#include <stdlib.h>
+#include <random>
+#include <functional>
+using namespace std;
+#include "turtleCostHill.hpp"
+
+
+const char* countryNames[2] = {"USA", "Other"};
+const char* stateNames[6] = {"Latent (L)", "Infectious TB (I)",
+							"Non-Infectious TB (J)", "Susceptible (S)", "TB Death", "Natural Death"};
+
+//Implementation
+//Constructor
+turtle::turtle(const COB &c, const State &s, int timeinfec)
+  : country(c), state(s), timeinfec(timeinfec)
+{}
+
+bool turtle::dead() {
+  return (state == NATURAL_DEATH || state == TB_DEATH);
+}
+
+double turtle::getResetCost(){
+  double tempcost = turtcost;
+  turtcost = 0;
+  return tempcost;
+}
+
+//Updates turtle state
+void turtle::updateState(){
+  //Initializations
+  double r  = (double)rand()/RAND_MAX; //random number from (0,1]
+  double rH;
+  double rS;
+  if(country == USA){
+    if (r < MU0) {  //Natural death rate (USB)
+      state = NATURAL_DEATH;
+      return;
+    }
+    r -= MU0;  //Natural death rate probability accounted for
+
+    //Disease progression and self-cure
+    if (state == LATENT) {
+      timeinfec++;
+      if (timeinfec <= 2/DELTA_T) {
+        if(r < PROB_ACUTE_PROGRESSION){  //Disease progression from Acute Latent to Active TB
+          if(r < q*PROB_ACUTE_PROGRESSION) {
+            state = INFECTIOUS_TB;
+          } else {
+            state = NONINFECTIOUS_TB;
+          }
+          return;
+        } else if (r - PROB_ACUTE_PROGRESSION < PROB_ACUTE_LATENT_CURE_0) {
+          turtcost = LATENT_ADJUSTED_COST;
+          /*rS  = (double)rand()/RAND_MAX;
+          if(rS < efficacyLTBI) {
+            state = SUSCEPTIBLE;
+          }*/
+          state = SUSCEPTIBLE;
+          return;
+        }
+      } else {
+        if (r < PROB_CHRONIC_PROGRESSION_0) {  //Disease progression from Chronic Latent to Active TB (USB)
[…]

### 2013-07-26 in_progress/models/agentHillModel/cppCostStrict/turtleCostHill.hpp

@@ -1,0 +1,98 @@
+// turtleCostHill.hpp
+
+// get round to work
+//check exogenous reinfection
+
+#ifndef ____turtle__
+#define ____turtle__
+
+#include <iostream>
+#include <math.h>
+
+const double DELTA_T = .05;  // measured in years
+
+//Hill model constants
+const double mu0     = 1./78;     // Natural mortality rate USB per year
+const double mu1     = 1./53;     // Natural mortality rate FB per year
+const double mud     = 0.115;     // Mortality rate due to TB per year
+const double ro      = 0.018;     // USB birth rate per year
+const double alpha   = 0.005;     // FB birth rate per year
+const double p       = 0.103;     // Fraction of new infections which are acute (fast progressors)
+const double q       = 0.708;     // Fraction of infections progressing to infectious disease
+const double r0      = 0.667;     // Fraction of cases due to reactivation in the USB population
+const double r1      = 0.780;     // Fraction of cases due to reactivation in the FB population
+const double x       = 0.111;     // Fraction of re-infected chronic LTBI moving to acute infection
+const double f       = 0.187;     // Fraction of FB arrivals with LTBI
+const double beta    = 10.39;     // Effective contact rate per year
+const double e0      = 0.965;     // Fraction of preferred contacts with own population for USB
+const double e1      = 0.985;     // Fraction of preferred contacts with own population for FB
+const double g       = 0.0047;    // Fraction of FB arrivals with LTBI who are fast progressors
+const double vF      = 1.5;       // Progression of acute infection per year
+const double vL0     = 0.0014;    // Progression rate for reactivation (chronic LTBI) in the USB population per year
+const double vL1     = 0.0010;    // Progression rate for reactivation (chronic LTBI) in the FB population per year
+const double phi0    = 1.114;     // Cumulative fraction self-cure and treatment of active disease for both populations per year RATES (USB)
+const double phi1    = 1.167;     // Cumulative fraction self-cure and treatment of active disease for both populations per year RATES (FB)
+const double sigmaL  = 0.057;     // Treatment rate for chronic LTBI per year
+const double sigmaF0 = 1.296;     // Treatment rate for acute LTBI (USB)
[…]

### 2013-07-27 in_progress/presentations/poster/reuMHC2013.tex
working on poster intro

@@
     \begin{column}{.3\textwidth}
-%      \begin{block}{Introduction}
-%        The most common epidemiological models are compartmental models, in
-%        which a system of differential equations describes how parts of the
-%        population move between different disease states, or
-%        \emph{compartments}. The canonical example of such a model is the SIR
-%        model, which has three compartments: Susceptible, Infected, and
-%        Recovered. The dynamics of a population modeled by this framework are
-%        shown in figure~\ref{fig:SIRFlowchart}, with associated system of
-%        differential equations~\ref{eq:SIRdes}.
+      \vspace{-8em}
+      \begin{block}{Introduction}
+        Epidemiological models offer insight into the structure of disease
+        outbreaks and the merits of various interventions. The most common
+        epidemiological models are compartmental differential equation models,
+        such as the SIR system, illustrated in figures~\ref{fig:SIRFlowchart}
+        and~\ref{eq:SIRdes}. 
        %TODO equalize figure heights
-%        \vspace{-3em}
-%        \begin{block}{}
-%          \begin{column}{.39\textwidth}
-%            \begin{figure}[h]
-%              \begin{center}
-%                \begin{tikzpicture}
-%                  \node [compartment] (S) {Susceptible (S)};
-%                  \node [compartment, below of=S] (I) {Infected (I)};
-%                  \node [compartment, below of=I] (R) {Recovered (R)};
-%                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
-%                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
-%                \end{tikzpicture}
-%              \end{center}
-%              \caption{This flowchart depicts the standard SIR epidemiological
-%                       model. It is accomponanied by the system of differential
-%                       equations~\ref{eq:SIRdes}.}
-%              \label{fig:SIRFlowchart}
-%            \end{figure}
-%          \end{column}
-%          \begin{column}{.39\textwidth}
-%            \begin{figure}[h]
-%              \begin{align*}
-%                \frac{dS}{dt} &= -\beta S(t)I(t) \\
-%                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
-%                \frac{dR}{dt} &= \gamma I(t)\\
-%                N             &= S(t) + I(t) + R(t)\\
-%              \end{align*}
-%              \caption{The system of differential equations governing the SIR
-%                       model.}
-%              \label{eq:SIRdes}
-%            \end{figure}
-%          \end{column}
-%        \end{block}
-%        The SIR system, though very informative about basic disease dynamics,
-%        fails to capture the intricacies of more complicated diseases. This
-%        project examines the spread of tuberculosis (TB) in the United States
-%        (US) via compartmental models and stochastic, agent-based models. These
-%        explorations allow one to explore the impact, both epidemiological and
-%        economic, of various intervention strategies. These models are based on
-%        a 2012 compartmental model of TB in the US created by A. N. Hill, J. E.
-%        Becerra, and K. G. Castro.
-%      \end{block}
+        \vspace{-2em}
+        \begin{block}{}
+          \begin{column}{.39\textwidth}
+            \begin{figure}[h]
+              \begin{center}
+                \begin{tikzpicture}
+                  \node [compartment] (S) {Susceptible (S)};
+                  \node [compartment, below of=S] (I) {Infected (I)};
+                  \node [compartment, below of=I] (R) {Recovered (R)};
+                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
+                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
+                \end{tikzpicture}
+              \end{center}
+              \caption{This flowchart depicts the standard SIR epidemiological
+                       model. It is accomponanied by the system of differential
+                       equations~\ref{eq:SIRdes}.}
+              \label{fig:SIRFlowchart}
+            \end{figure}
+          \end{column}
+          \begin{column}{.39\textwidth}
+            \begin{figure}[h]
+              \begin{align*}
+                \frac{dS}{dt} &= -\beta S(t)I(t) \\
+                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
+                \frac{dR}{dt} &= \gamma I(t)\\
+                N             &= S(t) + I(t) + R(t)\\
+              \end{align*}
+              \caption{The system of differential equations governing the SIR
+                       model.}
+              \label{eq:SIRdes}
+            \end{figure}
+          \end{column}
+        \end{block}
+      \end{block}
 
       \begin{block}{The Basic Hill Model}
+        In order to model tuberculosis (TB) in the United States (US), Hill,
+        Becerra, and Castro designed a complex compartmental model called the
+        hill model. 
+        \vspace{-2em}
         \begin{block}{}
+          \begin{column}{.6\textwidth}
             \begin{figure}[h]
               \begin{center}
-                \includegraphics[scale=.75]{HillModelFlowChart}
+                \includegraphics[scale=.5]{HillModelFlowChart}
               \end{center}
@@
             \end{figure}
+          \end{column}
+          \begin{column}{.33\textwidth}
+            Populations:
+            \begin{itemize}
+              \item US Born Individuals (USB) 
+              \item Foreign Born Individuals (FB)
+            \end{itemize}
+            Individuals also leave the model due to natural death.
+          \end{column}
         \end{block}
-%            The illustration of this model is not full, as there are two
-%            subpopulations in the Hill Model. TB dynamics in the US differ
-%            radically between US born (USB) individuals and foreign born (FB)
-%            individuals,  so this model maintains two distinct populations in
-%            which the disease can spread. There is a near identical diagram to
-%            describe the dynamics of the model for the FB population. Further,
-%            each compartment in this model also loses people to do natural
-%            death. The system of differential equations for this model is
-%            naturally more complex and is provided in an appendix. In order to
-%            implement this model, Hill, Becerra, and Castro used the \texttt{R}
-%            programming language, with the \texttt{lsoda} routine to numerically
-%            solve the differential equations.
-
-        For this implementation, various numerical solvers were implemented,
-        including an Eulerian Method, a Quadratic Method, a Fourth-order runge
-        kutta method, and the $\texttt{lsoda}$ routine. Once the basic Hill
-        model was implemented, further tracking capabilities were added as well
-        as economic modeling. This implementation tracks total active TB cases,
-        entering cases of LTBI, and treatment costs for active and latent disease
-        for all populations. Tracking was used to evaluate various interventions
-        explored in Hill, Becerra, and Castro's work, as well as interventions
-        exploring the possibility of treating incoming LTBI cases.
+        %For this implementation, various numerical solvers were implemented,
+        %including an Eulerian Method, a Quadratic Method, a Fourth-order runge
+        %kutta method, and the $\texttt{lsoda}$ routine. Once the basic Hill
+        %model was implemented, further tracking capabilities were added as well
+        %as economic modeling. This implementation tracks total active TB cases,
+        %entering cases of LTBI, and treatment costs for active and latent disease
+        %for all populations. Tracking was used to evaluate various interventions
+        %explored in Hill, Becerra, and Castro's work, as well as interventions
+        %exploring the possibility of treating incoming LTBI cases.
       \end{block}

### 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex
added distribution graphs to 3rd column

@@
         economic data of treatment costs for Active and Latent Tuberculosis.  
-        In our model, we estimate the average heath care costs to be \$14,014.90
-        and \$403.45 to treat a single case of Active or Latent TB respectively.  
-        Given these costs and the average treatment rates for Active and Latent
-        TB in the USA, we modeled the expected economic burden of Tuberculosis
-        projected over the next hundred years.
+%        In our model, we estimate the average heath care costs to be \$14,014.90
+%        and \$403.45 to treat a single case of Active or Latent TB respectively.  
+%        Given these costs and the average treatment rates for Active and Latent
+%        TB in the USA, we modeled the expected economic burden of Tuberculosis
+%        projected over the next hundred years.
 
@@
       \begin{block}{An Agent Based Implementation}
-        In addition to the extended Hill model (implemented in R), we also
-        created a stochastic agent-based counterpart in both NetLogo and C++.
-        Stochastic models add notions of uncertainty into the model structure,
-        while agent-based models simulate global behavior of the system by
-        describing local behavior of individual agents in the population.
+        We also wrote a stochastic agent-based version of the Hill model in both
+        NetLogo and C++.
         \begin{block}{}
@@
               \end{center}
-              \caption{Incidence per million for R and NetLogo models (12 runs)}
+              \caption{Incidence/million for R and NetLogo models (12 runs, $\Delta t$ = 0.1, popConst = 100)}
               \label{fig:NLHMinc}
@@
               \end{center}
-              \caption{Incidence per million for R and C++ models (2100 runs)}
+              \caption{Incidence/million for R and C++ models (2100 runs, $\Delta t$ = 0.01, popConst = 1)}
               \label{fig:finalRun}
@@
       \begin{block}{Stochastic Models as a Measure of Variability}
+        The stochastic model gives us a sense of the variability of the results
+        of the deterministic model.
+        \begin{block}{}
+          \begin{column}{.45\textwidth}
+            \begin{figure}[h]
+              \begin{center}
+                \includegraphics[width=\textwidth]{IN0dist}
+              \end{center}
+              \caption{Distribution of USB Incidence (C++) with fitted Normal curve}
+              \label{fig:IN0dist}
+            \end{figure}
+          \end{column}
+          \begin{column}{.45\textwidth}
+            \begin{figure}[h]
+              \begin{center}
+                \includegraphics[width=\textwidth]{IN1dist}
+              \end{center}
+              \caption{Distribution of FB Incidence (C++) with fitted Normal curve}
+              \label{fig:IN1dist}
+            \end{figure}
+          \end{column}
+        \end{block}
       \end{block}
@@
       \begin{block}{Future Extensions}
+        Possible extensions to our model include the incorporation of non-homogeneous
+        contact structures and MDR (multi-drug resistant) TB.
       \end{block}

### 2013-07-28 in_progress/models/agentHillModel/cppStrictHill/HMDistributions.R
added R script for generating historgrams to cppStritHill

@@ -1,0 +1,125 @@
+library(MASS)
+vF <- 1.5         #Progression rate of acute infection per year
+vL0 <- 0.0014     #Progression rate for reactivation (chronic LTBI) in the USB population per year
+vL1 <- 0.0010     #Progression rate for reactivation (chronic LTBI) in the FB population per year
+popConst <- 1000
+
+getIncidence <- function(slice) {
+  IN0   <- 1e6 * (vF*slice$F0 + vL0*slice$L0)/slice$N0
+  IN1   <- 1e6 * (vF*slice$F1 + vL1*slice$L1)/slice$N1
+  INall <- 1e6 * (vF*(slice$F0 + slice$F1) + vL0*slice$L0 + vL1*slice$L1)/(slice$N0 + slice$N1)
+  return(c(IN0,IN1,INall))
+}
+
+args <- commandArgs(trailingOnly = T)
+if (length(args) > 0) {
+  firstDataSet <- read.csv('modelDataRun1.csv')
+  deltaT  <- as.numeric(args[1])
+  print(deltaT)
+  if (length(args) > 2) {
+    initialYr <- as.integer(args[2])
+    finalYr   <- as.integer(args[3])
+  } else {
+    # Defaults:
+    initialYr <- 2000
+    finalYr   <- 2100
+  }
+} else if (!exists('noImport')) {
+  firstDataSet   <- read.csv('modelDataRun1.csv')
+  deltaT    <- .05
+  initialYr <- 2000
+  finalYr   <- 2100
+} else if (!exists('dataSet')) {
+  print('No Data to Plot! Either list the import file as a cmd argument, or define it in the calling script')
+  stop()
+} 
+if (Sys.info()['sysname'] == "Linux") {
+  #Making it plot on linux
+  X11.options(type='nbcairo')
+}
+
+finalValues <- matrix(nrow=2103, ncol=16)
+
+filename <- "modelDataRun"
+runNumber <- 1
+extension <- ".csv"
+rowNum <- 1
+fileNameFull <- "modelDataRun1.csv"
+while (file.exists(fileNameFull)) {
+	dataSet <- read.csv(fileNameFull)
+	finalValues[rowNum,] <- c(as.numeric(dataSet[2000,]), getIncidence(dataSet[2000,]))
+	rowNum <- rowNum + 1
+		
+	runNumber <- runNumber + 1
+        if (runNumber == 734) {
[…]

### 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex
working on poster more, first column more or less done? working on second

--- 2013-07-27 in_progress/presentations/poster/reuMHC2013.tex
@@
     \begin{column}{.3\textwidth}
-      \vspace{-8em}
+      \vspace{-30em}
       \begin{block}{Introduction}
@@
        %TODO equalize figure heights
-        \vspace{-2em}
         \begin{block}{}
@@
         \end{block}
-        %For this implementation, various numerical solvers were implemented,
-        %including an Eulerian Method, a Quadratic Method, a Fourth-order runge
-        %kutta method, and the $\texttt{lsoda}$ routine. Once the basic Hill
-        %model was implemented, further tracking capabilities were added as well
-        %as economic modeling. This implementation tracks total active TB cases,
-        %entering cases of LTBI, and treatment costs for active and latent disease
-        %for all populations. Tracking was used to evaluate various interventions
-        %explored in Hill, Becerra, and Castro's work, as well as interventions
-        %exploring the possibility of treating incoming LTBI cases.
       \end{block}
@@
     \begin{column}{.3\textwidth}
-      \begin{block}{TB Reduction Strategies for the United States}
-        From the Hill model, we 
+      \begin{block}{Analyzing US TB Reduction Strategies}
+        \begin{enumerate}
+          \item Implemented in \texttt{R}, with various numerical DE solvers.
+          \item Tracks US Health Care System (HCS) cost.
+          \item Tracks statistics about various health states.
+        \end{enumerate}
+        \begin{block}{Basic Hill Behaviour}
+          \begin{column}{.45\textwidth}
+            \begin{figure}[h]
+              \begin{center}
+                \includegraphics[scale=1]{incPlotSourced}
+              \end{center}
+              \caption{A plot showing the source population of yearly US TB
+              incindecence.}
+              \label{fig:incPlotSourced}
+            \end{figure}
+          \end{column}
+          \begin{column}{.45\textwidth}
+            \begin{figure}[h]
+              \begin{center}
+                \includegraphics[scale=1]{incPlotTotal}
+              \end{center}
+              \caption{New cases per year of various types of TB in the US.}
+              \label{fig:incPlotTotal}
+            \end{figure}
+          \end{column}
         \end{block}
-      \begin{block}{Intervention Analysis}
-        Intervention Analysis
         \begin{figure}[h]

### 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex

--- 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex
@@
     \begin{column}{.3\textwidth}
-      \vspace{-8em}
+      \vspace{-20em}
       \begin{block}{Introduction}

### 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex
still working

@@
     \begin{column}{.3\textwidth}
-      \vspace{-20em}
+      \vspace{-25em}
       \begin{block}{Introduction}
@@
         \end{block}
+        \begin{block}{Intervention Analysis}
+          \begin{column}{.45\textwidth}
             \begin{figure}[h]
               \begin{center}
-            \includegraphics[scale=1]{incidencePlotRedEnLTBI.pdf}
+                \includegraphics[scale=1]{incidencePlotRedEnLTBI}
               \end{center}
-          \caption{A graph of the projected incidence levels per million in
-                       the US-born, Foreign-born, and Total US population, given
-                       that LTBI rates in Foreign-born arrivals are reduced by 
-                       0\%, 50\%, 75\%, and 100\%.}
+              \caption{The projected incidence levels per million in
+                       USB, FB, and total populations, given 0\%, 50\%, 75\%, or
+                       100\% of incoming LTBI cases are cured.}
               \label{fig:redEnLTBI_incidence}
             \end{figure}
+          \end{column}
+          \begin{column}{.45\textwidth}
+            \begin{figure}[h]
+              \begin{center}
+                \includegraphics[scale=1]{incLTBItrmtIncGrouped}
+              \end{center}
+              \caption{The projected incidence levels per million in
+                       USB, FB, and total populations, given 0\%, 100\%, or
+                       300\% increase in LTBI treatment.}
+              \label{fig:incLTBItrmt_incidence}
+            \end{figure}
+          \end{column}
+        \end{block}
       \end{block}

### 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex
working on poster still. Need to check sizes, fix some graphs, make more concise, etc.

--- 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex
@@
 %Poster Packages: 
-%\usepackage[orientation=lanscape,size=a0]{beamerposter}
 %dimensions are in cm, scale is for font size
@@
 
-\newlength{\columnheight}
-\setlength{\columnheight}{105cm}
+%\newlength{\columnheight}
+%\setlength{\columnheight}{88cm}
 
-\title{\huge Modeling Intervention Strategies for TB Control in the United States}
+\title{\huge Modeling Intervention Strategies for United States TB Control}
 \author{Jessica Ginepro, Emma Hartman, Ryo Kimura, Matthew McDermott, Colin
@@
     \begin{column}{.3\textwidth}
-      \vspace{-20em}
+      \vspace{-3em}
       \begin{block}{Introduction}
@@
         \begin{block}{Basic Hill Behaviour}
+          \vspace{-1.6em}
           \begin{column}{.45\textwidth}
@@
               \begin{center}
-                \includegraphics[scale=1]{incPlotSourced}
+                \includegraphics[height=10cm,width=\textwidth]{incPlotSourced}
               \end{center}
-              \caption{A plot showing the source population of yearly US TB
-              incindecence.}
+              \caption{The source population of US TB incindecence}
               \label{fig:incPlotSourced}
@@
               \begin{center}
-                \includegraphics[scale=1]{incPlotTotal}
+                \includegraphics[height=10cm,width=\textwidth]{incPlotTotal}
               \end{center}
@@
         \end{block}
+        \begin{block}{Intervention Analysis}
+          \vspace{-1.6em}
+          \begin{column}{.45\textwidth}
             \begin{figure}[h]
               \begin{center}
-            \includegraphics[scale=1]{incidencePlotRedEnLTBI.pdf}
+                \includegraphics[height=10cm,width=\textwidth]{incidencePlotRedEnLTBI}
               \end{center}
-          \caption{A graph of the projected incidence levels per million in
-                       the US-born, Foreign-born, and Total US population, given
-                       that LTBI rates in Foreign-born arrivals are reduced by 
-                       0\%, 50\%, 75\%, and 100\%.}
+              \caption{Incidence/million in USB, FB, and total populations,
+                       given 0\%, 50\%, 75\%, or 100\% treatment of incoming
+                       LTBI.}
               \label{fig:redEnLTBI_incidence}
             \end{figure}
+          \end{column}
+          \begin{column}{.45\textwidth}
+            \begin{figure}[h]
+              \begin{center}
+                \includegraphics[height=10cm,width=\textwidth]{incLTBItrmtIncGrouped}
+              \end{center}
+              \caption{Incidence/million in USB, FB, and total populations,
+                       given 0\%, 100\%, or 300\% LTBI treatment increase.}
+              \label{fig:incLTBItrmt_incidence}
+            \end{figure}
+          \end{column}
+        \end{block}
       \end{block}
       \begin{block}{Economic Modeling}
-        We extended our basic implementation of the Hill model to incorporate
-        economic data of treatment costs for Active and Latent Tuberculosis.  
-%        In our model, we estimate the average heath care costs to be \$14,014.90
-%        and \$403.45 to treat a single case of Active or Latent TB respectively.  
-%        Given these costs and the average treatment rates for Active and Latent
-%        TB in the USA, we modeled the expected economic burden of Tuberculosis
-%        projected over the next hundred years.
-
+        \begin{enumerate}
+          \item Tracks treatment costs for various disease states
+          \item Estimates implementation cost of intervention
+        \end{enumerate}
+        \begin{block}{}
+          \vspace{-4em}
+          \begin{column}{.66\textwidth}
             \begin{figure}[h]
               \begin{center}
-            \includegraphics[scale=1]{EnLTBIRedGroupCost.pdf}
+                \includegraphics[width=\textwidth,height=13cm]{EnLTBIRedGroupCost.pdf}
               \end{center}
-          \caption{A graph of the cumulative implementation costs, savings, and 
-                       net US health care system costs of reducing rates of LTBI in
-                       Foreign-born arrivals by 50\%, 75\%, and 100\%.  To determine the 
-                       implementation cost for each intervention, the average cost
-                       to identify and treat entering Foreign-born individuals with LTBI
-                       was set to be \$600, \$800, and \$1000 for the 50\%, 75\%, 
-                       and 100\% reduction strategies respectively.}
+              \caption{Cumulative implementation costs, US HCS savings, and net
+                       US costs of LTBI arrival cure rates. Cost/case cured was
+                       \$600, \$800, and \$1000 for 50\%, 75\%, and 100\%
+                       cured.}
               \label{fig:redEnLTBI_costs}
             \end{figure}
+          \end{column}
+          \begin{column}{.26\textwidth}
+            Base HCS Costs:
+            \begin{enumerate}
+              \item Active TB: \$14,014.90
+              \item LTBI: \$403.45
+            \end{enumerate}
+          \end{column}
+        \end{block}
       \end{block}

### 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex
some little changes; about to start working on a cost source breakdown graph for the base system

@@
     \begin{column}{.3\textwidth}
-      \vspace{-3em}
+      \vspace{-3.6em}
       \begin{block}{Introduction}
@@
     \begin{column}{.3\textwidth}
+      \vspace{-1.5em}
       \begin{block}{Analyzing US TB Reduction Strategies}
-        \begin{enumerate}
+        \begin{itemize}
           \item Implemented in \texttt{R}, with various numerical DE solvers.
@@
           \item Tracks statistics about various health states.
-        \end{enumerate}
+        \end{itemize}
         \begin{block}{Basic Hill Behaviour}
@@
       \begin{block}{Economic Modeling}
-        \begin{enumerate}
+        \begin{itemize}
           \item Tracks treatment costs for various disease states
           \item Estimates implementation cost of intervention
-        \end{enumerate}
+        \end{itemize}
         \begin{block}{}
@@
             Base HCS Costs:
-            \begin{enumerate}
-              \item Active TB: \$14,014.90
-              \item LTBI: \$403.45
-            \end{enumerate}
+            \begin{description}
+              \item[Active TB:]\hfill \\ 
+                \$14,014.90
+              \item[LTBI:]\hfill \\ 
+                \$403.45
+            \end{description}
           \end{column}
@@
     \begin{column}{.3\textwidth}
+      \vspace{-.5em}
       \begin{block}{An Agent Based Implementation}
-        We also wrote a stochastic agent-based version of the Hill model in both
-        NetLogo and C++.
+        Agent based models capture disease dynamics on the individual level, and
+        reflect stochasticity and granularity lost in compartmental models.
+        Agent based counterparts to the Hill model were implemented in Netlogo
+        and \texttt{c++}.
         \begin{block}{}
+          \vspace{-2em}
           \begin{column}{.45\textwidth}
@@
       \begin{block}{Stochastic Models as a Measure of Variability}
-        The stochastic model gives us a sense of the variability of the results
+        The stochastic model provides data on the variability of the results
         of the deterministic model.
@@
       \begin{block}{Future Extensions}
-        Possible extensions to our model include the incorporation of non-homogeneous
-        contact structures and MDR (multi-drug resistant) TB.
+        \begin{itemize}
+          \item Including contact structure
+          \item Multi-drug resistant TB
+          \item HIV
+        \end{itemize}
       \end{block}

### 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex
made poster histograms nicer

@@
               \end{center}
-              \caption{Distribution of USB Incidence (C++) with fitted Normal curve}
+              \caption{Distribution of USB Incidence (C++) with fitted Normal curve ($\mu = 0.233196, \sigma = 0.0165344$)}
               \label{fig:IN0dist}
@@
               \end{center}
-              \caption{Distribution of FB Incidence (C++) with fitted Normal curve}
+              \caption{Distribution of FB Incidence (C++) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
               \label{fig:IN1dist}

### 2013-07-28 in_progress/models/agentHillModel/cppStrictHill/HMDistributions.R

@@ -1,4 +1,5 @@
 library(MASS)
+library(ggplot2)
 vF <- 1.5         #Progression rate of acute infection per year
 vL0 <- 0.0014     #Progression rate for reactivation (chronic LTBI) in the USB population per year
 vL1 <- 0.0010     #Progression rate for reactivation (chronic LTBI) in the FB population per year
@@ -10,6 +11,21 @@ getIncidence <- function(slice) {
   INall <- 1e6 * (vF*(slice$F0 + slice$F1) + vL0*slice$L0 + vL1*slice$L1)/(slice$N0 + slice$N1)
   return(c(IN0,IN1,INall))
 }
+
+# simpleHistogram <- function(data) {
+#   dev.new()
+#   hist(data, prob=TRUE, breaks=50)
+#   fitLine <- fitdistr(data, "Normal")
+#   datmean <- fitLine$estimate['mean']
+#   datsd <- fitLine$estimate['sd']
+#   curve(dnorm(x,datmean, datsd), add=TRUE,col='red')
+#   legend('topright', legend=c(
+#       paste('sample mean: ', signif(mean(data))),
+#       paste('sample stdev: ', signif(sd(data))),
+#       paste('fitted mean: ', signif(datmean)),
+#       paste('fitted stdev: ', signif(datsd))
+#   ))
+# }
 
 args <- commandArgs(trailingOnly = T)
 if (length(args) > 0) {
@@ -94,32 +110,30 @@ while (file.exists(fileNameFull)) {
     # paste('fitted stdev: ', signif(L1sd))
 # ))
 
+incFrame <- data.frame(USBIncidence  = finalValues[,14], FBIncidence = finalValues[,15])
+
 # IN0 histogram
-dev.new()
-USBIncidence <- finalValues[,14]
-hist(USBIncidence, prob=TRUE, breaks=50)
-fitLine <- fitdistr(USBIncidence, "Normal")
+fitLine <- fitdistr(incFrame$USBIncidence, "Normal")
 IN0mean <- fitLine$estimate['mean']
 IN0sd <- fitLine$estimate['sd']
-curve(dnorm(x,IN0mean, IN0sd), add=TRUE,col='red')
-legend('topright', legend=c(
-    paste('sample mean: ', signif(mean(USBIncidence))),
-    paste('sample stdev: ', signif(sd(USBIncidence))),
-    paste('fitted mean: ', signif(IN0mean)),
[…]

### 2013-07-28 in_progress/presentations/poster/reuMHC2013NoSIRIntro.tex
improving R graphs; started noSIR version

--- 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex
@@
     \begin{column}{.3\textwidth}
-      \vspace{-3.6em}
+      \vspace{-2em}
       \begin{block}{Introduction}
-        Epidemiological models offer insight into the structure of disease
-        outbreaks and the merits of various interventions. The most common
-        epidemiological models are compartmental differential equation models,
-        such as the SIR system, illustrated in figures~\ref{fig:SIRFlowchart}
-        and~\ref{eq:SIRdes}. 
-       %TODO equalize figure heights
+        \begin{itemize}
+          \item Epidemiological models describe disease outbreaks.
+          \item Compartmental Differential Equation models are common and
+            rigorous epidemiological models.
+          \item The Hill Model is a complex compartmental model of tuberculosis
+            (TB) in the United States (US).
+        \end{itemize}
+       % Epidemiological models offer insight into the structure of disease
+       % outbreaks and the merits of various interventions. The most common
+       % epidemiological models are compartmental differential equation models,
+       % in which the population is dispersed between a variety of distinct
+       % compartments, through which they move according to a system of
+       % Differential Equations. In order to model tuberculosis (TB) in the
+       % United States (US), Hill, Becerra, and Castro designed a complex
+       % compartmental model called the hill model.
+      \end{block}
+      \begin{block}{The Basic Hill Model}
+        \vspace{-2em}
         \begin{block}{}
-          \begin{column}{.39\textwidth}
+          \begin{column}{.5\textwidth}
             \begin{figure}[h]
               \begin{center}
-                \begin{tikzpicture}
-                  \node [compartment] (S) {Susceptible (S)};
-                  \node [compartment, below of=S] (I) {Infected (I)};
-                  \node [compartment, below of=I] (R) {Recovered (R)};
-                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
-                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
-                \end{tikzpicture}
-              \end{center}
-              \caption{This flowchart depicts the standard SIR epidemiological
-                       model. It is accomponanied by the system of differential
-                       equations~\ref{eq:SIRdes}.}
-              \label{fig:SIRFlowchart}
-            \end{figure}
-          \end{column}
-          \begin{column}{.39\textwidth}
-            \begin{figure}[h]
-              \begin{align*}
-                \frac{dS}{dt} &= -\beta S(t)I(t) \\
-                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
-                \frac{dR}{dt} &= \gamma I(t)\\
-                N             &= S(t) + I(t) + R(t)\\
-              \end{align*}
-              \caption{The system of differential equations governing the SIR
-                       model.}
-              \label{eq:SIRdes}
-            \end{figure}
-          \end{column}
-        \end{block}
-      \end{block}
-
-      \begin{block}{The Basic Hill Model}
-        In order to model tuberculosis (TB) in the United States (US), Hill,
-        Becerra, and Castro designed a complex compartmental model called the
-        hill model. 
-        \vspace{-2em}
-        \begin{block}{}
-          \begin{column}{.6\textwidth}
-            \begin{figure}[h]
-              \begin{center}
-                \includegraphics[scale=.5]{HillModelFlowChart}
+                \includegraphics[height=12cm,width=.9\textwidth]{HillModelFlowChart}
               \end{center}
@@
           \end{column}
-          \begin{column}{.33\textwidth}
+          \begin{column}{.43\textwidth}
             Populations:
@@
           \end{column}
+          \begin{figure}[h]
+            \begin{center}
+              \includegraphics[height=25cm,width=\textwidth]{incPlotSourced2}
+            \end{center}
+            \caption{The source population of US TB incindecence}
+            \label{fig:incPlotSourced}
+          \end{figure}
+          \vspace{-1em}
+          \begin{figure}[h]
+            \begin{center}
+              \includegraphics[height=15cm,width=\textwidth]{incPlotTotal}
+            \end{center}
+            \caption{New cases per year of various types of TB in the US.}
+            \label{fig:incPlotTotal}
+          \end{figure}
         \end{block}
@@
         \end{itemize}
-        \begin{block}{Basic Hill Behaviour}
-          \vspace{-1.6em}
-          \begin{column}{.45\textwidth}
-            \begin{figure}[h]
-              \begin{center}
-                \includegraphics[height=10cm,width=\textwidth]{incPlotSourced}
-              \end{center}
-              \caption{The source population of US TB incindecence}
-              \label{fig:incPlotSourced}
-            \end{figure}
-          \end{column}
-          \begin{column}{.45\textwidth}
-            \begin{figure}[h]
-              \begin{center}
-                \includegraphics[height=10cm,width=\textwidth]{incPlotTotal}
-              \end{center}
-              \caption{New cases per year of various types of TB in the US.}
-              \label{fig:incPlotTotal}
-            \end{figure}
-          \end{column}
-        \end{block}
         \begin{block}{Intervention Analysis}

### 2013-07-28 in_progress/models/costBenefitAnalysis/helpers.R

@@ -1,11 +1,11 @@
-acuteLatentFBL    <- rep("Acute Latent (FB)",totT)
-chronicLatentFBL  <- rep("Chronic Latent (FB)", totT)
-acuteLatentUSBL   <- rep("Acute Latent (USB)",totT)
-chronicLatentUSBL <- rep("Chronic Latent (USB)", totT)
-activeInfecFBL    <- rep("Active Infectious TB (FB)",totT)
-activeNoInfecFBL  <- rep("Active Non-infectious TB (FB)", totT)
-activeInfecUSBL   <- rep("Active Infectious TB (USB)",totT)
-activeNoInfecUSBL <- rep("Active Non-infectious TB (USB)", totT)
+acuteLatentFBL    <- rep("FB Acute Latent",totT)
+chronicLatentFBL  <- rep("FB Chronic Latent", totT)
+acuteLatentUSBL   <- rep("USB Acute Latent",totT)
+chronicLatentUSBL <- rep("USB Chronic Latent", totT)
+activeInfecFBL    <- rep("FB Active Infectious TB",totT)
+activeNoInfecFBL  <- rep("FB Active Non-infectious TB", totT)
+activeInfecUSBL   <- rep("USB Active Infectious TB",totT)
+activeNoInfecUSBL <- rep("USB Active Non-infectious TB", totT)
 
 generateSourcedIncidence <- function(dataSet) {
   with(as.list(parms), {
@@ -24,14 +24,15 @@ IdL0c <- IdF1c + baseSourcedInc$IdL0
 IdF0c <- IdL0c + baseSourcedInc$IdF0
 baseCumulativeSourcedInc <- data.frame(year=years,IdL1c,IdF1c,IdL0c,IdF0c)
 incPlotSourced <- ggplot(baseCumulativeSourcedInc, aes(x=year)) + 
-           labs(x="Years", y="Incidence", fill="Population and Health State") + 
-           plotTitle("Incidence Levels due to Various 
-Populations With No Intervention","") +
+           labs(x="Years", y="Incidence", fill="Incidence Source") + 
+           plotTitle("Sourced US TB Incidence/Million","") +
            geom_ribbon(aes(ymin=0,    ymax=IdL1c,fill=chronicLatentFBL))  + 
            geom_ribbon(aes(ymin=IdL1c,ymax=IdF1c,fill=acuteLatentFBL))    + 
[…]

### 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex

--- 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex
@@
               \end{center}
-              \caption{Incidence/million for R and NetLogo models (12 runs, $\Delta t$ = 0.1, popConst = 100)}
+              \caption{Incidence/million for \texttt{R} and NetLogo models (12 runs, $\Delta t$ = 0.1, popConst = 100)}
               \label{fig:NLHMinc}
@@
               \end{center}
-              \caption{Incidence/million for R and C++ models (2100 runs, $\Delta t$ = 0.01, popConst = 1)}
+              \caption{Incidence/million for \texttt{R} and \texttt{c++} models (2100 runs, $\Delta t$ = 0.01, popConst = 1)}
               \label{fig:finalRun}
@@
         \begin{block}{}
+          \vspace{-2em}
           \begin{column}{.45\textwidth}
@@
               \end{center}
-              \caption{Distribution of USB Incidence (C++) with fitted Normal curve}
+              \caption{USB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 0.233196, \sigma = 0.016534$)}
               \label{fig:IN0dist}
@@
               \end{center}
-              \caption{Distribution of FB Incidence (C++) with fitted Normal curve}
+              \caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
               \label{fig:IN1dist}

### 2013-07-28 in_progress/models/costBenefitAnalysis/helpers.R
reorganized labels

@@ -31,8 +31,15 @@ incPlotSourced <- ggplot(baseCumulativeSourcedInc, aes(x=year)) +
            geom_ribbon(aes(ymin=IdF1c,ymax=IdL0c,fill=chronicLatentUSBL)) + 
            geom_ribbon(aes(ymin=IdL0c,ymax=IdF0c,fill=acuteLatentUSBL))   + 
            theme_gray(base_size=20) + theme(legend.position=c(0.6,0.8)) + 
-           coord_fixed(ratio=1/200)
-ggsave('incPlotSourced2.pdf',incPlotSourced)
+           coord_fixed(ratio=1/200) + 
+           scale_fill_discrete(breaks=c('USB Acute Latent', 
+                                        'USB Chronic Latent',
+                                        'FB Acute Latent',
+                                        'FB Chronic Latent'), 
+                               levels=c(acuteLatentUSBc,chronicLatentUSBc,
+                                        acuteLatentFBc,chronicLatentFBc))
+incPlotSourced
+ggsave('forPoster/incPlotSourced2.pdf',incPlotSourced)
 
 #Order: IF1 = IF1c, IF1 + IL1 = IL1c 
 IF1c <- baseTotalInc$IF1

### 2013-07-29 in_progress/models/costBenefitAnalysis/helpers.R
added new graph, added new helper R functions, added stuff to gitignore

@@ -1,11 +1,25 @@
-acuteLatentFBL    <- rep("FB Acute Latent",totT)
-chronicLatentFBL  <- rep("FB Chronic Latent", totT)
-acuteLatentUSBL   <- rep("USB Acute Latent",totT)
-chronicLatentUSBL <- rep("USB Chronic Latent", totT)
-activeInfecFBL    <- rep("FB Active Infectious TB",totT)
-activeNoInfecFBL  <- rep("FB Active Non-infectious TB", totT)
-activeInfecUSBL   <- rep("USB Active Infectious TB",totT)
-activeNoInfecUSBL <- rep("USB Active Non-infectious TB", totT)
+acuteLatentFBL       <- rep("FB Acute Latent",totT)
+chronicLatentFBL     <- rep("FB Chronic Latent", totT)
+acuteLatentUSBL      <- rep("USB Acute Latent",totT)
+chronicLatentUSBL    <- rep("USB Chronic Latent", totT)
+
+activeInfecFBL       <- rep("FB Active Infectious TB",totT)
+activeNoInfecFBL     <- rep("FB Active Non-infectious TB", totT)
+activeInfecUSBL      <- rep("USB Active Infectious TB",totT)
+activeNoInfecUSBL    <- rep("USB Active Non-infectious TB", totT)
+
+latentFBLs           <- "FB LTBI"
+latentFBL            <- rep(latentFBLs,totT)
+latentUSBLs          <- "USB LTBI"
+latentUSBL           <- rep(latentUSBLs,totT)
+activeTBFBdL1Ls      <- "FB Active TB due to Activation of LTBI"
+activeTBFBdL1L       <- rep(activeTBFBdL1Ls,totT)
+activeTBFBdF1Ls      <- "FB Active TB due to Novel Infection"
+activeTBFBdF1L       <- rep(activeTBFBdF1Ls,totT)
+activeTBUSBdL0Ls     <- "USB Active TB due to Activation of LTBI"
+activeTBUSBdL0L      <- rep(activeTBUSBdL0Ls,totT)
+activeTBUSBdF0Ls     <- "USB Active TB due to Novel Infection"
+activeTBUSBdF0L      <- rep(activeTBUSBdF0Ls,totT)
 
 generateSourcedIncidence <- function(dataSet) {
   with(as.list(parms), {
[…]

### 2013-07-29 in_progress/models/costBenefitAnalysis/interventionConfig.R

@@ -26,7 +26,7 @@ redEnLTBI_Interventions <- allInterventions[1:3]
 redImm_Interventions <- allInterventions[5:6]
 incLTBItrmt_Interventions <- allInterventions[7:8]
                       
-curInterventions <- allInterventions
+curInterventions <- c()#allInterventions
 
 interventionConfig <- function(interventionStr, x=0) { #x is an integer refering to cost option, ranges 0 to 5
   error    <- F

### 2013-07-29 in_progress/presentations/poster/reuMHC2013NoSIRIntro.tex
with new text and visual stuff

@@
       \begin{block}{Introduction}
-        \begin{itemize}
-          \item Epidemiological models describe disease outbreaks.
-          \item Compartmental Differential Equation models are common and
-            rigorous epidemiological models.
-          \item The Hill Model is a complex compartmental model of tuberculosis
-            (TB) in the United States (US).
-        \end{itemize}
+        Epidemiological models offer insight into the structure of disease outbreaks and the merits of various interventions.
+Compartmental differential equation models are a common model in which populations move between various health states, or compartments, according to predetermined rates.
+This work is an extension of the Hill Model, a complex compartmental model of tuberculosis (TB) in the United States.
        % Epidemiological models offer insight into the structure of disease
@@
               \end{center}
-              \caption{A flow chart representing the compartments of the Hill
-                       Model.}
+              \caption{A flow chart representing the compartments of the Hill Model.}
               \label{fig:hillFlow}
@@
             \begin{itemize}
-              \item US Born Individuals (USB) 
-              \item Foreign Born Individuals (FB)
+              \item US Born (USB) 
+              \item Foreign Born (FB)
             \end{itemize}
@@
             \begin{center}
-              \includegraphics[height=25cm,width=\textwidth]{incPlotSourced2}
+              \includegraphics[height=20cm] {newfig}%{incPlotSourced2}
             \end{center}
-            \caption{The source population of US TB incindecence}
+            \caption{The source population of US TB incidence}
             \label{fig:incPlotSourced}
@@
           \vspace{-1em}
-          \begin{figure}[h]
-            \begin{center}
-              \includegraphics[height=15cm,width=\textwidth]{incPlotTotal}
-            \end{center}
-            \caption{New cases per year of various types of TB in the US.}
-            \label{fig:incPlotTotal}
-          \end{figure}
+%          \begin{figure}[h]
+%            \begin{center}
+%              \includegraphics[height=15cm]{incPlotTotal}
+%            \end{center}
+%            \caption{New cases per year of various types of TB in the US.}
+%            \label{fig:incPlotTotal}
+%          \end{figure}
         \end{block}
@@
         \begin{itemize}
-          \item Implemented in \texttt{R}, with various numerical DE solvers.
-          \item Tracks US Health Care System (HCS) cost.
-          \item Tracks statistics about various health states.
+          \item Implemented in \texttt{R}, with various numerical DE solvers
+          \item Tracks US Health Care System (HCS) cost
+          \item Tracks statistics about various health states
         \end{itemize}
@@
           \vspace{-1.6em}
-          \begin{column}{.45\textwidth}
+          %\begin{column}{.45\textwidth}
             \begin{figure}[h]
@@
             \end{figure}
-          \end{column}
-          \begin{column}{.45\textwidth}
+          %\end{column}
+          %\begin{column}{.45\textwidth}
             \begin{figure}[h]
@@
             \end{figure}
-          \end{column}
+          %\end{column}
         \end{block}
@@
       \vspace{-.5em}
-      \begin{block}{An Agent Based Implementation}
-        Agent based models capture disease dynamics on the individual level, and
+      \begin{block}{An Agent-Based Implementation}
+        Agent-based models capture disease dynamics on the individual level, and
         reflect stochasticity and granularity lost in compartmental models.
-        Agent based counterparts to the Hill model were implemented in Netlogo
-        and \texttt{c++}.
+        Agent-based counterparts to the Hill model were implemented in Netlogo
+        and \texttt{C++}.
         \begin{block}{}
@@
       \begin{block}{Stochastic Models as a Measure of Variability}
-        The stochastic model provides data on the variability of the results
-        of the deterministic model.
         \begin{block}{}
+          \vspace{-2em}
           \begin{column}{.45\textwidth}
@@
 
-      \begin{block}{Future Extensions}
-        \begin{itemize}
-          \item Including contact structure
-          \item Multi-drug resistant TB
-          \item HIV
-        \end{itemize}
+      \begin{block}{References}
+        Hill, A. N., Becerra, J. E., \& Castro, K. G. (2012). Modelling tuberculosis trends in the USA. Epidemiology and infection, 140(10), 1862.
       \end{block}

### 2013-07-29 in_progress/models/costBenefitAnalysis/helpers.R
updated plot

@@ -1,7 +1,15 @@
-acuteLatentFBL       <- rep("FB Acute Latent",totT)
-chronicLatentFBL     <- rep("FB Chronic Latent", totT)
-acuteLatentUSBL      <- rep("USB Acute Latent",totT)
-chronicLatentUSBL    <- rep("USB Chronic Latent", totT)
+acuteLatentFBLs      <- "FB Acute LTBI"
+acuteLatentFBL       <- rep(acuteLatentFBLs,totT)
+chronicLatentFBLs    <- "FB Chronic LTBI"
+chronicLatentFBL     <- rep(chronicLatentFBLs, totT)
+acuteLatentUSBLs     <- "USB Acute LTBI"
+acuteLatentUSBL      <- rep(acuteLatentUSBLs,totT)
+chronicLatentUSBLs   <- "USB Chronic LTBI"
+chronicLatentUSBL    <- rep(chronicLatentUSBLs, totT)
+acuteLatentFBc       <- "#FFA573"
+chronicLatentFBc     <- "#FFC973"
+acuteLatentUSBc      <- "#6999D3"
+chronicLatentUSBc    <- "#5FD3B3"
 
 activeInfecFBL       <- rep("FB Active Infectious TB",totT)
 activeNoInfecFBL     <- rep("FB Active Non-infectious TB", totT)
@@ -46,14 +54,14 @@ incPlotSourced <- ggplot(baseCumulativeSourcedInc, aes(x=year)) +
            geom_ribbon(aes(ymin=IdL0c,ymax=IdF0c,fill=acuteLatentUSBL))   + 
            theme_gray(base_size=20) + theme(legend.position=c(0.6,0.8)) + 
            coord_fixed(ratio=1/200) + 
-           scale_fill_discrete(breaks=c('USB Acute Latent', 
-                                        'USB Chronic Latent',
-                                        'FB Acute Latent',
-                                        'FB Chronic Latent'), 
-                               levels=c(acuteLatentUSBc,chronicLatentUSBc,
+           scale_fill_manual(breaks=c(acuteLatentUSBLs, 
+                                       chronicLatentUSBLs,
+                                       acuteLatentFBLs,
+                                       chronicLatentFBLs), 
+                               values=c(acuteLatentUSBc,chronicLatentUSBc,
                                         acuteLatentFBc,chronicLatentFBc))
 incPlotSourced
[…]

### 2013-07-29 in_progress/models/costBenefitAnalysis/helpers.R
fixing file width issue

@@ -10,6 +10,12 @@ acuteLatentFBc       <- "#FFA573"
 chronicLatentFBc     <- "#FFC973"
 acuteLatentUSBc      <- "#6999D3"
 chronicLatentUSBc    <- "#5FD3B3"
+latentFBc            <- "#FFB773"
+latentUSBc           <- "#64B6C3"
+activeTBFBdL1c       <- "#AA4DA6"
+activeTBFBdF1c       <- "#D56097"
+activeTBUSBdL0c      <- "#BFF27A"
+activeTBUSBdF0c      <- "#FFFE80"
 
 activeInfecFBL       <- rep("FB Active Infectious TB",totT)
 activeNoInfecFBL     <- rep("FB Active Non-infectious TB", totT)
@@ -99,7 +105,7 @@ intLabels <- function(type,magnitude) {
   return(eval(as.name(paste(c(type,magnitude,'L'),collapse=""))))
 }
 
-interventionTypes <- list('redEnLTBI','redImm','incLTBItrmt','redTrans')
+interventionTypes <- list('redEnLTBI')#,'redImm','incLTBItrmt','redTrans')
 interventionMags <- list(redEnLTBI=list(50,75,100),redImm=list(50,75),
                          incLTBItrmt=list(100,300),redTrans=list(100))
 incDataTypeGrouped <- list()
@@ -182,12 +188,10 @@ costPlotSourced <- ggplot(baseCumulativeSourcedInc, aes(x=year)) +
   geom_ribbon(aes(ymin=cActUSBdL0c, ymax=cActUSBdF0c, fill=activeTBUSBdF0L)) + 
   theme_gray(base_size=20) + theme(legend.position=c(0.2,0.85)) + 
   #coord_fixed(ratio=1/200) + 
-  scale_fill_discrete(breaks=c(activeTBUSBdF0Ls,
-                               activeTBUSBdL0Ls,
-                               latentUSBLs,
-                               activeTBFBdF1Ls,
-                               activeTBFBdL1Ls,
-                               latentFBLs))
+  scale_fill_manual(breaks=c(activeTBUSBdF0Ls,activeTBUSBdL0Ls,latentUSBLs,
+                             activeTBFBdF1Ls,activeTBFBdL1Ls,latentFBLs),
+                    values=c(activeTBUSBdF0c,activeTBUSBdL0c,latentUSBc,
+                             activeTBFBdF1c,activeTBFBdL1c,latentFBc))
[…]

### 2013-07-29 in_progress/models/costBenefitAnalysis/helpers.R
graph 1 for middle column

@@ -1,3 +1,7 @@
+#TODO: Make all values named vectors
+noIntLs              <- "No Intervention"
+noIntL               <- rep(noInts,totT)
+
 acuteLatentFBLs      <- "FB Acute LTBI"
 acuteLatentFBL       <- rep(acuteLatentFBLs,totT)
 chronicLatentFBLs    <- "FB Chronic LTBI"
@@ -91,60 +95,102 @@ incPlotTotalAll <- ggplot(baseCumulativeInc, aes(x=year)) +
            geom_ribbon(aes(ymin=IL0c,ymax=II0c,fill=activeInfecUSBL))   + 
            geom_ribbon(aes(ymin=II0c,ymax=IJ0c,fill=activeNoInfecUSBL))
 
-
-intLabels <- function(type,magnitude) {
-  redEnLTBI100L   <- rep("100% Reduction in Entering LTBI", totT)
-  redEnLTBI75L    <- rep("75% Reduction in Entering LTBI",  totT)
-  redEnLTBI50L    <- rep("50% Reduction in Entering LTBI",  totT)
-  redImm50L       <- rep("50% Reduction in Immigration",    totT)
-  redImm75L       <- rep("75% Reduction in Immigration",    totT)
-  incLTBItrmt100L <- rep("100% Increase in Immigration",    totT)
-  incLTBItrmt300L <- rep("300% Increase in Immigration",    totT)
-  redTrans100L    <- rep("100% Reduction in Transmission",  totT)
+  
+intLabels <- function(type,magnitude,vec=T) {
+  redEnLTBI100Ls   <- "100% Entering LTBI Cured"
+  redEnLTBI75Ls    <- "75% Entering LTBI Cured"
+  redEnLTBI50Ls    <- "50% Entering LTBI Cured"
+  redImm50Ls       <- "50% Immigration Reduction"
+  redImm75Ls       <- "75% Immigration Reduction"
+  incLTBItrmt100Ls <- "100% LTBI Treatment Increase"
+  incLTBItrmt300Ls <- "300% LTBI Treatment Increase"
+  redTrans100Ls    <- "100% Reduction in Transmission"
+  redEnLTBI100L    <- rep("100% Entering LTBI Cured",        totT)
+  redEnLTBI75L     <- rep("75% Entering LTBI Cured",         totT)
+  redEnLTBI50L     <- rep("50% Entering LTBI Cured",         totT)
+  redImm50L        <- rep("50% Immigration Reduction",       totT)
[…]

### 2013-07-29 in_progress/models/costBenefitAnalysis/helpers.R
squarer graph

@@ -240,5 +240,5 @@ costPlotSourced <- ggplot(baseCumulativeSourcedInc, aes(x=year)) +
                              activeTBFBdF1c,activeTBFBdL1c,latentFBc))
 
 costPlotSourced
-ggsave('forPoster/costPlotSourced.pdf',costPlotSourced,width=13.5,height=8)
+ggsave('forPoster/costPlotSourced.pdf',costPlotSourced,width=10,height=8)
 

### 2013-07-29 in_progress/presentations/poster/reuMHC2013NoSIRIntro.tex
added new fig
fixed block structure
ton of tweaks to poster
more tweaks
nothing really

@@
 \begin{frame}
-  \begin{columns}
+  \begin{columns}[T]
     \begin{column}{.3\textwidth}
-      \vspace{-2em}
       \begin{block}{Introduction}
@@
 This work is an extension of the Hill Model, a complex compartmental model of tuberculosis (TB) in the United States.
-       % Epidemiological models offer insight into the structure of disease
-       % outbreaks and the merits of various interventions. The most common
-       % epidemiological models are compartmental differential equation models,
-       % in which the population is dispersed between a variety of distinct
-       % compartments, through which they move according to a system of
-       % Differential Equations. In order to model tuberculosis (TB) in the
-       % United States (US), Hill, Becerra, and Castro designed a complex
-       % compartmental model called the hill model.
       \end{block}
+      \vspace{1em}
       \begin{block}{The Basic Hill Model}
-        \vspace{-2em}
-        \begin{block}{}
+        \begin{columns}[T]
           \begin{column}{.5\textwidth}
@@
               \begin{center}
-                \includegraphics[height=12cm,width=.9\textwidth]{HillModelFlowChart}
+                \includegraphics[width=\textwidth]{HillModelFlowChart}
               \end{center}
@@
           \end{column}
-          \begin{column}{.43\textwidth}
+          \begin{column}{.45\textwidth}
+              \vspace{1.5em}
             Populations:
@@
           \end{column}
+        \end{columns}
+
+        \vspace{1em}
+        \begin{itemize}
+          \item USB TB levels are declining
+          \item FB latent TB infection (LTBI) arrivals remain high
+          \item TB elimination in total US population not projected by 2100
+        \end{itemize}
+
+        \begin{columns}
+          \begin{column}{.47\textwidth}
             \begin{figure}[h]
               \begin{center}
-              \includegraphics[height=20cm] {newfig}%{incPlotSourced2}
+                \includegraphics[width=\textwidth] {incPlotSourced2}
               \end{center}
@@
             \end{figure}
-          \vspace{-1em}
-%          \begin{figure}[h]
-%            \begin{center}
-%              \includegraphics[height=15cm]{incPlotTotal}
-%            \end{center}
-%            \caption{New cases per year of various types of TB in the US.}
-%            \label{fig:incPlotTotal}
-%          \end{figure}
-        \end{block}
+          \end{column}
+          \begin{column}{.47\textwidth}
+            \begin{figure}[h]
+              \begin{center}
+                \includegraphics[width=\textwidth]{costPlotSourced2}
+              \end{center}
+              \caption{New cases per year of various types of TB in the US.}
+              \label{fig:incPlotTotal}
+             \end{figure}
+           \end{column}
+         \end{columns}
        \end{block}
@@
     \begin{column}{.3\textwidth}
-      \vspace{-1.5em}
+      %\vspace{-1.5em}
       \begin{block}{Analyzing US TB Reduction Strategies}
@@
         \end{itemize}
+      \end{block}
+
       \begin{block}{Intervention Analysis}
-          \vspace{-1.6em}
-          %\begin{column}{.45\textwidth}
+        %\vspace{-1.6em}
         \begin{figure}[h]
           \begin{center}
-                \includegraphics[height=10cm,width=\textwidth]{incidencePlotRedEnLTBI}
+            \includegraphics[height=.3\textwidth,width=.6\textwidth]{redEnLTBIIncGrouped}
           \end{center}
@@
         \end{figure}
-          %\end{column}
-          %\begin{column}{.45\textwidth}
         \begin{figure}[h]
           \begin{center}
-                \includegraphics[height=10cm,width=\textwidth]{incLTBItrmtIncGrouped}
+            \includegraphics[height=.3\textwidth,width=.6\textwidth]{incLTBItrmtIncGrouped}
           \end{center}
@@
       \end{block}
-      \end{block}
       \begin{block}{Economic Modeling}
@@
           \item Estimates implementation cost of intervention
+          \item Base HCS Costs:
+            \begin{description}
+              \item[Active TB:]\hfill 
+                \$14,014.90
+              \item[LTBI:]\hfill 
+                \$403.45
+            \end{description}
         \end{itemize}
-        \begin{block}{}
-          \vspace{-4em}
+        \begin{columns}[T]
           \begin{column}{.66\textwidth}
@@
               \end{center}
-              \caption{Cumulative implementation costs, US HCS savings, and net
-                       US costs of LTBI arrival cure rates. Cost/case cured was
-                       \$600, \$800, and \$1000 for 50\%, 75\%, and 100\%
-                       cured.}
+              \caption{}
               \label{fig:redEnLTBI_costs}
@@
           \begin{column}{.26\textwidth}
-            Base HCS Costs:
           \begin{description}
-              \item[Active TB:]\hfill \\ 
-                \$14,014.90
-              \item[LTBI:]\hfill \\ 
-                \$403.45
+            [Figure : ]Cumulative implementation costs, US HCS savings, and net
+                       US costs of LTBI arrival cure rates. Cost/case cured was
+                       \$600, \$800, and \$1000 for 50\%, 75\%, and 100\%
+                       cured.
           \end{description}
           \end{column}
-        \end{block}
+        \end{columns}
       \end{block}
     \end{column}
+
     \begin{column}{.3\textwidth}
-      \vspace{-.5em}
+      %\vspace{-.5em}
       \begin{block}{An Agent-Based Implementation}
@@
         and \texttt{C++}.
-        \begin{block}{}
-          \vspace{-2em}
+        \begin{columns}
+          %\vspace{-2em}
           \begin{column}{.45\textwidth}
@@
               \begin{center}
-                \includegraphics[width=\textwidth]{finalRunSmall}
+                \includegraphics[width=\textwidth]{finalRunSmall2}
               \end{center}
@@
           \end{column}
-        \end{block}
+        \end{columns}
       \end{block}
@@
       \begin{block}{Stochastic Models as a Measure of Variability}
-        \begin{block}{}
-          \vspace{-2em}
+        \begin{columns}
+          %\vspace{-2em}
           \begin{column}{.45\textwidth}
@@
           \end{column}
-        \end{block}
+        \end{columns}
       \end{block}
 
+      \vspace{1em}
       \begin{block}{References}

### 2013-07-29 in_progress/presentations/poster/reuMHC2013NoSIRIntro.tex

@@
               \end{center}
-              \caption{A flow chart representing the compartments of the Hill Model.}
+              \caption{The Hill Model schematic}
               \label{fig:hillFlow}
@@
               \item Foreign Born (FB)
+              %\item USB TB incidence declining
+              %\item FB latent TB infection (LTBI) high
+              %\item TB elimination in total population not projected by 2100
             \end{itemize}
@@
         \begin{itemize}
-          \item USB TB levels are declining
+          \item USB TB incidence rates are declining
           \item FB latent TB infection (LTBI) arrivals remain high
-          \item TB elimination in total US population not projected by 2100
+          \item TB elimination in total population not projected by 2100
         \end{itemize}
-
+        \vspace{1em}
         \begin{columns}
@@
               \end{center}
-              \caption{New cases per year of various types of TB in the US.}
+              \caption{Source population of US HCS TB cost}
               \label{fig:incPlotTotal}
@@
         \begin{figure}[h]
-          \begin{center}
-            \includegraphics[height=.3\textwidth,width=.6\textwidth]{redEnLTBIIncGrouped}
-          \end{center}
+          %\begin{center}
+            %\includegraphics[height=.3\textwidth,width=.6\textwidth]{redEnLTBIIncGrouped}
+          %\end{center}
+          %\caption{Incidence/million in USB, FB, and total populations,
+                   %given 0\%, 50\%, 75\%, or 100\% treatment of incoming
+                   %LTBI}
+          %\label{fig:redEnLTBI_incidence}
+          \begin{minipage}[l]{0.6\textwidth}
+            \includegraphics[height=.5\textwidth,width=\textwidth]{redEnLTBIIncGrouped}
+          \end{minipage}
+          \begin{minipage}[r]{0.35\textwidth}
             \caption{Incidence/million in USB, FB, and total populations,
                      given 0\%, 50\%, 75\%, or 100\% treatment of incoming
-                   LTBI.}
+                     LTBI}
+          \end{minipage}
           \label{fig:redEnLTBI_incidence}
@@
           \caption{Incidence/million in USB, FB, and total populations,
-                   given 0\%, 100\%, or 300\% LTBI treatment increase.}
+                   given 0\%, 100\%, or 300\% LTBI treatment increase}
           \label{fig:incLTBItrmt_incidence}
         \end{figure}
-        %\end{column}
       \end{block}
@@
           \item Estimates implementation cost of intervention
-          \item Base HCS Costs:
-            \begin{description}
-              \item[Active TB:]\hfill 
-                \$14,014.90
-              \item[LTBI:]\hfill 
-                \$403.45
-            \end{description}
         \end{itemize}
@@
               \end{center}
-              \caption{}
+              \caption{Cumulative implementation costs, US HCS savings, and net
+                       US costs of LTBI arrival cure rates. Cost/case cured was
+                       \$600, \$800, and \$1000 for 50\%, 75\%, and 100\%
+                       cured}
               \label{fig:redEnLTBI_costs}
@@
           \begin{column}{.26\textwidth}
+            Base HCS Costs:
             \begin{description}
-            [Figure : ]Cumulative implementation costs, US HCS savings, and net
-                       US costs of LTBI arrival cure rates. Cost/case cured was
-                       \$600, \$800, and \$1000 for 50\%, 75\%, and 100\%
-                       cured.
+              \item[Active TB:]\hfill \\ 
+                \$14,014.90
+              \item[LTBI:]\hfill \\ 
+                \$403.45
             \end{description}
@@
       \begin{block}{An Agent-Based Implementation}
-        Agent-based models capture disease dynamics on the individual level, and
+        Agent-based models capture disease dynamics on the individual level and
         reflect stochasticity and granularity lost in compartmental models.

### 2013-07-29 in_progress/models/costBenefitAnalysis/helpers.R
Another graph down

@@ -62,9 +62,9 @@ incPlotSourced <- ggplot(baseCumulativeSourcedInc, aes(x=year)) +
            geom_ribbon(aes(ymin=IdL1c,ymax=IdF1c,fill=acuteLatentFBL))    + 
            geom_ribbon(aes(ymin=IdF1c,ymax=IdL0c,fill=chronicLatentUSBL)) + 
            geom_ribbon(aes(ymin=IdL0c,ymax=IdF0c,fill=acuteLatentUSBL))   + 
-           theme_gray(base_size=20) + 
-           theme(legend.position=c(0.6,0.8), axis.title=element_text(size=40), 
-           axis.text=element_text(size=27), plot.title=element_text(size=40),
+           theme_gray(base_size=25) + 
+           theme(legend.position=c(0.6,0.8), axis.title=element_text(size=30), 
+           axis.text=element_text(size=17), plot.title=element_text(size=30),
            legend.key.height=unit(1.8,'line')) + 
            coord_fixed(ratio=1/200) + 
            scale_fill_manual(breaks=c(acuteLatentUSBLs, 
@@ -165,34 +165,35 @@ incPlotTypeGroupedG <- function(type, incDataTypeGrouped) {
   }
   plot <- ggplot() + 
     scale_y_log10(breaks=c(1,2,5,10,25,50,100,200),
-                 labels=c("Elimination (1)",2,5,10,25,50,100,200),
+                 labels=c(1,2,5,10,25,50,100,200),
                  limits=c(0.5,250)) + 
     labs(x="Years", y="Incidence/million", color="Population", 
           linetype="Intervention Status") + 
     plotTitle("Incidence/Million vs. Intervention Magnitude","") +
     scale_linetype_manual(values=ltvalues) +  
     geom_line(data = data.frame(year=years, baseInc), aes(x=year, y=IN0,   
-              color=USB, linetype=noIntL), size=.9)  + 
+              color=USB, linetype=noIntL))  + 
     geom_line(data = data.frame(year=years, baseInc), aes(x=year, y=IN1,   
-              color=FB,  linetype=noIntL), size=.9)  + 
+              color=FB,  linetype=noIntL))  + 
     geom_line(data = data.frame(year=years, baseInc), aes(x=year, y=INall, 
-              color=all, linetype=noIntL), size=.9)  +
-    theme_gray(base_size=18) + theme(legend.position=c(0.18,0.22))
[…]

### 2013-07-29 in_progress/models/costBenefitAnalysis/helpers.R
one more graph

@@ -192,8 +192,10 @@ incPlotTypeGroupedG <- function(type, incDataTypeGrouped) {
   }
   return(plot) 
 }
-J <- incPlotTypeGroupedG('redEnLTBI',incDataTypeGrouped)
-ggsave('forPoster/redEnLTBIIncGrouped.pdf',J,width=10,height=10)
+#J <- incPlotTypeGroupedG('redEnLTBI',incDataTypeGrouped)
+#ggsave('forPoster/redEnLTBIIncGrouped.pdf',J,width=10,height=10)
+J <- incPlotTypeGroupedG('incLTBItrmt',incDataTypeGrouped)
+ggsave('forPoster/incLTBItrmtIncGrouped.pdf',J,width=10,height=10)
 
 incPlot <- ggplot(incData, aes(x=year)) + 
            scale_y_log10(breaks=c(1,2,5,10,25,50,100,200),

### 2013-07-29 in_progress/models/costBenefitAnalysis/helpers.R
increased font size a bit more

@@ -178,8 +178,8 @@ incPlotTypeGroupedG <- function(type, incDataTypeGrouped) {
     geom_line(data = data.frame(year=years, baseInc), aes(x=year, y=INall, 
               color=all, linetype=noIntL))  +
     theme_gray(base_size=20) + 
-    theme(legend.position=c(0.18,0.22), axis.title=element_text(size=30), 
-          axis.text=element_text(size=20), plot.title=element_text(size=30),
+    theme(legend.position=c(0.18,0.22), axis.title=element_text(size=34), 
+          axis.text=element_text(size=25), plot.title=element_text(size=34),
           legend.key.height=unit(1.8,'line')) + 
     geom_hline(data=data.frame(year=years), aes(x=year,y=1))
   for (magnitude in names(data)) {
@@ -192,9 +192,10 @@ incPlotTypeGroupedG <- function(type, incDataTypeGrouped) {
   }
   return(plot) 
 }
-#J <- incPlotTypeGroupedG('redEnLTBI',incDataTypeGrouped)
-#ggsave('forPoster/redEnLTBIIncGrouped.pdf',J,width=10,height=10)
-J <- incPlotTypeGroupedG('incLTBItrmt',incDataTypeGrouped)
+J <- incPlotTypeGroupedG('redEnLTBI',incDataTypeGrouped)
+ggsave('forPoster/redEnLTBIIncGrouped.pdf',J,width=10,height=10)
+J <- incPlotTypeGroupedG('incLTBItrmt',incDataTypeGrouped) + 
+     theme(legend.position=c(0.78,0.22))
 ggsave('forPoster/incLTBItrmtIncGrouped.pdf',J,width=10,height=10)
 
 incPlot <- ggplot(incData, aes(x=year)) + 

### 2013-07-29 in_progress/models/costBenefitAnalysis/helpers.R
trying increasing line size

@@ -172,23 +172,26 @@ incPlotTypeGroupedG <- function(type, incDataTypeGrouped) {
     plotTitle("Incidence/Million vs. Intervention Magnitude","") +
     scale_linetype_manual(values=ltvalues) +  
     geom_line(data = data.frame(year=years, baseInc), aes(x=year, y=IN0,   
-              color=USB, linetype=noIntL))  + 
+              color=USB, linetype=noIntL), size=2)  + 
     geom_line(data = data.frame(year=years, baseInc), aes(x=year, y=IN1,   
-              color=FB,  linetype=noIntL))  + 
+              color=FB,  linetype=noIntL), size=2)  + 
     geom_line(data = data.frame(year=years, baseInc), aes(x=year, y=INall, 
-              color=all, linetype=noIntL))  +
+              color=all, linetype=noIntL), size=2)  +
     theme_gray(base_size=20) + 
     theme(legend.position=c(0.18,0.22), axis.title=element_text(size=34), 
           axis.text=element_text(size=25), plot.title=element_text(size=34),
           legend.key.height=unit(1.8,'line')) + 
-    geom_hline(data=data.frame(year=years), aes(x=year,y=1))
+    geom_hline(data=data.frame(year=years), aes(x=year,y=1), size=2)
   for (magnitude in names(data)) {
     incData   <- data.frame(year=years,data[[magnitude]],
                             label=intLabels(type,magnitude))
     plot <- plot + 
-    geom_line(data=incData, aes(x=year, y=IN0,   color=USB, linetype=label))+ 
-    geom_line(data=incData, aes(x=year, y=IN1,   color=FB,  linetype=label))+ 
-    geom_line(data=incData, aes(x=year, y=INall, color=all, linetype=label))
+    geom_line(data=incData, aes(x=year, y=IN0,   color=USB, linetype=label),
+      size=2)+ 
+    geom_line(data=incData, aes(x=year, y=IN1,   color=FB,  linetype=label),
+      size=2)+ 
+    geom_line(data=incData, aes(x=year, y=INall, color=all, linetype=label),
+      size=2)
   }
   return(plot) 
 }

### 2013-07-29 in_progress/models/costBenefitAnalysis/interventionGroupsPresenter.R
and fixed colin's plot some more

@@ -125,15 +125,16 @@ x <- ggplot(redEnLTBI,aes(x=year)) +
        plotTitle("Implementation Costs, Savings, and 
 US Health Care System (US HCS) 
 Costs for 100%, 75%, and 50% LTBI reduction","") + 
-       geom_line(aes(y=redEnLTBI100_costs,   color=costs,      linetype=redEnLTBI100L)) +
-       geom_line(aes(y=redEnLTBI75_costs,    color=costs,      linetype=redEnLTBI75L)) +
-       geom_line(aes(y=redEnLTBI50_costs,    color=costs,      linetype=redEnLTBI50L)) +
-       geom_line(aes(y=redEnLTBI100_savings, color=savings,    linetype=redEnLTBI100L)) +
-       geom_line(aes(y=redEnLTBI75_savings,  color=savings,    linetype=redEnLTBI75L)) +
-       geom_line(aes(y=redEnLTBI50_savings,  color=savings,    linetype=redEnLTBI50L)) +
-       geom_line(aes(y=redEnLTBI100_totCost, color=totalCosts, linetype=redEnLTBI100L)) +
-       geom_line(aes(y=redEnLTBI75_totCost,  color=totalCosts, linetype=redEnLTBI75L)) +
-       geom_line(aes(y=redEnLTBI50_totCost,  color=totalCosts, linetype=redEnLTBI50L)) +
+       geom_hline(aes(y=0),size=2) +
+       geom_line(aes(y=redEnLTBI100_costs,   color=costs,      linetype=redEnLTBI100L), size=2) +
+       geom_line(aes(y=redEnLTBI75_costs,    color=costs,      linetype=redEnLTBI75L), size=2) +
+       geom_line(aes(y=redEnLTBI50_costs,    color=costs,      linetype=redEnLTBI50L), size=2) +
+       geom_line(aes(y=redEnLTBI100_savings, color=savings,    linetype=redEnLTBI100L), size=2) +
+       geom_line(aes(y=redEnLTBI75_savings,  color=savings,    linetype=redEnLTBI75L), size=2) +
+       geom_line(aes(y=redEnLTBI50_savings,  color=savings,    linetype=redEnLTBI50L), size=2) +
+       geom_line(aes(y=redEnLTBI100_totCost, color=totalCosts, linetype=redEnLTBI100L), size=2) +
[…]

### 2013-07-29 in_progress/models/costBenefitAnalysis/interventionConfig.R
Added some R code and acknowledgments

@@ -26,7 +26,7 @@ redEnLTBI_Interventions <- allInterventions[1:3]
 redImm_Interventions <- allInterventions[5:6]
 incLTBItrmt_Interventions <- allInterventions[7:8]
                       
-curInterventions <- c()#allInterventions
+curInterventions <- c('redEnLTBI100')#allInterventions
 
 interventionConfig <- function(interventionStr, x=0) { #x is an integer refering to cost option, ranges 0 to 5
   error    <- F

### 2013-07-29 in_progress/models/costBenefitAnalysis/interventionPresenter.R

@@ -3,49 +3,8 @@ source('deSolConstants.R')
 source('hillFunctions.R') #for generateIncidence
 source('interventionConfig.R')
 
-#Title Generation:
-plotTitle <- function(base,interventionName,final="") {
-  if (final != "") {
-    return(ggtitle(paste(c(base,interventionName,final),collapse=" ")))
-  } else {
-    return(ggtitle(paste(c(base,interventionName),collapse=" ")))
-  }
-}
-
-#Data Labels
-USB             <- rep("USB",             totT)
-FB              <- rep("FB",              totT)
-all             <- rep("All",             totT)
-noInt           <- rep("No Intervention", totT)
-int             <- rep("Intervention",    totT)
-savings         <- rep("Savings",         totT)
-costs           <- rep("Cost",            totT)
-averted         <- rep("Cases Averted",   totT)
-TBdeathsAverted <- rep("TB Deaths Averted",   totT)
-
-#Aesthetics
-USBC             <- 'blue'
-FBC              <- 'green'
-allC             <- 'red'
-noIntC           <- 'black'
-intC             <- 'blue'
-savingsC         <- '#24913C'
-costsC           <- '#9F0013'
-avertedC         <- '#24913C'
-TBdeathsAvertedC <- '#24913C'
-
-baseData <- read.csv(baseFile)
-#Base Incidence
-baseInc <- generateIncidence(baseData)
-#US Health Care System (HCS) TB costs due to base system
-baseHCSCost <- (baseData$cN0 + baseData$cN1)/1e9
-#Base Cases
-baseCases  <- 1e6*(baseData$progAcute0 + baseData$progAcute1 + 
-                   baseData$progChron0 + baseData$progChron1)
-baseCasesD <- 1e6*(baseData$progTotalD0 + baseData$progTotalD1)
-#Base Deaths
-baseDeaths  <- 1e6*(baseData$tbdeath0 + baseData$tbdeath1)
-baseDeathsD <- 1e6*(baseData$tbdeathD0 + baseData$tbdeathD1)
+#plotting Functions:
+source('plotGenerators.R')
 
 #TODO: Remove Duplicated Code
 #TODO: Add active disease cost plot
@@ -55,241 +14,6 @@ baseDeathsD <- 1e6*(baseData$tbdeathD0 + baseData$tbdeathD1)
 #TODO: Fix titles
 #TODO: switch line type for intervention status
 #TODO: determine how to handle plot defaults for multiple interventions
-
[…]

### 2013-07-29 in_progress/models/costBenefitAnalysis/plotGenerators.R

@@ -1,0 +1,279 @@
+#Base Data:
+baseData <- read.csv(baseFile)
+#Base Incidence
+baseInc <- generateIncidence(baseData)
+#US Health Care System (HCS) TB costs due to base system
+baseHCSCost <- (baseData$cN0 + baseData$cN1)/1e9
+#Base Cases
+baseCases  <- 1e6*(baseData$progAcute0 + baseData$progAcute1 + 
+                   baseData$progChron0 + baseData$progChron1)
+baseCasesD <- 1e6*(baseData$progTotalD0 + baseData$progTotalD1)
+#Base Deaths
+baseDeaths  <- 1e6*(baseData$tbdeath0 + baseData$tbdeath1)
+baseDeathsD <- 1e6*(baseData$tbdeathD0 + baseData$tbdeathD1)
+
+
+#Title Generation:
+plotTitle <- function(base,interventionName,final="") {
+  if (final != "") {
+    return(ggtitle(paste(c(base,interventionName,final),collapse=" ")))
+  } else {
+    return(ggtitle(paste(c(base,interventionName),collapse=" ")))
+  }
+}
+
+#Data Labels
+USB             <- rep("USB",             totT)
+FB              <- rep("FB",              totT)
+all             <- rep("All",             totT)
+noInt           <- rep("No Intervention", totT)
+int             <- rep("Intervention",    totT)
+savings         <- rep("Savings",         totT)
+costs           <- rep("Cost",            totT)
+averted         <- rep("Cases Averted",   totT)
+TBdeathsAverted <- rep("TB Deaths Averted",   totT)
+
+#Aesthetics
+USBC             <- 'blue'
+FBC              <- 'green'
+allC             <- 'red'
+noIntC           <- 'black'
+intC             <- 'blue'
+savingsC         <- '#24913C'
+costsC           <- '#9F0013'
+avertedC         <- '#24913C'
+TBdeathsAvertedC <- '#24913C'
+
+incidencePlotG <- function(interventionData,interventionName) {
+  #Incidence Reports: Comparing Baseline Incidence against Intervention Incidence
+  interventionInc  <- generateIncidence(interventionData)
+  incData <- data.frame(year = years, 
+                        baseUSB = baseInc$IN0,   intUSB = interventionInc$IN0, 
+                        baseFB  = baseInc$IN1,    intFB = interventionInc$IN1, 
+                        baseAll = baseInc$INall, intAll = interventionInc$INall)
[…]

### 2013-07-29 in_progress/presentations/poster/reuMHC2013NoSIRIntro.tex
changed two middle graphs to side captions
changed dimensions of two middle graphs
economic modeling section changes
good economic modeling
fixed up middle column
Added some R code and acknowledgments
changed histogram captions

@@
         \end{columns}
-
-        \vspace{1em}
+        \vspace{0.6em}
         \begin{itemize}
@@
           \item TB elimination in total population not projected by 2100
+          \item TB cases and costs dominated by FB LTBI individuals
         \end{itemize}
-        \vspace{1em}
-        \begin{columns}
+        \vspace{0.6em}
+        \begin{columns}[T]
           \begin{column}{.47\textwidth}
@@
               \begin{center}
-                \includegraphics[width=\textwidth] {incPlotSourced2}
+                \includegraphics[height=0.83\textwidth,width=\textwidth] {incPlotSourced2}
               \end{center}
-              \caption{The source population of US TB incidence}
+              \caption{Source population of US TB incidence}
               \label{fig:incPlotSourced}
@@
               \begin{center}
-                \includegraphics[width=\textwidth]{costPlotSourced2}
+                \includegraphics[height=0.83\textwidth,width=\textwidth]{costPlotSourced2}
               \end{center}
@@
         \begin{figure}[h]
-          %\begin{center}
-            %\includegraphics[height=.3\textwidth,width=.6\textwidth]{redEnLTBIIncGrouped}
-          %\end{center}
-          %\caption{Incidence/million in USB, FB, and total populations,
-                   %given 0\%, 50\%, 75\%, or 100\% treatment of incoming
-                   %LTBI}
-          %\label{fig:redEnLTBI_incidence}
-          \begin{minipage}[l]{0.6\textwidth}
-            \includegraphics[height=.5\textwidth,width=\textwidth]{redEnLTBIIncGrouped}
+          \begin{minipage}[c]{0.6\textwidth}
+            \includegraphics[height=0.7\textwidth,width=\textwidth]{redEnLTBIIncGrouped}
           \end{minipage}
-          \begin{minipage}[r]{0.35\textwidth}
+          \hspace{0.5em}
+          \begin{minipage}[c]{0.35\textwidth}
             \caption{Incidence/million in USB, FB, and total populations,
@@
         \begin{figure}[h]
-          \begin{center}
-            \includegraphics[height=.3\textwidth,width=.6\textwidth]{incLTBItrmtIncGrouped}
-          \end{center}
+          \begin{minipage}[c]{0.6\textwidth}
+            \includegraphics[height=0.7\textwidth,width=\textwidth]{incLTBItrmtIncGrouped}
+          \end{minipage}
+          \hspace{0.5em}
+          \begin{minipage}[c]{0.35\textwidth}
             \caption{Incidence/million in USB, FB, and total populations,
                      given 0\%, 100\%, or 300\% LTBI treatment increase}
+          \end{minipage}
           \label{fig:incLTBItrmt_incidence}
@@
           \item Estimates implementation cost of intervention
+          \item Active TB Costs: \$14,014.90 LTBI Costs: \$403.45
+
         \end{itemize}
-        \begin{columns}[T]
-          \begin{column}{.66\textwidth}
+        \vspace{.5em}
+        %\begin{columns}[T]
+          %\begin{column}{.66\textwidth}
             \begin{figure}[h]
-              \begin{center}
-                \includegraphics[width=\textwidth,height=13cm]{EnLTBIRedGroupCost.pdf}
-              \end{center}
+
+              \begin{minipage}[c]{0.6\textwidth}
+                \includegraphics[height=0.7\textwidth, width=\textwidth]{EnLTBIRedGroupCost.pdf}
+              \end{minipage}
+              \hspace{0.5em}
+              \begin{minipage}[c]{0.35\textwidth}
                 \caption{Cumulative implementation costs, US HCS savings, and net
@@
                        cured}
+              \end{minipage}
               \label{fig:redEnLTBI_costs} 
             \end{figure}
-          \end{column}
-          \begin{column}{.26\textwidth}
-            Base HCS Costs:
-            \begin{description}
-              \item[Active TB:]\hfill \\ 
-                \$14,014.90
-              \item[LTBI:]\hfill \\ 
-                \$403.45
-            \end{description}
-          \end{column}
-        \end{columns}
+          %\end{column}
+          %\begin{column}{.26\textwidth}
+            % Base HCS Costs:
+            % \begin{description}
+            %   \item[Active TB:]\hfill \\ 
+            %     \$14,014.90
+            %   \item[LTBI:]\hfill \\ 
+            %     \$403.45
+            % \end{description}
+          %\end{column}
+        %\end{columns}
       \end{block}
@@
 
-      \vspace{1em}
-      \begin{block}{References}
-        Hill, A. N., Becerra, J. E., \& Castro, K. G. (2012). Modelling tuberculosis trends in the USA. Epidemiology and infection, 140(10), 1862.
+      \vspace{.9em}
+      \begin{block}{References \& Acknowledgments}
+        This research was supported via an NSF REU grant. 
+        \small{[1] Hill, A. N., Becerra, J. E., \& Castro, K. G. (2012). Modelling
+          tuberculosis trends in the USA. Epidemiology and infection, 140(10),
+          1862.}
       \end{block}

### 2013-07-29 in_progress/presentations/poster/reuMHC2013NoSIRIntro.tex
added summary block to third column

@@
         and \texttt{C++}.
-        \begin{columns}
-          %\vspace{-2em}
+        \begin{columns}[T]
+          \vspace{-2em}
           \begin{column}{.45\textwidth}
@@
               \begin{center}
-                \includegraphics[width=\textwidth]{NLHMinc}
+                \includegraphics[height=0.8\textwidth,width=\textwidth]{NLHMinc}
               \end{center}
@@
               \begin{center}
-                \includegraphics[width=\textwidth]{finalRunSmall2}
+                \includegraphics[height=0.8\textwidth,width=\textwidth]{finalRunSmall2}
               \end{center}
@@
       \begin{block}{Stochastic Models as a Measure of Variability}
-        \begin{columns}
-          %\vspace{-2em}
-          \begin{column}{.45\textwidth}
+        %\vspace{-0.5em}
+        %\begin{columns}[T]
+          %\begin{column}{.45\textwidth}
+            %\begin{figure}[h]
+              %\begin{center}
+                %\includegraphics[height=0.5\textwidth,width=\textwidth]{IN0dist}
+              %\end{center}
+              %\caption{USB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 0.233196, \sigma = 0.016534$)}
+              %\label{fig:IN0dist}
+            %\end{figure}
+          %\end{column}
+          %\begin{column}{.45\textwidth}
+            %\begin{figure}[h]
+              %\begin{center}
+                %\includegraphics[height=0.5\textwidth,width=\textwidth]{IN1dist}
+              %\end{center}
+              %\caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
+              %\label{fig:IN1dist}
+            %\end{figure}
+          %\end{column}
+        %\end{columns}
         \begin{figure}[h]
           \begin{center}
-                \includegraphics[width=\textwidth]{IN0dist}
+            \includegraphics[height=0.25\textwidth,width=0.45\textwidth]{IN0dist}
+            \includegraphics[height=0.25\textwidth,width=0.45\textwidth]{IN1dist}
           \end{center}
-              \caption{USB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 0.233196, \sigma = 0.016534$)}
-              \label{fig:IN0dist}
+          \caption{USB and FB Incidence (\texttt{c++}) with fitted Normal curves (USB: $\mu = 0.233, \sigma = 0.016534$, FB: $\mu = 98.6, \sigma = 0.525294$)}
+          \label{fig:INdist}
         \end{figure}
-          \end{column}
-          \begin{column}{.45\textwidth}
-            \begin{figure}[h]
-              \begin{center}
-                \includegraphics[width=\textwidth]{IN1dist}
-              \end{center}
-              \caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
-              \label{fig:IN1dist}
-            \end{figure}
-          \end{column}
-        \end{columns}
+              %\caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
+              %\label{fig:IN1dist}
       \end{block}
 
-      \vspace{.9em}
+      \begin{block}{Summary}
+        \begin{itemize}
+          \item TB elimination is possible
+          \item new framework for disease modeling
+          \item something else
+        \end{itemize}
+      \end{block}
+      %\vspace{.9em}
       \begin{block}{References \& Acknowledgments}

### 2013-07-31 in_progress/models/costBenefitAnalysis/hillFunctions.R
prepping for overnight sensitivity analysis

@@ -65,13 +65,6 @@ efficacyLTBI  <- .9  #LTBI treatement efficacy
 adherenceLTBI <- .64 #LTBI treatment adherence
 probLTBItreatsuccess <- efficacyLTBI*adherenceLTBI 
 
-#Cost Parameter Values: 
-costtb   <- 2985   #TB treatment cost w/o hopsitalization <- Dylan supp. p.11-12
-costhosp <- 25495  #TB treatment cost w/ hospitalization  <- Dylan supp. p.10
-costLTBI <- 403.45 #LTBI treatment cost
-Ct       <- costtb*(1-probHosp) + costhosp*probHosp #Cost of active TB treatment
-Cl       <- costLTBI/probLTBItreatsuccess           #Cost of LTBI treatment
-
 #Rate of time and health state discounting
 discRt   <- 0.03  
 
@@ -91,7 +84,6 @@ P$exogenous1[1]  <- 0
   #Differential Equation Functions
 Ddt <- function(t,v,parms) {
   with(as.list(c(t,v,parms)), {
-    #TODO: Is this right?
     discV   <- 1/(1.03^t)  #amount costs, health states discount constant
 
     #parameter values initialized for each time step
@@ -168,12 +160,13 @@ Ddt <- function(t,v,parms) {
   })
 }
 
-hill <- function(intervenCost,sigmaL,f,transmission=1,incLTBI=1,initial=cutoffT,final=totT,dataSet=P){
+hill <- function(intervenCost,sigmaL,f,transmission=1,incLTBI=1,activeTxC=F,LTBITxC=F,initial=cutoffT,final=totT,dataSet=P){
   # set values in parameters
   newparms <- c(iCnewCases=as.vector(intervenCost['newCases']), 
                 iCtotPop=as.vector(intervenCost['totPop']), 
                 iCLTBIEn=as.vector(intervenCost['LTBIEn']),
-                sigmaL=sigmaL, f=f, transmission=transmission, incLTBI=incLTBI)
+                sigmaL=sigmaL, f=f, transmission=transmission, incLTBI=incLTBI,
+                Ct=activeTxC,Cl=LTBITxC)
   parameters <- c(parms, newparms)
   # recursive=TRUE collapses dataframe to labeled vector
   initv <- c(dataSet[initial,], recursive=TRUE)

### 2013-07-31 in_progress/models/costBenefitAnalysis/interventionAnalyzer.R

@@ -1,16 +1,30 @@
 #Option Processing
 args <- commandArgs(trailingOnly = T)
 if (length(args) > 0) {
-  generateNewData <- as.logical(args[1])
+  #TODO: Remove later
+  #generateNewData <- F#as.logical(args[1])
+  analysisType    <- as.numeric(args[1])
+  index           <- as.numeric(args[2])
+  #LTBIEnCosts     <- as.numeric(args[2])
+  #activeTxC       <- as.numeric(args[3])
+  #LTBITxC         <- as.numeric(args[4])
+  #perIncLTBI      <- as.numeric(args[5])
 } else {
   generateNewData <- F
+  index <- 1
+  analysisType <- 1
 }
+generateNewData <- F
 
 #Which interventions to run:
 source('interventionConfig.R')
 
 #Hill Model:
 source('hillFunctions.R')
+
+LTBIEnCosts     <- 0
+activeTxC       <- parms[['CtBase']]
+LTBITxC         <- parms[['ClBase']]
 
 #Base Data: 
 C <- c(newCases=0,totPop=0,LTBIEn=0) 
@@ -25,13 +39,55 @@ if (generateNewData) {
 }
 baseInc <- generateIncidence(P)
 
+#TODO: Give this kind of power to the base user!
 #Intervention Analyzing:
-for (intervention in curInterventions) {
-  intConfig <- interventionConfig(intervention)
-  costs     <- intConfig$costs
-  params    <- intConfig$params
-  interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
-                    params[["incLTBI"]])
-  write.csv(interData, paste(c(intFilePrefix,intervention,intFileSuffix),
-                             collapse=""))
+
+if (analysisType == 1) {
+  activeTxCRange <- seq(0,40000,by=200)
+  if (index > 1) {
+    run <- 201*21*21 + (index-2)*201*21*20 + 1
+    LTBITxCRange <- seq((index-1)*200+10,index*200,by=10)
+  } else if (index == 1) {
+    run <- 1
+    LTBITxCRange <- seq(0,200,by=10)
+  }
+  #LTBITx and ActiveTx
+  for (LTBITxC in LTBITxCRange) {
+    for (activeTxC in activeTxCRange) {
+      for (intervention in curInterventions) {
+        intConfig <- interventionConfig(intervention)
+        costs     <- intConfig$costs
+        params    <- intConfig$params
[…]

### 2013-07-31 in_progress/models/costBenefitAnalysis/helpers.R
modified helpers I guess

@@ -39,41 +39,7 @@ activeTBUSBdL0L      <- rep(activeTBUSBdL0Ls,totT)
 activeTBUSBdF0Ls     <- "USB Active TB due to Novel Infection"
 activeTBUSBdF0L      <- rep(activeTBUSBdF0Ls,totT)
 
-generateSourcedIncidence <- function(dataSet) {
-  with(as.list(parms), {
-    IdF0  <- 1e6 * vF  * dataSet$F0
-    IdF1  <- 1e6 * vF  * dataSet$F1
-    IdL0  <- 1e6 * vL0 * dataSet$L0
-    IdL1  <- 1e6 * vL1 * dataSet$L1
-	  return(data.frame(IdF0,IdF1,IdL0,IdL1))
-  })
-}
-
-baseSourcedInc <- generateSourcedIncidence(baseData)
-IdL1c <- baseSourcedInc$IdL1
-IdF1c <- IdL1c + baseSourcedInc$IdF1
-IdL0c <- IdF1c + baseSourcedInc$IdL0
-IdF0c <- IdL0c + baseSourcedInc$IdF0
-baseCumulativeSourcedInc <- data.frame(year=years,IdL1c,IdF1c,IdL0c,IdF0c)
-incPlotSourced <- ggplot(baseCumulativeSourcedInc, aes(x=year)) + 
-           labs(x="Years", y="Incidence", fill="Incidence Source") + 
-           plotTitle("Sourced US TB Incidence","") +
-           geom_ribbon(aes(ymin=0,    ymax=IdL1c,fill=chronicLatentFBL))  + 
-           geom_ribbon(aes(ymin=IdL1c,ymax=IdF1c,fill=acuteLatentFBL))    + 
-           geom_ribbon(aes(ymin=IdF1c,ymax=IdL0c,fill=chronicLatentUSBL)) + 
-           geom_ribbon(aes(ymin=IdL0c,ymax=IdF0c,fill=acuteLatentUSBL))   + 
-           theme_gray(base_size=25) + 
-           theme(legend.position=c(0.6,0.8), axis.title=element_text(size=30), 
-           axis.text=element_text(size=17), plot.title=element_text(size=30),
-           legend.key.height=unit(1.8,'line')) + 
-           coord_fixed(ratio=1/200) + 
-           scale_fill_manual(breaks=c(acuteLatentUSBLs, 
-                                       chronicLatentUSBLs,
-                                       acuteLatentFBLs,
[…]

### 2013-08-09 in_progress/presentations/paper/draft.tex
added paper outline

\documentclass{amsart}

\title{INSERT TITLE HERE}
\begin{document}
\maketitle

\section{Introduction}
Epidemiological models allow public health professionals to predict and analyze
disease dynamics and intervention effectiveness. The most common examples of
such models are compartmental differential equation models, in which the
population is split between several possible health states, with flow between
each state given according to deterministic differential equations. In ++++++
(year of hill model), Hill, Becerra, and Castro implemented a compartmental
differential equaiton model of tuberculosis (TB) in the United States (US).
Their model utilized five health states and two subpopulations, US born (USB)
and foreign born (FB) for a total of 10 compartments. They used this model to
evaluate several possible intervention strategies, and ultimately conclude that
though increasing LTBI treatment was a good intervention strategy, the US was
unlikely to meet their stated goal of elimination of TB in the US by 2100. In
this work, the Hill model was extended in several key ways. First, additional
tracking capabilities were added to the Hill model, such that it can now report
further granularity in the disease dynamics. Further, economic components were
added to the model in order to project the US health care system (HCS) costs due
to TB given our current policy as well as for various interventions. Finally, a
population level, agent based implementation of the Hill Model was created, in
order to validate the Hill Model against the natural stochasticity present in
real world disease spread. 
\section{Methods}
\subsection{Basic Implementation}
Both the basic Hill Model and this extended Hill Model were implemented in
\texttt{R} as a system of differential equations, which were solved via the
$\texttt{lsoda}$ routine. The system of differential equations used in the Basic
Hill model are shown in figure INSERT FIGURE HERE, whereas the revised system of
differential equations used in the extended Hill Model are given in figure
INSERT FIGURE HERE. 
\subsection{Additional Tracking Capabilities}
In order to refine the tracking capabilities of the
Hill Model, the original differential equations used to describe TB spread were
separated into their component parts and each section was tracked separately.
These components were made into compartments, tracked by differential equations
EQUATION NUMBER SOMETHING TO SOMETHING, SORTED BY COMPARTMENT. In addition,
estimations of the basic reproductive number of FB or USB active, infectious TB
cases were made from a theoretical and an experimental perspective. Experimental
data were calculated by reducing the initial population of FB or USB active,
infectious TB cases by 1 and predicting the final number of cases seen in each
case, in $\texttt{R}$. 
\subsection{Economic Modeling}
Further, estimates for the cost of active TB treatment and for the cost of
latent TB infection (LTBI) treatment were obtained from Dylan et. al. and So and
So adherence effectivenss. CITE ME!
Both these costs and any health state outcomes were discounted at a rate of 3\%
per year. From these estimated cost per treatment, total costs were obtained in
the following way. It was assumed that every patient in the US with active TB is
treated, not necessarily successfully, but further that every treatment costs
exactly the average cost per treatment. Thus, active TB costs could be tracked
simply by tracking the number of new active TB cases, and scaling by a
discounted cost per treatment rate. Given the structure of the model, further
granularity was obtained from the cost data by tracking separately the cost due
to new cases that stemmed from activation of a chronic LTBI case, or activation
of an acute LTBI case. These values give estimates for the US HCS TB cost due to
exogenous infection of TB vs the US HCS TB cost due to activation of LTBI. Each
of these components of the cost was a new differential equation tracked by the
model, also solved by $\texttt{lsoda}$. For LTBI treatment cost, treatment was
charged upon leaving the LTBI compartment due to the cumulative self-cure and
treatment rate given in the Hill Model. The fraction of these indviduals who
leave this compartment due to self cure was assumed to be zero. Given the
uncertainty in measurments of LTBI treatment cost, extensive sensitivity
analysis was performed on this parameter relative to final cost outcomes, which
showed that it had an XXXXXXXXX effect. In addition to US HCS cost, the system
was implemented so as to also track projected intervention implementation cost,
given user-inputted parameters relating to various possible intervention cost
strategies. The extended Hill Model was used to track the effect of many
interventions tested by the Hill Model as well as an additional intervention
strategy of curing cases of immigrating LTBI prior to entry. This intervention
strategy proved very promising and elimination year, final cost, and cost per
case averted were tracked for various levels of entering LTBI cure rate. The
interventions were implemented so as to take effect during the year 2013 and run
to 2100. The numerical DE solver $\texttt{lsoda}$ used was run with a time step
of $0.8$. Sensitivity analysis was performed on this parameter and reducing the
time step was shown to have minimal effect on final size or cost values. 
\subsection{Agent Based}
The population level agent based model was implemented in several ways. Early
implementations were built in \texttt{Netlogo} and \texttt{Java}, but final
implementations were constructed in $\texttt{C++}$. An implementation was made
that tracked the hill model exactly, up to still including the Acute Latent
compartment in the model. Probabilites of agent progression between various
health states were computed given rates in the hill model and a variety of
approximations. The final size standard deviation and distribution data was
collected via 2160 (MINUS SOME) runs with each agent in the model truly
representing one individual and a time step of $0.01$. These data were analyzed
in $R$. 
\section{Results}
\subsection{Basic Population Breakdown}
The additional tracking capabilities offered several key insights into US TB
dynamics. Figure INSERT FIGURE HERE shows the yearly incidence of US TB, broken
down into infeciton source. It can be seen that the majority of the US TB load
is driven by activations of FB LTBI, followed by USB LTBI activations. This data
further agrees with the conclusions drawn by Hill, Becerra, and Castro about the
necessity of LTBI treatment in any valuable intervention strategy. Further,
figure INSERT FIGURE HERE shows a similarly sourced plot, but analyzing the
final US HCS costs due to TB. One can see that in this plot, roughly half of the
US TB HCS costs are due to activations of LTBI. Note that both of these plots
underestimate the impact LTBI activations play in the spread of TB, as every
LTBI activation to infectious TB contributes not only to incidence and costs
directly, but also indirectly by causing additional future cases, which is not
captured in these graphs. 
\subsubsection{Basic Reproduction Number}
The basic reproduction number of FB or USB cases of infectious TB was also
estimated by this system. From a theoretical perspective, we can think of the
total number of secondary infections over 100 years due to a FB or USB
infectious TB case as describing a geometric series in a large population.
Presuming there are no overlaps in infectious contacts, if a single case of
infectious TB in either population infects $p_f, p_u$ new cases in one year,
respectively, then we can say that over the course of 100 years, the total
number of cases infected will follow a geometric series. This analysis predicts
that over 100 years, one USB individual will infect $1.03$ other individuals,
whereas one FB individual will infect $.64$ other individuals. Experimentally,
these data were also analyzed, with results of $1.04$ and $.8$, respectively. 
\subsection{Intervention Analysis}
The primary interventions analyzed by the extended Hill were those that analyzed
curing various percentages of entering LTBI cases. Four indicative percentages
chosen were $20\%$, $35\%$, $50\%$, and $65\%$. Note that the hill model does
not distinguish documented immigration from undocumented immigration, and as
such estimates of entering LTBI cure rates higher than $65\%$ become much more
difficult to acheive. 
\subsection{Agent Based Evaluation}
\subsection{Sensitivity Analysis}
\end{document}

### 2013-08-09 in_progress/presentations/paper/interventions/interventions.tex

\documentclass{article}[11pt]
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\graphicspath{{../figures/}}
\begin{document}
\title{Interventions and Analysis}
\author{Ryo Kimura}
\date{}
\maketitle

\section{Interventions}
\subsection{Context}
%In our model, we considered the following interventions
%\begin{enumerate}
    %\item reduce entering LTBI by 100/75/50\%
    %\item reduce transmission by 100\%
    %\item reduce immigration by 75/50\%
    %\item increase (overall) LTBI treatment by 100/300\%
    %\item combinations of 3 and 4
    %\item combinations of 1 and 4
%\end{enumerate}
According to the article by Hill, Becerra, and Castro, foreign-born LTBI (latent tuberculosis infection) contributes significantly to TB (tuberculosis) incidence rates in the United States. Thus, we focus our attention on the cost effectiveness of reducing the number of foreign-born incoming LTBI cases.

The United States already screens for LTBI for immigrants, but does not require treatment. Thus, one way to reduce incoming LTBI cases is to offer treatment to such immigrants. However, this misses illegal immigrants, who may not enter the U.S. through traditional channels.

An alternative method is to invest in LTBI treatment programs abroad. This reduces the number of LTBI cases at the source, and (in theory) would also catch illegal immigrants.

\subsection{Methods}
In our model, we create separate compartments for foreign-borns and set different (but similar) transition rates between those compartments. An intervention is then represented by changing the parameters of the model. For example, the intervention in which we reduce the number of incoming LTBI cases can be modeled by reducing the rate at which FB LTBI cases enter the respective compartments..

\subsection{Results}
The results of this intervention are shown in figure \ref{fig:redEnLTBIIncGrouped}. There are several things to notice in these graphs. First, at high (but unrealistic) levels of intervention, the incidence rates drop dramatically, with 100\% reduction resulting in TB elimination from the foreign-born population. %Furthermore, even at low levels of interventions the reduction in cases is quite signifcant.

\begin{figure}
    \centering
    \includegraphics[width=3in]{redEnLTBIIncGrouped}
    \caption{Incidence/million With Reduced Incoming LTBI}
    \label{fig:redEnLTBIIncGrouped}
\end{figure}

The cost of these interventions is shown in figure \ref{fig:redEnLTBICostGrouped}. Here, the savings incurred from reducing incoming LTBI appears to grow linearly with respect to the size of the intervention. That is, if we cut the rate in half, then our cost (relative to the case in which we reduce the rate to zero) is also cut in half.

\begin{figure}
    \centering
    \includegraphics[width=3in]{redEnLTBICostGrouped}
    \caption{Total Cost of Reducing Incoming LTBI (over time)}
    \label{fig:redEnLTBICostGrouped}
\end{figure}

Table ?? summarizes the relative benefit of the cost when we reduce the number of incoming LTBI cases by 10\% (values for other interventions are listed in the supplement).

\subsection{Discussion}
As expected from the results of Hill et.al, reducing incoming LTBI has a significant impact on the TB incidence rate in the United States.
\end{document}

### 2013-08-12 in_progress/presentations/paper/sensitivity_analysis/sensitivityAnalysis.tex
added new folder sensitivity_analysis to paper

\documentclass{article}[11pt]
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\graphicspath{{../figures/}}
\begin{document}
\title{Sensitivity Analysis}
\author{Colin Pawlowski}
\date{}
\maketitle

%This document would most likely end up in the Supplementary Material for the paper

\section{Overview}
We divide our sensitivity analysis into two sections, to analyze the robustness of the deterministic and stochastic models separately.  For the deterministic model, we used Latin Hypercube Sampling to test the sensitivity of our model to input parameters from the Hill model and estimates for treatment costs.  We also
performed extensive multivariate analysis on the economic components of our deterministic model which go beyond the original Hill model, including treatment costs and intervention costs to reduce incoming LTBI.  
For the stochastic model, we fixed all input parameters and estimates for treatment costs to default values, and ran the model for 2,000 trials.

\section{Deterministic Model}
\subsection{Latin Hypercube Sampling}
We computed partial rank correlation coefficients for each of the initial parameters and treatment costs, and validated the results against the Sensitivity Analysis in the Hill model.  \\

%Add table of distributions for initial parameters and treatment costs
%Add table of Partial Rank Correlation Coefficients

\subsection{Variability due to Uncertainty of Treatment Costs}
Next, we performed more extensive multivariate analysis on the economic part of the deterministic model.  Keeping all of the input parameters from the Hill model at their default values, we ran the model approximately two million times, varying the cost of treatment for LTBI and Active TB and the treatment rate for incoming LTBI.  \\

%Add 3-D contour plot
%Add explanation of the effects of treatment costs, incoming LTBI treatment rate on total HCS cost

\subsection{Variability of Intervention Cost for Treating Cases of Incoming LTBI}
Similarly, we performed extensive multivariate analysis on the intervention cost for reducing incoming LTBI.  With all input parameters from the Hill model at their default values, we ran the model approximately two million times, varying the treatment rate, incidence, and cost to cure for incoming LTBI.  \\

%Add 3-D contour plot
%Add explanation of the effects of intervention costs, incoming LTBI treatment rate on total HCS cost

\section{Stochastic Model}
\subsection{Variability due to Probabilistic Nature of Disease Spread}

\section{Summary}
\end{document}

### 2013-08-12 in_progress/models/costBenefitAnalysis/interventionGroupsPresenter.R

@@ -107,38 +107,65 @@ TBdeathsAvertedC <- '#24913C'
 
 yrange <- round(seq(min(-1*saveOfInter[[1]])-0.5,max(costOfInter[[1]])+0.5,by=0.5),1)
 
+# redEnLTBI <- data.frame(year = years, 
+                        # redEnLTBI100_costs   = costOfInter[[1]], 
+                        # redEnLTBI75_costs    = costOfInter[[2]], 
+                        # redEnLTBI50_costs    = costOfInter[[3]],
+                        # redEnLTBI100_savings = -1*saveOfInter[[1]], 
+                        # redEnLTBI75_savings  = -1*saveOfInter[[2]], 
+                        # redEnLTBI50_savings  = -1*saveOfInter[[3]],
+                        # redEnLTBI100_totCost = totSpent[[1]], 
+                        # redEnLTBI75_totCost  = totSpent[[2]], 
+                        # redEnLTBI50_totCost  = totSpent[[3]])
+
+# x <- ggplot(redEnLTBI,aes(x=year)) + 
+       # labs(x="Years", y="Billions of USD", color="Economic Distinction", 
+            # linetype="% Reduction") +
+       # scale_y_continuous(breaks=yrange) + 
+       # plotTitle("Implementation Costs, Savings, and 
+# US Health Care System (US HCS) 
+# Costs for 100%, 75%, and 50% LTBI reduction","") + 
+       # geom_hline(aes(y=0),size=2) +
+       # geom_line(aes(y=redEnLTBI100_costs,   color=costs,      linetype=redEnLTBI100L), size=2) +
+       # geom_line(aes(y=redEnLTBI75_costs,    color=costs,      linetype=redEnLTBI75L), size=2) +
+       # geom_line(aes(y=redEnLTBI50_costs,    color=costs,      linetype=redEnLTBI50L), size=2) +
+       # geom_line(aes(y=redEnLTBI100_savings, color=savings,    linetype=redEnLTBI100L), size=2) +
+       # geom_line(aes(y=redEnLTBI75_savings,  color=savings,    linetype=redEnLTBI75L), size=2) +
+       # geom_line(aes(y=redEnLTBI50_savings,  color=savings,    linetype=redEnLTBI50L), size=2) +
+       # geom_line(aes(y=redEnLTBI100_totCost, color=totalCosts, linetype=redEnLTBI100L), size=2) +
[…]

### 2013-08-20 in_progress/models/costBenefitAnalysis/interventionAnalyzer.R
updated sensitivity analysis readme

@@ -66,28 +66,28 @@ baseInc <- generateIncidence(P)
       # }
     # }
   # }
-} else if (analysisType==2) {
-  fRange <- seq(0,50,by=0.5)
-  if (index > 1) {
-    run <- 101*21*41 + (index-2)*101*21*40 + 1
-    LTBIEnCostsRange <- seq(400*(index-1)+10,400*index,by=10)
-  } else if (index == 1) {
-    run <- 1
-    LTBIEnCostsRange <- seq(0,400,by=10)
-  }
-  for (LTBIEnCosts in LTBIEnCostsRange) {
-    for (f in fRange) {
-      for (intervention in curInterventions) {
-        intConfig <- interventionConfig(intervention)
-        costs     <- intConfig$costs
-        costs[['LTBIEn']] <- LTBIEnCosts
-        params    <- intConfig$params
-        interData <- hill(costs,params[["sigmaL"]],f,params[["trans"]],
-                          params[["incLTBI"]],activeTxC,LTBITxC)
-        write.csv(interData, paste(c(intFilePrefix,intervention,'Anl',analysisType,'Run',run,intFileSuffix),
-                                   collapse=""))
-        run <- run + 1
-      }
-    }
-  }
-}
+# } else if (analysisType==2) {
+  # fRange <- seq(0,50,by=0.5)
+  # if (index > 1) {
+    # run <- 101*21*41 + (index-2)*101*21*40 + 1
+    # LTBIEnCostsRange <- seq(400*(index-1)+10,400*index,by=10)
+  # } else if (index == 1) {
+    # run <- 1
+    # LTBIEnCostsRange <- seq(0,400,by=10)
+  # }
+  # for (LTBIEnCosts in LTBIEnCostsRange) {
+    # for (f in fRange) {
+      # for (intervention in curInterventions) {
+        # intConfig <- interventionConfig(intervention)
+        # costs     <- intConfig$costs
+        # costs[['LTBIEn']] <- LTBIEnCosts
+        # params    <- intConfig$params
+        # interData <- hill(costs,params[["sigmaL"]],f,params[["trans"]],
+                          # params[["incLTBI"]],activeTxC,LTBITxC)
+        # write.csv(interData, paste(c(intFilePrefix,intervention,'Anl',analysisType,'Run',run,intFileSuffix),
+                                   # collapse=""))
+        # run <- run + 1
+      # }
+    # }
+  # }
+# }

### 2013-08-20 in_progress/models/costBenefitAnalysis/interventionConfig.R

@@ -53,7 +53,7 @@ interventionConfig <- function(interventionStr, x=0) { #x is an integer refering
       #TODO: Make this a function depending on magnitude for greater flexibility
       # (minor)
       incLTBI <- incLTBI*(interventionMag/100)
-      LTBIEn  <- LTBIEn + 400 + 600*(interventionMag/100) + x*100
+      LTBIEn  <- 800 #LTBIEn + 400 + 600*(interventionMag/100) + x*100
     } else if (interventionType == "redImm") {
       #No Costs!
       if (interventionMag == 75) {

### 2013-08-20 in_progress/models/costBenefitAnalysis/interventionGroups.R

@@ -1,23 +1,23 @@
 source('interventionAnalyzer.R')
 #Group by type IMPORTANT: Reset all intervention costs to default values in interventionConfig.R before running
-# for(intervention in redEnLTBI_Interventions) {
-  # intConfig <- interventionConfig(intervention)
-  # costs     <- intConfig$costs
-  # params    <- intConfig$params
-  # interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
-                    # params[["incLTBI"]])
-  # write.csv(interData, paste(c(intFilePrefix,intervention,intFileSuffix),
-                             # collapse=""))
-# }
-# for(intervention in incLTBItrmt_Interventions) {
-  # intConfig <- interventionConfig(intervention)
-  # costs     <- intConfig$costs
-  # params    <- intConfig$params
-  # interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
-                    # params[["incLTBI"]])
-  # write.csv(interData, paste(c(intFilePrefix,intervention,intFileSuffix),
-                             # collapse=""))
-# }
+for(intervention in redEnLTBI_Interventions) {
+  intConfig <- interventionConfig(intervention)
+  costs     <- intConfig$costs
+  params    <- intConfig$params
+  interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
+                    params[["incLTBI"]])
+  write.csv(interData, paste(c(intFilePrefix,intervention,intFileSuffix),
+                             collapse=""))
+}
+for(intervention in incLTBItrmt_Interventions) {
+  intConfig <- interventionConfig(intervention)
+  costs     <- intConfig$costs
+  params    <- intConfig$params
+  interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
+                    params[["incLTBI"]])
+  write.csv(interData, paste(c(intFilePrefix,intervention,intFileSuffix),
+                             collapse=""))
+}
 
 
 #Cost Vary

### 2013-08-20 in_progress/models/costBenefitAnalysis/interventionGroupsPresenter.R

@@ -145,28 +145,30 @@ Costs for 100%, 75%, and 50% LTBI reduction","") +
 
 ggsave('costRedEnLTBI.pdf',x,width=15,height=12)
 
-#Plot of cost averted (savings)
-#Only includes costs for Active TB treatment
-#No treatment implementation costs accounted for
+# Plot of cost averted (savings)
+# Only includes costs for Active TB treatment
+# No treatment implementation costs accounted for
 
-# redEnLTBI <- data.frame(year = years, 
-                        # redEnLTBI10_savings = saveOfInter[[1]], 
-                        # redEnLTBI25_savings  = saveOfInter[[2]], 
-                        # redEnLTBI50_savings  = saveOfInter[[3]],
+redEnLTBI <- data.frame(year = years, 
+                        redEnLTBI10_savings = saveOfInter[[1]], 
+                        redEnLTBI25_savings  = saveOfInter[[2]], 
+                        redEnLTBI50_savings  = saveOfInter[[3]],
 
-# x <- ggplot(redEnLTBI,aes(x=year)) + 
-       # labs(x="Years", y="Billions of USD", color="Economic Distinction", 
-            # linetype="% Reduction") +
-       # scale_y_continuous(breaks=yrange) + 
-       # plotTitle("Averted TB Costs for the
-# US Health Care System (US HCS) given 10%, 25%, and 50% LTBI reduction","") + 
-       # geom_hline(aes(y=0),size=2) +
-       # geom_line(aes(y=redEnLTBI10_savings,  color=savings,    linetype=redEnLTBI10L), size=2) +
-       # geom_line(aes(y=redEnLTBI25_savings,  color=savings,    linetype=redEnLTBI25L), size=2) +
-       # geom_line(aes(y=redEnLTBI50_savings,  color=savings,    linetype=redEnLTBI50L), size=2) +
-       # guides(fill=F, alpha=F) + 
-       # theme_gray(base_size=25) +
-       # theme(legend.position=c(0.22,0.82), axis.title=element_text(size=40), 
-             # axis.text=element_text(size=27), plot.title=element_text(size=40))
+x <- ggplot(redEnLTBI,aes(x=year)) + 
+       labs(x="Years", y="Billions of USD", color="Economic Distinction", 
+            linetype="% Reduction") +
+       scale_y_continuous(breaks=yrange) + 
[…]

### 2013-08-20 in_progress/presentations/paper/draft.tex
started editing paper draft

@@
 population is split between several possible health states, with flow between
-each state given according to deterministic differential equations. In ++++++
-(year of hill model), Hill, Becerra, and Castro implemented a compartmental
+each state given according to deterministic differential equations. In 2012, 
+Hill, Becerra, and Castro implemented a compartmental
 differential equaiton model of tuberculosis (TB) in the United States (US).
@@
 real world disease spread.
+
 \section{Methods}
+
 \subsection{Basic Implementation}
@@
 \texttt{R} as a system of differential equations, which were solved via the
-$\texttt{lsoda}$ routine. The system of differential equations used in the Basic
-Hill model are shown in figure INSERT FIGURE HERE, whereas the revised system of
-differential equations used in the extended Hill Model are given in figure
-INSERT FIGURE HERE. 
+$\texttt{lsoda}$ routine. The systems of differential equations used in the Basic
+Hill Model and the extended Hill Model are shown below in Figure 1 and Figure 2
+respectively.
+
+INSERT FIGURES HERE
+
 \subsection{Additional Tracking Capabilities}
@@
 case, in $\texttt{R}$.
+
 \subsection{Economic Modeling}
@@
 time step was shown to have minimal effect on final size or cost values.
+
 \subsection{Agent Based}
@@
 in $R$.
+
 \section{Results}
+
 \subsection{Basic Population Breakdown}
@@
 these data were also analyzed, with results of $1.04$ and $.8$, respectively.
+
 \subsection{Intervention Analysis}
@@
 difficult to acheive.
+
 \subsection{Agent Based Evaluation}

### 2013-08-20 in_progress/presentations/paper/draft.tex
added background to paper

@@
 \documentclass{amsart}
+\usepackage[pdftex]{graphicx}
 
-\title{INSERT TITLE HERE}
+\title{Modeling Intervention Strategies for United States TB Control}
 \begin{document}
@@
 differential equaiton model of tuberculosis (TB) in the United States (US).
-Their model utilized five health states and two subpopulations, US born (USB)
-and foreign born (FB) for a total of 10 compartments. They used this model to
+Their model utilized five health states and two subpopulations, US-born (USB)
+and foreign-born (FB) for a total of 10 compartments. They used this model to
 evaluate several possible intervention strategies, and ultimately conclude that
@@
 
+\section{Background}
+
+\subsection{The Hill Model}
+A flowchart representation of the Hill Model is shown in Figure 1.  Each compartment
+represents a different possible health state with respect to TB for every 
+US-born or foreign-born individual, and arrows between different compartments
+represent possible transitions between states.  Individuals also leave the model 
+from all compartments due to natural death, which is left out of the figure for clarity.  \\
+
+\begin{figure}
+\includegraphics[scale=0.25]{figures/HillModelFlowChart.png}
+\end{figure}
+
+The majority of USB and FB individuals fall into the Susceptible (S) category, which includes everyone
+who is uninfected and has not been exposed to TB.  After exposure to an individual
+with TB, a person in the Susceptible compartment can develop Latent TB Infection (LTBI) and changes
+health states to either the Acute LTBI (F) or Chronic LTBI (L) compartment.  Latently
+infected individuals are not infectious, but have some risk of developing active TB infection
+over time.  However, the rates of disease progression are not equal, and individuals in the
+Acute LTBI compartment have a higher risk of developing active TB than those in
+the Chronic LTBI compartment.  Individuals in the Chronic LTBI compartment
+may also be exogenously re-infected and transition to the Acute LTBI compartment.  \\
+
+Latently infected individuals may progress to one of two active TB states: Infectious TB (I) or 
+Non-Infectious TB (J).  Individuals in both compartments have an increased risk of death from
+active TB infection, but only individuals in the Infectious TB compartment are contagious.  
+In addition, individuals in all of the infected compartments (F, L, I, J) may be treated or self-cure
+themselves of their respective TB health condition.  However, in the model, treatment or self-cure from TB
+does not grant immunity, and all healthy individuals are grouped in the Susceptible compartment
+and may be re-infected at a later time.  \\
+
 \section{Methods}
@@
 $\texttt{lsoda}$ routine. The systems of differential equations used in the Basic
-Hill Model and the extended Hill Model are shown below in Figure 1 and Figure 2
+Hill Model and the extended Hill Model are shown below in Figure 2 and Figure 3
 respectively.
 
-INSERT FIGURES HERE
+\begin{figure}
+\includegraphics[scale=0.75]{figures/BasicHillEquations.pdf}
+\end{figure}
+
+The vector variables $S_{0}, F_{0}, L_{0}, I_{0}, J_{0}$ contain the number of US-born individuals in the S, F, L, I, J compartments respectively, and $S_{1}, F_{1}, L_{1}, I_{1}, J_{1}$ contain foreign-born individuals.
+$N_{0}$ and $N_{1}$ are the total populations of US-born and foreign-born individuals.
+The constants $\rho$ and $\alpha$ are birth rates, while $\mu_{i}$, and $\mu_{d}$ are death rates.  
+A complete list and descriptions of all constants used in the model can be found in the appendix.
 

### 2013-08-20 in_progress/presentations/paper/draft.tex
made edits to paper draft

@@
 analysis was performed on this parameter relative to final cost outcomes, which
-showed that it had an XXXXXXXXX effect. In addition to US HCS cost, the system
+showed that it had an linear effect. In addition to US HCS cost, the system
 was implemented so as to also track projected intervention implementation cost,
@@
 dynamics. Figure INSERT FIGURE HERE shows the yearly incidence of US TB, broken
-down into infeciton source. It can be seen that the majority of the US TB load
+down into infection source. It can be seen that the majority of the US TB load
 is driven by activations of FB LTBI, followed by USB LTBI activations. This data
@@
 number of cases infected will follow a geometric series. This analysis predicts
-that over 100 years, one USB individual will infect $1.03$ other individuals,
-whereas one FB individual will infect $.64$ other individuals. Experimentally,
-these data were also analyzed, with results of $1.04$ and $.8$, respectively.
+that over 100 years, one USB infection will lead to $1.03$ subsequent infections,
+whereas one FB infection will lead to $.64$ subsequent infections. The full calculations
+are included in the appendix.  Experimentally, these data were also analyzed, 
+with results of $1.04$ and $.8$, respectively.
 

### 2013-08-21 in_progress/presentations/paper/draft.tex
continuing on paper

@@
 such estimates of entering LTBI cure rates higher than $65\%$ become much more
-difficult to acheive.
+difficult to acheive. It was seen that in this model as well as in the basic
+Hill, no analyzed intervention predicted elimination by 2100. In order to obtain
+elimiation by 2100, at least 95\% of entering LTBI cases had to be cured, which
+is practically impossible. However, it was seen that curing entering cases of
+LTBI resulted in a net US HCS cost per case averted of \$X at 2025, \$Y at 2050,
+and \$Z at 2100. Further, it was also found that the relationship between total
+incidence at 2100 and percentage of incoming LTBI cases cured was linear, and
+from this estimates were made of the yearly average US HCS savings garnered by
+curing one case of entering LTBI over the time scale 2000 to 2025, 2000 to 2050,
+and 2000 to 2100. This value peaked at \$X at 2100. This illustrates that it
+would be cost saving to cure cases of LTBI at the cost of X 2000 dollars over
+the time period 2000-2100. These intervention strategies also resulted in A, B,
+and C fewer cases of TB seen in the US, and D, E, and F fewer TB
+deaths, respectively.
 
 \subsection{Agent Based Evaluation}
+The Agent Based Model allowed the statistical properties of the system to be
+analyzed and verified. In particular, they illustrated that the deterministic
+Hill model provides a robust and consistent statistical measure of TB epidemic
+behavior in the US conditions. We found that the distribution of incidence and
+final population sizes were normal, with mean accurate to the deterministic
+model and standard deviations given in table X, in the appendix.
+
 \subsection{Sensitivity Analysis}
+\section{Discussion}
+These results confirm the hypothesis that curing incoming LTBI rates is a
+necessary step towards elimination and indicate that it is a cost effective
+option. 
 \end{document}

### 2013-08-21 in_progress/models/costBenefitAnalysis/interventionGroupsPresenter.R
fixed plotting error

@@ -152,7 +152,7 @@ ggsave('costRedEnLTBI.pdf',x,width=15,height=12)
 redEnLTBI <- data.frame(year = years, 
                         redEnLTBI10_savings = saveOfInter[[1]], 
                         redEnLTBI25_savings  = saveOfInter[[2]], 
-                        redEnLTBI50_savings  = saveOfInter[[3]],
+                        redEnLTBI50_savings  = saveOfInter[[3]])
 
 x <- ggplot(redEnLTBI,aes(x=year)) + 
        labs(x="Years", y="Billions of USD", color="Economic Distinction", 

### 2013-08-22 in_progress/models/costBenefitAnalysis/hillFunctions.R
reworked R code to be more utility like, as intended initially. Now is more function like and versatile. Also will not work to re-generate sensitivity analysis. Working on that soon. Also removed unnecessary incLTBI parameter, in favor of collapsing to f. Also added copied sensitivityAnalyzer file

@@ -91,7 +91,7 @@ Ddt <- function(t,v,parms) {
     c00          <- 1 - c01                                          #proportion of contacts made with USB individuals (USB)
     c10          <- (1-e1)*((1-e0)*N0)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with USB individuals (FB)
     c11          <- 1 - c10                                          #proportion of contacts made with FB individuals  (FB)
-    dLTBIEn      <- f*alpha*(N0+N1)                                  #FB arrivals with LTBI entering
+    dLTBIEn      <- alpha*(N0+N1)                                    #FB arrivals with LTBI entering
     dnatdeath0   <- mu0 * N0                                         #Natural deaths (USB)
     dnatdeath1   <- mu1 * N1                                         #Natural deaths (FB)
     dtbdeath0    <- mud * (I0 + J0)                                  #TB deaths (USB)
@@ -110,7 +110,7 @@ Ddt <- function(t,v,parms) {
     lambda1      <- transmission*(beta*(c10*(I0/N0) + c11*(I1/N1)))  #Forces of Infection (FB)
     dexogenous0	 <- x*p*lambda0*L0                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (USB)
     dexogenous1  <- x*p*lambda1*L1                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (FB)
-    dInterventionCost <- discV * (iCnewCases*1e6*(dprogTotal0+dprogTotal1) + iCtotPop*1e6*(N0+N1) + iCLTBIEn*1e6*dLTBIEn*(1-incLTBI))
+    dInterventionCost <- discV * (iCnewCases*1e6*(dprogTotal0+dprogTotal1) + iCtotPop*1e6*(N0+N1) + iCLTBIEn*1e6*dLTBIEn*(1-f))
     
     #Difference Equations (USB)
[…]

### 2013-08-22 in_progress/models/costBenefitAnalysis/interventionAnalyzer.R

@@ -1,30 +1,16 @@
 #Option Processing
 args <- commandArgs(trailingOnly = T)
 if (length(args) > 0) {
-  #TODO: Remove later
-  #generateNewData <- F#as.logical(args[1])
-  analysisType    <- as.numeric(args[1])
-  index           <- as.numeric(args[2])
-  #LTBIEnCosts     <- as.numeric(args[2])
-  #activeTxC       <- as.numeric(args[3])
-  #LTBITxC         <- as.numeric(args[4])
-  #perIncLTBI      <- as.numeric(args[5])
+  generateNewData <- as.logical(args[1])
 } else {
   generateNewData <- F
-  index <- 1
-  analysisType <- 1
 }
-generateNewData <- F
 
 #Which interventions to run:
 source('interventionConfig.R')
 
 #Hill Model:
 source('hillFunctions.R')
-
-LTBIEnCosts     <- 0
-activeTxC       <- parms[['CtBase']]
-LTBITxC         <- parms[['ClBase']]
 
 #Base Data: 
 C <- c(newCases=0,totPop=0,LTBIEn=0) 
@@ -39,55 +25,12 @@ if (generateNewData) {
 }
 baseInc <- generateIncidence(P)
 
-#TODO: Give this kind of power to the base user!
 #Intervention Analyzing:
-
-# if (analysisType == 1) {
-  # activeTxCRange <- seq(0,40000,by=200)
-  # if (index > 1) {
-    # run <- 201*21*21 + (index-2)*201*21*20 + 1
-    # LTBITxCRange <- seq((index-1)*200+10,index*200,by=10)
-  # } else if (index == 1) {
-    # run <- 1
-    # LTBITxCRange <- seq(0,200,by=10)
-  # }
-  # #LTBITx and ActiveTx
-  # for (LTBITxC in LTBITxCRange) {
-    # for (activeTxC in activeTxCRange) {
-      # for (intervention in curInterventions) {
-        # intConfig <- interventionConfig(intervention)
-        # costs     <- intConfig$costs
-        # params    <- intConfig$params
-        # interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
-                          # params[["incLTBI"]],activeTxC,LTBITxC)
-        # write.csv(interData, paste(c(intFilePrefix,intervention,'Anl',analysisType,'Run',run,intFileSuffix),
-                                   # collapse=""))
-        # run <- run + 1
-      # }
-    # }
-  # }
-# } else if (analysisType==2) {
[…]

### 2013-08-22 in_progress/models/costBenefitAnalysis/interventionConfig.R

@@ -21,76 +21,56 @@ allInterventions <- c("redEnLTBI100","redEnLTBI75","redEnLTBI50","redTrans100",
                       "incLTBItrmt100&redEnLTBI100","incLTBItrmt100&redEnLTBI75",
                       "incLTBItrmt100&redEnLTBI50","incLTBItrmt300&redEnLTBI100",
                       "incLTBItrmt300&redEnLTBI75","incLTBItrmt300&redEnLTBI50")
-                      
 
 redImm_Interventions <- allInterventions[5:6]
 incLTBItrmt_Interventions <- allInterventions[7:8]
-split20RedEnLTBIInter <- c('redEnLTBI0','redEnLTBI5','redEnLTBI10',
-                           'redEnLTBI15','redEnLTBI20','redEnLTBI25',
-                           'redEnLTBI30','redEnLTBI35','redEnLTBI40',
-                           'redEnLTBI45','redEnLTBI50','redEnLTBI55',
-                           'redEnLTBI60','redEnLTBI65','redEnLTBI70',
-                           'redEnLTBI75','redEnLTBI80','redEnLTBI85',
-                           'redEnLTBI90','redEnLTBI95','redEnLTBI100')
-redEnLTBI_Interventions <- c(allInterventions[3],allInterventions[6],allInterventions[11])                  
-curInterventions <- split20RedEnLTBIInter#allInterventions
-incLTBICost <- 0
+redEnLTBI_Interventions <- allInterventions[1:3]
+
+curInterventions <- redEnLTBI_Interventions
+
+printError <- function(intervention,error) {
+  print("I didn't recognize that intervention strategy. I'm sorry.")
+  print("Here's the intervention you gave me: ")
+  print(intervention)
+  print("And here's the error")
+  print(error)
+}
+
+redEnLTBICFun   <- function(mag,baseCost){return(baseCost+600*(mag/100))}
+incLTBItrmtCFun <- function(mag,baseCost){return(baseCost+0.025)}
+redTransCFun    <- function(mag,baseCost){return(baseCost+1000*(mag/100))}
+interventionProps <- list(
+  redEnLTBI   =list(prop='f',      cost=list(c('LTBIEn',   redEnLTBICFun))),
+  redImm      =list(prop='f',      cost=list()),
+  incLTBItrmt =list(prop='sigmaL', cost=list(c('totPop',   incLTBItrmtCFun))),
+  redTrans    =list(prop='trans',  cost=list(c('newCases', redTransCFun))))
 
[…]

### 2013-08-22 in_progress/models/costBenefitAnalysis/sensitivityAnalyzer.R

@@ -1,0 +1,93 @@
+#Option Processing
+args <- commandArgs(trailingOnly = T)
+if (length(args) > 0) {
+  #TODO: Remove later
+  #generateNewData <- F#as.logical(args[1])
+  analysisType    <- as.numeric(args[1])
+  index           <- as.numeric(args[2])
+  #LTBIEnCosts     <- as.numeric(args[2])
+  #activeTxC       <- as.numeric(args[3])
+  #LTBITxC         <- as.numeric(args[4])
+  #perIncLTBI      <- as.numeric(args[5])
+} else {
+  generateNewData <- F
+  index <- 1
+  analysisType <- 1
+}
+generateNewData <- F
+
+#Which interventions to run:
+source('interventionConfig.R')
+
+#Hill Model:
+source('hillFunctions.R')
+
+LTBIEnCosts     <- 0
+activeTxC       <- parms[['CtBase']]
+LTBITxC         <- parms[['ClBase']]
+
+#Base Data: 
+C <- c(newCases=0,totPop=0,LTBIEn=0) 
+if (!generateNewData) {
+  P               <- read.csv(baseFile)
+  generateNewData <- (length(P$X) != length(years))
+  P$X             <- NULL
+} 
+if (generateNewData) {
+  P <- hill(C,sigmaLBase,fBase,transBase,incLTBIBase,1,totT)
+  write.csv(P,baseFile)
+}
+baseInc <- generateIncidence(P)
+
+#TODO: Give this kind of power to the base user!
+#Intervention Analyzing:
+
+# if (analysisType == 1) {
+  # activeTxCRange <- seq(0,40000,by=200)
+  # if (index > 1) {
+    # run <- 201*21*21 + (index-2)*201*21*20 + 1
+    # LTBITxCRange <- seq((index-1)*200+10,index*200,by=10)
+  # } else if (index == 1) {
+    # run <- 1
+    # LTBITxCRange <- seq(0,200,by=10)
+  # }
+  # #LTBITx and ActiveTx
+  # for (LTBITxC in LTBITxCRange) {
+    # for (activeTxC in activeTxCRange) {
+      # for (intervention in curInterventions) {
+        # intConfig <- interventionConfig(intervention)
+        # costs     <- intConfig$costs
+        # params    <- intConfig$params
+        # interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
+                          # params[["incLTBI"]],activeTxC,LTBITxC)
[…]

### 2013-08-23 in_progress/models/costBenefitAnalysis/hillFunctions.R
continue working

@@ -87,29 +87,29 @@ Ddt <- function(t,v,parms) {
     discV   <- 1/(1.03^t)  #amount costs, health states discount constant
 
     #parameter values initialized for each time step
-    c01          <- (1-e0)*((1-e1)*N1)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with FB individuals  (USB)
-    c00          <- 1 - c01                                          #proportion of contacts made with USB individuals (USB)
-    c10          <- (1-e1)*((1-e0)*N0)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with USB individuals (FB)
-    c11          <- 1 - c10                                          #proportion of contacts made with FB individuals  (FB)
-    dLTBIEn      <- alpha*(N0+N1)                                    #FB arrivals with LTBI entering
-    dnatdeath0   <- mu0 * N0                                         #Natural deaths (USB)
-    dnatdeath1   <- mu1 * N1                                         #Natural deaths (FB)
-    dtbdeath0    <- mud * (I0 + J0)                                  #TB deaths (USB)
-    dtbdeath1    <- mud * (I1 + J1)                                  #TB deaths (FB)
-    dtbdeathD0   <- discV * dtbdeath0                                #TB deaths with discounting (USB)
-    dtbdeathD1   <- discV * dtbdeath1                                #TB deaths with discounting (FB)
-    dprogAcute0  <- vF*F0                                            #Acute LTBI progressions to Active TB disease (USB)
-    dprogAcute1  <- vF*F1                                            #Acute LTBI progressions to Active TB disease (FB)
-    dprogChron0  <- vL0*L0                                           #Chronic LTBI progressions to Active TB disease (USB)
-    dprogChron1  <- vL1*L1                                           #Chronic LTBI progressions to Active TB disease (FB)
-    dprogTotal0  <- dprogAcute0 + dprogChron0                        #Progression to Active TB (USB)
-    dprogTotal1  <- dprogAcute1 + dprogChron1                        #Progression to Active TB (FB)
-    dprogTotalD0 <- discV * dprogTotal0                              #Progression to Active TB with discounting (USB)
[…]

### 2013-08-23 in_progress/models/costBenefitAnalysis/interventionAnalyzer.R

@@ -20,17 +20,14 @@ if (!generateNewData) {
   P$X             <- NULL
 } 
 if (generateNewData) {
-  P <- hill(C,sigmaLBase,fBase,transBase,incLTBIBase,1,totT)
+  P <- hill(C,1,totT)
   write.csv(P,baseFile)
 }
 baseInc <- generateIncidence(P)
 
 #Intervention Analyzing:
 for (intervention in curInterventions) {
-  intConfig <- interventionConfig(intervention)
-  costs     <- intConfig$costs
-  params    <- intConfig$params
-  interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]])
+  interData <- hill(interventionConfig(intervention))
   write.csv(interData, paste(c(intFilePrefix,intervention,intFileSuffix),
                              collapse=""))
 }

### 2013-08-23 in_progress/models/costBenefitAnalysis/interventionConfig.R

@@ -15,18 +15,16 @@ intFileSuffix <- '.csv'
 # redImm25&incLTBItrmt100   --> reduce immigration by 25% and increase LTBI 
 #                               treatment by 100%
 allInterventions <- c("redEnLTBI100","redEnLTBI75","redEnLTBI50","redTrans100",
-                      "redImm75","redImm50","incLTBItrmt100","incLTBItrmt300",
-                      "redImm75&incLTBItrmt100","redImm50&incLTBItrmt100",
-                      "redImm75&incLTBItrmt100","redImm50&incLTBItrmt300",
+                      "incLTBItrmt100","incLTBItrmt300",
                       "incLTBItrmt100&redEnLTBI100","incLTBItrmt100&redEnLTBI75",
                       "incLTBItrmt100&redEnLTBI50","incLTBItrmt300&redEnLTBI100",
                       "incLTBItrmt300&redEnLTBI75","incLTBItrmt300&redEnLTBI50")
 
-redImm_Interventions <- allInterventions[5:6]
-incLTBItrmt_Interventions <- allInterventions[7:8]
-redEnLTBI_Interventions <- allInterventions[1:3]
+incLTBItrmtInterventions <- allInterventions[5:6]
+redTransInterventions    <- allInterventions[4]
+redEnLTBIInterventions   <- allInterventions[1:3]
 
-curInterventions <- redEnLTBI_Interventions
+curInterventions <- redEnLTBIInterventions
 
 printError <- function(intervention,error) {
   print("I didn't recognize that intervention strategy. I'm sorry.")
@@ -40,14 +38,13 @@ redEnLTBICFun   <- function(mag,baseCost){return(baseCost+600*(mag/100))}
 incLTBItrmtCFun <- function(mag,baseCost){return(baseCost+0.025)}
 redTransCFun    <- function(mag,baseCost){return(baseCost+1000*(mag/100))}
 interventionProps <- list(
-  redEnLTBI   =list(prop='f',      cost=list(c('LTBIEn',   redEnLTBICFun))),
-  redImm      =list(prop='f',      cost=list()),
-  incLTBItrmt =list(prop='sigmaL', cost=list(c('totPop',   incLTBItrmtCFun))),
-  redTrans    =list(prop='trans',  cost=list(c('newCases', redTransCFun))))
[…]

### 2013-08-23 in_progress/models/costBenefitAnalysis/interventionGroupsPresenter.R
working on plotitng code

@@ -109,41 +109,41 @@ TBdeathsAvertedC <- '#24913C'
 
 yrange <- round(seq(min(-1*saveOfInter[[1]])-0.5,max(costOfInter[[1]])+0.5,by=0.5),1)
 
-redEnLTBI <- data.frame(year = years, 
-                        redEnLTBI100_costs   = costOfInter[[1]], 
-                        redEnLTBI75_costs    = costOfInter[[2]], 
-                        redEnLTBI50_costs    = costOfInter[[3]],
-                        redEnLTBI100_savings = -1*saveOfInter[[1]], 
-                        redEnLTBI75_savings  = -1*saveOfInter[[2]], 
-                        redEnLTBI50_savings  = -1*saveOfInter[[3]],
-                        redEnLTBI100_totCost = totSpent[[1]], 
-                        redEnLTBI75_totCost  = totSpent[[2]], 
-                        redEnLTBI50_totCost  = totSpent[[3]])
-
-x <- ggplot(redEnLTBI,aes(x=year)) + 
-       labs(x="Years", y="Billions of USD", color="Economic Distinction", 
-            linetype="% Reduction") +
-       scale_y_continuous(breaks=yrange) + 
-       plotTitle("Implementation Costs, Savings, and 
-US Health Care System (US HCS) 
-Costs for 100%, 75%, and 50% LTBI reduction","") + 
-       geom_hline(aes(y=0),size=2) +
-       geom_line(aes(y=redEnLTBI100_costs,   color=costs,      linetype=redEnLTBI100L), size=2) +
-       geom_line(aes(y=redEnLTBI75_costs,    color=costs,      linetype=redEnLTBI75L), size=2) +
-       geom_line(aes(y=redEnLTBI50_costs,    color=costs,      linetype=redEnLTBI50L), size=2) +
-       geom_line(aes(y=redEnLTBI100_savings, color=savings,    linetype=redEnLTBI100L), size=2) +
-       geom_line(aes(y=redEnLTBI75_savings,  color=savings,    linetype=redEnLTBI75L), size=2) +
-       geom_line(aes(y=redEnLTBI50_savings,  color=savings,    linetype=redEnLTBI50L), size=2) +
-       geom_line(aes(y=redEnLTBI100_totCost, color=totalCosts, linetype=redEnLTBI100L), size=2) +
-       geom_line(aes(y=redEnLTBI75_totCost,  color=totalCosts, linetype=redEnLTBI75L), size=2) +
[…]

### 2013-08-23 in_progress/models/costBenefitAnalysis/interventionGroupsPresenter.R
fixed graph and poster

@@ -158,7 +158,8 @@ x <- ggplot(redEnLTBI,aes(x=year)) +
        labs(x="Years", y="Billions of USD", color="Economic Distinction", 
             linetype="% Reduction") +
        #scale_y_continuous(breaks=yrange) + 
-       plotTitle("Averted TB Costs for US HCS given 10%, 25%, and 50% LTBI reduction","") + 
+       plotTitle("Averted TB Costs for US HCS given 
+10%, 25%, and 50% LTBI reduction","") + 
        geom_hline(aes(y=0),size=2) +
        geom_line(aes(y=redEnLTBI10_savings,  color=savings,    linetype=redEnLTBI10L), size=2) +
        geom_line(aes(y=redEnLTBI25_savings,  color=savings,    linetype=redEnLTBI25L), size=2) +
@@ -166,7 +167,8 @@ x <- ggplot(redEnLTBI,aes(x=year)) +
        guides(fill=F, alpha=F) + 
        theme_gray(base_size=25) +
        theme(legend.position=c(0.22,0.82), axis.title=element_text(size=40), 
-             axis.text=element_text(size=27), plot.title=element_text(size=40))
+             axis.text=element_text(size=27), plot.title=element_text(size=40)) +
+       scale_color_manual(values=c(savingsC))
 			 
 
 ggsave('costAvertedRedEnLTBI.pdf',x,width=15,height=12)

### 2013-08-23 in_progress/presentations/poster/reuMHC2013NoSIRIntro.tex
minor tweaks
some summary points
fixed graph and poster
changed caption for averted TB costs in poster graph

@@
               \begin{center}
-                \includegraphics[height=0.83\textwidth,width=\textwidth] {incPlotSourced2}
+                \includegraphics[height=0.83\textwidth,width=\textwidth] {incPlotSourced}
               \end{center}
@@
               \begin{center}
-                \includegraphics[height=0.83\textwidth,width=\textwidth]{costPlotSourced2}
+                \includegraphics[height=0.83\textwidth,width=\textwidth]{costPlotSourced}
               \end{center}
@@
           \item Estimates implementation cost of intervention
-          \item Active TB Costs: \$14,014.90 LTBI Costs: \$403.45
+          \item Mean Active TB Treatment Cost: \$14,014.90
 
@@
               \begin{minipage}[c]{0.6\textwidth}
-                \includegraphics[height=0.7\textwidth, width=\textwidth]{EnLTBIRedGroupCost.pdf}
+                \includegraphics[height=0.7\textwidth,width=\textwidth]{costAvertedRedEnLTBI}
               \end{minipage}
@@
               \begin{minipage}[c]{0.35\textwidth}
-                \caption{Cumulative implementation costs, US HCS savings, and net
-                       US costs of LTBI arrival cure rates. Cost/case cured was
-                       \$600, \$800, and \$1000 for 50\%, 75\%, and 100\%
-                       cured}
+                   \caption{Cumulative US HCS savings from averted Active TB 
+                                treatment costs given intervention magnitude.  
+                                Does not include savings from averted LTBI treatment costs.  
+%                \caption{Cumulative implementation costs, US HCS savings, and net
+%                       US costs of LTBI arrival cure rates. Cost/case cured was
+%                       \$600, \$800, and \$1000 for 50\%, 75\%, and 100\%
+%                       cured}
               \end{minipage}
@@
         \begin{columns}[T]
-          \vspace{-2em}
           \begin{column}{.45\textwidth}
@@
               \begin{center}
-                \includegraphics[height=0.8\textwidth,width=\textwidth]{finalRunSmall2}
+                \includegraphics[height=0.8\textwidth,width=\textwidth]{finalRunSmall}
               \end{center}
-              \caption{Incidence/million for R and C++ models (2100 runs, $\Delta t$ = 0.01, popConst = 1)}
+              \caption{Incidence/million for R and \texttt{C++} models (2100 runs, $\Delta t$ = 0.01, popConst = 1)}
               \label{fig:finalRun}
@@
       \begin{block}{Stochastic Models as a Measure of Variability}
-        %\vspace{-0.5em}
         %\begin{columns}[T]
@@
           \begin{center}
-            \includegraphics[height=0.25\textwidth,width=0.45\textwidth]{IN0dist}
-            \includegraphics[height=0.25\textwidth,width=0.45\textwidth]{IN1dist}
+            \includegraphics[width=0.45\textwidth]{IN0dist}
+            \hspace{0.8em}
+            \includegraphics[width=0.45\textwidth]{IN1dist}
           \end{center}
@@
         \begin{itemize}
-          \item TB elimination is possible
-          \item new framework for disease modeling
-          \item something else
+          \item LTBI dominates US TB dynamics
+          \item Reducing FB LTBI most cost effective
+          \item Agent-based models effective for evaluating robustness
         \end{itemize}

### 2013-08-23 in_progress/models/costBenefitAnalysis/hillFunctions.R
fixed cost bug

@@ -160,13 +160,13 @@ Ddt <- function(t,v,parms) {
   })
 }
 
-hill <- function(intervenCost,sigmaL,f,transmission=1,incLTBI=1,activeTxC=F,LTBITxC=F,initial=cutoffT,final=totT,dataSet=P){
+hill <- function(intervenCost,sigmaL,f,transmission=1,incLTBI=1,initial=cutoffT,final=totT,dataSet=P){
   # set values in parameters
   newparms <- c(iCnewCases=as.vector(intervenCost['newCases']), 
                 iCtotPop=as.vector(intervenCost['totPop']), 
                 iCLTBIEn=as.vector(intervenCost['LTBIEn']),
-                sigmaL=sigmaL, f=f, transmission=transmission, incLTBI=incLTBI,
-                Ct=activeTxC,Cl=LTBITxC)
+                sigmaL=sigmaL, f=f, transmission=transmission, incLTBI=incLTBI)
+                #Ct=activeTxC,Cl=LTBITxC)
   parameters <- c(parms, newparms)
   # recursive=TRUE collapses dataframe to labeled vector
   initv <- c(dataSet[initial,], recursive=TRUE)

### 2013-08-23 in_progress/models/costBenefitAnalysis/interventionConfig.R

@@ -32,7 +32,7 @@ split20RedEnLTBIInter <- c('redEnLTBI0','redEnLTBI5','redEnLTBI10',
                            'redEnLTBI60','redEnLTBI65','redEnLTBI70',
                            'redEnLTBI75','redEnLTBI80','redEnLTBI85',
                            'redEnLTBI90','redEnLTBI95','redEnLTBI100')
-redEnLTBI_Interventions <- c(allInterventions[3],allInterventions[6],allInterventions[11])                  
+redEnLTBI_Interventions <- allInterventions[1:3]                 
 curInterventions <- split20RedEnLTBIInter#allInterventions
 incLTBICost <- 0
 

### 2013-08-23 in_progress/models/costBenefitAnalysis/interventionGroupsPresenter.R

@@ -67,6 +67,7 @@ redEnLTBI10L    <- rep("10% reduction",       totT)
 # }
 
 #Graphs
+interventionData <- as.list(1:3)
 interHCSCost <- as.list(1:3)
 costOfInter <- as.list(1:3)  #additional cost of intervention
 saveOfInter <- as.list(1:3)  #additional savings of intervention
@@ -74,13 +75,15 @@ interTot <- as.list(1:3)
 totSpent <- as.list(1:3)  #net cost
 
 y <- 1
+print(redEnLTBI_Interventions)
 for (interventionName in redEnLTBI_Interventions) {
-  interventionData <- read.csv(paste(c(intFilePrefix,interventionName,
+  interventionData[[y]] <- read.csv(paste(c(intFilePrefix,interventionName,
                                        intFileSuffix),collapse=""))
+  print(interventionData[[y]][125,])
   #HCS cost borne by intervention
-  interHCSCost[[y]] <- (interventionData$cN0 + interventionData$cN1)/1e9
+  interHCSCost[[y]] <- (interventionData[[y]]$cN0 + interventionData[[y]]$cN1)/1e9
   #Implementation cost of intervention
-  costOfInter[[y]] <- (interventionData$interventionCost)/1e9
+  costOfInter[[y]] <- (interventionData[[y]]$interventionCost)/1e9
   #Savings from intervention
   saveOfInter[[y]] <- baseHCSCost - interHCSCost[[y]]
   #Total US HCS cost due to intervention
@@ -89,7 +92,7 @@ for (interventionName in redEnLTBI_Interventions) {
   totSpent[[y]]  <- interTot[[y]] - baseHCSCost 
   
   #Cost per cases averted
-  intCasesD         <- 1e6*(interventionData$progTotalD0 + interventionData$progTotalD1)
+  intCasesD         <- 1e6*(interventionData[[y]]$progTotalD0 + interventionData[[y]]$progTotalD1)
   casesAvertedD     <- baseCasesD - intCasesD
   cpcaDataD <- 1e9*totSpent[[y]]/casesAvertedD
   
@@ -150,7 +153,7 @@ yrange <- round(seq(min(-1*saveOfInter[[1]])-0.5,max(costOfInter[[1]])+0.5,by=0.
 # No treatment implementation costs accounted for
 
 redEnLTBI <- data.frame(year = years, 
-                        redEnLTBI10_savings = saveOfInter[[1]], 
[…]

### 2013-08-24 in_progress/models/costBenefitAnalysis/interventionAnalyzer.R
updated poster, fixed graph

@@ -14,7 +14,7 @@ if (length(args) > 0) {
   index <- 1
   analysisType <- 1
 }
-generateNewData <- F
+generateNewData <- T
 
 #Which interventions to run:
 source('interventionConfig.R')

### 2013-08-24 in_progress/models/costBenefitAnalysis/interventionConfig.R

@@ -33,7 +33,8 @@ split20RedEnLTBIInter <- c('redEnLTBI0','redEnLTBI5','redEnLTBI10',
                            'redEnLTBI75','redEnLTBI80','redEnLTBI85',
                            'redEnLTBI90','redEnLTBI95','redEnLTBI100')
 redEnLTBI_Interventions <- allInterventions[1:3]                 
-curInterventions <- split20RedEnLTBIInter#allInterventions
+redEnLTBI_Interventions_specialMag <- c('redEnLTBI10','redEnLTBI25','redEnLTBI50')                 
+curInterventions <- redEnLTBI_Interventions
 incLTBICost <- 0
 
 interventionConfig <- function(interventionStr, x=0) { #x is an integer refering to cost option, ranges 0 to 5
@@ -52,7 +53,7 @@ interventionConfig <- function(interventionStr, x=0) { #x is an integer refering
     if (interventionType == "redEnLTBI") {
       #TODO: Make this a function depending on magnitude for greater flexibility
       # (minor)
-      incLTBI <- incLTBI*(interventionMag/100)
+      incLTBI <- incLTBI*(1-interventionMag/100)
       LTBIEn  <- 800 #LTBIEn + 400 + 600*(interventionMag/100) + x*100
     } else if (interventionType == "redImm") {
       #No Costs!

### 2013-08-24 in_progress/models/costBenefitAnalysis/interventionGroups.R

@@ -1,6 +1,6 @@
 source('interventionAnalyzer.R')
 #Group by type IMPORTANT: Reset all intervention costs to default values in interventionConfig.R before running
-for(intervention in redEnLTBI_Interventions) {
+for(intervention in redEnLTBI_Interventions_specialMag) {
   intConfig <- interventionConfig(intervention)
   costs     <- intConfig$costs
   params    <- intConfig$params
@@ -22,7 +22,7 @@ for(intervention in incLTBItrmt_Interventions) {
 
 #Cost Vary
 for(x in 0:9){
-  for(intervention in redEnLTBI_Interventions) {
+  for(intervention in redEnLTBI_Interventions_specialMag) {
     intConfig <- interventionConfig(intervention,x)
     costs     <- intConfig$costs
     params    <- intConfig$params

### 2013-08-24 in_progress/models/costBenefitAnalysis/interventionGroupsPresenter.R

@@ -75,17 +75,17 @@ interTot <- as.list(1:3)
 totSpent <- as.list(1:3)  #net cost
 
 y <- 1
-print(redEnLTBI_Interventions)
-for (interventionName in redEnLTBI_Interventions) {
+for (interventionName in redEnLTBI_Interventions_specialMag) {
   interventionData[[y]] <- read.csv(paste(c(intFilePrefix,interventionName,
                                        intFileSuffix),collapse=""))
-  print(interventionData[[y]][125,])
   #HCS cost borne by intervention
   interHCSCost[[y]] <- (interventionData[[y]]$cN0 + interventionData[[y]]$cN1)/1e9
   #Implementation cost of intervention
   costOfInter[[y]] <- (interventionData[[y]]$interventionCost)/1e9
   #Savings from intervention
   saveOfInter[[y]] <- baseHCSCost - interHCSCost[[y]]
+  print(interventionName)
+  print(saveOfInter[[y]])
   #Total US HCS cost due to intervention
   interTot[[y]] <- interHCSCost[[y]] + costOfInter[[y]]
   #Total additional spent by US HCS due to intervention

### 2013-08-24 in_progress/models/costBenefitAnalysis/helpers.R
fixed other graph and finalized poster

@@ -50,10 +50,10 @@ USBInfecTBC          <- "#FF4040"
 USBNonInfecTBC       <- "#A60000"
 
 #old colors
-acuteLatentFBc       <- "#FFA573"
-chronicLatentFBc     <- "#FFC973"
-acuteLatentUSBc      <- "#6999D3"
-chronicLatentUSBc    <- "#5FD3B3"
+acuteLatentFBc       <- "#6999D3"
+chronicLatentFBc     <- "#5FD3B3"
+acuteLatentUSBc      <- "#FFA573"
+chronicLatentUSBc    <- "#FFC973"
 latentFBc            <- "#FFB773"
 latentUSBc           <- "#64B6C3"
 activeTBFBdL1c       <- "#AA4DA6"
@@ -118,7 +118,6 @@ activeTBUSBdF0L      <- rep(activeTBUSBdF0Ls,totT)
 #                                      chronicLatentFBLs), 
 #                             values=scale_fill_values)
 #ggsave('forPoster/incPlotSourced2.pdf',incPlotSourced,width=10,height=8)
->>>>>>> 922876bf9af44fa2f7e61e41ccd64bea4d0e5709
 
 #Order: IF1 = IF1c, IF1 + IL1 = IL1c 
 #IF1c <- baseTotalInc$IF1
@@ -143,109 +142,109 @@ activeTBUSBdF0L      <- rep(activeTBUSBdF0Ls,totT)
 #           geom_ribbon(aes(ymin=II0c,ymax=IJ0c,fill=activeNoInfecUSBL))
 #
 #  
-intLabels <- function(type,magnitude,vec=T) {
-  redEnLTBI100Ls   <- "100% Entering LTBI Cured"
-  redEnLTBI75Ls    <- "75% Entering LTBI Cured"
-  redEnLTBI50Ls    <- "50% Entering LTBI Cured"
-  redImm50Ls       <- "50% Immigration Reduction"
-  redImm75Ls       <- "75% Immigration Reduction"
-  incLTBItrmt100Ls <- "100% LTBI Treatment Increase"
-  incLTBItrmt300Ls <- "300% LTBI Treatment Increase"
-  redTrans100Ls    <- "100% Reduction in Transmission"
-  redEnLTBI100L    <- rep("100% Entering LTBI Cured",        totT)
-  redEnLTBI75L     <- rep("75% Entering LTBI Cured",         totT)
[…]

### 2013-08-24 in_progress/models/costBenefitAnalysis/interventionTable.R
added interventionTable.R (requires 'xtable' R library) to explicitly calculate the cost of redEnLTBI interventions and output it as a table

@@ -1,0 +1,90 @@
+#
+# Generates table showing savings for redEnLTBI interventions
+# (assuming default cost of curing LTBI, which is ...............)
+#
+
+library(xtable) # library for turning R objects into LaTeX tables
+source('interventionAnalyzer.R')
+
+
+
+### PART 1 - GENERATE DATA FROM MODEL ###
+
+#Make sure you reset all intervention costs to default values in interventionConfig.R before running!!!
+
+# Set of interventions
+redEnLTBI_Interventions_paper <- c('redEnLTBI20', 'redEnLTBI35', 'redEnLTBI50', 'redEnLTBI65')
+
+baseData <- read.csv(baseFile)
+#Base Incidence
+baseInc <- generateIncidence(baseData)
+#US Health Care System (HCS) TB costs due to base system
+baseHCSCost <- (baseData$cN0 + baseData$cN1)/1e9
+baseCasesD <- 1e6*(baseData$progTotalD0 + baseData$progTotalD1)
+
+#Costs related to Interventions
+for(intervention in redEnLTBI_Interventions_paper) {
+  intConfig <- interventionConfig(intervention)
+  costs     <- intConfig$costs
+  params    <- intConfig$params
+  interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
+                    params[["incLTBI"]])
+  write.csv(interData, paste(c(intFilePrefix,intervention,intFileSuffix),
+                             collapse=""))
+}
+
+
+
+### PART 2 - ORGANIZE DATA INTO MEANINGFUL CHUNKS ###
+
+#Graphs (actually, not really)
+interventionData <- as.list(1:4)
+interHCSCost <- as.list(1:4)
+costOfInter <- as.list(1:4)  #additional cost of intervention
+saveOfInter <- as.list(1:4)  #additional savings of intervention
+interTot <- as.list(1:4)
+totSpent <- as.list(1:4)  #net cost
+
+y <- 1
+for (interventionName in redEnLTBI_Interventions_paper) {
+  
+  interventionData[[y]] <- read.csv(paste(c(intFilePrefix,interventionName,
+                                       intFileSuffix),collapse=""))
+  #HCS cost borne by intervention
+  interHCSCost[[y]] <- (interventionData[[y]]$cN0 + interventionData[[y]]$cN1)/1e9
[…]

### 2013-08-24 in_progress/presentations/paper/draft.tex
tightened up interventionTable.R and incorporated some results into draft

@@
 such estimates of entering LTBI cure rates higher than $65\%$ become much more
-difficult to acheive. It was seen that in this model as well as in the basic
+difficult to achieve. It was seen that in this model as well as in the basic
 Hill, no analyzed intervention predicted elimination by 2100. In order to obtain
-elimiation by 2100, at least 95\% of entering LTBI cases had to be cured, which
+elimination by 2100, at least 95\% of entering LTBI cases had to be cured, which
 is practically impossible. However, it was seen that curing entering cases of
-LTBI resulted in a net US HCS cost per case averted of \$X at 2025, \$Y at 2050,
-and \$Z at 2100. Further, it was also found that the relationship between total
-incidence at 2100 and percentage of incoming LTBI cases cured was linear, and
+LTBI resulted in a net US HCS cost per case averted of \$67,722.96 at 2025, \$28,759.00 at 2050,
+and \$17,967.39 at 2100 (assuming 20\% reduction with one cure costing \$XXXX; see Table
+\ref{tab:cpcaRes} for other percentages). Further, it was also found that the relationship
+between total incidence at 2100 and percentage of incoming LTBI cases cured was linear, and
 from this estimates were made of the yearly average US HCS savings garnered by
@@
 deaths, respectively.
+
+% latex table generated in R 3.0.1 by xtable 1.7-1 package
+% Sat Aug 24 18:08:52 2013
+\begin{table}
+\centering
+\begin{tabular}{|r|cccc|}
+  \hline
+ & red20 & red35 & red50 & red65 \\ 
+  \hline
+2000 & ND & ND & ND & ND \\ 
+  2025 & 67722.96 & 67527.15 & 67332.53 & 67138.90 \\ 
+  2050 & 28759.00 & 28581.09 & 28404.13 & 28227.50 \\ 
+  2075 & 20876.80 & 20709.13 & 20541.77 & 20374.49 \\ 
+  2100 & 17967.39 & 17804.94 & 17642.64 & 17480.33 \\ 
+   \hline
+\end{tabular}
+\caption{Cost Per Case Averted by Reducing Incoming LTBI by 20\%, 35\%, 50\%, and 65\% (in dollar per case)} 
+\label{tab:cpcaRes}
+\end{table}
 

### 2013-08-24 in_progress/models/costBenefitAnalysis/interventionTable.R

@@ -37,36 +37,40 @@ for(intervention in redEnLTBI_Interventions_paper) {
 
 ### PART 2 - ORGANIZE DATA INTO MEANINGFUL CHUNKS ###
 
-#Graphs (actually, not really)
+#Containers
 interventionData <- as.list(1:4)
 interHCSCost <- as.list(1:4)
 costOfInter <- as.list(1:4)  #additional cost of intervention
 saveOfInter <- as.list(1:4)  #additional savings of intervention
 interTot <- as.list(1:4)
 totSpent <- as.list(1:4)  #net cost
+intCasesD <- as.list(1:4)
+casesAvertedD <- as.list(1:4)
+cpcaDataD <- as.list(1:4) #cost per case averted
 
 y <- 1
 for (interventionName in redEnLTBI_Interventions_paper) {
   
   interventionData[[y]] <- read.csv(paste(c(intFilePrefix,interventionName,
                                        intFileSuffix),collapse=""))
-  #HCS cost borne by intervention
+  #HCS cost borne by intervention [in billions $]
   interHCSCost[[y]] <- (interventionData[[y]]$cN0 + interventionData[[y]]$cN1)/1e9
-  #Implementation cost of intervention
+  #Implementation cost of intervention [in billions $]
   costOfInter[[y]] <- (interventionData[[y]]$interventionCost)/1e9
-  #Savings from intervention
+  #Savings from intervention [in billions $]
   saveOfInter[[y]] <- baseHCSCost - interHCSCost[[y]]
   #print(interventionName)
   #print(saveOfInter[[y]])
-  #Total US HCS cost due to intervention
+  #Total US HCS cost due to intervention [in billions $]
   interTot[[y]] <- interHCSCost[[y]] + costOfInter[[y]]
-  #Total additional spent by US HCS due to intervention
+  #Total additional spent by US HCS due to intervention [in billions $]
   totSpent[[y]]  <- interTot[[y]] - baseHCSCost 
   
-  #Cost per cases averted
-  intCasesD         <- 1e6*(interventionData[[y]]$progTotalD0 + interventionData[[y]]$progTotalD1)
-  casesAvertedD     <- baseCasesD - intCasesD
-  cpcaDataD <- 1e9*totSpent[[y]]/casesAvertedD
[…]

### 2013-08-24 in_progress/presentations/paper/draft.tex
added more details to interventions section of draft; updated interventionTable.R respectively

@@
 curing various percentages of entering LTBI cases. Four indicative percentages
-chosen were $20\%$, $35\%$, $50\%$, and $65\%$. Note that the hill model does
+chosen were $20\%$, $35\%$, $50\%$, and $65\%$. Note that the Hill model does
 not distinguish documented immigration from undocumented immigration, and as
@@
 curing one case of entering LTBI over the time scale 2000 to 2025, 2000 to 2050,
-and 2000 to 2100. This value peaked at \$X at 2100. This illustrates that it
-would be cost saving to cure cases of LTBI at the cost of X 2000 dollars over
-the time period 2000-2100. These intervention strategies also resulted in A, B,
-and C fewer cases of TB seen in the US, and D, E, and F fewer TB
-deaths, respectively.
+and 2000 to 2100. This value peaked at \$1.026 million at 2100 (20\% reduction). This illustrates that it
+would be cost saving to cure cases of LTBI at the cost of \$1.026 million ``2000'' dollars over
+the time period 2000-2100. These intervention strategies also resulted in 23,870; 41,952;
+and 60,189 fewer cases of TB seen in the US, and 2,056; 3,614; and 5,185 fewer TB
+deaths, for 20\%, 35\%, and 50\% reduction, respectively.
 

### 2013-08-24 in_progress/models/costBenefitAnalysis/interventionTable.R

@@ -21,6 +21,7 @@ baseInc <- generateIncidence(baseData)
 #US Health Care System (HCS) TB costs due to base system
 baseHCSCost <- (baseData$cN0 + baseData$cN1)/1e9
 baseCasesD <- 1e6*(baseData$progTotalD0 + baseData$progTotalD1)
+baseDeathsD <- 1e6*(baseData$tbdeathD0 + baseData$tbdeathD1)
 
 #Costs related to Interventions
 for(intervention in redEnLTBI_Interventions_paper) {
@@ -47,6 +48,8 @@ totSpent <- as.list(1:4)  #net cost
 intCasesD <- as.list(1:4)
 casesAvertedD <- as.list(1:4)
 cpcaDataD <- as.list(1:4) #cost per case averted
+intDeathsD <- as.list(1:4)
+deathsAvertedD <- as.list(1:4) #TB deaths averted
 
 y <- 1
 for (interventionName in redEnLTBI_Interventions_paper) {
@@ -71,6 +74,10 @@ for (interventionName in redEnLTBI_Interventions_paper) {
   casesAvertedD[[y]]     <- baseCasesD - intCasesD[[y]]
   #Cost per cases averted [in $/case]
   cpcaDataD[[y]] <- 1e9*totSpent[[y]]/casesAvertedD[[y]]
+
+  intDeathsD[[y]]     <- 1e6*(interventionData[[y]]$tbdeathD0 + interventionData[[y]]$tbdeathD1)
+  #Number of TB deaths averted [in people]
+  deathsAvertedD[[y]] <- baseDeathsD - intDeathsD[[y]]
   
   y <- y + 1
 
@@ -81,9 +88,19 @@ for (interventionName in redEnLTBI_Interventions_paper) {
 ### PART 3 - PUT IT ALL IN A TABLE ###
 
 # Sample 5 points in time
+rownames <- c('2000', '2025', '2050', '2075', '2100')
+
+# Savings from Intervention
+svngResults <- data.frame(red20=rep(0,5), red35=rep(0,5), red50=rep(0,5), red65=rep(0,5), row.names = rownames)
+for (interventionNumber in 1:4) {
+    svngResults[,interventionNumber] <- saveOfInter[[interventionNumber]][seq(1, totT, floor(totT/4))]
+}
+print(svngResults)
+svngRes.table <- xtable(svngResults, digits=6, align="|r|cccc|", caption = "Savings from Reducing Incoming LTBI by X percent (in billions of dollars)")
+
 
[…]

### 2013-08-25 in_progress/presentations/paper/draft.tex
working on paper

--- 2013-08-21 in_progress/presentations/paper/draft.tex
@@
 \section{Methods}
-
 \subsection{Basic Implementation}
@@
 $\texttt{lsoda}$ routine. The systems of differential equations used in the Basic
-Hill Model and the extended Hill Model are shown below in Figure 2 and Figure 3
-respectively.
+Hill Model and the extended Hill Model to capture basic disease dynamics are
+shown below in Figure 2 and Figure 3 respectively. In the extended Hill model,
+more differential equations were implemented to add additional tracking and
+economic modeling. These equations are detailed in the appendix.
 
@@
 
-The vector variables $S_{0}, F_{0}, L_{0}, I_{0}, J_{0}$ contain the number of US-born individuals in the S, F, L, I, J compartments respectively, and $S_{1}, F_{1}, L_{1}, I_{1}, J_{1}$ contain foreign-born individuals.
-$N_{0}$ and $N_{1}$ are the total populations of US-born and foreign-born individuals.
+The vector variables $S_{0}, F_{0}, L_{0}, I_{0}, J_{0}$ contain the number of
+US-born individuals in the S, F, L, I, J compartments respectively, whereas $S_{1},
+F_{1}, L_{1}, I_{1}, J_{1}$ contain foreign-born individuals.  $N_{0}$ and
+$N_{1}$ are the total populations of US-born and foreign-born individuals.
 The constants $\rho$ and $\alpha$ are birth rates, while $\mu_{i}$, and $\mu_{d}$ are death rates.  
@@
 These components were made into compartments, tracked by differential equations
-EQUATION NUMBER SOMETHING TO SOMETHING, SORTED BY COMPARTMENT. In addition,
-estimations of the basic reproductive number of FB or USB active, infectious TB
-cases were made from a theoretical and an experimental perspective. Experimental
-data were calculated by reducing the initial population of FB or USB active,
-infectious TB cases by 1 and predicting the final number of cases seen in each
-case, in $\texttt{R}$.
+detailed in the appendix. These equations allowed the model to track the total
+number of TB cases, TB deaths, and  natural deaths. Further, the model tracks,
+the sourced cost on the US HCS. Progressions into
+active TB due to activations of LTBI or exogenous infection were tracked,
+allowing for sourced incidence data to be generated. The entering cases of LTBI
+(acute or chronic) were also tracked. In the case of intervention testing, the
+number of cured cases of entering LTBI and the number of untreated entering LTBI
+were both tracked. Cured cases of LTBI entering, TB deaths, total TB cases, and
+total cost were also tracked discounted at 3\% annually. This discounting was
+converted to a continuous differential equation for use within the model. In
+general, incidence data is calculated in the same way in the extended hill as it
+was in the basic Hill.
 
+In addition, estimations of the basic reproductive number of FB or USB active,
+infectious TB cases were made from a theoretical and an experimental
+perspective. Experimental data were calculated by reducing the initial
+population of FB or USB active, infectious TB cases by one and allowing the
+model to progress otherwise as normal. The decreased number of total TB cases
+seen details how many infections can be thought to be due to one infected
+individual in the given population.
+
+From an experimental perspective, the spread of TB was thought to be a geometric
+series. If one infectious individual infects $x$ people annually, over the
+course of $N$ years the total number of infections caused by this individual can
+be approximated by the geometric series of $N$ terms with rate $x$ and initial
+term $1$. In this case, $N = 100$, and the ratios for FB infectious individuals
+and USB infectious individuals were obtained from RATIO CITATION COLIN. 
 \subsection{Economic Modeling}
-Further, estimates for the cost of active TB treatment and for the cost of
-latent TB infection (LTBI) treatment were obtained from Dylan et. al. and So and
-So adherence effectivenss. CITE ME!
-Both these costs and any health state outcomes were discounted at a rate of 3\%
-per year. From these estimated cost per treatment, total costs were obtained in
-the following way. It was assumed that every patient in the US with active TB is
-treated, not necessarily successfully, but further that every treatment costs
-exactly the average cost per treatment. Thus, active TB costs could be tracked
-simply by tracking the number of new active TB cases, and scaling by a
-discounted cost per treatment rate. Given the structure of the model, further
-granularity was obtained from the cost data by tracking separately the cost due
-to new cases that stemmed from activation of a chronic LTBI case, or activation
-of an acute LTBI case. These values give estimates for the US HCS TB cost due to
-exogenous infection of TB vs the US HCS TB cost due to activation of LTBI. Each
-of these components of the cost was a new differential equation tracked by the
-model, also solved by $\texttt{lsoda}$. For LTBI treatment cost, treatment was
+When tracking the economic implications of current US TB load and various
+intervention strategies, active TB costs were given by \$14,000. This cost is
+the weighted mean of the costs of cases requiring hospitalization (happening
+49\% of the time) and cases not requiring hospitalization (51\%). These data
+were found in DYLAN COST STUDY CITATION. LTBI treatment costs were given by
+\$468.00. These data were based on the cost of a successfull treatment, given by
+DYLAN COST STUDY CITATION, as well as adherence and efficacy data found in
+ADHERENCE CITATION.
+
+From these estimated cost per treatment, total costs were obtained by assuming
+that every patient with active TB in the US is treated at full price, though the
+treatment may fail. As individuals with active
+TB are charged upon entry to the active TB compartment, the model can also
+accurately estimate sourced US HCS cost data. Cost data were separately tracked
+due to incoming active TB costs stemming from activation of LTBI vs exogenous
+reinfection. These data were modelled as additional compartments and also solved
+by $\texttt{lsoda}$. For LTBI treatment cost, treatment was
 charged upon leaving the LTBI compartment due to the cumulative self-cure and
@@
 uncertainty in measurments of LTBI treatment cost, extensive sensitivity
-analysis was performed on this parameter relative to final cost outcomes, which
-showed that it had an linear effect. In addition to US HCS cost, the system
-was implemented so as to also track projected intervention implementation cost,
-given user-inputted parameters relating to various possible intervention cost
-strategies. The extended Hill Model was used to track the effect of many
-interventions tested by the Hill Model as well as an additional intervention
-strategy of curing cases of immigrating LTBI prior to entry. This intervention
-strategy proved very promising and elimination year, final cost, and cost per
-case averted were tracked for various levels of entering LTBI cure rate. The
+analysis was performed on this parameter relative to final cost outcomes. In
+addition to US HCS cost, the system was implemented so as to also track
+projected intervention implementation cost, given user-inputted parameters
+relating to various possible intervention cost strategies. The extended Hill
+Model was used to track the effect of many interventions tested by the Hill
+Model. In particular, the intervention strategy of curing entering cases of LTBI
+proved very promising and elimination year, final cost, and cost per case
+averted were tracked for various levels of entering LTBI cure rate. The
 interventions were implemented so as to take effect during the year 2013 and run
@@
 health states were computed given rates in the hill model and a variety of
-approximations. The final size standard deviation and distribution data was
-collected via 2160 (MINUS SOME) runs with each agent in the model truly
-representing one individual and a time step of $0.01$. These data were analyzed
-in $R$.
+approximations. The model maintained scaled individual records for every
+individual with LTBI, with susceptible individuals not modelled as agents.
+Instead, a binomial distribution was used to probabilistically pick the number
+of new infections each time step. Similarlly, immigration was also handeled
+outside of the agent-based modelling. The final size standard deviation and
+distribution data was collected via 2160 (MINUS SOME) runs with each agent in
+the model truly representing one infected individual and a time step of $0.01$.
+These data were analyzed in $R$. This model was also made to track deaths, total
+TB cases, and infection sources. This data were consistent with the
+deterministic model, and not reproduced in this write-up.
 
+Further implementations of the \texttt{C++} model were made that deviated from
+the basic Hill Model. Specifically, the acute latent compartment in the basic
+Hill Model is a vestigal necessity of compartmental modeling and not reflective
+of the biology of tuberculosis, and an agent based model was implemented that
+more closely respects the biology of tuberculosis. Results from this model or
+the strict Hill model did not differ significantly. 
 \section{Results}

### 2013-08-25 in_progress/presentations/paper/draft.tex

@@
 curing various percentages of entering LTBI cases. Four indicative percentages
-chosen were $20\%$, $35\%$, $50\%$, and $65\%$. Note that the hill model does
+chosen were $20\%$, $35\%$, $50\%$, and $65\%$. Note that the Hill model does
 not distinguish documented immigration from undocumented immigration, and as
 such estimates of entering LTBI cure rates higher than $65\%$ become much more
-difficult to acheive. It was seen that in this model as well as in the basic
+difficult to achieve. It was seen that in this model as well as in the basic
 Hill, no analyzed intervention predicted elimination by 2100. In order to obtain
-elimiation by 2100, at least 95\% of entering LTBI cases had to be cured, which
+elimination by 2100, at least 95\% of entering LTBI cases had to be cured, which
 is practically impossible. However, it was seen that curing entering cases of
-LTBI resulted in a net US HCS cost per case averted of \$X at 2025, \$Y at 2050,
-and \$Z at 2100. Further, it was also found that the relationship between total
-incidence at 2100 and percentage of incoming LTBI cases cured was linear, and
+LTBI resulted in a net US HCS cost per case averted of \$67,722.96 at 2025, \$28,759.00 at 2050,
+and \$17,967.39 at 2100 (assuming 20\% reduction with one cure costing \$XXXX; see Table
+\ref{tab:cpcaRes} for other percentages). Further, it was also found that the relationship
+between total incidence at 2100 and percentage of incoming LTBI cases cured was linear, and
 from this estimates were made of the yearly average US HCS savings garnered by
 curing one case of entering LTBI over the time scale 2000 to 2025, 2000 to 2050,
-and 2000 to 2100. This value peaked at \$X at 2100. This illustrates that it
-would be cost saving to cure cases of LTBI at the cost of X 2000 dollars over
-the time period 2000-2100. These intervention strategies also resulted in A, B,
-and C fewer cases of TB seen in the US, and D, E, and F fewer TB
-deaths, respectively.
+and 2000 to 2100. This value peaked at \$1.026 million at 2100 (20\% reduction). This illustrates that it
+would be cost saving to cure cases of LTBI at the cost of \$1.026 million ``2000'' dollars over
+the time period 2000-2100. These intervention strategies also resulted in 23,870; 41,952;
+and 60,189 fewer cases of TB seen in the US, and 2,056; 3,614; and 5,185 fewer TB
+deaths, for 20\%, 35\%, and 50\% reduction, respectively.
+
+% latex table generated in R 3.0.1 by xtable 1.7-1 package
+% Sat Aug 24 18:08:52 2013
+\begin{table}
+\centering
+\begin{tabular}{|r|cccc|}
+  \hline
+ & red20 & red35 & red50 & red65 \\ 
+  \hline
+2000 & ND & ND & ND & ND \\ 
+  2025 & 67722.96 & 67527.15 & 67332.53 & 67138.90 \\ 
+  2050 & 28759.00 & 28581.09 & 28404.13 & 28227.50 \\ 
+  2075 & 20876.80 & 20709.13 & 20541.77 & 20374.49 \\ 
+  2100 & 17967.39 & 17804.94 & 17642.64 & 17480.33 \\ 
+   \hline
+\end{tabular}
+\caption{Cost Per Case Averted by Reducing Incoming LTBI by 20\%, 35\%, 50\%, and 65\% (in dollar per case)} 
+\label{tab:cpcaRes}
+\end{table}
 

### 2013-08-25 in_progress/presentations/paper/draft.tex
working on paper

@@
 \usepackage[pdftex]{graphicx}
+\graphicspath{{figures/}}
 
@@
 \section{Results}
-
 \subsection{Basic Population Breakdown}
 The additional tracking capabilities offered several key insights into US TB
-dynamics. Figure INSERT FIGURE HERE shows the yearly incidence of US TB, broken
+dynamics. Figure~\ref{fig:incPlotSourced} shows the yearly incidence of US TB, broken
 down into infection source. It can be seen that the majority of the US TB load
@@
 further agrees with the conclusions drawn by Hill, Becerra, and Castro about the
-necessity of LTBI treatment in any valuable intervention strategy. Further,
-figure INSERT FIGURE HERE shows a similarly sourced plot, but analyzing the
+necessity of LTBI treatment in any valuable intervention strategy. 
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[scale=.5]{incPlotSourced}
+  \end{center}
+  \caption{Sourced yearly incidence data generated by the extended Hill Model.}
+  \label{fig:incPlotSourced}
+\end{figure}
+Further, figure~\ref{fig:costPlotSourced} shows a similarly sourced plot, but analyzing the
 final US HCS costs due to TB. One can see that in this plot, roughly half of the
-US TB HCS costs are due to activations of LTBI. Note that both of these plots
-underestimate the impact LTBI activations play in the spread of TB, as every
-LTBI activation to infectious TB contributes not only to incidence and costs
-directly, but also indirectly by causing additional future cases, which is not
-captured in these graphs. 
+US TB HCS costs are due to activations of LTBI. In this data, it is appropriate
+to think of the costs due to acute LTBI are due to exogenous re-inection,
+whereas active TB costs due to chronic LTBI are activations of LTBI into active
+TB. 
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[scale=.35]{costPlotSourced}
+  \end{center}
+  \caption{Sourced US HCS economic TB load. Note that this data only illustrates
+    the load due to treating active TB, but illustrates where the infections
+    driving this cost come from.}
+  \label{fig:costPlotSourced}
+\end{figure}
+Note that both of these plots underestimate the impact LTBI activations play in
+the spread of TB, as every LTBI activation to infectious TB contributes not only
+to incidence and costs directly, but also indirectly by causing additional
+future cases, which is not captured in these graphs. Further, there is also US
+HCS costs due to treating LTBI, which is not illustrated in these graphs. 
 \subsubsection{Basic Reproduction Number}
@@
 are included in the appendix.  Experimentally, these data were also analyzed, 
-with results of $1.04$ and $.8$, respectively.
+with results of $1.04$ and $.8$, respectively. WHAT CAUSES THIS DIFFERENCE? WE
+NEED TO ANSWER THAT.
 
@@
 and \$17,967.39 at 2100 (assuming 20\% reduction with one cure costing \$XXXX; see Table
-\ref{tab:cpcaRes} for other percentages). Further, it was also found that the relationship
-between total incidence at 2100 and percentage of incoming LTBI cases cured was linear, and
-from this estimates were made of the yearly average US HCS savings garnered by
-curing one case of entering LTBI over the time scale 2000 to 2025, 2000 to 2050,
-and 2000 to 2100. This value peaked at \$1.026 million at 2100 (20\% reduction). This illustrates that it
-would be cost saving to cure cases of LTBI at the cost of \$1.026 million ``2000'' dollars over
-the time period 2000-2100. These intervention strategies also resulted in 23,870; 41,952;
-and 60,189 fewer cases of TB seen in the US, and 2,056; 3,614; and 5,185 fewer TB
-deaths, for 20\%, 35\%, and 50\% reduction, respectively.
+\ref{tab:cpcaRes} for other percentages). Given the variable nature of LTBI
+treatment cost, the model code is extendible such that a user can adjust these
+costs themselves to explore more specific methods of curing entering LTBI.
+Further, it was also found that the relationship between total incidence at 2100
+and percentage of incoming LTBI cases cured was linear, and from this estimates
+were made of the yearly average US HCS savings garnered by curing one case of
+entering LTBI over the time scale 2000 to 2025, 2000 to 2050, and 2000 to 2100.
+This value peaked at \$1.026 million at 2100 (20\% reduction). This illustrates
+that it would be cost saving to cure cases of LTBI at the cost of \$1.026
+million ``2000'' dollars over the time period 2000-2100. These intervention
+strategies also resulted in 23,870; 41,952; and 60,189 fewer cases of TB seen in
+the US, and 2,056; 3,614; and 5,185 fewer TB deaths, for 20\%, 35\%, and 50\%
+reduction, respectively.
 
@@
 option. 
+\subsection{Future Work}
+This work could be extended by examining different classes of interventions or
+more accurately estimating intervention cost with the deterministic extended
+Hill. Further work could also be done with the agent-based Hill Model, by using
+it to examine the effect contact structure plays on US TB incidence levels or to
+examine the effects drug-resistant TB will have on US TB dynamics. 
 \end{document}

### 2013-08-26 in_progress/models/sensitivityAnalysis/hillFunctions.R
added sensitivity analysis folder to models for latin hypercube sampling

@@ -1,0 +1,228 @@
+library(deSolve) # for lsoda routine
+
+#Hill Constants
+source('hillConstants.R')
+
+#DE Solving Parameters + runge-kutta solver: 
+source('deSolConstants.R')
+
+#Initializations:
+# Compartments:
+S0<-S1<-F0<-F1<-L0<-L1<-I0<-I1<-J0<-J1<-N0<-N1<-rep(0,totT)
+# Compartment Costs:
+cL0<-cF0<-cI0<-cJ0<-cL1<-cF1<-cI1<-cJ1<-cN0<-cN1<-rep(0,totT)
+# Compartment Cost Sources:
+cI0dL0<-cI0dF0<-cJ0dL0<-cJ0dF0<-cI1dL1<-cI1dF1<-cJ1dL1<-cJ1dF1<-rep(0,totT)
+# Tracking Data:
+LTBIEn       <- rep(0,totT)                #LTBI arrivals
+LTBIEnD      <- rep(0,totT)                #Discounted LTBI arrivals
+curedLTBIEn  <- rep(0,totT)                #Cured LTBI arrivals
+curedLTBIEnD <- rep(0,totT)                #Discounted Cured LTBI arrivals
+natdeath0    <- natdeath1   <- rep(0,totT) #Natural Deaths
+tbdeath0     <- tbdeath1    <- rep(0,totT) #TB Deaths
+tbdeathD0    <- tbdeathD1   <- rep(0,totT) #Discounted TB Deaths
+progAcute0   <- progAcute1  <- rep(0,totT) #Acute LTBI Progressions
+progChron0   <- progChron1  <- rep(0,totT) #Chronic LTBI Progressions
+progTotalD0  <- progTotalD1 <- rep(0,totT) #Discounted Progressions
+exogenous0   <- exogenous1  <- rep(0,totT) #Exogenous re-Infections
+interventionCost <- rep(0,totT)            #Cumulative intervention cost
+
+#Intervention per time step cost array 
+# cost of new cases, total population, and LTBI cases entering
+P <- data.frame(S0,F0,L0,I0,J0,S1,F1,L1,I1,J1,N0,N1,cL0,cF0,cI0,cI0dL0,cI0dF0,
+                cJ0,cJ0dL0,cJ0dF0,cL1,cF1,cI1,cI1dL1,cI1dF1,cJ1,cJ1dL1,cJ1dF1,
[…]

### 2013-08-27 in_progress/presentations/poster/reuMHC2013NoSIRIntro.tex
added bracket to caption
fixed other graph and finalized poster
fixed poster

@@
             \caption{Incidence/million in USB, FB, and total populations,
-                     given 0\%, 50\%, 75\%, or 100\% treatment of incoming
+                     given 0\%, 50\%, 75\%, or 100\% cure rate of incoming
                      LTBI}
@@
           \item Estimates implementation cost of intervention
-          \item Mean Active TB Treatment Cost: \$14,014.90
-
+          \item Assumed Mean Active TB Treatment Cost: \$14,015
         \end{itemize}
@@
                                 treatment costs given intervention magnitude.  
-                                Does not include savings from averted LTBI treatment costs.  
+                                Does not include savings from averted LTBI treatment costs.}  
 %                \caption{Cumulative implementation costs, US HCS savings, and net
@@
 
+      \vspace{.33em}
       \begin{block}{Stochastic Models as a Measure of Variability}
@@
 
+      \vspace{.33em}
       \begin{block}{Summary}
@@
       \end{block}
-      %\vspace{.9em}
+      \vspace{.33em}
       \begin{block}{References \& Acknowledgments}

### 2013-08-27 in_progress/models/sensitivityAnalysis/hillConstantsLHS.R
worked on hillConstantsLHS.R

@@ -1,6 +1,10 @@
 library(lhs)
 library(triangle)
 
+#Uniform Latin Hypercube with 16 parameters, resolution: n
+n <- 10  #number of divisions in probability distributions
+uniformRandLHS <- randomLHS(n,16)
+
 sigmaLBase  <- 0.057
 fBase       <- 0.187
 transBase   <- 1
@@ -56,3 +60,10 @@ newCases1 = .007554,  #Foreign-born
 CtBase = Ct,
 ClBase = Cl
 )
+
+#Ordered by PRCC absolute value from Hill's sensitivity analysis
+randLHS <- data.frame(sigmaL=1:n,vL1=1:n,f=1:n,p=1:n,ARI0=1:n,
+                      q=1:n,g=1:n,sigmaF=1:n,r1=1:n,r0=1:n,
+                      mud=1:n,x=1:n,vL0=1:n,phi=1:n,e0=1:n,
+                      e1=1:n)
+					  

### 2013-09-08 in_progress/models/sensitivityAnalysis/hillFunctionsLHS.R
fixed minor error in incResult

@@ -218,7 +218,7 @@ costActiveResult <- rep(0,n)
 costTotalResult <- rep(0,n)
 for(i in 1:n) {
     temp <- hill(i)
-    incResult <- generateIncidence(temp)
+    incResult[i] <- generateIncidence(temp)
     costLatentResult[i] <- temp['cLatent']
     costActiveResult[i] <- temp['cActive']
     costTotalResult[i]  <- temp['cTotal']

### 2013-09-08 in_progress/models/sensitivityAnalysis/hillConstantsLHS.R
changed times vector so no intermediate values are recorded (slight speedup)

@@ -120,4 +120,4 @@ for(i in 1:n){
   # randLHS$e1[i]     <- uniformRandLHS[i,16]*(0.15)  + 0.85               #Uniform(0.85,1)
 }
 
-save(randLHS, file = 'randLHS.RData')
+#save(randLHS, file = 'randLHS.RData')

### 2013-09-08 in_progress/models/sensitivityAnalysis/hillFunctionsLHS.R

@@ -181,24 +181,18 @@ hill <- function(i,transmission=1,incLTBI=1,initial=cutoffT,final=totT){
 	# parameters['beta'] <- ARI0/(c00*P$I0[1]/P$N0[1] + c01*P$I1[1]/P$N1[1])
 	# return(parameters)
   # })
-  # This next line is a temporary fix to get sane values... the real problem is
-  # probably in the formula for beta above
-  # print(parameters)
-  # parameters['beta'] <- 10.39
   
   # recursive=TRUE collapses dataframe to labeled vector
   initv <- c(P[initial,], recursive=TRUE)
-  #initv <- c(P[1,], recursive=TRUE)
   # times = data points to be calculuated
-  times <- (initial:final)*deltaT
+  #times <- (initial:final)*deltaT
+  times <- c(initial,final)*deltaT
   
   # compute master results
   mres <- lsoda(initv, times, Ddt, parameters)
   # mres[,-1] = mres without 1st column
-  # print(P[final,])
-  # print(mres[final,])
-  return(mres[final,-1])
-  #return(P$cLatent[final])
+  #return(mres[final,-1])
+  return(mres[2,-1])
 }
 
 generateIncidence <- function(dataSet) {
@@ -207,7 +201,7 @@ generateIncidence <- function(dataSet) {
     #IN1   <- 1e6 * (vF*dataSet$F1 + vL1*dataSet$L1)/dataSet$N1
     INall <- 1e6 * (vF*(dataSet['F0'] + dataSet['F1']) + vL0*dataSet['L0'] + vL1*dataSet['L1'])/(dataSet['N0'] + dataSet['N1'])
     return(INall)
-	  #return(data.frame(IN0,IN1,INall))
+    #return(data.frame(IN0,IN1,INall))
   })
 }
 

### 2013-09-09 in_progress/presentations/paper/draft.tex
worked on adding appendix

@@
 \end{table}
-
+Several other intervention strategies analyzed by the Hill Model were refined
+with the Extended Hill, and economic properties about each of them were tracked.
+The results for these interventions, which are less effective than curing
+entering LTBI cases across the board, are given in the appendix. 
 \subsection{Agent Based Evaluation}
@@
 examine the effects drug-resistant TB will have on US TB dynamics. 
+\section{Appendix}
+\subsection{Hill Constants}
+Below, we detail some of the relevant constants in the Basic Hill Model. A full
+listing of constants used in the original Hill Model can be found in CITATION!
+\begin{figure}[h]
+  \begin{center}
+    \tiny{
+    \begin{verbatim}
+sigmaLBase  <- 0.057
+fBase       <- 0.187
+transBase   <- 1
+incLTBIBase <- 1
+
+#Treatment Effectiveness Data:
+probHosp      <- .49 #Probability of hospitalization for active TB treatment
+efficacyLTBI  <- .9  #LTBI treatement efficacy
+adherenceLTBI <- .64 #LTBI treatment adherence
+probLTBItreatsuccess <- efficacyLTBI*adherenceLTBI
+
+#Cost Parameter Values: 
+costtb   <- 2985   #TB treatment cost w/o hopsitalization <- Dylan supp. p.11-12
+costhosp <- 25495  #TB treatment cost w/ hospitalization  <- Dylan supp. p.10
+costLTBI <- 403.45 #LTBI treatment cost
+Ct       <- costtb*(1-probHosp) + costhosp*probHosp #Cost of active TB treatment
+Cl       <- costLTBI/probLTBItreatsuccess           #Cost of LTBI treatment
+
+parms <- c(
+mu0   = 1/78,      #Natural mortality rate USB per year
+mu1   = 1/53,      #Natural mortality rate FB per year
+ro    = 0.018,     #USB birth rate per year
+alpha = 0.005,     #FB arrival rate per year
+p     = 0.103,     #Fraction of new infections which are acute (fast
+progressors)
+vF    = 1.5,       #Progression rate of acute infection per year
+l0    = 0.015,     #Prevalence of LTBI in the USB population in 2000
+l1    = 0.211,     #Prevalence of LTBI in the FB population in 2000: 
+r0    = 0.667,     #Fraction of cases due to reactivation in the USB population
+r1    = 0.780,     #Fraction of cases due to reactivation in the FB population
+vL0   = 0.0014,    #Progression rate for reactivation (chronic LTBI) in the USB
+population per year
+vL1   = 0.0010,    #Progression rate for reactivation (chronic LTBI) in the FB
+population per year
+q     = 0.708,     #Fraction of infections progressing to infectious disease
+mud   = 0.115,     #Mortality rate due to TB per year
+x     = 0.111,     #Fraction of re-infected chronic LTBI moving to acute
+infection
+ARI0  = 0.030/100, #Annual risk of infection for USB in 2000
+beta  = 10.39,     #Effective contact rate per year
+e0    = 0.965,     #Fraction of preferred contacts with own population for USB
+e1    = 0.985,     #Fraction of preferred contacts with own population for FB
+g     = 0.0047,    #Fraction of FB arrivals with LTBI who are fast progressors
+phi0  = 1.114,     #Cumulative fraction self-cure and treatment of active
+disease for both populations pre year RATES (USB)
+phi1  = 1.167,     #Cumulative fraction self-cure and treatment of active
+disease for both populations pre year RATES (FB)
+sigmaF0 = 1.296,   #Cumulative fraction of treatment for acute infection for
+both populations per year RATES (USB)
+sigmaF1 = 1.301,   #Cumulative fraction of treatment for acute infection for
+both populations per year RATES (FB)
+sigmaLBase = sigmaLBase, #Treatment rate for chronic LTBI per year
+fBase = fBase,      #Fraction of FB arrivals with LTBI
+
+#2010 New Cases in Population i (millions)
+#source: http://www.cdc.gov/mmwr/preview/mmwrhtml/mm5105a3.htm
+newCases0 = .008714,  #US-born
+newCases1 = .007554,  #Foreign-born
+
+CtBase = Ct,
+ClBase = Cl
+)
+    \end{verbatim}
+  }
+  \end{center}
+  \caption{A list of relevant constants in the Basic \& Extended Hill Model}
+  \label{fig:basicHillConstants}
+\end{figure}<++>
+\subsection{The Extended Hill Equations}
+Below, we detail the full equations used in the extended hill model. These
+equations extend those used in the standard Hill Model. In many cases, the
+equations of the Hill model were split into their component parts, which could
+then be tracked separately. 
+\begin{figure}[h]
+  \begin{center}
+  \tiny{
+    \begin{verbatim}
+discV   <- 1/(1.03^t)  #amount costs, health states discount constant
+
+#parameter values initialized for each time step
+c01          <- (1-e0)*((1-e1)*N1)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with FB individuals  (USB)
+c00          <- 1 - c01                                          #proportion of contacts made with USB individuals (USB)
+c10          <- (1-e1)*((1-e0)*N0)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with USB individuals (FB)
+c11          <- 1 - c10                                          #proportion of contacts made with FB individuals  (FB)
+dLTBIEn      <- f*alpha*(N0+N1)                                  #FB arrivals with LTBI entering
+dnatdeath0   <- mu0 * N0                                         #Natural deaths (USB)
+dnatdeath1   <- mu1 * N1                                         #Natural deaths (FB)
+dtbdeath0    <- mud * (I0 + J0)                                  #TB deaths (USB)
+dtbdeath1    <- mud * (I1 + J1)                                  #TB deaths (FB)
+dtbdeathD0   <- discV * dtbdeath0                                #TB deaths with discounting (USB)
+dtbdeathD1   <- discV * dtbdeath1                                #TB deaths with discounting (FB)
+dprogAcute0  <- vF*F0                                            #Acute LTBI progressions to Active TB disease (USB)
+dprogAcute1  <- vF*F1                                            #Acute LTBI progressions to Active TB disease (FB)
+dprogChron0  <- vL0*L0                                           #Chronic LTBI progressions to Active TB disease (USB)
+dprogChron1  <- vL1*L1                                           #Chronic LTBI progressions to Active TB disease (FB)
+dprogTotal0  <- dprogAcute0 + dprogChron0                        #Progression to Active TB (USB)
+dprogTotal1  <- dprogAcute1 + dprogChron1                        #Progression to Active TB (FB)
+dprogTotalD0 <- discV * dprogTotal0                              #Progression to Active TB with discounting (USB)
+dprogTotalD1 <- discV * dprogTotal1                              #Progression to Active TB with discounting (FB)
+lambda0      <- transmission*(beta*(c00*(I0/N0) + c01*(I1/N1)))  #Forces of Infection (USB)
+lambda1      <- transmission*(beta*(c10*(I0/N0) + c11*(I1/N1)))  #Forces of Infection (FB)
+dexogenous0	 <- x*p*lambda0*L0                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (USB)
+dexogenous1  <- x*p*lambda1*L1                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (FB)
+dInterventionCost <- discV * (iCnewCases*1e6*(dprogTotal0+dprogTotal1) + iCtotPop*1e6*(N0+N1) + iCLTBIEn*1e6*dLTBIEn*(1-incLTBI))
+
+#Difference Equations (USB)
+dS0 <- ro*(N0+N1) + sigmaF0*F0 + sigmaL*L0 + phi0*(I0+J0) - lambda0*S0 - mu0*S0
+dF0 <- p*lambda0*S0 + dexogenous0 - (mu0 + vF + sigmaF0)*F0
+dL0 <- (1-p)*lambda0*S0 - dexogenous0 - (mu0 + vL0 + sigmaL)*L0
+dI0 <- q*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*I0
+dJ0 <- (1-q)*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*J0
+
+#Difference Equations (FB)
+dS1 <- (1-incLTBI)*dLTBIEn+(1-f)*alpha*(N0+N1) + sigmaF1*F1 + sigmaL*L1 + phi1*(I1 + J1) - lambda1*S1 - mu1*S1
+dF1 <- g*p*dLTBIEn*incLTBI + p*lambda1*S1 + dexogenous1 - (mu1 + vF + sigmaF1)*F1
+dL1 <- (1-g*p)*dLTBIEn*incLTBI + (1-p)*lambda1*S1 - dexogenous1 - (mu1 + vL1 +sigmaL)*L1
+dI1 <- q*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*I1
+dJ1 <- (1-q)*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*J1
+
+dN0 <- dS0 + dF0 + dL0 + dI0 + dJ0
+dN1 <- dS1 + dF1 + dL1 + dI1 + dJ1
+
+#Cost calculations
+dcL0 <- discV * Cl * sigmaL  * 1e6 * L0                    #cost for Chronic LTBI cures      (USB)
+dcF0 <- discV * Cl * sigmaF0 * 1e6 * F0                    #cost for Acute LTBI cures        (USB)
+dcI0 <- discV * Ct * q*(dprogAcute0 + dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
+dcJ0 <- discV * Ct * (1-q)*(dprogAcute0 + dprogChron0) * 1e6 #cost for Non-Infectious TB cures (USB)
+dcI0dL0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
+dcI0dF0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
+dcJ0dL0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
+dcJ0dF0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
+dcL1 <- discV * Cl * sigmaL  * 1e6 * L1                    #cost for Chronic LTBI cures      (FB)
+dcF1 <- discV * Cl * sigmaF1 * 1e6 * F1                    #cost for Acute LTBI cures        (FB)
+dcI1 <- discV * Ct * q*(dprogAcute1 + dprogChron1) * 1e6     #cost for Infectious TB cures     (FB)
+dcJ1 <- discV * Ct * (1-q)*(dprogAcute1 + dprogChron1) * 1e6 #cost for Non-Infectious TB cures (FB)
+dcI1dL1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
+dcI1dF1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
+dcJ1dL1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
+dcJ1dF1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
+dcN0 <- dcF0 + dcL0 + dcI0 + dcJ0                            #Total cost for all treatments (USB)
+dcN1 <- dcF1 + dcL1 + dcI1 + dcJ1                            #Total cost for all treatments (FB)
+    \end{verbatim}
+  }
+  \end{center}
+  \label{fig:extendedHillEqs}
+  \caption{
+    The equations defining the Extended Hill Model, shown in \texttt{R} syntax.
+    In this model, compartments share the same names as they did in the Hill
+    Model, \emph{i.e.} \texttt{S1} is the Foreign Born susceptible population. 
+  }
+\end{figure}
+Here, a continuous discounting approximation is used to a discount rate of $3\%$
+yearly, found via $discV$. In many of the differential equations, a small $c$ is
+used to denote \emph{cost of}. 
+\subsection{Estimations for Infectious Rates of FB and USB}
+Colin to add. 
+\subsection{Statistical Qualities of the Agent Based Model}
+\subsection{Finer Intervention Analysis}
+\subsection{Sensitivity Analysis}
 \end{document}

### 2013-10-05 in_progress/presentations/paper/sensitivity_analysis/sensitivityAnalysis.tex
added PRCC tables to sensitivity analysis write-up

@@
 For the deterministic model, we used Latin Hypercube Sampling to test the sensitivity of our model to input parameters from the Hill model and estimates for treatment costs.
-We also
-performed extensive multivariate analysis on the economic components of our deterministic model which go beyond the original Hill model, including treatment costs and intervention costs to reduce incoming LTBI.
 For the stochastic model, we fixed all input parameters and estimates for treatment costs to default values, and ran the model for 2,000 trials.
@@
 \subsection{Latin Hypercube Sampling}
-We computed partial rank correlation coefficients for each of the initial parameters and treatment costs, and validated the results against the Sensitivity Analysis in the Hill model.  \\
+Following the example of the Hill model, we generated a Latin Hypercube Sample varying 18 of the input parameters.
+From these parameters, 16 are identical to the input parameters varied in the sensitivity analysis of the original Hill model, and the remaining two parameters, $C_{t}$ and $C_{l}$, are variables for the average cost of Active and Latent TB treatment in the US.
+Probability distributions for the original 16 parameters of the Hill model were all set to be Triangular, with mode at the best fit value and end points at the 2.5 and 97.5 percentile values reported in the Hill model.
+Probability distributions for $C_{t}$ and $C_{l}$ were set to be Uniform, with range +/- 10\% of the estimated value.
+
+With a random Latin Hypercube Sample of size n=100,000, we computed partial rank correlation coefficients (PRCC) for each of the initial parameters and treatment costs, according to four different outcomes: 1) projected annual incidence in 2100 in the overall population, 2) projected cumulative cost of Latent TB treatments by 2100, 3) projected cumulative cost of Active TB treatments by 2100, 4) projected cumulative total cost of TB treatments by 2100.
+For outcome 1, PRCC values are shown alongside PRCC values computed in the original Hill model for the same outcome in Table 1, showing the closeness of our findings to the sensitivity results of the original Hill model.
+PRCC values for the remaining outcomes are reported in Table 2.
+
+\begin{table}
+\centering
+\begin{tabular}{l r r}
+\hline\hline\\
+Parameter & Extended Hill Model & Original Hill model \\ [0.5ex]
+\hline\\
+$\sigma_{L}$  & -0.9303 & -0.9381 \\
+$v^{L}_{1}$   & 0.7871  & 0.8309 \\
+$f$                 & 0.7050  & 0.8072 \\
+$p$                & 0.8369  & 0.6100 \\
+$ARI_{0}$      & 0.5950  & 0.4939 \\
+$q$                & 0.5797  & 0.4543 \\
+$g$                & 0.6122  & 0.4517 \\
+$\sigma_{F}$ & -0.4911 & -0.3772 \\
+$r_{1}$          & 0.0028  & -0.1109 \\
+$r_{0}$          & 0.0018  & 0.0760 \\
+$\mu_{d}$      & 0.0923 & 0.0513 \\
+$x$                 & 0.0999 & 0.0345 \\
+$v^{L}_{0}$    & 0.0133 & 0.0266 \\
+$\phi$             & 0.0082 & 0.0177 \\
+$e_{0}$          & 0.0178 & -0.0072 \\
+$e_{1}$          & 0.1154 & 0.0046 \\
+$C_{t}$          & -0.0023 & N/A \\
+$C_{l}$           & 0.0009 & N/A \\ [1ex]
+\hline
+\end{tabular}\\[1ex]
+
+{\bf Table 1.} PRCC values for projected annual incidence in 2100
+ in the overall population, alongside corresponding values from the
+original Hill model.
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{l r r r}
+\hline\hline\\
+Parameter & Latent & Active & Total\\ [0.5ex]
+\hline\\
+$\sigma_{L}$  & 0.9612  & -0.9284 & 0.4169 \\
+$v^{L}_{1}$   & -0.4190 & 0.6470  & 0.3533 \\
+$f$                 & 0.7467  & 0.5493  & 0.8083 \\
+$p$                & 0.3371  & 0.8810  & 0.8776 \\
+$ARI_{0}$      & 0.3920  & 0.6728  & 0.7337 \\
+$q$                & 0.3837  & 0.6573  & 0.7200 \\
+$g$                & 0.1120  & 0.5369  & 0.5182 \\
+$\sigma_{F}$ & -0.1138 & -0.5631 &-0.5435 \\
+$r_{1}$          & 0.1253 &  0.0658  & 0.1401 \\
+$r_{0}$          & 0.1325  & 0.0878  & 0.1658 \\
+$\mu_{d}$      & 0.0249 & 0.0560  & 0.0613 \\
+$x$                 & 0.0214 & 0.1282  & 0.1253 \\
+$v^{L}_{0}$   & -0.3103 & 0.0502  &-0.1867 \\
+$\phi$            & -0.0023 & -0.0102 &-0.0107 \\
+$e_{0}$          & 0.0081 & 0.0253   & 0.0269 \\
+$e_{1}$          & 0.0804 & 0.1653   & 0.1926 \\
+$C_{t}$          & 0.0011 & 0.7024   & 0.6385 \\
+$C_{l}$           & 0.8515 & 0.0013  & 0.7598 \\ [1ex]
+\hline
+\end{tabular}\\[1ex]
+
+{\bf Table 2.} PRCC values for cumulative US Health Care system costs from 
+Latent TB treatment, Active TB treatment, and Total treatment costs
+\end{table}
 

### 2013-10-05 in_progress/models/sensitivityAnalysis/hillConstantsLHS.R

@@ -2,7 +2,7 @@ library(lhs)
 library(triangle)
 
 #Uniform Latin Hypercube with 18 parameters, resolution: n
-n <- 100  #number of divisions in probability distributions
+n <- 100000  #number of divisions in probability distributions
 uniformRandLHS <- randomLHS(n,18)
 
 sigmaLBase  <- 0.057
@@ -62,8 +62,8 @@ ClBase = Cl
 )
 
 #Ordered by PRCC absolute value from Hill's sensitivity analysis
-randLHS <- data.frame(sigmaL=1:n,vL1=1:n,f=1:n,p=1:n,beta=1:n,
-                      #ARI0=1:n,
+randLHS <- data.frame(sigmaL=1:n,vL1=1:n,f=1:n,p=1:n,#beta=1:n,
+                      ARI0=1:n,
                       q=1:n,g=1:n,sigmaF=1:n,r1=1:n,r0=1:n,
                       mud=1:n,x=1:n,vL0=1:n,phi=1:n,e0=1:n,
                       e1=1:n,Ct=1:n,Cl=1:n)
@@ -76,16 +76,18 @@ randLHS <- data.frame(sigmaL=1:n,vL1=1:n,f=1:n,p=1:n,beta=1:n,
 # given by the best fit.  (See Table 1 in Hill paper)
 # Probability distributions used in the original Hill
 # model are given below for each parameter, commented out.
+print("n = ")
+print(n)
 for(i in 1:n){
   # Track progress 
-  #if(i%%(n/100)==0) {print(i/(n/100))}
+  print(i)#if(i%%(n/100)==0) {print(i/(n/100))}
   #Original Hill parameters (best-fit distributions)
   randLHS$sigmaL[i] <- qtriangle(uniformRandLHS[i,1],0.015,0.086,0.057)       #Triangle(0.015,0.057,0.086)
   randLHS$vL1[i]    <- qtriangle(uniformRandLHS[i,2],0.0009,0.0014,0.0010)    #Triangle(0.0009,0.0010,0.0014)
   randLHS$f[i]      <- qtriangle(uniformRandLHS[i,3],0.157,0.232,0.187)       #Triangle(0.157,0.187,0.232)
   randLHS$p[i]      <- qtriangle(uniformRandLHS[i,4],0.053,0.137,0.103)       #Triangle(0.053,0.103,0.137)
[…]

### 2013-10-05 in_progress/models/sensitivityAnalysis/hillFunctionsLHS.R

@@ -141,7 +141,7 @@ hill <- function(i,transmission=1,incLTBI=1,initial=cutoffT,final=totT){
   newCases1 = .007554  #Foreign-born
 
   # set values in parameters
-  parameters <- c(randLHS[i,],phi0=0,phi1=0,sigmaF0=0,sigmaF1=0,#beta=0,
+  parameters <- c(randLHS[i,],phi0=0,phi1=0,sigmaF0=0,sigmaF1=0,beta=0,
                   mu0=mu0,mu1=mu1,ro=ro,alpha=alpha,vF=vF,transmission=1,recursive=TRUE)
   parameters <- with(as.list(randLHS[i,]), {
     parameters['phi0'] <- phi*(mu0 + mud)/(1-phi)
@@ -175,16 +175,17 @@ hill <- function(i,transmission=1,incLTBI=1,initial=cutoffT,final=totT){
   })
   
   # Set beta
-  # parameters <- with(as.list(parameters), {
-    # c01  <- (1-e0)*((1-e1)*P$N1[1])/((1-e0)*P$N0[1] + (1-e1)*P$N1[1])       #proportion of contacts made with FB individuals  (USB)
-    # c00  <- 1 - c01                                                         #proportion of contacts made with USB individuals (USB)
-	# parameters['beta'] <- ARI0/(c00*P$I0[1]/P$N0[1] + c01*P$I1[1]/P$N1[1])
-	# return(parameters)
-  # })
+  parameters <- with(as.list(parameters), {
+    c01  <- (1-e0)*((1-e1)*P$N1[1])/((1-e0)*P$N0[1] + (1-e1)*P$N1[1])       #proportion of contacts made with FB individuals  (USB)
+    c00  <- 1 - c01                                                         #proportion of contacts made with USB individuals (USB)
+	#parameters['beta'] <- ARI0/(c00*P$I0[1]/P$N0[1] + c01*P$I1[1]/P$N1[1])
+	parameters['beta'] <- ARI0*((mu0 + mud + phi0)/0.708)/(c00*(35/1000000) + c01*(273/1000000)) 
+	return(parameters)
+  })
   # This next line is a temporary fix to get sane values... the real problem is
   # probably in the formula for beta above
   # print(parameters)
-  parameters['beta'] <- 10.39
+  # parameters['beta'] <- 10.39
   
[…]

### 2013-10-05 in_progress/presentations/paper/sensitivity_analysis/sensitivityAnalysis.tex
added table of probability distributions to sensitivity analysis

--- 2013-08-12 in_progress/presentations/paper/sensitivity_analysis/sensitivityAnalysis.tex
@@
 \subsection{Latin Hypercube Sampling}
-We computed partial rank correlation coefficients for each of the initial parameters and treatment costs, and validated the results against the Sensitivity Analysis in the Hill model.  \\
+Following the example of the Hill model, we generated a Latin Hypercube Sample varying 18 of the input parameters.
+From these parameters, 16 are identical to the input parameters varied in the sensitivity analysis of the original Hill model, and the remaining two parameters, $C_{t}$ and $C_{l}$, are variables for the average cost of Active and Latent TB treatment in the US.
+Probability distributions for the original 16 parameters of the Hill model were all set to be Triangular, with mode at the best fit value and end points at the 2.5 and 97.5 percentile values reported in the Hill model.
+Probability distributions for $C_{t}$ and $C_{l}$ were set to be Uniform, with range +/- 10\% of the estimated value.
+All probabilty distributions used to generate the Latin Hypercube are listed in Table 1.\\
+
+\begin{table}
+\centering
+\begin{tabular}{l l}
+\hline\hline\\
+Parameter & Distribution\\ [0.5ex]
+\hline\\
+$\sigma_{L}$  & Tri(0.015,0.057,0.086) \\
+$v^{L}_{1}$   & Tri(0.0009,0.0010,0.0014) \\
+$f$                 & Tri(0.157,0.187,0.232) \\
+$p$                & Tri(0.053,0.103,0.137) \\
+$ARI_{0}$      & Tri(0.00021,0.00030,0.00030) \\
+$q$                & Tri(0.569,0.708,0.825) \\
+$g$                & Tri(0.0008,0.0047,0.0815)  \\
+$\sigma_{F}$ & Tri(0.419,0.461,0.574) \\
+$r_{1}$          & Tri(0.759,0.780,0.831) \\
+$r_{0}$          & Tri(0.623,0.667,0.694) \\
+$\mu_{d}$      & Tri(0.071,0.115,0.231) \\
+$x$                 & Tri(0.088,0.111,0.860) \\
+$v^{L}_{0}$   & Tri(0.0011,0.0014,0.0015) \\
+$\phi$            & Tri(0.861,0.897,0.938) \\
+$e_{0}$          & Tri(0.853,0.965,0.995) \\
+$e_{1}$          & Tri(0.877,0.985,0.999) \\
+$C_{t}$           & Uniform(12613,15416) \\
+$C_{l}$           & Uniform(630,770) \\ [1ex]
+\hline
+\end{tabular}\\[1ex]
+
+{\bf Table 1.} Probability distributions for model parameters, where Tri(x,y,z) denotes the 
+Triangular distribution with endpoints (x,z) and mode y.
+\end{table}
+
+With a random Latin Hypercube Sample of size n=100,000, we computed partial rank correlation coefficients (PRCC) for each of the initial parameters and treatment costs, according to four different outcomes: 1) projected annual incidence in 2100 in the overall population, 2) projected cumulative cost of Latent TB treatments by 2100, 3) projected cumulative cost of Active TB treatments by 2100, 4) projected cumulative total cost of TB treatments by 2100.
+For outcome 1, PRCC values are shown alongside PRCC values computed in the original Hill model for the same outcome in Table 2, showing the closeness of our findings to the sensitivity results of the original Hill model.
+PRCC values for the remaining outcomes are reported in Table 3.
+\\
+
+\begin{table}
+\centering
+\begin{tabular}{l r r}
+\hline\hline\\
+Parameter & Extended Hill Model & Original Hill model \\ [0.5ex]
+\hline\\
+$\sigma^{L}$  & -0.9303 & -0.9381 \\
+$v^{L}_{1}$   & 0.7871  & 0.8309 \\
+$f$                 & 0.7050  & 0.8072 \\
+$p$                & 0.8369  & 0.6100 \\
+$ARI_{0}$      & 0.5950  & 0.4939 \\
+$q$                & 0.5797  & 0.4543 \\
+$g$                & 0.6122  & 0.4517 \\
+$\sigma^{F}$ & -0.4911 & -0.3772 \\
+$r_{1}$          & 0.0028  & -0.1109 \\
+$r_{0}$          & 0.0018  & 0.0760 \\
+$\mu_{d}$      & 0.0923 & 0.0513 \\
+$x$                 & 0.0999 & 0.0345 \\
+$v^{L}_{0}$    & 0.0133 & 0.0266 \\
+$\phi$             & 0.0082 & 0.0177 \\
+$e_{0}$          & 0.0178 & -0.0072 \\
+$e_{1}$          & 0.1154 & 0.0046 \\
+$C_{t}$          & -0.0023 & N/A \\
+$C_{l}$           & 0.0009 & N/A \\ [1ex]
+\hline
+\end{tabular}\\[1ex]
+
+{\bf Table 2.} PRCC values for projected annual incidence in 2100
+ in the overall population, alongside corresponding values from the
+original Hill model.
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{l r r r}
+\hline\hline\\
+Parameter & Latent Costs & Active Costs & Total Costs\\ [0.5ex]
+\hline\\
+$\sigma^{L}$  & 0.9612  & -0.9284 & 0.4169 \\
+$v^{L}_{1}$   & -0.4190 & 0.6470  & 0.3533 \\
+$f$                 & 0.7467  & 0.5493  & 0.8083 \\
+$p$                & 0.3371  & 0.8810  & 0.8776 \\
+$ARI_{0}$      & 0.3920  & 0.6728  & 0.7337 \\
+$q$                & 0.3837  & 0.6573  & 0.7200 \\
+$g$                & 0.1120  & 0.5369  & 0.5182 \\
+$\sigma^{F}$ & -0.1138 & -0.5631 &-0.5435 \\
+$r_{1}$          & 0.1253 &  0.0658  & 0.1401 \\
+$r_{0}$          & 0.1325  & 0.0878  & 0.1658 \\
+$\mu_{d}$      & 0.0249 & 0.0560  & 0.0613 \\
+$x$                 & 0.0214 & 0.1282  & 0.1253 \\
+$v^{L}_{0}$   & -0.3103 & 0.0502  &-0.1867 \\
+$\phi$            & -0.0023 & -0.0102 &-0.0107 \\
+$e_{0}$          & 0.0081 & 0.0253   & 0.0269 \\
+$e_{1}$          & 0.0804 & 0.1653   & 0.1926 \\
+$C_{t}$          & 0.0011 & 0.7024   & 0.6385 \\
+$C_{l}$           & 0.8515 & 0.0013  & 0.7598 \\ [1ex]
+\hline
+\end{tabular}\\[1ex]
+
+{\bf Table 3.} PRCC values for cumulative US Health Care system costs from 
+Latent TB treatment, Active TB treatment, and Total treatment costs
+\end{table}
 

### 2013-10-05 in_progress/presentations/paper/sensitivity_analysis/sensitivityAnalysis.tex
added discussion of PRCC values to sensitivity analysis

@@
 \usepackage{graphicx}
+\usepackage{placeins}
 \graphicspath{{../figures/}}
@@
 For the stochastic model, we fixed all input parameters and estimates for treatment costs to default values, and ran the model for 2,000 trials.
+The model parameters and variable names referred to in this analysis are listed below, along with best-fit or estimated values.
+\\
+
+{\bf Original Hill Model Parameters}
+(USB = US born, FB = Foriegn born)
+\begin{enumerate} \itemsep 0em
+\item{$\sigma^{L}$ = 0.057 (Treatment rate for chronic LTBI)}
+\item{$v^{L}_{0}$   = 0.0014 (Progression rate for reactivation in the USB population)}
+\item{$v^{L}_{1}$  = 0.0010 (Progression rate for reactivation in the FB population)}
+\item{$f$                = 0.187 (Fraction of FB arrivals with LTBI)}
+\item{$p$               = 0.103 (Fraction of new infections which are acute)}
+\item{$ARI_{0}$     = 0.00030 (2000 Annual Risk of Infection, USB)}
+\item{$q$               = 0.708 (Fraction of infections progressing to infectious disease)}
+\item{$g$               = 0.0047 (Fraction of FB arrivals with LTBI who are fast progressors)}
+\item{$\sigma^{F}$ = 0.461 (Cumulative fraction of treatment for acute infection)}
+\item{$r_{0}$          = 0.667 (Fraction of cases due to reactivation in USB population)}
+\item{$r_{1}$          = 0.780 (Fraction of cases due to reactivation in FB population)}
+\item{$\mu^{d}$      = 0.115 (Mortality rate due to TB)}
+\item{$x$                 = 0.111 (Fraction of re-infected chronic LTBI moving to acute infection)}
+\item{$\phi$            = 0.897 (Cumulative fraction self-cure and treatment of active disease)}
+\item{$e_{0}$          = 0.965 (Fraction of preferred contacts within own population for USB)}
+\item{$e_{1}$          = 0.985 (Fraction of preferred contacts within own population for FB)}
+\end{enumerate}
+{\bf Additional Cost Parameters}
+\begin{enumerate} \itemsep 0em
+\item{$C_{A}$           = \$14,014.50 (Cost per Active TB treatment)}
+\item{$C_{L}$           = \$700 (Cost per Latent TB treatment)}
+\end{enumerate}
 
@@
 Following the example of the Hill model, we generated a Latin Hypercube Sample varying 18 of the input parameters.
-From these parameters, 16 are identical to the input parameters varied in the sensitivity analysis of the original Hill model, and the remaining two parameters, $C_{t}$ and $C_{l}$, are variables for the average cost of Active and Latent TB treatment in the US.
+From these parameters, 16 are identical to the input parameters varied in the sensitivity analysis of the original Hill model, and the remaining two parameters, $C_{A}$ and $C_{L}$, are variables for the average cost of Active and Latent TB treatment in the US.
 Probability distributions for the original 16 parameters of the Hill model were all set to be Triangular, with mode at the best fit value and end points at the 2.5 and 97.5 percentile values reported in the Hill model.
-Probability distributions for $C_{t}$ and $C_{l}$ were set to be Uniform, with range +/- 10\% of the estimated value.
+Probability distributions for $C_{A}$ and $C_{L}$ were set to be Uniform, with range +/- 10\% of the estimated value.
 All probabilty distributions used to generate the Latin Hypercube are listed in Table 1.\\
 
-\begin{table}
+\begin{table}[h]
 \centering
@@
 $r_{0}$          & Tri(0.623,0.667,0.694) \\
-$\mu_{d}$      & Tri(0.071,0.115,0.231) \\
+$\mu^{d}$      & Tri(0.071,0.115,0.231) \\
 $x$                 & Tri(0.088,0.111,0.860) \\
@@
 $e_{1}$          & Tri(0.877,0.985,0.999) \\
-$C_{t}$           & Uniform(12613,15416) \\
-$C_{l}$           & Uniform(630,770) \\ [1ex]
+$C_{A}$           & Uniform(12613,15416) \\
+$C_{L}$           & Uniform(630,770) \\ [1ex]
 \hline
@@
 
-\begin{table}
+\begin{table}[h]
 \centering
@@
 $r_{0}$          & 0.0018  & 0.0760 \\
-$\mu_{d}$      & 0.0923 & 0.0513 \\
+$\mu^{d}$      & 0.0923 & 0.0513 \\
 $x$                 & 0.0999 & 0.0345 \\
@@
 $e_{1}$          & 0.1154 & 0.0046 \\
-$C_{t}$          & -0.0023 & N/A \\
-$C_{l}$           & 0.0009 & N/A \\ [1ex]
+$C_{A}$          & -0.0023 & N/A \\
+$C_{L}$           & 0.0009 & N/A \\ [1ex]
 \hline
@@
 \end{table}
+
+From Table 2, we see that the PRCC values in the Extended Hill Model and the Original Hill Model match up reasonably well.
+In both cases, $\sigma^{L}$ is the most influential parameter, with PRCC values around -0.93.
+The cost parameters $C_{A}$ and $C_{L}$ have PRCC values close to zero, which is expected because varying the treatment costs should not affect the incidence rate of TB.
+Parameters in the original Hill model with small PRCC magnitudes (less than 0.15) also have small PRCC values in the extended model, while parameters with larger PRCC magnitudes (greater than 0.35) similarly have large PRCC values in the extended model.
+This validates the non-economic components of our model against the original Hill model.
+\\
+
+In Table 3, we see that the cost parameters $C_{A}$ and $C_{L}$ are highly correlated with Active treatment costs and Latent treatment costs respectively.
+These high PRCC values are expected because there is a linear relationship between $C_{A}$ and the cumulative Active treatment cost, and similarly for $C_{L}$ and the cumulative Latent treatment cost.
+In addition, we note that both $C_{A}$ and $C_{L}$ are influential in the total overall cost, with PRCC values of 0.6385 and 0.7598 respectively.
+Because the PRCC value for $C_{L}$ is greater here, despite the fact that $C_{A} > C_{L}$, we can infer that cumulative Latent TB treatment costs are projected to be greater than cumulative Active TB costs with these estimates for cost parameters, so $C_{L}$ is a more influential parameter for total cumulative treatment costs.
+\\
+
+Other variables with significant PRCC magnitudes (greater than 0.5) in Table 3 include $\sigma^{L}$, $v^{L}_{1}$, $f$, $p$, $ARI_{0}$, $q$, $g$, and $\sigma^{F}$.
+Two of these parameters, $\sigma^{L}$ and $v^{L}_{1}$, have relatively large PRCC magnitudes for both Latent and Active Costs, but smaller PRCC magnitudes for Total Costs.
+Because their PRCC values for each of these two outcomes is different in sign, the net change to the total cost is partially cancelled out, so these parameters have a reduced influence on final US healthcare system costs.
+On the other hand, parameters such as $f$ and $p$ have large positive PRCC values for both Latent Costs and Active Costs, and we observe large positive PRCC values for Total Costs as well.\\
+
+To gain insight about strategies to reduce the cost burden for TB in the US, we focus on the parameters with the greatest PRCC magnitudes for Total Cost aside from $C_{A}$ and $C_{L}$, namely $f$, $p$, $ARI_{0}$, and $q$.
+All of these parameter have PRCC magnitudes above 0.7, and are highly correlated with the total cost burden of TB borne by the US projected over the next 100 years.
+Out of these, $ARI_{0}$ is based on a historical fixed value, the Annual Risk of Infection among the US born population in the year 2000, and therefore is unchangeable under any intervention strategy.
+The parameters $p$ (the fraction of new infections which are acute) and $q$ (the fraction of infections progressing to infectious disease) are variables which depend on physiological disease dynamics, and may be altered with advances in medicine or mutations in the bacterial strains of TB.
+The parameter $f$ is the fraction of the FB arrivals with LTBI, which may vary depending on US immigration policies and medical practices for new immigrants.
+These results suggest that treating cases of LTBI among new FB arrivals may be the most cost efficient intervention strategy to reduce the projected cost burden for TB in the US, under the assumptions of the Hill model.
+\\
 
@@
 $e_{1}$          & 0.0804 & 0.1653   & 0.1926 \\
-$C_{t}$          & 0.0011 & 0.7024   & 0.6385 \\
-$C_{l}$           & 0.8515 & 0.0013  & 0.7598 \\ [1ex]
+$C_{A}$          & 0.0011 & 0.7024   & 0.6385 \\
+$C_{L}$           & 0.8515 & 0.0013  & 0.7598 \\ [1ex]
 \hline

### 2013-10-05 in_progress/presentations/paper/sensitivity_analysis/sensitivityAnalysis.tex
fixed graph placement in sensitivity analysis

@@
 
-In Table 3, we see that the cost parameters $C_{A}$ and $C_{L}$ are highly correlated with Active treatment costs and Latent treatment costs respectively.
-These high PRCC values are expected because there is a linear relationship between $C_{A}$ and the cumulative Active treatment cost, and similarly for $C_{L}$ and the cumulative Latent treatment cost.
-In addition, we note that both $C_{A}$ and $C_{L}$ are influential in the total overall cost, with PRCC values of 0.6385 and 0.7598 respectively.
-Because the PRCC value for $C_{L}$ is greater here, despite the fact that $C_{A} > C_{L}$, we can infer that cumulative Latent TB treatment costs are projected to be greater than cumulative Active TB costs with these estimates for cost parameters, so $C_{L}$ is a more influential parameter for total cumulative treatment costs.
-\\
-
-Other variables with significant PRCC magnitudes (greater than 0.5) in Table 3 include $\sigma^{L}$, $v^{L}_{1}$, $f$, $p$, $ARI_{0}$, $q$, $g$, and $\sigma^{F}$.
-Two of these parameters, $\sigma^{L}$ and $v^{L}_{1}$, have relatively large PRCC magnitudes for both Latent and Active Costs, but smaller PRCC magnitudes for Total Costs.
-Because their PRCC values for each of these two outcomes is different in sign, the net change to the total cost is partially cancelled out, so these parameters have a reduced influence on final US healthcare system costs.
-On the other hand, parameters such as $f$ and $p$ have large positive PRCC values for both Latent Costs and Active Costs, and we observe large positive PRCC values for Total Costs as well.\\
-
-To gain insight about strategies to reduce the cost burden for TB in the US, we focus on the parameters with the greatest PRCC magnitudes for Total Cost aside from $C_{A}$ and $C_{L}$, namely $f$, $p$, $ARI_{0}$, and $q$.
-All of these parameter have PRCC magnitudes above 0.7, and are highly correlated with the total cost burden of TB borne by the US projected over the next 100 years.
-Out of these, $ARI_{0}$ is based on a historical fixed value, the Annual Risk of Infection among the US born population in the year 2000, and therefore is unchangeable under any intervention strategy.
-The parameters $p$ (the fraction of new infections which are acute) and $q$ (the fraction of infections progressing to infectious disease) are variables which depend on physiological disease dynamics, and may be altered with advances in medicine or mutations in the bacterial strains of TB.
-The parameter $f$ is the fraction of the FB arrivals with LTBI, which may vary depending on US immigration policies and medical practices for new immigrants.
-These results suggest that treating cases of LTBI among new FB arrivals may be the most cost efficient intervention strategy to reduce the projected cost burden for TB in the US, under the assumptions of the Hill model.
-\\
-
-\begin{table}
+\begin{table}[h]
 \centering
@@
 
+In Table 3, we see that the cost parameters $C_{A}$ and $C_{L}$ are highly correlated with Active treatment costs and Latent treatment costs respectively.
+These high PRCC values are expected because there is a linear relationship between $C_{A}$ and the cumulative Active treatment cost, and similarly for $C_{L}$ and the cumulative Latent treatment cost.
+In addition, we note that both $C_{A}$ and $C_{L}$ are influential in the total overall cost, with PRCC values of 0.6385 and 0.7598 respectively.
+Because the PRCC value for $C_{L}$ is greater here, despite the fact that $C_{A} > C_{L}$, we can infer that cumulative Latent TB treatment costs are projected to be greater than cumulative Active TB costs with these estimates for cost parameters, so $C_{L}$ is a more influential parameter for total cumulative treatment costs.
+\\
+
+Other variables with significant PRCC magnitudes (greater than 0.5) in Table 3 include $\sigma^{L}$, $v^{L}_{1}$, $f$, $p$, $ARI_{0}$, $q$, $g$, and $\sigma^{F}$.
+Two of these parameters, $\sigma^{L}$ and $v^{L}_{1}$, have relatively large PRCC magnitudes for both Latent and Active Costs, but smaller PRCC magnitudes for Total Costs.
+Because their PRCC values for each of these two outcomes is different in sign, the net change to the total cost is partially cancelled out, so these parameters have a reduced influence on final US healthcare system costs.
+On the other hand, parameters such as $f$ and $p$ have large positive PRCC values for both Latent Costs and Active Costs, and we observe large positive PRCC values for Total Costs as well.\\
+
+To gain insight about strategies to reduce the cost burden for TB in the US, we focus on the parameters with the greatest PRCC magnitudes for Total Cost aside from $C_{A}$ and $C_{L}$, namely $f$, $p$, $ARI_{0}$, and $q$.
+All of these parameter have PRCC magnitudes above 0.7, and are highly correlated with the total cost burden of TB borne by the US projected over the next 100 years.
+Out of these, $ARI_{0}$ is based on a historical fixed value, the Annual Risk of Infection among the US born population in the year 2000, and therefore is unchangeable under any intervention strategy.
+The parameters $p$ (the fraction of new infections which are acute) and $q$ (the fraction of infections progressing to infectious disease) are variables which depend on physiological disease dynamics, and may be altered with advances in medicine or mutations in the bacterial strains of TB.
+The parameter $f$ is the fraction of the FB arrivals with LTBI, which may vary depending on US immigration policies and medical practices for new immigrants.
+These results suggest that treating cases of LTBI among new FB arrivals may be the most cost efficient intervention strategy to reduce the projected cost burden for TB in the US, under the assumptions of the Hill model.
+\\
+
 %Add table of distributions for initial parameters and treatment costs
@@
 
-\subsection{Variability due to Uncertainty of Treatment Costs}
-Next, we performed more extensive multivariate analysis on the economic part of the deterministic model.
+%\subsection{Variability due to Uncertainty of Treatment Costs}
+%Next, we performed more extensive multivariate analysis on the economic part of the deterministic model.
 Keeping all of the input parameters from the Hill model at their default values, we ran the model approximately two million times, varying the cost of treatment for LTBI and Active TB and the treatment rate for incoming LTBI.
@@
 
-\subsection{Variability of Intervention Cost for Treating Cases of Incoming LTBI}
-Similarly, we performed extensive multivariate analysis on the intervention cost for reducing incoming LTBI.
+%\subsection{Variability of Intervention Cost for Treating Cases of Incoming LTBI}
+%Similarly, we performed extensive multivariate analysis on the intervention cost for reducing incoming LTBI.
 With all input parameters from the Hill model at their default values, we ran the model approximately two million times, varying the treatment rate, incidence, and cost to cure for incoming LTBI.

### 2013-10-07 in_progress/presentations/paper/draft.tex
added abstract to paper

@@
 \maketitle
+
+\section{Abstract}
+An extended epidemiological model for Tuberculosis in the US was developed, based on an existing
+epidemiological model developed in 2012 by the Centers for Disease Control and Prevention.  
+Economic parameters to track the cost burden of TB for the US health care system were added,
+and an agent-based stochastic version of the model was implemented.  The sensitivity of the extended
+model to changes in parameters was analyzed, and the percentage of foreign-born immigrants with
+LTBI appears to be a highly influential parameter in the model.  Intervention strategies to reduce LTBI
+among foreign-born arrivals were evaluated, and estimates of the cost per case averted were found.
 

### 2013-10-13 in_progress/presentations/paper/draft.tex
added sensitivity analysis section to paper, updated basic reproduction number section

@@
 The basic reproduction number of FB or USB cases of infectious TB was also
-estimated by this system. From a theoretical perspective, we can think of the
+estimated by this system. Using the best-fit values of parameters from the 
+Hill model, we found the average number of secondary infections arising from
+a single case of infectious TB to be 0.423 and 0.370 for USB and FB populations
+respectively.  These values differ because in the model, there are different
+estimates for death rates and the rate of TB treatment and self-cure in the USB and FB populations, 
+so the average infectious period differs between the two populations.
+Extrapolating these results, we can think of the
 total number of secondary infections over 100 years due to a FB or USB
@@
 Presuming there are no overlaps in infectious contacts, if a single case of
-infectious TB in either population infects $p_f, p_u$ new cases in one year,
+infectious TB in either population infects $p_f, p_u$ new cases,
 respectively, then we can say that over the course of 100 years, the total
 number of cases infected will follow a geometric series. This analysis predicts
-that over 100 years, one USB infection will lead to $1.03$ subsequent infections,
-whereas one FB infection will lead to $.64$ subsequent infections. The full calculations
-are included in the appendix.  Experimentally, these data were also analyzed, 
-with results of $1.04$ and $.8$, respectively. WHAT CAUSES THIS DIFFERENCE? WE
-NEED TO ANSWER THAT.
+that over 100 years, one USB infection will lead to $1.04$ subsequent infections,
+whereas one FB infection will lead to $.83$ subsequent infections. Experimentally, 
+these data were also analyzed, with results of $1.03$ and $.64$, respectively. 
+Full calculations are included in the appendix.
 
@@
 \subsection{Sensitivity Analysis}
+To account for uncertainty of input parameter values and to gain insight about the
+most influential parameters in the model, we used Latin Hypercube Sampling to 
+analyze the deterministic model, implemented with the 'lhs' package in R.  We varied 
+the 16 parameters from the original Hill model according to triangular distributions centered
+around their best-fit values in the Hill model, and two additional treatment cost parameters according to uniform distributions.  We obtained similar results to the Hill model 
+analyzing non-economic outcomes, as expected for validation.  For economic 
+outcomes, we found the parameter $f$, the fraction of FB arrivals with LTBI,
+to be highly correlated with the projected overall cost burden of TB in the United States
+over the next 100 years.  Another highly influential parameter in the model was $\sigma^{L}$, 
+the treatment rate for chronic LTBI.  However, while increasing $\sigma^{L}$ significantly
+decreases the cost burden due to Active TB treatment, it increases the cost burden due to Latent TB treatment by a greater amount, given the model estimates that Latent TB treament and Active
+TB treatment health care costs are \$14,014.90 \$403.45 per case cured respectively.  
+A full description of the Latin Hypercube Sampling analysis and tables of Partial Rank Correlation Coefficient (PRCC) results for all parameters are given in the appendix, section X.
+
 \section{Discussion}
@@
 \subsection{Estimations for Infectious Rates of FB and USB}
-Colin to add. 
+
 \subsection{Statistical Qualities of the Agent Based Model}

### 2013-10-13 in_progress/presentations/paper/draft.tex
formatted paper

@@
 \usepackage[pdftex]{graphicx}
+\usepackage{enumerate,placeins}
 \graphicspath{{figures/}}
@@
 the 16 parameters from the original Hill model according to triangular distributions centered
-around their best-fit values in the Hill model, and two additional treatment cost parameters according to uniform distributions.  We obtained similar results to the Hill model 
+around their best-fit values, and two additional treatment cost parameters according to uniform distributions.  We obtained similar results to the Hill model 
 analyzing non-economic outcomes, as expected for validation.  For economic 
@@
 decreases the cost burden due to Active TB treatment, it increases the cost burden due to Latent TB treatment by a greater amount, given the model estimates that Latent TB treament and Active
-TB treatment health care costs are \$14,014.90 \$403.45 per case cured respectively.  
-A full description of the Latin Hypercube Sampling analysis and tables of Partial Rank Correlation Coefficient (PRCC) results for all parameters are given in the appendix, section X.
+TB treatment health care costs are approximately \$700 and \$14,000 per case cured respectively.  
+A full description of the Latin Hypercube Sampling analysis and tables of Partial Rank Correlation Coefficient (PRCC) results for all parameters are given in the Appendix, section 7.6.  \\
 
@@
 \subsection{Hill Constants}
-Below, we detail some of the relevant constants in the Basic Hill Model. A full
-listing of constants used in the original Hill Model can be found in CITATION!
+Below, we detail some of the relevant constants in the Basic Hill Model, and their best-fit
+values. A full listing of constants used in the original Hill Model can be found in <CITATION HERE> 
 \begin{figure}[h]
@@
 used to denote \emph{cost of}. 
+\FloatBarrier
 \subsection{Estimations for Infectious Rates of FB and USB}
@@
 \subsection{Finer Intervention Analysis}
-\subsection{Sensitivity Analysis}
+\subsection{Latin Hypercube Sampling}
+The model parameters and variable names referred to in this analysis are listed below, along with best-fit or estimated values.
+Following the example of the Hill model, we generated a Latin Hypercube Sample varying 18 of the input parameters.
+From these parameters, 16 are identical to the input parameters varied in the sensitivity analysis of the original Hill model, and the remaining two parameters, $C_{A}$ and $C_{L}$, are variables for the average cost of Active and Latent TB treatment in the US.
+Probability distributions for the original 16 parameters of the Hill model were all set to be Triangular, with mode at the best fit value and end points at the 2.5 and 97.5 percentile values reported in the Hill model.
+Probability distributions for $C_{A}$ and $C_{L}$ were set to be Uniform, with range +/- 10\% of the estimated value.
+All probabilty distributions used to generate the Latin Hypercube are listed in Table 1.\\
+
+\vspace{5mm}
+{\bf Original Hill Model Parameters} 
+(USB = US born, FB = Foriegn born)
+\begin{enumerate}[1.] \itemsep 0em
+\item{$\sigma^{L}$ = 0.057 (Treatment rate for chronic LTBI)}
+\item{$v^{L}_{0}$   = 0.0014 (Progression rate for reactivation in the USB population)}
+\item{$v^{L}_{1}$  = 0.0010 (Progression rate for reactivation in the FB population)}
+\item{$f$                = 0.187 (Fraction of FB arrivals with LTBI)}
+\item{$p$               = 0.103 (Fraction of new infections which are acute)}
+\item{$ARI_{0}$     = 0.00030 (2000 Annual Risk of Infection, USB)}
+\item{$q$               = 0.708 (Fraction of infections progressing to infectious disease)}
+\item{$g$               = 0.0047 (Fraction of FB arrivals with LTBI who are fast progressors)}
+\item{$\sigma^{F}$ = 0.461 (Cumulative fraction of treatment for acute infection)}
+\item{$r_{0}$          = 0.667 (Fraction of cases due to reactivation in USB population)}
+\item{$r_{1}$          = 0.780 (Fraction of cases due to reactivation in FB population)}
+\item{$\mu^{d}$      = 0.115 (Mortality rate due to TB)}
+\item{$x$                 = 0.111 (Fraction of re-infected chronic LTBI moving to acute infection)}
+\item{$\phi$            = 0.897 (Cumulative fraction self-cure and treatment of active disease)}
+\item{$e_{0}$          = 0.965 (Fraction of preferred contacts within own population for USB)}
+\item{$e_{1}$          = 0.985 (Fraction of preferred contacts within own population for FB)}
+\end{enumerate}
+\vspace{2mm}
+{\bf Additional Cost Parameters}
+\begin{enumerate}[1.] \itemsep 0em
+\item{$C_{A}$           = \$14,014.50 (Cost per Active TB treatment)}
+\item{$C_{L}$           = \$700 (Cost per Latent TB treatment)}
+\end{enumerate}
+\vspace{5mm}
+
+\begin{table}[h]
+\centering
+\begin{tabular}{l l}
+\hline\hline\\
+Parameter & Distribution\\ [0.5ex]
+\hline\\
+$\sigma_{L}$  & Tri(0.015,0.057,0.086) \\
+$v^{L}_{1}$   & Tri(0.0009,0.0010,0.0014) \\
+$f$                 & Tri(0.157,0.187,0.232) \\
+$p$                & Tri(0.053,0.103,0.137) \\
+$ARI_{0}$      & Tri(0.00021,0.00030,0.00030) \\
+$q$                & Tri(0.569,0.708,0.825) \\
+$g$                & Tri(0.0008,0.0047,0.0815)  \\
+$\sigma_{F}$ & Tri(0.419,0.461,0.574) \\
+$r_{1}$          & Tri(0.759,0.780,0.831) \\
+$r_{0}$          & Tri(0.623,0.667,0.694) \\
+$\mu^{d}$      & Tri(0.071,0.115,0.231) \\
+$x$                 & Tri(0.088,0.111,0.860) \\
+$v^{L}_{0}$   & Tri(0.0011,0.0014,0.0015) \\
+$\phi$            & Tri(0.861,0.897,0.938) \\
+$e_{0}$          & Tri(0.853,0.965,0.995) \\
+$e_{1}$          & Tri(0.877,0.985,0.999) \\
+$C_{A}$           & Uniform(12613,15416) \\
+$C_{L}$           & Uniform(630,770) \\ [1ex]
+\hline
+\end{tabular}\\[1ex]
+
+{\bf Table 1.} Probability distributions for model parameters, where Tri(x,y,z) denotes the 
+Triangular distribution with endpoints (x,z) and mode y.
+\end{table}
+
+With a random Latin Hypercube Sample of size n=100,000, we computed partial rank correlation coefficients (PRCC) for each of the initial parameters and treatment costs, according to four different outcomes: 1) projected annual incidence in 2100 in the overall population, 2) projected cumulative cost of Latent TB treatments by 2100, 3) projected cumulative cost of Active TB treatments by 2100, 4) projected cumulative total cost of TB treatments by 2100.
+For outcome 1, PRCC values are shown alongside PRCC values computed in the original Hill model for the same outcome in Table 2, showing the closeness of our findings to the sensitivity results of the original Hill model.
+PRCC values for the remaining outcomes are reported in Table 3.
+\\
+
+\begin{table}[h]
+\centering
+\begin{tabular}{l r r}
+\hline\hline\\
+Parameter & Extended Hill Model & Original Hill model \\ [0.5ex]
+\hline\\
+$\sigma^{L}$  & -0.9303 & -0.9381 \\
+$v^{L}_{1}$   & 0.7871  & 0.8309 \\
+$f$                 & 0.7050  & 0.8072 \\
+$p$                & 0.8369  & 0.6100 \\
+$ARI_{0}$      & 0.5950  & 0.4939 \\
+$q$                & 0.5797  & 0.4543 \\
+$g$                & 0.6122  & 0.4517 \\
+$\sigma^{F}$ & -0.4911 & -0.3772 \\
+$r_{1}$          & 0.0028  & -0.1109 \\
+$r_{0}$          & 0.0018  & 0.0760 \\
+$\mu^{d}$      & 0.0923 & 0.0513 \\
+$x$                 & 0.0999 & 0.0345 \\
+$v^{L}_{0}$    & 0.0133 & 0.0266 \\
+$\phi$             & 0.0082 & 0.0177 \\
+$e_{0}$          & 0.0178 & -0.0072 \\
+$e_{1}$          & 0.1154 & 0.0046 \\
+$C_{A}$          & -0.0023 & N/A \\
+$C_{L}$           & 0.0009 & N/A \\ [1ex]
+\hline
+\end{tabular}\\[1ex]
+
+{\bf Table 2.} PRCC values for projected annual incidence in 2100
+ in the overall population, alongside corresponding values from the
+original Hill model.
+\end{table}
+
+From Table 2, we see that the PRCC values in the Extended Hill Model and the Original Hill Model match up reasonably well.
+In both cases, $\sigma^{L}$ is the most influential parameter, with PRCC values around -0.93.
+The cost parameters $C_{A}$ and $C_{L}$ have PRCC values close to zero, which is expected because varying the treatment costs should not affect the incidence rate of TB.
+Parameters in the original Hill model with small PRCC magnitudes (less than 0.15) also have small PRCC values in the extended model, while parameters with larger PRCC magnitudes (greater than 0.35) similarly have large PRCC values in the extended model.
+This validates the non-economic components of our model against the original Hill model.
+\\
+
+\begin{table}[h]
+\centering
+\begin{tabular}{l r r r}
+\hline\hline\\
+Parameter & Latent Costs & Active Costs & Total Costs\\ [0.5ex]
+\hline\\
+$\sigma^{L}$  & 0.9612  & -0.9284 & 0.4169 \\
+$v^{L}_{1}$   & -0.4190 & 0.6470  & 0.3533 \\
+$f$                 & 0.7467  & 0.5493  & 0.8083 \\
+$p$                & 0.3371  & 0.8810  & 0.8776 \\
+$ARI_{0}$      & 0.3920  & 0.6728  & 0.7337 \\
+$q$                & 0.3837  & 0.6573  & 0.7200 \\
+$g$                & 0.1120  & 0.5369  & 0.5182 \\
+$\sigma^{F}$ & -0.1138 & -0.5631 &-0.5435 \\
+$r_{1}$          & 0.1253 &  0.0658  & 0.1401 \\
+$r_{0}$          & 0.1325  & 0.0878  & 0.1658 \\
+$\mu_{d}$      & 0.0249 & 0.0560  & 0.0613 \\
+$x$                 & 0.0214 & 0.1282  & 0.1253 \\
+$v^{L}_{0}$   & -0.3103 & 0.0502  &-0.1867 \\
+$\phi$            & -0.0023 & -0.0102 &-0.0107 \\
+$e_{0}$          & 0.0081 & 0.0253   & 0.0269 \\
+$e_{1}$          & 0.0804 & 0.1653   & 0.1926 \\
+$C_{A}$          & 0.0011 & 0.7024   & 0.6385 \\
+$C_{L}$           & 0.8515 & 0.0013  & 0.7598 \\ [1ex]
+\hline
+\end{tabular}\\[1ex]
+
+{\bf Table 3.} PRCC values for cumulative US Health Care system costs from 
+Latent TB treatment, Active TB treatment, and Total treatment costs
+\end{table}
+
+In Table 3, we see that the cost parameters $C_{A}$ and $C_{L}$ are highly correlated with Active treatment costs and Latent treatment costs respectively.
+These high PRCC values are expected because there is a linear relationship between $C_{A}$ and the cumulative Active treatment cost, and similarly for $C_{L}$ and the cumulative Latent treatment cost.
+In addition, we note that both $C_{A}$ and $C_{L}$ are influential in the total overall cost, with PRCC values of 0.6385 and 0.7598 respectively.
+Because the PRCC value for $C_{L}$ is greater here, despite the fact that $C_{A} > C_{L}$, we can infer that cumulative Latent TB treatment costs are projected to be greater than cumulative Active TB costs with these estimates for cost parameters, so $C_{L}$ is a more influential parameter for total cumulative treatment costs.
+\\
+
+Other variables with significant PRCC magnitudes (greater than 0.5) in Table 3 include $\sigma^{L}$, $v^{L}_{1}$, $f$, $p$, $ARI_{0}$, $q$, $g$, and $\sigma^{F}$.
+Two of these parameters, $\sigma^{L}$ and $v^{L}_{1}$, have relatively large PRCC magnitudes for both Latent and Active Costs, but smaller PRCC magnitudes for Total Costs.
+Because their PRCC values for each of these two outcomes is different in sign, the net change to the total cost is partially cancelled out, so these parameters have a reduced influence on final US healthcare system costs.
+On the other hand, parameters such as $f$ and $p$ have large positive PRCC values for both Latent Costs and Active Costs, and we observe large positive PRCC values for Total Costs as well.\\
+
+To gain insight about strategies to reduce the cost burden for TB in the US, we focus on the parameters with the greatest PRCC magnitudes for Total Cost aside from $C_{A}$ and $C_{L}$, namely $f$, $p$, $ARI_{0}$, and $q$.
+All these parameters have PRCC magnitudes above 0.7, and are highly correlated with the total cost burden of TB borne by the US projected over the next 100 years.
+Out of these, $ARI_{0}$ is based on a historical fixed value, the Annual Risk of Infection among the US born population in the year 2000, and therefore is unchangeable under any intervention strategy.
+The parameters $p$ (the fraction of new infections which are acute) and $q$ (the fraction of infections progressing to infectious disease) are variables which depend on physiological disease dynamics, and may be altered with advances in medicine or mutations in the bacterial strains of TB.
+The parameter $f$ is the fraction of FB arrivals with LTBI, which may vary depending on US immigration policies and medical practices.
+These results suggest that treating cases of LTBI among new FB arrivals may be the most cost efficient intervention strategy to reduce the disease burden for TB in the US, under the assumptions of the Hill model.
+\\
+
+\subsection{Stochastic Model}
+
 \end{document}

### 2013-10-14 in_progress/presentations/paper/draft.tex
wording change

@@
 
-The majority of USB and FB individuals fall into the Susceptible (S) category, which includes everyone
-who is uninfected and has not been exposed to TB.  After exposure to an individual
-with TB, a person in the Susceptible compartment can develop Latent TB Infection (LTBI) and changes
-health states to either the Acute LTBI (F) or Chronic LTBI (L) compartment.  Latently
-infected individuals are not infectious, but have some risk of developing active TB infection
-over time.  However, the rates of disease progression are not equal, and individuals in the
-Acute LTBI compartment have a higher risk of developing active TB than those in
-the Chronic LTBI compartment.  Individuals in the Chronic LTBI compartment
-may also be exogenously re-infected and transition to the Acute LTBI compartment.  \\
+The majority of USB and FB individuals fall into the Susceptible (S) category,
+which includes everyone who is uninfected and has not been exposed to TB.  After
+exposure to an individual with TB, a person in the Susceptible compartment can
+develop Latent TB Infection (LTBI). Latently infected individuals are
+asymptomatic and non-infectious, but have some risk of developing active TB
+infection over time. In order to reflect the fact that real LTBI patients have a
+much higher risk of developing active TB within two years of exposure, the Hill
+Model splits the LTBI compartment into Acute LTBI (fast progressors) and Chronic
+LTBI (slow progressors). Accordingly, individuals in the Acute LTBI compartment
+have a higher risk of developing active TB than those in the Chronic LTBI
+compartment.  Individuals in the Chronic LTBI compartment may also be
+exogenously re-infected and transition to the Acute LTBI compartment.  \\
 
@@
   \label{fig:basicHillConstants}
-\end{figure}<++>
+\end{figure}
 \subsection{The Extended Hill Equations}

### 2013-10-14 in_progress/presentations/paper/draft.tex
condensified

@@
 asymptomatic and non-infectious, but have some risk of developing active TB
-infection over time. In order to reflect the fact that real LTBI patients have a
+infection over time. To reflect the fact that real LTBI patients have a
 much higher risk of developing active TB within two years of exposure, the Hill

### 2013-10-14 in_progress/presentations/paper/draft.tex
edited Basic Structure

@@
 \section{Methods}
-\subsection{Basic Implementation}
-Both the basic Hill Model and this extended Hill Model were implemented in
+\subsection{Basic Structure}
+Both the Hill Model (Basic Hill Model) and an extended version of the Hill Model (Extended Hill 
+Model) were implemented in 
 \texttt{R} as a system of differential equations, which were solved via the
-$\texttt{lsoda}$ routine. The systems of differential equations used in the Basic
-Hill Model and the extended Hill Model to capture basic disease dynamics are
-shown below in Figure 2 and Figure 3 respectively. In the extended Hill model,
+$\texttt{lsoda}$ routine. The systems of differential equations usedto capture basic disease dynamics in the Basic Hill Model and the Extended Hill Model are
+shown below in Figure 2 and Figure 3 respectively. In the Extended Hill Model,
 more differential equations were implemented to add additional tracking and
-economic modeling. These equations are detailed in the appendix.
+economic modeling. These equations are detailed in the Appendix.
 

### 2013-10-14 in_progress/presentations/paper/draft.tex
changed appendix citations

@@
 more differential equations were implemented to add additional tracking and
-economic modeling. These equations are detailed in the Appendix.
+economic modeling. These equations are detailed in the Appendix, Section 7.2.
 
@@
 The constants $\rho$ and $\alpha$ are birth rates, while $\mu_{i}$, and $\mu_{d}$ are death rates.  
-A complete list and descriptions of all constants used in the model can be found in the appendix.
+A complete list and descriptions of all constants used in the model can be found in the Appendix,
+Section 7.1.
 

### 2013-10-14 in_progress/presentations/paper/draft.tex
minor edit
changed intervention percentages to 5, 10, 25, and 50 percent

@@
 (acute or chronic) were also tracked. In the case of intervention testing, the
-number of cured cases of entering LTBI and the number of untreated entering LTBI
-were both tracked. Cured cases of LTBI entering, TB deaths, total TB cases, and
-total cost were also tracked discounted at 3\% annually. This discounting was
-converted to a continuous differential equation for use within the model. In
-general, incidence data is calculated in the same way in the extended hill as it
-was in the basic Hill.
+number of cured and untreated cases of entering LTBI were both tracked. Cured
+cases of LTBI entering, TB deaths, total TB cases, and total cost were also
+tracked discounted at 3\% annually. This discounting was converted to a
+continuous differential equation for use within the model. In general, incidence
+data is calculated in the same way in the extended hill as it was in the basic
+Hill.
 
@@
 curing various percentages of entering LTBI cases. Four indicative percentages
-chosen were $20\%$, $35\%$, $50\%$, and $65\%$. Note that the Hill model does
+chosen were $5\%$, $10\%$, $25\%$, and $50\%$. Note that the Hill model does
 not distinguish documented immigration from undocumented immigration, and as
-such estimates of entering LTBI cure rates higher than $65\%$ become much more
+such estimates of entering LTBI cure rates higher than $50\%$ become much more
 difficult to achieve. It was seen that in this model as well as in the basic
@@
 is practically impossible. However, it was seen that curing entering cases of
-LTBI resulted in a net US HCS cost per case averted of \$67,722.96 at 2025, \$28,759.00 at 2050,
-and \$17,967.39 at 2100 (assuming 20\% reduction with one cure costing \$XXXX; see Table
-\ref{tab:cpcaRes} for other percentages). Given the variable nature of LTBI
+LTBI resulted in a net US HCS cost per case averted of \$67,654.07 at 2025, \$28,699.15 at 2050,
+and \$17,912.95 at 2100 (assuming 25\% reduction with each cure costing \$800; see Table
+\ref{tab:cpcaArt} for other percentages). Given the variable nature of LTBI
 treatment cost, the model code is extendible such that a user can adjust these
@@
 entering LTBI over the time scale 2000 to 2025, 2000 to 2050, and 2000 to 2100.
-This value peaked at \$1.026 million at 2100 (20\% reduction). This illustrates
-that it would be cost saving to cure cases of LTBI at the cost of \$1.026
-million ``2000'' dollars over the time period 2000-2100. These intervention
-strategies also resulted in 23,870; 41,952; and 60,189 fewer cases of TB seen in
-the US, and 2,056; 3,614; and 5,185 fewer TB deaths, for 20\%, 35\%, and 50\%
+This value peaked at \$1.283 billion at 2100 (25\% reduction). This illustrates
+that it would be cost saving to cure cases of LTBI at the cost of \$1.283
+billion ``2000'' dollars over the time period 2000-2100. These intervention
+strategies also resulted in 11,900; 29,880; and 60,189 fewer cases of TB seen in
+the US, and 1,025; 2,573; and 5,185 fewer TB deaths, for 10\%, 25\%, and 50\%
 reduction, respectively.
@@
 % latex table generated in R 3.0.1 by xtable 1.7-1 package
-% Sat Aug 24 18:08:52 2013
+% Mon Oct 14 00:36:15 2013
 \begin{table}
@@
   \hline
- & red20 & red35 & red50 & red65 \\ 
+ & red5 & red10 & red25 & red50 \\ 
   \hline
 2000 & ND & ND & ND & ND \\ 
-  2025 & 67722.96 & 67527.15 & 67332.53 & 67138.90 \\ 
-  2050 & 28759.00 & 28581.09 & 28404.13 & 28227.50 \\ 
-  2075 & 20876.80 & 20709.13 & 20541.77 & 20374.49 \\ 
-  2100 & 17967.39 & 17804.94 & 17642.64 & 17480.33 \\ 
+  2025 & 67908.81 & 67855.46 & 67654.07 & 67332.53 \\ 
+  2050 & 28938.23 & 28878.70 & 28699.15 & 28404.13 \\ 
+  2075 & 21044.88 & 20989.16 & 20820.53 & 20541.77 \\ 
+  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ 
    \hline
 \end{tabular}
-\caption{Cost Per Case Averted by Reducing Incoming LTBI by 20\%, 35\%, 50\%, and 65\% (in dollar per case)} 
-\label{tab:cpcaRes}
+\caption{Cost Per Case Averted by Reducing Incoming LTBI by X percent (in dollar per case)} 
+\label{tab:cpcaArt}
 \end{table}
+
 Several other intervention strategies analyzed by the Hill Model were refined
@@
 \subsection{Finer Intervention Analysis}
+
+% latex table generated in R 3.0.1 by xtable 1.7-1 package
+% Mon Oct 14 00:36:15 2013
+\begin{table}
+\centering
+\begin{tabular}{|r|cccc|}
+  \hline
+ & red5 & red10 & red25 & red50 \\ 
+  \hline
+2000 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
+  2025 & 1115.12 & 2231.70 & 5592.43 & 11227.57 \\ 
+  2050 & 3406.41 & 6821.27 & 17117.18 & 34447.71 \\ 
+  2075 & 4976.77 & 9967.15 & 25021.33 & 50389.58 \\ 
+  2100 & 5942.02 & 11900.90 & 29880.03 & 60189.49 \\ 
+   \hline
+\end{tabular}
+\caption{Cases of TB Averted by Reducing Incoming LTBI by X percent} 
+\label{tab:caRed}
+\end{table}
+
+% latex table generated in R 3.0.1 by xtable 1.7-1 package
+% Mon Oct 14 00:36:15 2013
+\begin{table}
+\centering
+\begin{tabular}{|r|cccc|}
+  \hline
+ & red5 & red10 & red25 & red50 \\ 
+  \hline
+2000 & ND & ND & ND & ND \\ 
+  2025 & 67908.81 & 67855.46 & 67654.07 & 67332.53 \\ 
+  2050 & 28938.23 & 28878.70 & 28699.15 & 28404.13 \\ 
+  2075 & 21044.88 & 20989.16 & 20820.53 & 20541.77 \\ 
+  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ 
+   \hline
+\end{tabular}
+\caption{Cost Per Case Averted by Reducing Incoming LTBI by X percent (in dollar per case)} 
+\label{tab:cpcaRed}
+\end{table}
+
 \subsection{Latin Hypercube Sampling}

### 2013-10-14 in_progress/models/costBenefitAnalysis/interventionTable.R

@@ -13,7 +13,7 @@ source('interventionAnalyzer.R')
 #Make sure you reset all intervention costs to default values in interventionConfig.R before running!!!
 
 # Set of interventions
-redEnLTBI_Interventions_paper <- c('redEnLTBI20', 'redEnLTBI35', 'redEnLTBI50', 'redEnLTBI65')
+redEnLTBI_Interventions_paper <- c('redEnLTBI5', 'redEnLTBI10', 'redEnLTBI25', 'redEnLTBI50')
 
 baseData <- read.csv(baseFile)
 #Base Incidence
@@ -91,7 +91,7 @@ for (interventionName in redEnLTBI_Interventions_paper) {
 rownames <- c('2000', '2025', '2050', '2075', '2100')
 
 # Savings from Intervention
-svngResults <- data.frame(red20=rep(0,5), red35=rep(0,5), red50=rep(0,5), red65=rep(0,5), row.names = rownames)
+svngResults <- data.frame(red5=rep(0,5), red10=rep(0,5), red25=rep(0,5), red50=rep(0,5), row.names = rownames)
 for (interventionNumber in 1:4) {
     svngResults[,interventionNumber] <- saveOfInter[[interventionNumber]][seq(1, totT, floor(totT/4))]
 }
@@ -100,7 +100,7 @@ svngRes.table <- xtable(svngResults, digits=6, align="|r|cccc|", caption = "Savi
 
 
 # Additional Cost of Intervention
-aciResults <- data.frame(red20=rep(0,5), red35=rep(0,5), red50=rep(0,5), red65=rep(0,5), row.names = rownames)
+aciResults <- data.frame(red5=rep(0,5), red10=rep(0,5), red25=rep(0,5), red50=rep(0,5), row.names = rownames)
 for (interventionNumber in 1:4) {
     aciResults[,interventionNumber] <- totSpent[[interventionNumber]][seq(1, totT, floor(totT/4))]
 }
@@ -108,7 +108,7 @@ print(aciResults)
 aciRes.table <- xtable(aciResults, digits=6, align="|r|cccc|", caption = "Additional Cost of Reducing Incoming LTBI by X percent (in billions of dollars)")
 
 # Number of Case Averted
-ncavResults <- data.frame(red20=rep(0,5), red35=rep(0,5), red50=rep(0,5), red65=rep(0,5), row.names = rownames)
[…]

### 2013-10-14 in_progress/models/costBenefitAnalysis/interventionConfig.R
added capability to change LTBI Cure Cost when generating tables for intervention cost

@@ -55,6 +55,8 @@ interventionConfig <- function(interventionStr, x=0) { #x is an integer refering
       # (minor)
       incLTBI <- incLTBI*(1-interventionMag/100)
       LTBIEn  <- 800 #LTBIEn + 400 + 600*(interventionMag/100) + x*100
+    } else if (interventionType == "setLTBICost") {
+      LTBIEn <- interventionMag
     } else if (interventionType == "redImm") {
       #No Costs!
       if (interventionMag == 75) {

### 2013-10-14 in_progress/models/costBenefitAnalysis/interventionTable.R

@@ -13,7 +13,9 @@ source('interventionAnalyzer.R')
 #Make sure you reset all intervention costs to default values in interventionConfig.R before running!!!
 
 # Set of interventions
-redEnLTBI_Interventions_paper <- c('redEnLTBI5', 'redEnLTBI10', 'redEnLTBI25', 'redEnLTBI50')
+redEnLTBI_Percentages <- c('redEnLTBI5', 'redEnLTBI10', 'redEnLTBI25', 'redEnLTBI50')
+redEnLTBI_Costs <- c('setLTBICost800', 'setLTBICost1000', 'setLTBICost1200', 'setLTBICost1400', 'setLTBICost1600', 'setLTBICost2000')
+redEnLTBI_Interventions_paper <- apply(expand.grid(redEnLTBI_Percentages, redEnLTBI_Costs), 1, function(x) paste(x[1], x[2], sep='&'))
 
 baseData <- read.csv(baseFile)
 #Base Incidence

### 2013-10-14 in_progress/models/costBenefitAnalysis/interventionConfig.R
added helpful comment to interventionConfig.R

@@ -8,6 +8,8 @@ intFileSuffix <- '.csv'
 # inc/red                   --> increase/reduce 
 # EnLTBI/Imm/LTBItrmt/Trans --> Entering LTBI, Immigration, LTBI Treatment, 
 #                               Transmission.
+# setLTBICost               --> set cost of LTBI Treatment (usually used
+#                               in conjunction with EnLTBI)
 # Magnitude (the numbers)   --> Interpert these by placing a 'by' prior to the 
 #                               number and adding a percent at the end. 
 # &                         --> 'and'. This chains interventions.

### 2013-10-14 in_progress/presentations/paper/draft.tex
added capability to change LTBI Cure Cost when generating tables for intervention cost
added figure captions

@@
 
-\begin{figure}
+\begin{figure}[h]
+  \begin{center}
     \includegraphics[scale=0.25]{figures/HillModelFlowChart.png}
+  \end{center}
+  \caption{Schematic of the Hill Model.}
+  \label{fig:hillModelSchematic}
 \end{figure}
@@
 \texttt{R} as a system of differential equations, which were solved via the
-$\texttt{lsoda}$ routine. The systems of differential equations usedto capture basic disease dynamics in the Basic Hill Model and the Extended Hill Model are
-shown below in Figure 2 and Figure 3 respectively. In the Extended Hill Model,
+$\texttt{lsoda}$ routine. The systems of differential equations used to capture basic disease dynamics in the Basic Hill Model are shown in Figure 2. In the Extended Hill Model,
 more differential equations were implemented to add additional tracking and
@@
 \begin{figure}
+  \begin{center}
     \includegraphics[scale=0.75]{figures/BasicHillEquations.pdf}
+  \end{center}
+  \caption{System of Differential Equations given in the Hill Model.}
+  \label{fig:hillEquations}
 \end{figure}
@@
 continuous differential equation for use within the model. In general, incidence
-data is calculated in the same way in the extended hill as it was in the basic
-Hill.
+data is calculated in the same way in the Extended Hill Model as it was in the Basic
+Hill Model.
 
@@
 these data were also analyzed, with results of $1.03$ and $.64$, respectively. 
-Full calculations are included in the appendix.
+Full calculations are included in the Appendix.
 
@@
 final population sizes were normal, with mean accurate to the deterministic
-model and standard deviations given in table X, in the appendix.
+model and standard deviations given in table X, in the Appendix.
 
@@
 To account for uncertainty of input parameter values and to gain insight about the
-most influential parameters in the model, we used Latin Hypercube Sampling to 
-analyze the deterministic model, implemented with the 'lhs' package in R.  We varied 
+most influential parameters in the model, we used Latin Hypercube Sampling to analyze the deterministic model, implemented with the \texttt{lhs} package in \texttt{R}.  We varied 
 the 16 parameters from the original Hill model according to triangular distributions centered
@@
 TB treatment health care costs are approximately \$700 and \$14,000 per case cured respectively.  
-A full description of the Latin Hypercube Sampling analysis and tables of Partial Rank Correlation Coefficient (PRCC) results for all parameters are given in the Appendix, section 7.6.  \\
+A full description of the Latin Hypercube Sampling analysis and tables of Partial Rank Correlation Coefficient (PRCC) results for all parameters are given in the Appendix, Section 7.6.  \\
 
@@
 \end{tabular}
-\caption{Cases of TB Averted by Reducing Incoming LTBI by X percent} 
+\caption{Cases of TB Averted by Reducing Incoming LTBI by X percent (Cure=\$800)} 
 \label{tab:caRed}
@@
 \end{tabular}
-\caption{Cost Per Case Averted by Reducing Incoming LTBI by X percent (in dollar per case)} 
+\caption{Cost Per Case Averted by Reducing Incoming LTBI by X percent (in dollar per case, Cure=\$800)} 
 \label{tab:cpcaRed}

### 2014-02-08 in_progress/presentations/paper/draft.tex
added reference for historical data to initialize model in Methods section
added Q-Q plots to paper

@@
 economic modeling. These equations are detailed in the Appendix, Section 7.2. 
+Historical data from 2000-2008 was used to initialize the model, which was then run up to the
+year 2100.
 
@@
 entering LTBI cases across the board, are given in the appendix.
-\subsection{Agent Based Evaluation}
-The Agent Based Model allowed the statistical properties of the system to be
-analyzed and verified. In particular, they illustrated that the deterministic
-Hill model provides a robust and consistent statistical measure of TB epidemic
-behavior in the US conditions. We found that the distribution of incidence and
-final population sizes were normal, with mean accurate to the deterministic
-model and standard deviations given in table X, in the Appendix.
 
@@
 A full description of the Latin Hypercube Sampling analysis and tables of Partial Rank Correlation Coefficient (PRCC) results for all parameters are given in the Appendix, Section 7.6.  \\
+
+\subsection{Agent Based Evaluation}
+The Agent Based Model allowed the statistical properties of the system to be
+analyzed and verified. In particular, they illustrated that the deterministic
+Hill model provides a robust and consistent statistical measure of TB epidemic
+behavior in the US conditions. We found that the distribution of incidence and
+final population sizes were normal, with mean accurate to the deterministic
+model and standard deviations given in table X, in the Appendix.
 
@@
 
+\begin{figure}
+    \includegraphics[scale=0.4]{figures/qqnormUSBInc.pdf}
+    \includegraphics[scale=0.4]{figures/qqnormFBInc.pdf}
+    \includegraphics[scale=0.4]{figures/qqnormUSBPop.pdf}
+    \includegraphics[scale=0.4]{figures/qqnormFBPop.pdf}
+  \caption{Normal Q-Q Plots for 2103 runs of the Stochastic Model with population constant = 1.}
+  \label{fig:qqnormPlots}
+\end{figure}
+
+Results for USB Incidence, FB Incidence, USB Population, and FB Population in the year
+2100 shown, overlayed with linear (normal) fit.
 \end{document}

### 2014-02-08 in_progress/presentations/paper/draft.tex
working on paper

--- 2013-10-14 in_progress/presentations/paper/draft.tex
@@
 \section{Abstract}
-An extended epidemiological model for Tuberculosis in the US was developed, based on an existing
-epidemiological model developed in 2012 by the Centers for Disease Control and Prevention.  
-Economic parameters to track the cost burden of TB for the US health care system were added,
-and an agent-based stochastic version of the model was implemented.  The sensitivity of the extended
-model to changes in parameters was analyzed, and the percentage of foreign-born immigrants with
-LTBI appears to be a highly influential parameter in the model.  Intervention strategies to reduce LTBI
-among foreign-born arrivals were evaluated, and estimates of the cost per case averted were found.
+An extended epidemiological model for Tuberculosis in the US was developed,
+based on an existing epidemiological model developed in 2012 by the Centers for
+Disease Control and Prevention.  Economic parameters to track the cost burden of
+TB for the US health care system were added.  The sensitivity of the extended
+model to changes in parameters was analyzed, and the percentage of foreign-born
+immigrants with LTBI appears to be a highly influential parameter in the model.
+Intervention strategies to reduce LTBI among foreign-born arrivals were
+evaluated, and estimates of the cost per case averted were found. Additionally,
+a population-level, stochastic, agent-based model was built to provide
+statistical verification of the results of the deterministic model and to
+demonstrate feasibility of agent-based modeling even on such large population
+scales.
 
@@
 added to the model in order to project the US health care system (HCS) costs due
-to TB given our current policy as well as for various interventions. Finally, a
+to TB given our current policy as well as for various interventions.
+
+Though compartmental, differential equation models 
+Finally, a
 population level, agent based implementation of the Hill Model was created, in
@@
 curing various percentages of entering LTBI cases. Four indicative percentages
-chosen were $5\%$, $10\%$, $25\%$, and $50\%$. Note that the Hill model does
+chosen were $20\%$, $35\%$, $50\%$, and $65\%$. Note that the Hill model does
 not distinguish documented immigration from undocumented immigration, and as
-such estimates of entering LTBI cure rates higher than $50\%$ become much more
+such estimates of entering LTBI cure rates higher than $65\%$ become much more
 difficult to achieve. It was seen that in this model as well as in the basic
@@
 is practically impossible. However, it was seen that curing entering cases of
-LTBI resulted in a net US HCS cost per case averted of \$67,654.07 at 2025, \$28,699.15 at 2050,
-and \$17,912.95 at 2100 (assuming 25\% reduction with each cure costing \$800; see Table
-\ref{tab:cpcaArt} for other percentages). Given the variable nature of LTBI
+LTBI resulted in a net US HCS cost per case averted of \$67,722.96 at 2025, \$28,759.00 at 2050,
+and \$17,967.39 at 2100 (assuming 20\% reduction with one cure costing \$XXXX; see Table
+\ref{tab:cpcaRes} for other percentages). Given the variable nature of LTBI
 treatment cost, the model code is extendible such that a user can adjust these
@@
 entering LTBI over the time scale 2000 to 2025, 2000 to 2050, and 2000 to 2100.
-This value peaked at \$1.283 billion at 2100 (25\% reduction). This illustrates
-that it would be cost saving to cure cases of LTBI at the cost of \$1.283
-billion ``2000'' dollars over the time period 2000-2100. These intervention
-strategies also resulted in 11,900; 29,880; and 60,189 fewer cases of TB seen in
-the US, and 1,025; 2,573; and 5,185 fewer TB deaths, for 10\%, 25\%, and 50\%
+This value peaked at \$1.026 million at 2100 (20\% reduction). This illustrates
+that it would be cost saving to cure cases of LTBI at the cost of \$1.026
+million ``2000'' dollars over the time period 2000-2100. These intervention
+strategies also resulted in 23,870; 41,952; and 60,189 fewer cases of TB seen in
+the US, and 2,056; 3,614; and 5,185 fewer TB deaths, for 20\%, 35\%, and 50\%
 reduction, respectively.
@@
 % latex table generated in R 3.0.1 by xtable 1.7-1 package
-% Mon Oct 14 00:36:15 2013
+% Sat Aug 24 18:08:52 2013
 \begin{table}
@@
   \hline
- & red5 & red10 & red25 & red50 \\ 
+ & red20 & red35 & red50 & red65 \\ 
   \hline
 2000 & ND & ND & ND & ND \\ 
-  2025 & 67908.81 & 67855.46 & 67654.07 & 67332.53 \\ 
-  2050 & 28938.23 & 28878.70 & 28699.15 & 28404.13 \\ 
-  2075 & 21044.88 & 20989.16 & 20820.53 & 20541.77 \\ 
-  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ 
+  2025 & 67722.96 & 67527.15 & 67332.53 & 67138.90 \\ 
+  2050 & 28759.00 & 28581.09 & 28404.13 & 28227.50 \\ 
+  2075 & 20876.80 & 20709.13 & 20541.77 & 20374.49 \\ 
+  2100 & 17967.39 & 17804.94 & 17642.64 & 17480.33 \\ 
    \hline
 \end{tabular}
-\caption{Cost Per Case Averted by Reducing Incoming LTBI by X percent (in dollar per case)} 
-\label{tab:cpcaArt}
+\caption{Cost Per Case Averted by Reducing Incoming LTBI by 20\%, 35\%, 50\%, and 65\% (in dollar per case)} 
+\label{tab:cpcaRes}
 \end{table}
-
 Several other intervention strategies analyzed by the Hill Model were refined
@@
 \subsection{Finer Intervention Analysis}
-
-% latex table generated in R 3.0.1 by xtable 1.7-1 package
-% Mon Oct 14 00:36:15 2013
-\begin{table}
-\centering
-\begin{tabular}{|r|cccc|}
-  \hline
- & red5 & red10 & red25 & red50 \\ 
-  \hline
-2000 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
-  2025 & 1115.12 & 2231.70 & 5592.43 & 11227.57 \\ 
-  2050 & 3406.41 & 6821.27 & 17117.18 & 34447.71 \\ 
-  2075 & 4976.77 & 9967.15 & 25021.33 & 50389.58 \\ 
-  2100 & 5942.02 & 11900.90 & 29880.03 & 60189.49 \\ 
-   \hline
-\end{tabular}
-\caption{Cases of TB Averted by Reducing Incoming LTBI by X percent} 
-\label{tab:caRed}
-\end{table}
-
-% latex table generated in R 3.0.1 by xtable 1.7-1 package
-% Mon Oct 14 00:36:15 2013
-\begin{table}
-\centering
-\begin{tabular}{|r|cccc|}
-  \hline
- & red5 & red10 & red25 & red50 \\ 
-  \hline
-2000 & ND & ND & ND & ND \\ 
-  2025 & 67908.81 & 67855.46 & 67654.07 & 67332.53 \\ 
-  2050 & 28938.23 & 28878.70 & 28699.15 & 28404.13 \\ 
-  2075 & 21044.88 & 20989.16 & 20820.53 & 20541.77 \\ 
-  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ 
-   \hline
-\end{tabular}
-\caption{Cost Per Case Averted by Reducing Incoming LTBI by X percent (in dollar per case)} 
-\label{tab:cpcaRed}
-\end{table}
-
 \subsection{Latin Hypercube Sampling}

### 2014-02-08 in_progress/presentations/paper/draft.tex
updated intro

@@
 
-Though compartmental, differential equation models 
-Finally, a
-population level, agent based implementation of the Hill Model was created, in
-order to validate the Hill Model against the natural stochasticity present in
-real world disease spread.
+Though compartmental, differential equation models are the most common strategy
+when modeling large-scale diseases at the population level with minimal age
+stratification, an alternative approach is to use an agent-based model. Agent
+based models provide a more nuanced view of disease spread as they provide a
+more biologically reasonable framework; however, they are often considered to be
+computationally infeasible at population level. In this work, a stochastic,
+agent-based model of US TB was implemented which was used at the population
+level to both provide statistical verification of the Hill Model and to
+demonstrate the computational feasibility of an agent-based modeling framework
+for general disease modeling.
 

### 2014-02-08 in_progress/presentations/paper/draft.tex
updated 5.4 and looked at discussion/future work

@@
 \usepackage{enumerate,placeins}
+\usepackage{color}
 \graphicspath{{figures/}}
@@
 \subsection{Agent Based Evaluation}
-The Agent Based Model allowed the statistical properties of the system to be
-analyzed and verified. In particular, they illustrated that the deterministic
+The agent-based model allowed the statistical properties of the system to be
+analyzed and verified. In particular, it illustrated that the deterministic
 Hill model provides a robust and consistent statistical measure of TB epidemic
@@
 final population sizes were normal, with mean accurate to the deterministic
-model and standard deviations given in table X, in the Appendix.
+model and standard deviations given in table X, in the Appendix. Additionally,
+the agent-based model provided a computational framework to produce
+meaningful intervention results. On lab-grade, student hardware, a statistically
+meaningful experiment could be run overnight, producing data in a day. This
+demonstrates that this modeling strategy is feasible in this general case.
 
@@
 necessary step towards elimination and indicate that it is a cost effective
-option. 
+option. \\
+{\huge \color{red} Where did we show it was cost effective relative to other
+interventions? Also, the section below (future work) might be better just
+directly included in the discussion}\\
 \subsection{Future Work}
@@
 examine the effects drug-resistant TB will have on US TB dynamics.
+
 \section{Appendix}

### 2014-02-08 in_progress/presentations/paper/draft.tex
Appendix

@@
 \subsection{Statistical Qualities of the Agent Based Model}
+
+\begin{figure}
+    \includegraphics[scale=0.4]{figures/qqnormUSBInc.pdf}
+    \includegraphics[scale=0.4]{figures/qqnormFBInc.pdf}
+    \includegraphics[scale=0.4]{figures/qqnormUSBPop.pdf}
+    \includegraphics[scale=0.4]{figures/qqnormFBPop.pdf}
+  \caption{Normal Q-Q Plots for 2103 runs of the Stochastic Model with population constant = 1.}
+  \label{fig:qqnormPlots}
+\end{figure}
+
+Results for USB Incidence, FB Incidence, USB Population, and FB Population in the year
+2100 shown, overlayed with linear (normal) fit are shown in
+figure~\ref{fig:qqnormPlots}. These plots demonstrate the normality of the
+Stocahstic Data. 
 \subsection{Finer Intervention Analysis}
@@
 
-From Table 2, we see that the PRCC values in the Extended Hill Model and the Original Hill Model match up reasonably well.
-In both cases, $\sigma^{L}$ is the most influential parameter, with PRCC values around -0.93.
-The cost parameters $C_{A}$ and $C_{L}$ have PRCC values close to zero, which is expected because varying the treatment costs should not affect the incidence rate of TB.
-Parameters in the original Hill model with small PRCC magnitudes (less than 0.15) also have small PRCC values in the extended model, while parameters with larger PRCC magnitudes (greater than 0.35) similarly have large PRCC values in the extended model.
-This validates the non-economic components of our model against the original Hill model.
-\\
+From Table 2, we see that the PRCC values in the Extended Hill Model and the
+Original Hill Model match up reasonably well.  In both cases, $\sigma^{L}$ is
+the most influential parameter, with PRCC values around -0.93.  The cost
+parameters $C_{A}$ and $C_{L}$ have PRCC values close to zero, which is expected
+because varying the treatment costs should not affect the incidence rate of TB.
+Parameters in the original Hill model with small PRCC magnitudes (less than
+0.15) also have small PRCC values in the extended model, while parameters with
+larger PRCC magnitudes (greater than 0.35) similarly have large PRCC values in
+the extended model.  This validates the non-economic components of our model
+against the original Hill model.   \\
 
@@
 
-In Table 3, we see that the cost parameters $C_{A}$ and $C_{L}$ are highly correlated with Active treatment costs and Latent treatment costs respectively.
-These high PRCC values are expected because there is a linear relationship between $C_{A}$ and the cumulative Active treatment cost, and similarly for $C_{L}$ and the cumulative Latent treatment cost.
-In addition, we note that both $C_{A}$ and $C_{L}$ are influential in the total overall cost, with PRCC values of 0.6385 and 0.7598 respectively.
-Because the PRCC value for $C_{L}$ is greater here, despite the fact that $C_{A} > C_{L}$, we can infer that cumulative Latent TB treatment costs are projected to be greater than cumulative Active TB costs with these estimates for cost parameters, so $C_{L}$ is a more influential parameter for total cumulative treatment costs.
-\\
+In Table 3, we see that the cost parameters $C_{A}$ and $C_{L}$ are highly
+correlated with Active treatment costs and Latent treatment costs respectively.
+These high PRCC values are expected because there is a linear relationship
+between $C_{A}$ and the cumulative Active treatment cost, and similarly for
+$C_{L}$ and the cumulative Latent treatment cost.  In addition, we note that
+both $C_{A}$ and $C_{L}$ are influential in the total overall cost, with PRCC
+values of 0.6385 and 0.7598 respectively.  Because the PRCC value for $C_{L}$ is
+greater here, despite the fact that $C_{A} > C_{L}$, we can infer that
+cumulative Latent TB treatment costs are projected to be greater than cumulative
+Active TB costs with these estimates for cost parameters, so $C_{L}$ is a more
+influential parameter for total cumulative treatment costs.
 
-Other variables with significant PRCC magnitudes (greater than 0.5) in Table 3 include $\sigma^{L}$, $v^{L}_{1}$, $f$, $p$, $ARI_{0}$, $q$, $g$, and $\sigma^{F}$.
-Two of these parameters, $\sigma^{L}$ and $v^{L}_{1}$, have relatively large PRCC magnitudes for both Latent and Active Costs, but smaller PRCC magnitudes for Total Costs.
-Because their PRCC values for each of these two outcomes is different in sign, the net change to the total cost is partially cancelled out, so these parameters have a reduced influence on final US healthcare system costs.
-On the other hand, parameters such as $f$ and $p$ have large positive PRCC values for both Latent Costs and Active Costs, and we observe large positive PRCC values for Total Costs as well.\\
+Other variables with significant PRCC magnitudes (greater than 0.5) in Table 3
+include $\sigma^{L}$, $v^{L}_{1}$, $f$, $p$, $ARI_{0}$, $q$, $g$, and
+$\sigma^{F}$.  Two of these parameters, $\sigma^{L}$ and $v^{L}_{1}$, have
+relatively large PRCC magnitudes for both Latent and Active Costs, but smaller
+PRCC magnitudes for Total Costs.  Because their PRCC values for each of these
+two outcomes is different in sign, the net change to the total cost is partially
+cancelled out, so these parameters have a reduced influence on final US
+healthcare system costs.  On the other hand, parameters such as $f$ and $p$ have
+large positive PRCC values for both Latent Costs and Active Costs, and we
+observe large positive PRCC values for Total Costs as well.\\
 
-To gain insight about strategies to reduce the cost burden for TB in the US, we focus on the parameters with the greatest PRCC magnitudes for Total Cost aside from $C_{A}$ and $C_{L}$, namely $f$, $p$, $ARI_{0}$, and $q$.
-All these parameters have PRCC magnitudes above 0.7, and are highly correlated with the total cost burden of TB borne by the US projected over the next 100 years.
-Out of these, $ARI_{0}$ is based on a historical fixed value, the Annual Risk of Infection among the US born population in the year 2000, and therefore is unchangeable under any intervention strategy.
-The parameters $p$ (the fraction of new infections which are acute) and $q$ (the fraction of infections progressing to infectious disease) are variables which depend on physiological disease dynamics, and may be altered with advances in medicine or mutations in the bacterial strains of TB.
-The parameter $f$ is the fraction of FB arrivals with LTBI, which may vary depending on US immigration policies and medical practices.
-These results suggest that treating cases of LTBI among new FB arrivals may be the most cost efficient intervention strategy to reduce the disease burden for TB in the US, under the assumptions of the Hill model.
-\\
+To gain insight about strategies to reduce the cost burden for TB in the US, we
+focus on the parameters with the greatest PRCC magnitudes for Total Cost aside
+from $C_{A}$ and $C_{L}$, namely $f$, $p$, $ARI_{0}$, and $q$.  All these
+parameters have PRCC magnitudes above 0.7, and are highly correlated with the
+total cost burden of TB borne by the US projected over the next 100 years.  Out
+of these, $ARI_{0}$ is based on a historical fixed value, the Annual Risk of
+Infection among the US born population in the year 2000, and therefore is
+unchangeable under any intervention strategy.  The parameters $p$ (the fraction
+of new infections which are acute) and $q$ (the fraction of infections
+progressing to infectious disease) are variables which depend on physiological
+disease dynamics, and may be altered with advances in medicine or mutations in
+the bacterial strains of TB.  The parameter $f$ is the fraction of FB arrivals
+with LTBI, which may vary depending on US immigration policies and medical
+practices.  These results suggest that treating cases of LTBI among new FB
+arrivals may be the most cost efficient intervention strategy to reduce the
+disease burden for TB in the US, under the assumptions of the Hill model.  \\
 
 \subsection{Stochastic Model}
-
-\begin{figure}
-    \includegraphics[scale=0.4]{figures/qqnormUSBInc.pdf}
-    \includegraphics[scale=0.4]{figures/qqnormFBInc.pdf}
-    \includegraphics[scale=0.4]{figures/qqnormUSBPop.pdf}
-    \includegraphics[scale=0.4]{figures/qqnormFBPop.pdf}
-  \caption{Normal Q-Q Plots for 2103 runs of the Stochastic Model with population constant = 1.}
-  \label{fig:qqnormPlots}
-\end{figure}
-
-Results for USB Incidence, FB Incidence, USB Population, and FB Population in the year
-2100 shown, overlayed with linear (normal) fit.
 \end{document}

### 2014-02-08 in_progress/presentations/paper/draft.tex
Appendix
style things

@@
 \subsection{Hill Constants}
-Below, we detail some of the relevant constants in the Basic Hill Model, and their best-fit
-values. A full listing of constants used in the original Hill Model can be found in <CITATION HERE> 
-\begin{figure}[h]
-  \begin{center}
-    \tiny{
-    \begin{verbatim}
-sigmaLBase  <- 0.057
-fBase       <- 0.187
-transBase   <- 1
-incLTBIBase <- 1
-
-#Treatment Effectiveness Data:
-probHosp      <- .49 #Probability of hospitalization for active TB treatment
-efficacyLTBI  <- .9  #LTBI treatement efficacy
-adherenceLTBI <- .64 #LTBI treatment adherence
-probLTBItreatsuccess <- efficacyLTBI*adherenceLTBI
-
-#Cost Parameter Values: 
-costtb   <- 2985   #TB treatment cost w/o hopsitalization <- Dylan supp. p.11-12
-costhosp <- 25495  #TB treatment cost w/ hospitalization  <- Dylan supp. p.10
-costLTBI <- 403.45 #LTBI treatment cost
-Ct       <- costtb*(1-probHosp) + costhosp*probHosp #Cost of active TB treatment
-Cl       <- costLTBI/probLTBItreatsuccess           #Cost of LTBI treatment
-
-parms <- c(
-mu0   = 1/78,      #Natural mortality rate USB per year
-mu1   = 1/53,      #Natural mortality rate FB per year
-ro    = 0.018,     #USB birth rate per year
-alpha = 0.005,     #FB arrival rate per year
-p     = 0.103,     #Fraction of new infections which are acute (fast
-progressors)
-vF    = 1.5,       #Progression rate of acute infection per year
-l0    = 0.015,     #Prevalence of LTBI in the USB population in 2000
-l1    = 0.211,     #Prevalence of LTBI in the FB population in 2000: 
-r0    = 0.667,     #Fraction of cases due to reactivation in the USB population
-r1    = 0.780,     #Fraction of cases due to reactivation in the FB population
-vL0   = 0.0014,    #Progression rate for reactivation (chronic LTBI) in the USB
-population per year
-vL1   = 0.0010,    #Progression rate for reactivation (chronic LTBI) in the FB
-population per year
-q     = 0.708,     #Fraction of infections progressing to infectious disease
-mud   = 0.115,     #Mortality rate due to TB per year
-x     = 0.111,     #Fraction of re-infected chronic LTBI moving to acute
-infection
-ARI0  = 0.030/100, #Annual risk of infection for USB in 2000
-beta  = 10.39,     #Effective contact rate per year
-e0    = 0.965,     #Fraction of preferred contacts with own population for USB
-e1    = 0.985,     #Fraction of preferred contacts with own population for FB
-g     = 0.0047,    #Fraction of FB arrivals with LTBI who are fast progressors
-phi0  = 1.114,     #Cumulative fraction self-cure and treatment of active
-disease for both populations pre year RATES (USB)
-phi1  = 1.167,     #Cumulative fraction self-cure and treatment of active
-disease for both populations pre year RATES (FB)
-sigmaF0 = 1.296,   #Cumulative fraction of treatment for acute infection for
-both populations per year RATES (USB)
-sigmaF1 = 1.301,   #Cumulative fraction of treatment for acute infection for
-both populations per year RATES (FB)
-sigmaLBase = sigmaLBase, #Treatment rate for chronic LTBI per year
-fBase = fBase,      #Fraction of FB arrivals with LTBI
-
-#2010 New Cases in Population i (millions)
-#source: http://www.cdc.gov/mmwr/preview/mmwrhtml/mm5105a3.htm
-newCases0 = .008714,  #US-born
-newCases1 = .007554,  #Foreign-born
-
-CtBase = Ct,
-ClBase = Cl
-)
-    \end{verbatim}
-  }
-  \end{center}
-  \caption{A list of relevant constants in the Basic \& Extended Hill Model}
-  \label{fig:basicHillConstants}
-\end{figure}
+Below, we detail some of the relevant constants in the Basic Hill Model, and
+their best-fit values. A full listing of constants used in the original Hill
+Model can be found in <+CITATION HERE+>. 
+%\begin{figure}[h]
+%  \begin{center}
+%    \tiny{
+%    \begin{verbatim}
+%sigmaLBase  <- 0.057
+%fBase       <- 0.187
+%transBase   <- 1
+%incLTBIBase <- 1
+%
+%
+%#Treatment Effectiveness Data:
+%probHosp      <- .49 #Probability of hospitalization for active TB treatment
+%efficacyLTBI  <- .9  #LTBI treatement efficacy
+%adherenceLTBI <- .64 #LTBI treatment adherence
+%probLTBItreatsuccess <- efficacyLTBI*adherenceLTBI 
+%
+%#Cost Parameter Values: 
+%costtb   <- 2985   #TB treatment cost w/o hopsitalization <- Dylan supp. p.11-12
+%costhosp <- 25495  #TB treatment cost w/ hospitalization  <- Dylan supp. p.10
+%costLTBI <- 403.45 #LTBI treatment cost
+%Ct       <- costtb*(1-probHosp) + costhosp*probHosp #Cost of active TB treatment
+%Cl       <- costLTBI/probLTBItreatsuccess           #Cost of LTBI treatment
+%
+%parms <- c(
+%mu0   = 1/78,      #Natural mortality rate USB per year
+%mu1   = 1/53,      #Natural mortality rate FB per year
+%ro    = 0.018,     #USB birth rate per year
+%alpha = 0.005,     #FB arrival rate per year
+%p     = 0.103,     #Fraction of new infections which are acute (fast
+%progressors)
+%vF    = 1.5,       #Progression rate of acute infection per year
+%l0    = 0.015,     #Prevalence of LTBI in the USB population in 2000
+%l1    = 0.211,     #Prevalence of LTBI in the FB population in 2000: 
+%r0    = 0.667,     #Fraction of cases due to reactivation in the USB population
+%r1    = 0.780,     #Fraction of cases due to reactivation in the FB population
+%vL0   = 0.0014,    #Progression rate for reactivation (chronic LTBI) in the USB
+%population per year
+%vL1   = 0.0010,    #Progression rate for reactivation (chronic LTBI) in the FB
+%population per year
+%q     = 0.708,     #Fraction of infections progressing to infectious disease
+%mud   = 0.115,     #Mortality rate due to TB per year
+%x     = 0.111,     #Fraction of re-infected chronic LTBI moving to acute
+%infection
+%ARI0  = 0.030/100, #Annual risk of infection for USB in 2000
+%beta  = 10.39,     #Effective contact rate per year
+%e0    = 0.965,     #Fraction of preferred contacts with own population for USB
+%e1    = 0.985,     #Fraction of preferred contacts with own population for FB
+%g     = 0.0047,    #Fraction of FB arrivals with LTBI who are fast progressors
+%phi0  = 1.114,     #Cumulative fraction self-cure and treatment of active
+%disease for both populations pre year RATES (USB)
+%phi1  = 1.167,     #Cumulative fraction self-cure and treatment of active
+%disease for both populations pre year RATES (FB)
+%sigmaF0 = 1.296,   #Cumulative fraction of treatment for acute infection for
+%both populations per year RATES (USB)
+%sigmaF1 = 1.301,   #Cumulative fraction of treatment for acute infection for
+%both populations per year RATES (FB)
+%sigmaLBase = sigmaLBase, #Treatment rate for chronic LTBI per year
+%fBase = fBase,      #Fraction of FB arrivals with LTBI
+%
+%#2010 New Cases in Population i (millions)
+%#source: http://www.cdc.gov/mmwr/preview/mmwrhtml/mm5105a3.htm
+%newCases0 = .008714,  #US-born
+%newCases1 = .007554,  #Foreign-born
+%
+%CtBase = Ct,
+%ClBase = Cl
+%)
+%    \end{verbatim}
+%  }
+%  \end{center}
+%  \caption{A list of relevant constants in the Basic \& Extended Hill Model}
+%  \label{fig:basicHillConstants}
+%\end{figure}
 \subsection{The Extended Hill Equations}
@@
 then be tracked separately. 
-\begin{figure}[h]
-  \begin{center}
-  \tiny{
-    \begin{verbatim}
-discV   <- 1/(1.03^t)  #amount costs, health states discount constant
-
-#parameter values initialized for each time step
-c01          <- (1-e0)*((1-e1)*N1)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with FB individuals  (USB)
-c00          <- 1 - c01                                          #proportion of contacts made with USB individuals (USB)
-c10          <- (1-e1)*((1-e0)*N0)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with USB individuals (FB)
-c11          <- 1 - c10                                          #proportion of contacts made with FB individuals  (FB)
-dLTBIEn      <- f*alpha*(N0+N1)                                  #FB arrivals with LTBI entering
-dnatdeath0   <- mu0 * N0                                         #Natural deaths (USB)
-dnatdeath1   <- mu1 * N1                                         #Natural deaths (FB)
-dtbdeath0    <- mud * (I0 + J0)                                  #TB deaths (USB)
-dtbdeath1    <- mud * (I1 + J1)                                  #TB deaths (FB)
-dtbdeathD0   <- discV * dtbdeath0                                #TB deaths with discounting (USB)
-dtbdeathD1   <- discV * dtbdeath1                                #TB deaths with discounting (FB)
-dprogAcute0  <- vF*F0                                            #Acute LTBI progressions to Active TB disease (USB)
-dprogAcute1  <- vF*F1                                            #Acute LTBI progressions to Active TB disease (FB)
-dprogChron0  <- vL0*L0                                           #Chronic LTBI progressions to Active TB disease (USB)
-dprogChron1  <- vL1*L1                                           #Chronic LTBI progressions to Active TB disease (FB)
-dprogTotal0  <- dprogAcute0 + dprogChron0                        #Progression to Active TB (USB)
-dprogTotal1  <- dprogAcute1 + dprogChron1                        #Progression to Active TB (FB)
-dprogTotalD0 <- discV * dprogTotal0                              #Progression to Active TB with discounting (USB)
-dprogTotalD1 <- discV * dprogTotal1                              #Progression to Active TB with discounting (FB)
-lambda0      <- transmission*(beta*(c00*(I0/N0) + c01*(I1/N1)))  #Forces of Infection (USB)
-lambda1      <- transmission*(beta*(c10*(I0/N0) + c11*(I1/N1)))  #Forces of Infection (FB)
-dexogenous0	 <- x*p*lambda0*L0                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (USB)
-dexogenous1  <- x*p*lambda1*L1                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (FB)
-dInterventionCost <- discV * (iCnewCases*1e6*(dprogTotal0+dprogTotal1) + iCtotPop*1e6*(N0+N1) + iCLTBIEn*1e6*dLTBIEn*(1-incLTBI))
-
-#Difference Equations (USB)
-dS0 <- ro*(N0+N1) + sigmaF0*F0 + sigmaL*L0 + phi0*(I0+J0) - lambda0*S0 - mu0*S0
-dF0 <- p*lambda0*S0 + dexogenous0 - (mu0 + vF + sigmaF0)*F0
-dL0 <- (1-p)*lambda0*S0 - dexogenous0 - (mu0 + vL0 + sigmaL)*L0
-dI0 <- q*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*I0
-dJ0 <- (1-q)*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*J0
-
-#Difference Equations (FB)
-dS1 <- (1-incLTBI)*dLTBIEn+(1-f)*alpha*(N0+N1) + sigmaF1*F1 + sigmaL*L1 + phi1*(I1 + J1) - lambda1*S1 - mu1*S1
-dF1 <- g*p*dLTBIEn*incLTBI + p*lambda1*S1 + dexogenous1 - (mu1 + vF + sigmaF1)*F1
-dL1 <- (1-g*p)*dLTBIEn*incLTBI + (1-p)*lambda1*S1 - dexogenous1 - (mu1 + vL1 +sigmaL)*L1
-dI1 <- q*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*I1
-dJ1 <- (1-q)*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*J1
-
-dN0 <- dS0 + dF0 + dL0 + dI0 + dJ0
-dN1 <- dS1 + dF1 + dL1 + dI1 + dJ1
-
-#Cost calculations
-dcL0 <- discV * Cl * sigmaL  * 1e6 * L0                    #cost for Chronic LTBI cures      (USB)
-dcF0 <- discV * Cl * sigmaF0 * 1e6 * F0                    #cost for Acute LTBI cures        (USB)
-dcI0 <- discV * Ct * q*(dprogAcute0 + dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
-dcJ0 <- discV * Ct * (1-q)*(dprogAcute0 + dprogChron0) * 1e6 #cost for Non-Infectious TB cures (USB)
-dcI0dL0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
-dcI0dF0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
-dcJ0dL0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
-dcJ0dF0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
-dcL1 <- discV * Cl * sigmaL  * 1e6 * L1                    #cost for Chronic LTBI cures      (FB)
-dcF1 <- discV * Cl * sigmaF1 * 1e6 * F1                    #cost for Acute LTBI cures        (FB)
-dcI1 <- discV * Ct * q*(dprogAcute1 + dprogChron1) * 1e6     #cost for Infectious TB cures     (FB)
-dcJ1 <- discV * Ct * (1-q)*(dprogAcute1 + dprogChron1) * 1e6 #cost for Non-Infectious TB cures (FB)
-dcI1dL1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
-dcI1dF1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
-dcJ1dL1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
-dcJ1dF1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
-dcN0 <- dcF0 + dcL0 + dcI0 + dcJ0                            #Total cost for all treatments (USB)
-dcN1 <- dcF1 + dcL1 + dcI1 + dcJ1                            #Total cost for all treatments (FB)
-    \end{verbatim}
-  }
-  \end{center}
-  \label{fig:extendedHillEqs}
-  \caption{
-    The equations defining the Extended Hill Model, shown in \texttt{R} syntax.
-    In this model, compartments share the same names as they did in the Hill
-    Model, \emph{i.e.} \texttt{S1} is the Foreign Born susceptible population. 
-  }
-\end{figure}
+%\begin{figure}[h]
+%  \begin{center}
+%  \tiny{
+%    \begin{verbatim}
+%discV   <- 1/(1.03^t)  #amount costs, health states discount constant
+%
+%#parameter values initialized for each time step
+%c01          <- (1-e0)*((1-e1)*N1)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with FB individuals  (USB)
+%c00          <- 1 - c01                                          #proportion of contacts made with USB individuals (USB)
+%c10          <- (1-e1)*((1-e0)*N0)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with USB individuals (FB)
+%c11          <- 1 - c10                                          #proportion of contacts made with FB individuals  (FB)
+%dLTBIEn      <- f*alpha*(N0+N1)                                  #FB arrivals with LTBI entering
+%dnatdeath0   <- mu0 * N0                                         #Natural deaths (USB)
+%dnatdeath1   <- mu1 * N1                                         #Natural deaths (FB)
+%dtbdeath0    <- mud * (I0 + J0)                                  #TB deaths (USB)
+%dtbdeath1    <- mud * (I1 + J1)                                  #TB deaths (FB)
+%dtbdeathD0   <- discV * dtbdeath0                                #TB deaths with discounting (USB)
+%dtbdeathD1   <- discV * dtbdeath1                                #TB deaths with discounting (FB)
+%dprogAcute0  <- vF*F0                                            #Acute LTBI progressions to Active TB disease (USB)
+%dprogAcute1  <- vF*F1                                            #Acute LTBI progressions to Active TB disease (FB)
+%dprogChron0  <- vL0*L0                                           #Chronic LTBI progressions to Active TB disease (USB)
+%dprogChron1  <- vL1*L1                                           #Chronic LTBI progressions to Active TB disease (FB)
+%dprogTotal0  <- dprogAcute0 + dprogChron0                        #Progression to Active TB (USB)
+%dprogTotal1  <- dprogAcute1 + dprogChron1                        #Progression to Active TB (FB)
+%dprogTotalD0 <- discV * dprogTotal0                              #Progression to Active TB with discounting (USB)
+%dprogTotalD1 <- discV * dprogTotal1                              #Progression to Active TB with discounting (FB)
+%lambda0      <- transmission*(beta*(c00*(I0/N0) + c01*(I1/N1)))  #Forces of Infection (USB)
+%lambda1      <- transmission*(beta*(c10*(I0/N0) + c11*(I1/N1)))  #Forces of Infection (FB)
+%dexogenous0	 <- x*p*lambda0*L0                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (USB)
+%dexogenous1  <- x*p*lambda1*L1                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (FB)
+%dInterventionCost <- discV * (iCnewCases*1e6*(dprogTotal0+dprogTotal1) + iCtotPop*1e6*(N0+N1) + iCLTBIEn*1e6*dLTBIEn*(1-incLTBI))
+%
+%#Difference Equations (USB)
+%dS0 <- ro*(N0+N1) + sigmaF0*F0 + sigmaL*L0 + phi0*(I0+J0) - lambda0*S0 - mu0*S0
+%dF0 <- p*lambda0*S0 + dexogenous0 - (mu0 + vF + sigmaF0)*F0
+%dL0 <- (1-p)*lambda0*S0 - dexogenous0 - (mu0 + vL0 + sigmaL)*L0
+%dI0 <- q*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*I0
+%dJ0 <- (1-q)*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*J0
+%
+%#Difference Equations (FB)
+%dS1 <- (1-incLTBI)*dLTBIEn+(1-f)*alpha*(N0+N1) + sigmaF1*F1 + sigmaL*L1 + phi1*(I1 + J1) - lambda1*S1 - mu1*S1
+%dF1 <- g*p*dLTBIEn*incLTBI + p*lambda1*S1 + dexogenous1 - (mu1 + vF + sigmaF1)*F1
+%dL1 <- (1-g*p)*dLTBIEn*incLTBI + (1-p)*lambda1*S1 - dexogenous1 - (mu1 + vL1 +sigmaL)*L1
+%dI1 <- q*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*I1
+%dJ1 <- (1-q)*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*J1
+%
+%dN0 <- dS0 + dF0 + dL0 + dI0 + dJ0
+%dN1 <- dS1 + dF1 + dL1 + dI1 + dJ1
+%
+%#Cost calculations
+%dcL0 <- discV * Cl * sigmaL  * 1e6 * L0                    #cost for Chronic LTBI cures      (USB)
+%dcF0 <- discV * Cl * sigmaF0 * 1e6 * F0                    #cost for Acute LTBI cures        (USB)
+%dcI0 <- discV * Ct * q*(dprogAcute0 + dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
+%dcJ0 <- discV * Ct * (1-q)*(dprogAcute0 + dprogChron0) * 1e6 #cost for Non-Infectious TB cures (USB)
+%dcI0dL0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
+%dcI0dF0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
+%dcJ0dL0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
+%dcJ0dF0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
+%dcL1 <- discV * Cl * sigmaL  * 1e6 * L1                    #cost for Chronic LTBI cures      (FB)
+%dcF1 <- discV * Cl * sigmaF1 * 1e6 * F1                    #cost for Acute LTBI cures        (FB)
+%dcI1 <- discV * Ct * q*(dprogAcute1 + dprogChron1) * 1e6     #cost for Infectious TB cures     (FB)
+%dcJ1 <- discV * Ct * (1-q)*(dprogAcute1 + dprogChron1) * 1e6 #cost for Non-Infectious TB cures (FB)
+%dcI1dL1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
+%dcI1dF1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
+%dcJ1dL1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
+%dcJ1dF1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
+%dcN0 <- dcF0 + dcL0 + dcI0 + dcJ0                            #Total cost for all treatments (USB)
+%dcN1 <- dcF1 + dcL1 + dcI1 + dcJ1                            #Total cost for all treatments (FB)
+%    \end{verbatim}
+%  }
+%  \end{center}
+%  \label{fig:extendedHillEqs}
+%  \caption{
+%    The equations defining the Extended Hill Model, shown in \texttt{R} syntax.
+%    In this model, compartments share the same names as they did in the Hill
+%    Model, \emph{i.e.} \texttt{S1} is the Foreign Born susceptible population. 
+%  }
+%\end{figure}
 Here, a continuous discounting approximation is used to a discount rate of $3\%$
@@
 \centering
-\begin{tabular}{|r|cccc|}
-  \hline
- & red5 & red10 & red25 & red50 \\ 
-  \hline
+\begin{tabular}{|r|cccc|} \hline
+       & red5    & red10    & red25    & red50    \\ \hline
   2000 & 0.00    & 0.00     & 0.00     & 0.00     \\ 
@@
 \subsection{Latin Hypercube Sampling}
-The model parameters and variable names referred to in this analysis are listed below, along with best-fit or estimated values.
-Following the example of the Hill model, we generated a Latin Hypercube Sample varying 18 of the input parameters.
-From these parameters, 16 are identical to the input parameters varied in the sensitivity analysis of the original Hill model, and the remaining two parameters, $C_{A}$ and $C_{L}$, are variables for the average cost of Active and Latent TB treatment in the US.
-Probability distributions for the original 16 parameters of the Hill model were all set to be Triangular, with mode at the best fit value and end points at the 2.5 and 97.5 percentile values reported in the Hill model.
-Probability distributions for $C_{A}$ and $C_{L}$ were set to be Uniform, with range +/- 10\% of the estimated value.
-All probabilty distributions used to generate the Latin Hypercube are listed in Table 1.\\
+The model parameters and variable names referred to in this analysis are listed
+below, along with best-fit or estimated values.  Following the example of the
+Hill model, we generated a Latin Hypercube Sample varying 18 of the input
+parameters.  From these parameters, 16 are identical to the input parameters
+varied in the sensitivity analysis of the original Hill model, and the remaining
+two parameters, $C_{A}$ and $C_{L}$, are variables for the average cost of
+Active and Latent TB treatment in the US.   Probability distributions for the
+original 16 parameters of the Hill model were all set to be Triangular, with
+mode at the best fit value and end points at the 2.5 and 97.5 percentile values
+reported in the Hill model.  Probability distributions for $C_{A}$ and $C_{L}$
+were set to be Uniform, with range +/- 10\% of the estimated value.  All
+probabilty distributions used to generate the Latin Hypercube are listed in
+Table 1.\\
 
@@
 (USB = US born, FB = Foriegn born)
-\begin{enumerate}[1.] \itemsep 0em
-\item{$\sigma^{L}$ = 0.057 (Treatment rate for chronic LTBI)}
-\item{$v^{L}_{0}$   = 0.0014 (Progression rate for reactivation in the USB population)}
-\item{$v^{L}_{1}$  = 0.0010 (Progression rate for reactivation in the FB population)}
-\item{$f$                = 0.187 (Fraction of FB arrivals with LTBI)}
-\item{$p$               = 0.103 (Fraction of new infections which are acute)}
-\item{$ARI_{0}$     = 0.00030 (2000 Annual Risk of Infection, USB)}
-\item{$q$               = 0.708 (Fraction of infections progressing to infectious disease)}
-\item{$g$               = 0.0047 (Fraction of FB arrivals with LTBI who are fast progressors)}
-\item{$\sigma^{F}$ = 0.461 (Cumulative fraction of treatment for acute infection)}
-\item{$r_{0}$          = 0.667 (Fraction of cases due to reactivation in USB population)}
-\item{$r_{1}$          = 0.780 (Fraction of cases due to reactivation in FB population)}
-\item{$\mu^{d}$      = 0.115 (Mortality rate due to TB)}
-\item{$x$                 = 0.111 (Fraction of re-infected chronic LTBI moving to acute infection)}
-\item{$\phi$            = 0.897 (Cumulative fraction self-cure and treatment of active disease)}
-\item{$e_{0}$          = 0.965 (Fraction of preferred contacts within own population for USB)}
-\item{$e_{1}$          = 0.985 (Fraction of preferred contacts within own population for FB)}
-\end{enumerate}
-\vspace{2mm}
-{\bf Additional Cost Parameters}
-\begin{enumerate}[1.] \itemsep 0em
-\item{$C_{A}$           = \$14,014.50 (Cost per Active TB treatment)}
-\item{$C_{L}$           = \$700 (Cost per Latent TB treatment)}
-\end{enumerate}
+%\begin{enumerate}[1.] \itemsep 0em
+%  \item $\sigma^{L}$ = 0.057 (Treatment rate for chronic LTBI)
+%  \item $v^{L}_{0}$  = 0.0014 (Progression rate for reactivation in the USB population)
+%  \item $v^{L}_{1}$  = 0.0010 (Progression rate for reactivation in the FB population)
+%  \item $f$          = 0.187 (Fraction of FB arrivals with LTBI)
+%  \item $p$          = 0.103 (Fraction of new infections which are acute)
+%  \item $ARI_{0}$    = 0.00030 (2000 Annual Risk of Infection, USB)
+%  \item $q$          = 0.708 (Fraction of infections progressing to infectious disease)
+%  \item $g$          = 0.0047 (Fraction of FB arrivals with LTBI who are fast progressors)
+%  \item $\sigma^{F}$ = 0.461 (Cumulative fraction of treatment for acute infection)
+%  \item $r_{0}$      = 0.667 (Fraction of cases due to reactivation in USB population)
+%  \item $r_{1}$      = 0.780 (Fraction of cases due to reactivation in FB population)
+%  \item $\mu^{d}$    = 0.115 (Mortality rate due to TB)
+%  \item $x$          = 0.111 (Fraction of re-infected chronic LTBI moving to acute infection)
+%  \item $\phi$       = 0.897 (Cumulative fraction self-cure and treatment of active disease)
+%  \item $e_{0}$      = 0.965 (Fraction of preferred contacts within own population for USB)
+%  \item $e_{1}$      = 0.985 (Fraction of preferred contacts within own population for FB)
+%\end{enumerate}
+%\vspace{2mm}
+\begin{align*}
+  \sigma^{L} &= 0.057   &&\text{(Treatment rate for chronic LTBI)}\\
+  v^{L}_{0}  &= 0.0014  &&\text{(Progression rate for reactivation in the USB
+                                 population)}\\
+  v^{L}_{1}  &= 0.0010  &&\text{(Progression rate for reactivation in the FB
+                                 population)}\\
+  f          &= 0.187   &&\text{(Fraction of FB arrivals with LTBI)}\\
+  p          &= 0.103   &&\text{(Fraction of new infections which are acute)}\\
+  ARI_{0}    &= 0.00030 &&\text{(2000 Annual Risk of Infection, USB)}\\
+  q          &= 0.708   &&\text{(Fraction of infections progressing to infectious
+                                 disease)}\\
+  g          &= 0.0047  &&\text{(Fraction of FB arrivals with LTBI who are fast
+                                 progressors)}\\
+  \sigma^{F} &= 0.461   &&\text{(Cumulative fraction of treatment for acute
+                                 infection)}\\
+  r_{0}      &= 0.667   &&\text{(Fraction of cases due to reactivation in USB
+                                 population)}\\
+  r_{1}      &= 0.780   &&\text{(Fraction of cases due to reactivation in FB
+                                 population)}\\
+  \mu^{d}    &= 0.115   &&\text{(Mortality rate due to TB)}\\
+  x          &= 0.111   &&\text{(Fraction of re-infected chronic LTBI moving to
+                                 acute infection)}\\
+  \phi       &= 0.897   &&\text{(Cumulative fraction self-cure and treatment of
+                                 active disease)}\\
+  e_{0}      &= 0.965   &&\text{(Fraction of preferred contacts within own
+                                 population for USB)}\\
+  e_{1}      &= 0.985   &&\text{(Fraction of preferred contacts within own
+                                population for FB)}\\
+%\end{align*}
+&\text{\bf Additional Cost Parameters}\\
+%\begin{align*}
+  C_{A} &= \$14,014.50 &&\text{(Cost per Active TB treatment)}\\
+  C_{L} &= \$700       &&\text{(Cost per Latent TB treatment)}
+\end{align*}
+%\begin{enumerate}[1.] \itemsep 0em
+%  \item $C_{A}$ = \$14,014.50 (Cost per Active TB treatment)
+%  \item $C_{L}$ = \$700 (Cost per Latent TB treatment)
+%\end{enumerate}
 \vspace{5mm}
@@
 disease burden for TB in the US, under the assumptions of the Hill model.  \\
-
-\subsection{Stochastic Model}
 \end{document}

### 2014-02-08 in_progress/presentations/paper/draft.tex
Modifying appendix structure

@@
 their best-fit values. A full listing of constants used in the original Hill
-Model can be found in <+CITATION HERE+>. 
-%\begin{figure}[h]
-%  \begin{center}
-%    \tiny{
-%    \begin{verbatim}
-%sigmaLBase  <- 0.057
-%fBase       <- 0.187
-%transBase   <- 1
-%incLTBIBase <- 1
-%
-%
-%#Treatment Effectiveness Data:
-%probHosp      <- .49 #Probability of hospitalization for active TB treatment
-%efficacyLTBI  <- .9  #LTBI treatement efficacy
-%adherenceLTBI <- .64 #LTBI treatment adherence
-%probLTBItreatsuccess <- efficacyLTBI*adherenceLTBI 
-%
-%#Cost Parameter Values: 
-%costtb   <- 2985   #TB treatment cost w/o hopsitalization <- Dylan supp. p.11-12
-%costhosp <- 25495  #TB treatment cost w/ hospitalization  <- Dylan supp. p.10
-%costLTBI <- 403.45 #LTBI treatment cost
-%Ct       <- costtb*(1-probHosp) + costhosp*probHosp #Cost of active TB treatment
-%Cl       <- costLTBI/probLTBItreatsuccess           #Cost of LTBI treatment
-%
-%parms <- c(
-%mu0   = 1/78,      #Natural mortality rate USB per year
-%mu1   = 1/53,      #Natural mortality rate FB per year
-%ro    = 0.018,     #USB birth rate per year
-%alpha = 0.005,     #FB arrival rate per year
-%p     = 0.103,     #Fraction of new infections which are acute (fast
-%progressors)
-%vF    = 1.5,       #Progression rate of acute infection per year
-%l0    = 0.015,     #Prevalence of LTBI in the USB population in 2000
-%l1    = 0.211,     #Prevalence of LTBI in the FB population in 2000: 
-%r0    = 0.667,     #Fraction of cases due to reactivation in the USB population
-%r1    = 0.780,     #Fraction of cases due to reactivation in the FB population
-%vL0   = 0.0014,    #Progression rate for reactivation (chronic LTBI) in the USB
-%population per year
-%vL1   = 0.0010,    #Progression rate for reactivation (chronic LTBI) in the FB
-%population per year
-%q     = 0.708,     #Fraction of infections progressing to infectious disease
-%mud   = 0.115,     #Mortality rate due to TB per year
-%x     = 0.111,     #Fraction of re-infected chronic LTBI moving to acute
-%infection
-%ARI0  = 0.030/100, #Annual risk of infection for USB in 2000
-%beta  = 10.39,     #Effective contact rate per year
-%e0    = 0.965,     #Fraction of preferred contacts with own population for USB
-%e1    = 0.985,     #Fraction of preferred contacts with own population for FB
-%g     = 0.0047,    #Fraction of FB arrivals with LTBI who are fast progressors
-%phi0  = 1.114,     #Cumulative fraction self-cure and treatment of active
-%disease for both populations pre year RATES (USB)
-%phi1  = 1.167,     #Cumulative fraction self-cure and treatment of active
-%disease for both populations pre year RATES (FB)
-%sigmaF0 = 1.296,   #Cumulative fraction of treatment for acute infection for
-%both populations per year RATES (USB)
-%sigmaF1 = 1.301,   #Cumulative fraction of treatment for acute infection for
-%both populations per year RATES (FB)
-%sigmaLBase = sigmaLBase, #Treatment rate for chronic LTBI per year
-%fBase = fBase,      #Fraction of FB arrivals with LTBI
-%
-%#2010 New Cases in Population i (millions)
-%#source: http://www.cdc.gov/mmwr/preview/mmwrhtml/mm5105a3.htm
-%newCases0 = .008714,  #US-born
-%newCases1 = .007554,  #Foreign-born
-%
-%CtBase = Ct,
-%ClBase = Cl
-%)
-%    \end{verbatim}
-%  }
-%  \end{center}
-%  \caption{A list of relevant constants in the Basic \& Extended Hill Model}
-%  \label{fig:basicHillConstants}
-%\end{figure}
+Model can be found in <+CITATION HERE+>. \\
+\textit{(USB = US born, FB = Foriegn born)}
+\begin{align*}
+  \sigma^{L} &= 0.057   &&\text{(Treatment rate for chronic LTBI)}\\
+  v^{L}_{0}  &= 0.0014  &&\text{(Progression rate for reactivation in the USB
+                                 population)}\\
+  v^{L}_{1}  &= 0.0010  &&\text{(Progression rate for reactivation in the FB
+                                 population)}\\
+  f          &= 0.187   &&\text{(Fraction of FB arrivals with LTBI)}\\
+  p          &= 0.103   &&\text{(Fraction of new infections which are acute)}\\
+  ARI_{0}    &= 0.00030 &&\text{(2000 Annual Risk of Infection, USB)}\\
+  q          &= 0.708   &&\text{(Fraction of infections progressing to infectious
+                                 disease)}\\
+  g          &= 0.0047  &&\text{(Fraction of FB arrivals with LTBI who are fast
+                                 progressors)}\\
+  \sigma^{F} &= 0.461   &&\text{(Cumulative fraction of treatment for acute
+                                 infection)}\\
+  r_{0}      &= 0.667   &&\text{(Fraction of cases due to reactivation in USB
+                                 population)}\\
+  r_{1}      &= 0.780   &&\text{(Fraction of cases due to reactivation in FB
+                                 population)}\\
+  \mu^{d}    &= 0.115   &&\text{(Mortality rate due to TB)}\\
+  x          &= 0.111   &&\text{(Fraction of re-infected chronic LTBI moving to
+                                 acute infection)}\\
+  \phi       &= 0.897   &&\text{(Cumulative fraction self-cure and treatment of
+                                 active disease)}\\
+  e_{0}      &= 0.965   &&\text{(Fraction of preferred contacts within own
+                                 population for USB)}\\
+  e_{1}      &= 0.985   &&\text{(Fraction of preferred contacts within own
+                                population for FB)}\\
+\end{align*}
 \subsection{The Extended Hill Equations}
-Below, we detail the full equations used in the extended hill model. These
-equations extend those used in the standard Hill Model. In many cases, the
-equations of the Hill model were split into their component parts, which could
-then be tracked separately. 
-%\begin{figure}[h]
-%  \begin{center}
-%  \tiny{
-%    \begin{verbatim}
-%discV   <- 1/(1.03^t)  #amount costs, health states discount constant
-%
-%#parameter values initialized for each time step
-%c01          <- (1-e0)*((1-e1)*N1)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with FB individuals  (USB)
-%c00          <- 1 - c01                                          #proportion of contacts made with USB individuals (USB)
-%c10          <- (1-e1)*((1-e0)*N0)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with USB individuals (FB)
-%c11          <- 1 - c10                                          #proportion of contacts made with FB individuals  (FB)
-%dLTBIEn      <- f*alpha*(N0+N1)                                  #FB arrivals with LTBI entering
-%dnatdeath0   <- mu0 * N0                                         #Natural deaths (USB)
-%dnatdeath1   <- mu1 * N1                                         #Natural deaths (FB)
-%dtbdeath0    <- mud * (I0 + J0)                                  #TB deaths (USB)
-%dtbdeath1    <- mud * (I1 + J1)                                  #TB deaths (FB)
-%dtbdeathD0   <- discV * dtbdeath0                                #TB deaths with discounting (USB)
-%dtbdeathD1   <- discV * dtbdeath1                                #TB deaths with discounting (FB)
-%dprogAcute0  <- vF*F0                                            #Acute LTBI progressions to Active TB disease (USB)
-%dprogAcute1  <- vF*F1                                            #Acute LTBI progressions to Active TB disease (FB)
-%dprogChron0  <- vL0*L0                                           #Chronic LTBI progressions to Active TB disease (USB)
-%dprogChron1  <- vL1*L1                                           #Chronic LTBI progressions to Active TB disease (FB)
-%dprogTotal0  <- dprogAcute0 + dprogChron0                        #Progression to Active TB (USB)
-%dprogTotal1  <- dprogAcute1 + dprogChron1                        #Progression to Active TB (FB)
-%dprogTotalD0 <- discV * dprogTotal0                              #Progression to Active TB with discounting (USB)
-%dprogTotalD1 <- discV * dprogTotal1                              #Progression to Active TB with discounting (FB)
-%lambda0      <- transmission*(beta*(c00*(I0/N0) + c01*(I1/N1)))  #Forces of Infection (USB)
-%lambda1      <- transmission*(beta*(c10*(I0/N0) + c11*(I1/N1)))  #Forces of Infection (FB)
-%dexogenous0	 <- x*p*lambda0*L0                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (USB)
-%dexogenous1  <- x*p*lambda1*L1                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (FB)
-%dInterventionCost <- discV * (iCnewCases*1e6*(dprogTotal0+dprogTotal1) + iCtotPop*1e6*(N0+N1) + iCLTBIEn*1e6*dLTBIEn*(1-incLTBI))
-%
-%#Difference Equations (USB)
-%dS0 <- ro*(N0+N1) + sigmaF0*F0 + sigmaL*L0 + phi0*(I0+J0) - lambda0*S0 - mu0*S0
-%dF0 <- p*lambda0*S0 + dexogenous0 - (mu0 + vF + sigmaF0)*F0
-%dL0 <- (1-p)*lambda0*S0 - dexogenous0 - (mu0 + vL0 + sigmaL)*L0
-%dI0 <- q*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*I0
-%dJ0 <- (1-q)*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*J0
-%
-%#Difference Equations (FB)
-%dS1 <- (1-incLTBI)*dLTBIEn+(1-f)*alpha*(N0+N1) + sigmaF1*F1 + sigmaL*L1 + phi1*(I1 + J1) - lambda1*S1 - mu1*S1
-%dF1 <- g*p*dLTBIEn*incLTBI + p*lambda1*S1 + dexogenous1 - (mu1 + vF + sigmaF1)*F1
-%dL1 <- (1-g*p)*dLTBIEn*incLTBI + (1-p)*lambda1*S1 - dexogenous1 - (mu1 + vL1 +sigmaL)*L1
-%dI1 <- q*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*I1
-%dJ1 <- (1-q)*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*J1
-%
-%dN0 <- dS0 + dF0 + dL0 + dI0 + dJ0
-%dN1 <- dS1 + dF1 + dL1 + dI1 + dJ1
-%
-%#Cost calculations
-%dcL0 <- discV * Cl * sigmaL  * 1e6 * L0                    #cost for Chronic LTBI cures      (USB)
-%dcF0 <- discV * Cl * sigmaF0 * 1e6 * F0                    #cost for Acute LTBI cures        (USB)
-%dcI0 <- discV * Ct * q*(dprogAcute0 + dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
-%dcJ0 <- discV * Ct * (1-q)*(dprogAcute0 + dprogChron0) * 1e6 #cost for Non-Infectious TB cures (USB)
-%dcI0dL0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
-%dcI0dF0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
-%dcJ0dL0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
-%dcJ0dF0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
-%dcL1 <- discV * Cl * sigmaL  * 1e6 * L1                    #cost for Chronic LTBI cures      (FB)
-%dcF1 <- discV * Cl * sigmaF1 * 1e6 * F1                    #cost for Acute LTBI cures        (FB)
-%dcI1 <- discV * Ct * q*(dprogAcute1 + dprogChron1) * 1e6     #cost for Infectious TB cures     (FB)
-%dcJ1 <- discV * Ct * (1-q)*(dprogAcute1 + dprogChron1) * 1e6 #cost for Non-Infectious TB cures (FB)
-%dcI1dL1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
-%dcI1dF1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
-%dcJ1dL1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
-%dcJ1dF1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
-%dcN0 <- dcF0 + dcL0 + dcI0 + dcJ0                            #Total cost for all treatments (USB)
-%dcN1 <- dcF1 + dcL1 + dcI1 + dcJ1                            #Total cost for all treatments (FB)
-%    \end{verbatim}
-%  }
-%  \end{center}
-%  \label{fig:extendedHillEqs}
-%  \caption{
-%    The equations defining the Extended Hill Model, shown in \texttt{R} syntax.
-%    In this model, compartments share the same names as they did in the Hill
-%    Model, \emph{i.e.} \texttt{S1} is the Foreign Born susceptible population. 
-%  }
-%\end{figure}
+Below, we detail some of the relevant equations used in the extended hill model.
+In many cases, the equations of the Hill model were split into their component
+parts, which could then be tracked separately.
+
+{\huge \color{red} TODO: What equations should be put in here?}
+
 Here, a continuous discounting approximation is used to a discount rate of $3\%$
@@
 \end{tabular}
-\caption{Cases of TB Averted by Reducing Incoming LTBI by X percent (Cure=\$800)} 
+\caption{Cases of TB Averted by Reducing Incoming LTBI by various percentages
+         (Cure=\$800)} 
 \label{tab:caRed}
@@
 \centering
-\begin{tabular}{|r|cccc|}
-  \hline
- & red5 & red10 & red25 & red50 \\ 
-  \hline
+\begin{tabular}{|r|cccc|} \hline
+       & red5     & red10    & red25    & red50    \\ \hline
   2000 & ND       & ND       & ND       & ND       \\ 
@@
   2075 & 21044.88 & 20989.16 & 20820.53 & 20541.77 \\ 
-  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ 
-   \hline
+  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ \hline
 \end{tabular}
-\caption{Cost Per Case Averted by Reducing Incoming LTBI by X percent (in dollar per case, Cure=\$800)} 
+\caption{Cost Per Case Averted by Reducing Incoming LTBI by various percent (in
+dollars per case, Cure=\$800)} 
 \label{tab:cpcaRed}
@@
 \subsection{Latin Hypercube Sampling}
-The model parameters and variable names referred to in this analysis are listed
-below, along with best-fit or estimated values.  Following the example of the
+%The model parameters and variable names referred to in this analysis are listed
+%below, along with best-fit or estimated values. 
+Following the example of the
 Hill model, we generated a Latin Hypercube Sample varying 18 of the input
@@
 varied in the sensitivity analysis of the original Hill model, and the remaining
-two parameters, $C_{A}$ and $C_{L}$, are variables for the average cost of
+two parameters, $C_{A}$ and $C_{L}$, detailed below, are variables for the average cost of
 Active and Latent TB treatment in the US.   Probability distributions for the
@@
 
-\vspace{5mm}
-{\bf Original Hill Model Parameters} 
-(USB = US born, FB = Foriegn born)
-%\begin{enumerate}[1.] \itemsep 0em
-%  \item $\sigma^{L}$ = 0.057 (Treatment rate for chronic LTBI)
-%  \item $v^{L}_{0}$  = 0.0014 (Progression rate for reactivation in the USB population)
-%  \item $v^{L}_{1}$  = 0.0010 (Progression rate for reactivation in the FB population)
-%  \item $f$          = 0.187 (Fraction of FB arrivals with LTBI)
-%  \item $p$          = 0.103 (Fraction of new infections which are acute)
-%  \item $ARI_{0}$    = 0.00030 (2000 Annual Risk of Infection, USB)
-%  \item $q$          = 0.708 (Fraction of infections progressing to infectious disease)
-%  \item $g$          = 0.0047 (Fraction of FB arrivals with LTBI who are fast progressors)
-%  \item $\sigma^{F}$ = 0.461 (Cumulative fraction of treatment for acute infection)
-%  \item $r_{0}$      = 0.667 (Fraction of cases due to reactivation in USB population)
-%  \item $r_{1}$      = 0.780 (Fraction of cases due to reactivation in FB population)
-%  \item $\mu^{d}$    = 0.115 (Mortality rate due to TB)
-%  \item $x$          = 0.111 (Fraction of re-infected chronic LTBI moving to acute infection)
-%  \item $\phi$       = 0.897 (Cumulative fraction self-cure and treatment of active disease)
-%  \item $e_{0}$      = 0.965 (Fraction of preferred contacts within own population for USB)
-%  \item $e_{1}$      = 0.985 (Fraction of preferred contacts within own population for FB)
-%\end{enumerate}
-%\vspace{2mm}
+{\bf Additional Cost Parameters}
 \begin{align*}
-  \sigma^{L} &= 0.057   &&\text{(Treatment rate for chronic LTBI)}\\
-  v^{L}_{0}  &= 0.0014  &&\text{(Progression rate for reactivation in the USB
-                                 population)}\\
-  v^{L}_{1}  &= 0.0010  &&\text{(Progression rate for reactivation in the FB
-                                 population)}\\
-  f          &= 0.187   &&\text{(Fraction of FB arrivals with LTBI)}\\
-  p          &= 0.103   &&\text{(Fraction of new infections which are acute)}\\
-  ARI_{0}    &= 0.00030 &&\text{(2000 Annual Risk of Infection, USB)}\\
-  q          &= 0.708   &&\text{(Fraction of infections progressing to infectious
-                                 disease)}\\
-  g          &= 0.0047  &&\text{(Fraction of FB arrivals with LTBI who are fast
-                                 progressors)}\\
-  \sigma^{F} &= 0.461   &&\text{(Cumulative fraction of treatment for acute
-                                 infection)}\\
-  r_{0}      &= 0.667   &&\text{(Fraction of cases due to reactivation in USB
-                                 population)}\\
-  r_{1}      &= 0.780   &&\text{(Fraction of cases due to reactivation in FB
-                                 population)}\\
-  \mu^{d}    &= 0.115   &&\text{(Mortality rate due to TB)}\\
-  x          &= 0.111   &&\text{(Fraction of re-infected chronic LTBI moving to
-                                 acute infection)}\\
-  \phi       &= 0.897   &&\text{(Cumulative fraction self-cure and treatment of
-                                 active disease)}\\
-  e_{0}      &= 0.965   &&\text{(Fraction of preferred contacts within own
-                                 population for USB)}\\
-  e_{1}      &= 0.985   &&\text{(Fraction of preferred contacts within own
-                                population for FB)}\\
-%\end{align*}
-&\text{\bf Additional Cost Parameters}\\
-%\begin{align*}
   C_{A} &= \$14,014.50 &&\text{(Cost per Active TB treatment)}\\
@@
 \end{align*}
-%\begin{enumerate}[1.] \itemsep 0em
-%  \item $C_{A}$ = \$14,014.50 (Cost per Active TB treatment)
-%  \item $C_{L}$ = \$700 (Cost per Latent TB treatment)
-%\end{enumerate}
 \vspace{5mm}

### 2014-02-08 in_progress/presentations/paper/draft.tex
Modifying discussion to discuss plateauing effect

@@
 \subsection{Basic Structure}
-Both the Hill Model (Basic Hill Model) and an extended version of the Hill Model (Extended Hill 
-Model) were implemented in 
-\texttt{R} as a system of differential equations, which were solved via the
-$\texttt{lsoda}$ routine. The systems of differential equations used to capture basic disease dynamics in the Basic Hill Model are shown in Figure 2. In the Extended Hill Model,
-more differential equations were implemented to add additional tracking and
-economic modeling. These equations are detailed in the Appendix, Section 7.2. 
-Historical data from 2000-2008 was used to initialize the model, which was then run up to the
+Both the Hill Model (Basic Hill Model) and an extended version of the Hill Model
+(Extended Hill Model) were implemented in \texttt{R} as a system of differential
+equations, which were solved via the $\texttt{lsoda}$ routine. The systems of
+differential equations used to capture basic disease dynamics in the Basic Hill
+Model are shown in Figure 2. In the Extended Hill Model, more differential
+equations were implemented to add additional tracking and economic modeling.
+These equations are detailed in the Appendix, Section 7.2.  Historical data from
+2000-2008 was used to initialize the model, which was then run up to the
 year 2100.
@@
 the strict Hill model did not differ significantly.
+
 \section{Results}
@@
 \centering
-\begin{tabular}{|r|cccc|}
-  \hline
- & red5 & red10 & red25 & red50 \\ 
-  \hline
-2000 & ND & ND & ND & ND \\ 
+\begin{tabular}{|r|cccc|} \hline
+       & red5     & red10    & red25    & red50    \\ \hline
+  %2000 & ND       & ND       & ND       & ND       \\ 
   2025 & 67908.81 & 67855.46 & 67654.07 & 67332.53 \\ 
@@
   2075 & 21044.88 & 20989.16 & 20820.53 & 20541.77 \\ 
-  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ 
-   \hline
+  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ \hline
 \end{tabular}
@@
 \subsection{Sensitivity Analysis}
-To account for uncertainty of input parameter values and to gain insight about the
-most influential parameters in the model, we used Latin Hypercube Sampling to analyze the deterministic model, implemented with the \texttt{lhs} package in \texttt{R}.  We varied 
-the 16 parameters from the original Hill model according to triangular distributions centered
-around their best-fit values, and two additional treatment cost parameters according to uniform distributions.  We obtained similar results to the Hill model 
-analyzing non-economic outcomes, as expected for validation.  For economic 
-outcomes, we found the parameter $f$, the fraction of FB arrivals with LTBI,
-to be highly correlated with the projected overall cost burden of TB in the United States
-over the next 100 years.  Another highly influential parameter in the model was $\sigma^{L}$, 
-the treatment rate for chronic LTBI.  However, while increasing $\sigma^{L}$ significantly
-decreases the cost burden due to Active TB treatment, it increases the cost burden due to Latent TB treatment by a greater amount, given the model estimates that Latent TB treament and Active
-TB treatment health care costs are approximately \$700 and \$14,000 per case cured respectively.  
-A full description of the Latin Hypercube Sampling analysis and tables of Partial Rank Correlation Coefficient (PRCC) results for all parameters are given in the Appendix, Section 7.6.  \\
+To account for uncertainty of input parameter values and to gain insight about
+the most influential parameters in the model, we used Latin Hypercube Sampling
+to analyze the deterministic model, implemented with the \texttt{lhs} package in
+\texttt{R}.  We varied the 16 parameters from the original Hill model according
+to triangular distributions centered around their best-fit values, and two
+additional treatment cost parameters according to uniform distributions.  We
+obtained similar results to the Hill model analyzing non-economic outcomes, as
+expected for validation.  For economic outcomes, we found the parameter $f$, the
+fraction of FB arrivals with LTBI, to be highly correlated with the projected
+overall cost burden of TB in the United States over the next 100 years.  Another
+highly influential parameter in the model was $\sigma^{L}$, the treatment rate
+for chronic LTBI.  However, while increasing $\sigma^{L}$ significantly
+decreases the cost burden due to Active TB treatment, it increases the cost
+burden due to Latent TB treatment by a greater amount, given the model estimates
+that Latent TB treament and Active TB treatment health care costs are
+approximately \$700 and \$14,000 per case cured respectively.  A full
+description of the Latin Hypercube Sampling analysis and tables of Partial Rank
+Correlation Coefficient (PRCC) results for all parameters are given in the
+Appendix, Section 7.6.
 
@@
 interventions? Also, the section below (future work) might be better just
-directly included in the discussion}\\
+directly included in the discussion. Also, if we want to make this claim here we
+need to include other interventions in the main body.}\\
+In addition, beyond demonstrating quantitatively that this intervention strategy
+is a necessary step towards US elimination, we also obtained qualitative
+indications that this is the case. In every intervention we tested (see, for
+example, Intervention <+ADD ME+> and <+ADD ME+> in section <+ADD ME+>) we
+observed a plateauing effect, where the incidence per million stabilized after
+some time and resisted further change. In particular, even when transmission was
+reduced to $0\%$, we still observed this plateauing effect, which implies that
+something other than active transmission was generating enough incidence to
+sustain TB in an endemic state in the US population. However, when the FB LTBI
+immigration was cut, this effect vanished. These results therefore support the
+argument that the USB LTBI population is sufficiently large to sustain a
+sizable, endemic TB-disease state in the United States provided it is
+continually refueled via the entering LTBI immigrants. Thus, there is no
+intervention that can ignore the LTBI population that can hope to eliminate TB
+in the United States. Among those interventions that treat cases of LTBI,
+targeting the immigrating LTBI requires no additional US HCS dollars beyond what
+is spent now to identify the LTBI population and is therefore extremely
+efficient. Additionally, our analysis shows that paying for the treatment of
+these individuals is extremely cost effective {\huge \color{red} TODO: Show
+this}.
 \subsection{Future Work}
@@
        & red5     & red10    & red25    & red50    \\ \hline
-  2000 & ND       & ND       & ND       & ND       \\ 
+  %2000 & ND       & ND       & ND       & ND       \\ 
   2025 & 67908.81 & 67855.46 & 67654.07 & 67332.53 \\ 

### 2014-02-15 in_progress/presentations/paper/draft.tex
Modifying discussion to discuss plateauing effect
working on draft. Edited Abstract and starting Introduction

@@
 
+{\huge \color{red} Check if first person is better.}
+
 \section{Abstract}
-An extended epidemiological model for Tuberculosis in the US was developed,
-based on an existing epidemiological model developed in 2012 by the Centers for
-Disease Control and Prevention.  Economic parameters to track the cost burden of
-TB for the US health care system were added.  The sensitivity of the extended
-model to changes in parameters was analyzed, and the percentage of foreign-born
-immigrants with LTBI appears to be a highly influential parameter in the model.
-Intervention strategies to reduce LTBI among foreign-born arrivals were
-evaluated, and estimates of the cost per case averted were found. Additionally,
-a population-level, stochastic, agent-based model was built to provide
-statistical verification of the results of the deterministic model and to
-demonstrate feasibility of agent-based modeling even on such large population
-scales.
+A deterministic, compartmental epidemiological and economic model for US
+Tuberculosis was developed, extending a model developed in 2012 by the Centers
+for Disease Control and Prevention. Sensitivity analysis of this model reveals
+that the percentage of foreign-born immigrants with LTBI is a highly influential
+parameter. Various intervention strategies, particularly those that reduced LTBI
+among foreign-born arrivals, were evaluated, and cost per case averted estimates
+were found.  Additionally, a population-level, stochastic, agent-based model was
+built. This model demonstrated the feasibility of using agent-based modeling in
+the context of minimal population heterogeneity and provided statistical
+characterization of the results of the compartmental model. Specifically, it
+revealed that final population sizes were normal, with the compartmental model
+sampling the mean of these distributions.
 
@@
 disease dynamics and intervention effectiveness. The most common examples of
-such models are compartmental differential equation models, in which the
-population is split between several possible health states, with flow between
-each state given according to deterministic differential equations. In 2012, 
-Hill, Becerra, and Castro implemented a compartmental
-differential equaiton model of tuberculosis (TB) in the United States (US).
-Their model utilized five health states and two subpopulations, US-born (USB)
-and foreign-born (FB) for a total of 10 compartments. They used this model to
-evaluate several possible intervention strategies, and ultimately conclude that
-though increasing LTBI treatment was a good intervention strategy, the US was
-unlikely to meet their stated goal of elimination of TB in the US by 2100. In
-this work, the Hill model was extended in several key ways. First, additional
+such models are detereministic, compartmental, differential equation models. In
+these models, the population is split between several possible health states, or
+compartments, and a system of differential equations governs population flow
+between the various compartments. In 2012, Hill, Becerra, and Castro implemented
+a compartmental differential equaiton model of tuberculosis (TB) in the United
+States (US).  Their model characterized five health states across two
+subpopulations, US-born (USB) and foreign-born (FB), for a total of 10
+compartments. They used this model to evaluate several possible intervention
+strategies and ultimately concluded that though increasing LTBI treatment was an
+effective intervention strategy, the US was unlikely to meet their stated goal
+of elimination of TB in the US by 2100. Here, we present an extended Hill model
+in which additional
 tracking capabilities were added to the Hill model, such that it can now report
@@
 
+{\huge \color{red}TODO: Update this to the one I made for my talk}
 \begin{figure}[h]
@@
        & red5    & red10    & red25    & red50    \\ \hline
-  2000 & 0.00    & 0.00     & 0.00     & 0.00     \\ 
+  %2000 & 0.00    & 0.00     & 0.00     & 0.00     \\ 
   2025 & 1115.12 & 2231.70  & 5592.43  & 11227.57 \\ 

### 2014-02-15 in_progress/presentations/paper/draft.tex
Finished Intro and Background

@@
 of elimination of TB in the US by 2100. Here, we present an extended Hill model
-in which additional
-tracking capabilities were added to the Hill model, such that it can now report
-further granularity in the disease dynamics. Further, economic components were
-added to the model in order to project the US health care system (HCS) costs due
-to TB given our current policy as well as for various interventions.
+with additional tracking capabilities, such that it can now report
+further granularity in the disease dynamics. Furthermore, this model also tracks
+economic data in order to project the US health care system (HCS) costs due to
+TB given our current policy as well as in the context of various interventions.
+
+{\huge \color{red} Fix this paragraph. Its not the best. \textbackslash/}
 
 Though compartmental, differential equation models are the most common strategy
-when modeling large-scale diseases at the population level with minimal age
-stratification, an alternative approach is to use an agent-based model. Agent
+when modeling large-scale diseases at the population level, an alternative
+approach is to use an agent-based model. Agent
 based models provide a more nuanced view of disease spread as they provide a
-more biologically reasonable framework; however, they are often considered to be
-computationally infeasible at population level. In this work, a stochastic,
-agent-based model of US TB was implemented which was used at the population
-level to both provide statistical verification of the Hill Model and to
-demonstrate the computational feasibility of an agent-based modeling framework
-for general disease modeling.
+more biologically accurate modeling framework; however, they are often
+considered to be computationally infeasible at population level. In order to
+challenge this assumption of infeasibility and provide statistical verification
+of the results of the compartmental model, we implemented a stochastic,
+agent-based model of US TB dynamics at the population level.
 
 \section{Background}
+\subsection{Tuberculosis}
+{\huge \color{red} Add background info about TB. Latent phase, etc. I think it
+makes sense to give it its own section.}
+\subsection{The Hill Model}
+A flowchart representation of the Hill Model is shown in
+Figure~\ref{fig:hillModelSchematic}. Each compartment represents a different
+possible health state with respect to TB for every US-born or foreign-born
+individual, and arrows between different compartments represent possible
+transitions between states.  Individuals also leave the model from all
+compartments due to natural death, which is left out of the figure for clarity.
 
-\subsection{The Hill Model}
-A flowchart representation of the Hill Model is shown in Figure 1.  Each compartment
-represents a different possible health state with respect to TB for every 
-US-born or foreign-born individual, and arrows between different compartments
-represent possible transitions between states.  Individuals also leave the model 
-from all compartments due to natural death, which is left out of the figure for clarity.  \\
-
-{\huge \color{red}TODO: Update this to the one I made for my talk}
 \begin{figure}[h]
@@
 compartment. Individuals in the Chronic LTBI compartment may also be
-exogenously re-infected and transition to the Acute LTBI compartment.  \\
+exogenously re-infected and transition to the Acute LTBI compartment.
 
@@
 does not grant immunity, and all healthy individuals are grouped in the Susceptible compartment
-and may be re-infected at a later time.  \\
+and may be re-infected at a later time.
+
+{\huge\color{red} This section is good, but we may want to give a summary of the
+differential equations at the end.}
 

### 2014-02-15 in_progress/presentations/paper/draft.tex
Working on Methods

@@
 \subsection{Basic Structure}
-Both the Hill Model (Basic Hill Model) and an extended version of the Hill Model
-(Extended Hill Model) were implemented in \texttt{R} as a system of differential
-equations, which were solved via the $\texttt{lsoda}$ routine. The systems of
-differential equations used to capture basic disease dynamics in the Basic Hill
-Model are shown in Figure 2. In the Extended Hill Model, more differential
-equations were implemented to add additional tracking and economic modeling.
-These equations are detailed in the Appendix, Section 7.2.  Historical data from
-2000-2008 was used to initialize the model, which was then run up to the
-year 2100.
+Both the Hill Model (Basic Hill Model) and our extended Model (Extended Hill
+Model) were implemented in \texttt{R} as a system of differential equations,
+which were solved via the $\texttt{lsoda}$ routine. The systems of differential
+equations used to capture basic disease dynamics in the Basic Hill Model are
+shown in Figure~\ref{fig:hillEquations}. In the Extended Hill Model, more
+differential equations were implemented to add additional tracking and economic
+modeling. These equations are detailed in the\\
+{\huge\color{red} Should appendix be capitalized? What about Figure?}\\
+appendix,
+section~\ref{sec:extendedHillEqs}.  Historical data from 2000-2008 was used to
+initialize the model, which was then run up to the year 2100.
 
 \begin{figure} 
+  {\huge\color{red} Make this not a figure. This should definitely just be tex.}
   \begin{center}
@@
 
-The vector variables $S_{0}, F_{0}, L_{0}, I_{0}, J_{0}$ contain the number of
-US-born individuals in the S, F, L, I, J compartments respectively, whereas $S_{1},
-F_{1}, L_{1}, I_{1}, J_{1}$ contain foreign-born individuals.  $N_{0}$ and
-$N_{1}$ are the total populations of US-born and foreign-born individuals.
-The constants $\rho$ and $\alpha$ are birth rates, while $\mu_{i}$, and $\mu_{d}$ are death rates.  
-A complete list and descriptions of all constants used in the model can be found in the Appendix,
-Section 7.1.
+The vector variables $S_0, F_0, L_0, I_0, J_0$ contain the number of US-born
+individuals in the S, F, L, I, J compartments respectively, whereas $S_1, F_1,
+L_1, I_1, J_1$ contain the number of foreign-born individuals. $N_0$ and $N_1$
+are the total populations of US-born and foreign-born individuals.  The
+constants $\rho$ and $\alpha$ are birth rates, while $\mu_{i}$, and $\mu_{d}$
+are death rates. A complete list and descriptions of all constants used in the
+model can be found in the Appendix, Section~\ref{subsec:hillConstants}.
 
@@
 \subsection{Hill Constants}
+\label{subsec:hillConstants}
 Below, we detail some of the relevant constants in the Basic Hill Model, and
@@
 \subsection{The Extended Hill Equations}
+\label{sec:extendedHillEqs}
 Below, we detail some of the relevant equations used in the extended hill model.

### 2014-02-15 in_progress/presentations/paper/draft.tex
Starting agent-based methods section

@@
 equations used to capture basic disease dynamics in the Basic Hill Model are
-shown in Figure~\ref{fig:hillEquations}. In the Extended Hill Model, more
-differential equations were implemented to add additional tracking and economic
-modeling. These equations are detailed in the\\
+shown in Figure~\ref{fig:hillEquations}.  In the Extended Hill Model, each flow
+rate equation from the Basic Hill Model was separated into its component part
+and these were tracked separately. In other words, rather than tracking net flow
+into various compartments, the Extended Hill Model tracks flow between all pairs
+of compartments separately. Furthermore, these equations were each also supplemented to
+also estimate their corresponding US HCS costs.  These equations are detailed in
+the\\
 {\huge\color{red} Should appendix be capitalized? What about Figure?}\\
@@
 are the total populations of US-born and foreign-born individuals.  The
-constants $\rho$ and $\alpha$ are birth rates, while $\mu_{i}$, and $\mu_{d}$
-are death rates. A complete list and descriptions of all constants used in the
-model can be found in the Appendix, Section~\ref{subsec:hillConstants}.
+constants $\rho$ and $\alpha$ are birth rates, while $\mu_i$, and $\mu_d$ are
+death rates. A complete list and descriptions of all constants used in the model
+can be found in the Appendix, Section~\ref{subsec:hillConstants}.
 
 \subsection{Additional Tracking Capabilities}
-In order to refine the tracking capabilities of the
-Hill Model, the original differential equations used to describe TB spread were
-separated into their component parts and each section was tracked separately.
+In order to refine the tracking capabilities of the Hill Model, the original
+differential equations used to describe TB spread were separated into their
+component parts and each section was tracked separately.
 These components were made into compartments, tracked by differential equations
-detailed in the appendix. These equations allowed the model to track the total
-number of TB cases, TB deaths, and  natural deaths. Further, the model tracks,
-the sourced cost on the US HCS. Progressions into
-active TB due to activations of LTBI or exogenous infection were tracked,
-allowing for sourced incidence data to be generated. The entering cases of LTBI
-(acute or chronic) were also tracked. In the case of intervention testing, the
-number of cured and untreated cases of entering LTBI were both tracked. Cured
-cases of LTBI entering, TB deaths, total TB cases, and total cost were also
-tracked discounted at 3\% annually. This discounting was converted to a
-continuous differential equation for use within the model. In general, incidence
-data is calculated in the same way in the Extended Hill Model as it was in the Basic
-Hill Model.
+detailed in the appendix. Progressions into active TB due to activations of LTBI
+or exogenous infection were tracked, allowing for sourced incidence data to be
+generated. These equations allowed the model to track the sourced number of TB
+cases, TB deaths, and natural deaths. Furthermore, the model also tracks the
+sourced cost on the US HCS. The immigrating cases of LTBI (acute or chronic)
+were also tracked. In the case of intervention testing, the number of cured and
+untreated cases of entering LTBI were both tracked. Cured cases of LTBI
+entering, TB deaths, total TB cases, and total cost were also tracked discounted
+at 3\% annually. This discounting was converted to a continuous differential
+equation for use within the model. In general, incidence data is calculated in
+the same way in the Extended Hill Model as it was in the Basic Hill Model.
 
@@
 perspective. Experimental data were calculated by reducing the initial
-population of FB or USB active, infectious TB cases by one and allowing the
+FB or USB infectious TB populations by one and allowing the
 model to progress otherwise as normal. The decreased number of total TB cases
 seen details how many infections can be thought to be due to one infected
-individual in the given population.
+individual in the given population. In the agent-based model, this \emph{one}
+was a true model agent whereas in the compartmental model, this decrease of
+\emph{one} was a proportional decrease based on the scaled population level.
 
-From an experimental perspective, the spread of TB was thought to be a geometric
+From a theoretical perspective, the spread of TB was thought to be a geometric
 series. If one infectious individual infects $x$ people annually, over the
@@
 term $1$. In this case, $N = 100$, and the ratios for FB infectious individuals
-and USB infectious individuals were obtained from RATIO CITATION COLIN. 
+and USB infectious individuals were obtained from <+RATIO CITATION COLIN+>
 \subsection{Economic Modeling}
-When tracking the economic implications of current US TB load and various
-intervention strategies, active TB costs were given by \$14,000. This cost is
-the weighted mean of the costs of cases requiring hospitalization (happening
-49\% of the time) and cases not requiring hospitalization (51\%). These data
-were found in DYLAN COST STUDY CITATION. LTBI treatment costs were given by
-\$468.00. These data were based on the cost of a successfull treatment, given by
-DYLAN COST STUDY CITATION, as well as adherence and efficacy data found in
-ADHERENCE CITATION.
+In order to track the US HCS economic load given the TB rates, we made the
+following treatment cost assumptions. A single case of active TB was assumed to
+yield a \$14,000 US HCS cost, charged immediately upon disease contraction. This
+cost is the weighted mean of the costs of cases requiring hospitalization
+(happening 49\% of the time) and cases not requiring hospitalization (51\%).
+These cost estimates were found in <+DYLAN COST STUDY CITATION+>. LTBI treatment
+costs were given by \$468.00 US HCS cost, charged immediately upon successful
+treatment. These estimates were calculated based on the cost of a successfull
+treatment, and the typical adherence and efficacy of said treatment <+DYLAN COST
+STUDY CITATION, ADHERENCE CITATION+>. It is important to note that the charging
+assumptions are different for treatment of active TB as opposed to treatment of
+latent TB. In particular, cases of active TB imply a cost immediately upon
+disease contraction, whereas latent TB costs are charged only upon successful
+treatment. The motivation for this distinction is that active TB treatment is
+mandated by the US for all known cases and, further, most treatment costs are
+incurred at the beginning of the treatment cycle. As such, charging for every
+known case, immediately at contraction is a well motivated assumption. On the
+other hand, latent TB is only rarely treated in discovered cases and the costs
+are more evenly distributed. Furthermore, the choice to charge only upon
+successful treatment yields a more conservative estimate of the success of any
+intervention analyzed.
 
-From these estimated cost per treatment, total costs were obtained by assuming
-that every patient with active TB in the US is treated at full price, though the
-treatment may fail. As individuals with active
-TB are charged upon entry to the active TB compartment, the model can also
-accurately estimate sourced US HCS cost data. Cost data were separately tracked
-due to incoming active TB costs stemming from activation of LTBI vs exogenous
-reinfection. These data were modelled as additional compartments and also solved
-by $\texttt{lsoda}$. For LTBI treatment cost, treatment was
-charged upon leaving the LTBI compartment due to the cumulative self-cure and
-treatment rate given in the Hill Model. The fraction of these indviduals who
-leave this compartment due to self cure was assumed to be zero. Given the
+Cost data were separately tracked due to incoming active TB costs stemming from
+activation of LTBI vs exogenous reinfection. These data were modelled as
+additional compartments and also solved by $\texttt{lsoda}$.  Given the
 uncertainty in measurments of LTBI treatment cost, extensive sensitivity

### 2014-02-15 in_progress/presentations/paper/draft.tex
added table comment
Finished methods

@@
 implementations were built in \texttt{Netlogo} and \texttt{Java}, but final
-implementations were constructed in $\texttt{C++}$. An implementation was made
-that tracked the hill model exactly, up to still including the Acute Latent
-compartment in the model. Probabilites of agent progression between various
-health states were computed given rates in the hill model and a variety of
-approximations. The model maintained scaled individual records for every
-individual with LTBI, with susceptible individuals not modelled as agents.
-Instead, a binomial distribution was used to probabilistically pick the number
-of new infections each time step. Similarlly, immigration was also handeled
-outside of the agent-based modelling. The final size standard deviation and
-distribution data was collected via 2160 (MINUS SOME) runs with each agent in
-the model truly representing one infected individual and a time step of $0.01$.
-These data were analyzed in $R$. This model was also made to track deaths, total
-TB cases, and infection sources. This data were consistent with the
-deterministic model, and not reproduced in this write-up.
+implementations were constructed in $\texttt{C++}$. Probabilites of agent
+progression between various health states were computed given rates in the hill
+model and a variety of integration approximations. The model maintained
+individual records for every individual with LTBI or active TB. Susceptible
+individuals were not modelled as agents; instead, a binomial distribution was used to
+probabilistically determine the number of new infections each time step.
+Similarlly, the number of new immigrants each time step was chosen from a
+probability distribution. We collected final population distribution data via
+<+NUMBER OF RUNS 2160+> runs with each agent in the model truly representing one
+infected individual and a time step of $0.01$.  These data were analyzed in $R$.
+This model was also made to track deaths, total TB cases, and infection sources,
+as well as economic data. These data were consistently normal and matched the
+deterministic model.
 
@@
 Hill Model is a vestigal necessity of compartmental modeling and not reflective
-of the biology of tuberculosis, and an agent based model was implemented that
-more closely respects the biology of tuberculosis. Results from this model or
-the strict Hill model did not differ significantly.
+of the biology of tuberculosis. As such, an agent based model was implemented
+that more closely respects the biology of tuberculosis. Results from this model
+were also normal and did not differ significantly from the strict Hill model.
 

### 2014-02-15 in_progress/presentations/paper/draft.tex
Starting results

@@
 further agrees with the conclusions drawn by Hill, Becerra, and Castro about the
-necessity of LTBI treatment in any valuable intervention strategy. 
+necessity of LTBI treatment in any effective intervention strategy. 
 \begin{figure}[h]
@@
 Further, figure~\ref{fig:costPlotSourced} shows a similarly sourced plot, but analyzing the
-final US HCS costs due to TB. One can see that in this plot, roughly half of the
-US TB HCS costs are due to activations of LTBI. In this data, it is appropriate
-to think of the costs due to acute LTBI are due to exogenous re-inection,
-whereas active TB costs due to chronic LTBI are activations of LTBI into active
-TB. 
+final US HCS costs due to active TB. One can see that in this plot, roughly half
+of the US TB HCS costs are due to activations of LTBI. Note that In this data,
+it is appropriate to think of the costs due to acute LTBI as costs due to
+exogenous re-inection, whereas active TB costs due to chronic LTBI are
+activations of long standing latent infections into active TB. 
 \begin{figure}[h]

### 2014-02-15 in_progress/presentations/paper/draft.tex
Final commit for a while so Colin can look over stuff

@@
 to incidence and costs directly, but also indirectly by causing additional
-future cases, which is not captured in these graphs. Further, there is also US
-HCS costs due to treating LTBI, which is not illustrated in these graphs. 
+future cases, which is not captured in these graphs. Further, there are also US
+HCS costs due to LTBI treatment, which is not illustrated in these graphs. 
 \subsubsection{Basic Reproduction Number}
@@
 \label{tab:cpcaRed}
+{\huge\color{red} We need to remake this table for Cure = $600, $1000, $1200, $1400, $1600
+and put it in the appendix.}
 \end{table}

### 2014-02-15 in_progress/presentations/paper/draft.tex
editted abstract

@@
 \section{Abstract}
-A deterministic, compartmental epidemiological and economic model for US
+A epidemiological and economic model for US
 Tuberculosis was developed, extending a model developed in 2012 by the Centers
@@
 figure~\ref{fig:qqnormPlots}. These plots demonstrate the normality of the
-Stocahstic Data. 
+Stochastic data. 
 \subsection{Finer Intervention Analysis}
@@
 \label{tab:cpcaRed}
-{\huge\color{red} We need to remake this table for Cure = $600, $1000, $1200, $1400, $1600
-and put it in the appendix.}
 \end{table}

### 2014-02-15 in_progress/presentations/paper/draft.tex
not much

@@
 
-{\huge \color{red} Check if first person is better.}
+{\huge \color{red} Check if first person is better. List of results}
 
 \section{Abstract}
-A epidemiological and economic model for US
+An epidemiological and economic model for US
 Tuberculosis was developed, extending a model developed in 2012 by the Centers

### 2014-02-15 in_progress/presentations/paper/draft.tex
editted paper comments

@@
 
-{\huge \color{red} Check if first person is better. List of results}
+{\huge \color{red} List of results}
 
@@
 does not grant immunity, and all healthy individuals are grouped in the Susceptible compartment
-and may be re-infected at a later time.
-
-{\huge\color{red} This section is good, but we may want to give a summary of the
-differential equations at the end.}
+and may be re-infected at a later time.\\
 
@@
 the\\
-{\huge\color{red} Should appendix be capitalized? What about Figure?}\\
+{\huge\color{red} Add extended Hill equations to the appendix.}\\
 appendix,

### 2014-02-15 in_progress/presentations/paper/draft.tex
improved abstract

@@
 \section{Abstract}
-An epidemiological and economic model for US
-Tuberculosis was developed, extending a model developed in 2012 by the Centers
+An epidemiological and economic model for tuberculosis in the United States
+ was developed, extending a model developed in 2012 by the Centers
 for Disease Control and Prevention. Sensitivity analysis of this model reveals
@@
 the context of minimal population heterogeneity and provided statistical
-characterization of the results of the compartmental model. Specifically, it
-revealed that final population sizes were normal, with the compartmental model
-sampling the mean of these distributions.
+characterization of the results of the compartmental model. The distributions
+of the final population sizes and incidence rates projected by the stochastic model
+were found to be approximately normal, with means centered at the results of
+compartmental model.
 
@@
 {\huge \color{red} Add background info about TB. Latent phase, etc. I think it
-makes sense to give it its own section.}
+makes sense to give it its own section. COLIN}
 \subsection{The Hill Model}

### 2014-03-02 in_progress/presentations/paper/draftOld.tex

@@
 
-\title{Modeling Intervention Strategies for United States TB Control}
+\title{Modeling Intervention Strategies for United States Tuberculosis Control}
 \begin{document}
@@
 \section{Abstract}
-An extended epidemiological model for Tuberculosis in the US was developed,
-based on an existing epidemiological model developed in 2012 by the Centers for
+An extended epidemiological model of tuberculosis in the United States was developed,
+based on an existing model developed in 2012 by the Centers for
 Disease Control and Prevention.  Economic parameters to track the cost burden of
-TB for the US health care system were added.  The sensitivity of the extended
+tuberculosis for the United States health care system were added.  The sensitivity of the extended
 model to changes in parameters was analyzed, and the percentage of foreign-born
-immigrants with LTBI appears to be a highly influential parameter in the model.
-Intervention strategies to reduce LTBI among foreign-born arrivals were
-evaluated, and estimates of the cost per case averted were found. Additionally,
+immigrants with latent tuberculosis infection appears to be a highly influential parameter
+ in the model. Intervention strategies to reduce latent tuberculosis infection among foreign-born arrivals were evaluated, and estimates of the cost per case averted were found. Additionally,
 a population-level, stochastic, agent-based model was built to provide

### 2014-03-02 in_progress/presentations/paper/draft.tex
modified draft

@@
 {\huge \color{red} List of results}
+\begin{itemize}
+  \item Plateauing Effect
+  \item Intervention Analysis
+  \item Statistical Analysis of Hill Model
+  \item Agent-Based Feasibility
+  \item Theoretical/Experimental justification of basic reproduction number
+  \item Overall qualitative strategy conclusions. 
+\end{itemize}<++>
 
@@
 final US HCS costs due to active TB. One can see that in this plot, roughly half
-of the US TB HCS costs are due to activations of LTBI. Note that In this data,
+of the US TB HCS costs are due to activations of LTBI. Note that in this data,
 it is appropriate to think of the costs due to acute LTBI as costs due to
-exogenous re-inection, whereas active TB costs due to chronic LTBI are
-activations of long standing latent infections into active TB. 
+exogenous re-inection, whereas costs due to chronic LTBI are activations of long
+standing latent infections. 
 \begin{figure}[h]
@@
 \end{figure}
-Note that both of these plots underestimate the impact LTBI activations play in
-the spread of TB, as every LTBI activation to infectious TB contributes not only
+Note that both of these plots underestimate the impact of LTBI on the spread of
+TB, as every LTBI activation contributes not only
 to incidence and costs directly, but also indirectly by causing additional
@@
 respectively, then we can say that over the course of 100 years, the total
-number of cases infected will follow a geometric series. This analysis predicts
+number of cases infected will follow a geometric series.
+{\huge \color{red} TODO: formalize this with math. We can fit it here.}
+This analysis predicts
 that over 100 years, one USB infection will lead to $1.04$ subsequent infections,
@@
 curing various percentages of entering LTBI cases. Four indicative percentages
-chosen were $5\%$, $10\%$, $25\%$, and $50\%$. Note that the Hill model does
-not distinguish documented immigration from undocumented immigration, and as
-such estimates of entering LTBI cure rates higher than $50\%$ become much more
-difficult to achieve. It was seen that in this model as well as in the basic
-Hill, no analyzed intervention predicted elimination by 2100. In order to obtain
+chosen were $5\%$, $10\%$, $25\%$, and $50\%$. Note that the Hill model does not
+distinguish between documented and undocumented immigration, so these
+percentages are over \emph{all} immigration into the United States, and can thus
+be thought to represent significantly higher percentages of documented
+immigration. It was seen that in this model as well as in the Basic Hill Model,
+no analyzed intervention predicted elimination by 2100. In order to obtain
 elimination by 2100, at least 95\% of entering LTBI cases had to be cured, which
-is practically impossible. However, it was seen that curing entering cases of
+is infeasible in the real world. However, it was seen that curing entering cases of
 LTBI resulted in a net US HCS cost per case averted of \$67,654.07 at 2025, \$28,699.15 at 2050,
@@
 treatment cost, the model code is extendible such that a user can adjust these
-costs themselves to explore more specific methods of curing entering LTBI.
+costs themselves to explore more specific methods of curing entering LTBI,
+especially as the treatment methods and associated costs evolve in future years.
 Further, it was also found that the relationship between total incidence at 2100
@@
 reduction, respectively.
+{\huge \color{red} TODO: This section is a bit confusing. Also, a graph would
+make things much prettier.}
 
@@
 
-Several other intervention strategies analyzed by the Hill Model were refined
-with the Extended Hill, and economic properties about each of them were tracked.
-The results for these interventions, which are less effective than curing
-entering LTBI cases across the board, are given in the appendix.
+Several other intervention strategies analyzed by the Hill Model were also
+examined via the Extended Hill, and economic properties about each were tracked.
+The results for these interventions, which were consistently less effective than
+curing entering LTBI cases, are given in the appendix. {\huge \color{red} TODO:
+Which section?}
 
@@
 to triangular distributions centered around their best-fit values, and two
-additional treatment cost parameters according to uniform distributions.  We
-obtained similar results to the Hill model analyzing non-economic outcomes, as
-expected for validation.  For economic outcomes, we found the parameter $f$, the
-fraction of FB arrivals with LTBI, to be highly correlated with the projected
-overall cost burden of TB in the United States over the next 100 years.  Another
-highly influential parameter in the model was $\sigma^{L}$, the treatment rate
-for chronic LTBI.  However, while increasing $\sigma^{L}$ significantly
-decreases the cost burden due to Active TB treatment, it increases the cost
-burden due to Latent TB treatment by a greater amount, given the model estimates
-that Latent TB treament and Active TB treatment health care costs are
-approximately \$700 and \$14,000 per case cured respectively.  A full
-description of the Latin Hypercube Sampling analysis and tables of Partial Rank
-Correlation Coefficient (PRCC) results for all parameters are given in the
-Appendix, Section 7.6.
+additional treatment cost parameters according to uniform distributions.
+{\huge\color{red} TODO: These distributions were chosen because\ldots}. All
+non-economic parameters analyzed reported statistically similar results to their
+analysis in the Basic Hill Model. For economic outcomes, we found the parameter
+$f$, the fraction of FB arrivals with LTBI, to be highly correlated with the
+projected overall cost burden of TB in the United States over the next 100
+years.  Another highly influential parameter in the model was $\sigma^{L}$, the
+treatment rate for chronic LTBI.  However, while increasing $\sigma^{L}$
+significantly decreases the cost burden due to Active TB treatment, it increases
+the cost burden due to Latent TB treatment by a greater amount, given the
+treatment cost estimates of \$700 and \$14,000 for LTBI and Active TB,
+respectively.  A full description of the Latin Hypercube Sampling analysis and
+tables of Partial Rank Correlation Coefficient (PRCC) results for all parameters
+are given in the appendix, in Section~\ref{subsec:lhs}.
 
@@
 final population sizes were normal, with mean accurate to the deterministic
-model and standard deviations given in table X, in the Appendix. Additionally,
+model and standard deviations given in table {\huge\color{red} TODO: Add table
+\# and section \# here}, in the Appendix. Additionally,
 the agent-based model provided a computational framework to produce
-meaningful intervention results. On lab-grade, student hardware, a statistically
-meaningful experiment could be run overnight, producing data in a day. This
+meaningful intervention results. On student lab gradet hardware, a statistically
+meaningful experiment could be run overnight, producing data in one day. This
 demonstrates that this modeling strategy is feasible in this general case.
+Furthermore, the agent-based model provides a greater extensibility to more
+specific and biologically reasonable scenarios, such as geographic dependency or
+greater population heterogenity.
 
@@
 option. \\
-{\huge \color{red} Where did we show it was cost effective relative to other
+{\huge \color{red} TODO: Where did we show it was cost effective relative to other
 interventions? Also, the section below (future work) might be better just
@@
 indications that this is the case. In every intervention we tested (see, for
-example, Intervention <+ADD ME+> and <+ADD ME+> in section <+ADD ME+>) we
+example, Intervention {\huge\color{red} TODO}<+ADD ME+> and <+ADD ME+> in section <+ADD ME+>) we
 observed a plateauing effect, where the incidence per million stabilized after
@@
 
-\subsection{Latin Hypercube Sampling}
+\subsection{Latin H ypercube Sampling}
+\label{subsec:lhs}
 %The model parameters and variable names referred to in this analysis are listed

### 2014-03-02 in_progress/presentations/paper/draft.tex
modified draft.tex to remove formatting weirdness
added results plan
spelling correction
added Background on TB

@@
 {\huge \color{red} List of results}
+Plan:
+\begin{enumerate}
+  \item Intervention Analysis: 
+    \begin{enumerate}
+      \item Reducing Entering LTBI
+      \item Cutting Transmission
+      \item Reducing Progression Rate
+    \end{enumerate}
+  \item Qualitative Strategy Conclusions:
+    \begin{enumerate}
+      \item Sourced Incidence \& Cost
+      \item Plateauing Effect
+      \item Extremal values for entering LTBI reduction
+      \item Linearity in Cost/Incidence for entering LTBI reduction
+      \item CPCA data
+    \end{enumerate}
+  \item Statistical Verification/Agent Based Feasibility
+    \begin{enumerate}
+      \item Normal Distributions
+      \item Basic Reproductive Numbers
+      \item Agetn based running time \& Extensibility. 
+    \end{enumerate}
+\end{enumerate}
+Ideas:
 \begin{itemize}
@@
   \item Overall qualitative strategy conclusions. 
-\end{itemize}<++>
+\end{itemize}
 
@@
 \subsection{Tuberculosis}
-{\huge \color{red} Add background info about TB. Latent phase, etc. I think it
-makes sense to give it its own section. COLIN}
+Tuberculosis is an infectious bacterial disease that primarily affects the lungs,
+with common symptoms including severe coughing, fevers, and chest pain.
+Tuberculosis is a major global health concern, the World Health Organization
+ estimates that 8.6 million developed TB and and 1.3 million people died from
+ the disease in 2012.  As an airborne disease, \emph{Mycobacterium tuberculosis}
+ is typically transmitted from person-to-person by coughing, sneezing, and the 
+exchange of other respiratory fluids.  Infected individuals first enter a latent phase,
+ during which \emph{Mycobacterium tuberculosis} is present in their bodies,
+but the individuals remain asymptomatic and noncontagious. 
+The lifetime risk of progressing from Latent TB Infection (LTBI) to Active TB is approximately
+5-10\%, although individuals with LTBI have the greatest chance of developing 
+Active TB during the first two years immediately following infection. 
+Cases of Active TB may be classified as pulmonary (~80\% of cases) or 
+non-pulmonary (~20\% of cases), depending upon the biological location of infection.
+In the Hill model, pulmonary Active TB is treated as contagious and non-pulmonary 
+Active TB is treated as  non-contagious, which is an assumption we also use here.  \\
+
+In the United States, 9,951 new cases of TB were reported in 2012 by the Centers for Disease
+Control. The disease burden varied for different subpopulations in the U.S., and in particular
+the incidence rate of TB was 11.5 times higher for the foreign-born (FB) population
+than the US-born (USB) population.  For the past 20 years, the overall incidence of
+TB in the U.S. has declined each year, but in 2012 the annual incidence level of 32 new cases/million
+remains above the desired goal of the $<$1 new case/million, which is the target
+for disease elimination set by the Centers for Disease Control. \\
+
+citations: CDC Tuberuclosis 2013 Report - http://www.cdc.gov/mmwr/preview/mmwrhtml/mm6211a2.htm
+WHO Global Tuberculosis Report 2013 - http://www.who.int/tb/publications/global\_report/en/ \\
+
 \subsection{The Hill Model}

### 2014-03-02 in_progress/presentations/paper/draft.tex
notation edits

@@
       \item Basic Reproductive Numbers
-      \item Agetn based running time \& Extensibility. 
+      \item Agent based running time \& Extendibility. 
     \end{enumerate}
@@
 Active TB during the first two years immediately following infection. 
-Cases of Active TB may be classified as pulmonary (~80\% of cases) or 
-non-pulmonary (~20\% of cases), depending upon the biological location of infection.
+Cases of Active TB may be classified as pulmonary ($\sim$80\% of cases) or 
+non-pulmonary ($\sim$20\% of cases), depending upon the biological location of infection.
 In the Hill model, pulmonary Active TB is treated as contagious and non-pulmonary 

### 2014-07-14 in_progress/presentations/paper/draft.tex
Working on draft. This paper is definitely getting out.

@@
+% arara: pdflatex
+% arara: bibtex
+% arara: pdflatex
+% arara: pdflatex
 \documentclass{amsart}
@@
 \graphicspath{{figures/}}
+
+\newcommand{\TODO}[1]{\hfill\\{\huge \color{red} TO DO:} #1 \hfill \\}
 
@@
 for Disease Control and Prevention. Sensitivity analysis of this model reveals
-that the percentage of foreign-born immigrants with LTBI is a highly influential
+that the percentage of foreign born immigrants with LTBI is a highly influential
 parameter. Various intervention strategies, particularly those that reduced LTBI
@@
 economic data in order to project the US health care system (HCS) costs due to
-TB given our current policy as well as in the context of various interventions.
+TB given our current policy, as well as in the context of various interventions.
 
@@
 \section{Background}
-\subsection{Tuberculosis}
+\subsection{Tuberculosis} x 
+\TODO{Use TB instead of Tuberculosis maybe?}
 Tuberculosis is an infectious bacterial disease that primarily affects the lungs,
 with common symptoms including severe coughing, fevers, and chest pain.
-Tuberculosis is a major global health concern, the World Health Organization
- estimates that 8.6 million developed TB and and 1.3 million people died from
- the disease in 2012.  As an airborne disease, \emph{Mycobacterium tuberculosis}
- is typically transmitted from person-to-person by coughing, sneezing, and the 
-exchange of other respiratory fluids.  Infected individuals first enter a latent phase,
- during which \emph{Mycobacterium tuberculosis} is present in their bodies,
-but the individuals remain asymptomatic and noncontagious. 
-The lifetime risk of progressing from Latent TB Infection (LTBI) to Active TB is approximately
+Tuberculosis is a major global health concern; The World Health Organization
+estimates that 8.6 million developed TB and 1.3 million people died from
+the disease in 2012. Tuberculosis is an airborne disease and is typically
+transmitted from person-to-person by coughing, sneezing, and the exchange of
+other respiratory fluids.  Infected individuals first enter a latent phase,
+during which the disease causing agent, \emph{Mycobacterium tuberculosis}, is
+present in their bodies, but the individuals remain asymptomatic and
+noncontagious. During this phase, individuals are said to have latent TB
+infection (LTBI). Eventually, some number of individuals with LTBI progress into
+what is known as the active phase of the disease, or active TB. Individuals with
+an active TB infection are symptomatic and contagious. The lifetime risk of
+progressing from Latent TB Infection (LTBI) to active TB is approximately
 5-10\%, although individuals with LTBI have the greatest chance of developing
-Active TB during the first two years immediately following infection. 
-Cases of Active TB may be classified as pulmonary ($\sim$80\% of cases) or 
-non-pulmonary ($\sim$20\% of cases), depending upon the biological location of infection.
-In the Hill model, pulmonary Active TB is treated as contagious and non-pulmonary 
-Active TB is treated as  non-contagious, which is an assumption we also use here.  \\
+Active TB during the first two years immediately following infection, and if
+they have a suppressed immune system, such as in the case of a comorbid HIV
+infection. Cases of Active TB may be classified as pulmonary ($\sim$80\% of
+cases) or non-pulmonary ($\sim$20\% of cases), depending upon the biological
+location of infection. In the Hill model, pulmonary Active TB is treated as
+contagious and non-pulmonary Active TB is treated as non-contagious, which is an
+assumption we also use here.
 
-In the United States, 9,951 new cases of TB were reported in 2012 by the Centers for Disease
-Control. The disease burden varied for different subpopulations in the U.S., and in particular
-the incidence rate of TB was 11.5 times higher for the foreign-born (FB) population
-than the US-born (USB) population.  For the past 20 years, the overall incidence of
-TB in the U.S. has declined each year, but in 2012 the annual incidence level of 32 new cases/million
-remains above the desired goal of the $<$1 new case/million, which is the target
-for disease elimination set by the Centers for Disease Control. \\
+In the United States, 9,951 new cases of TB were reported in 2012 by the Centers
+for Disease Control. The disease burden varied for different subpopulations in
+the U.S., and, in particular, the incidence rate of TB was 11.5 times higher for
+the FB population than the USB population.  For the
+past 20 years, the overall incidence of TB in the U.S. has declined each year,
+but in 2012 the annual incidence level of 32 new cases/million remains above the
+desired goal of the $<$1 new case/million, which is the target for disease
+elimination set by the Centers for Disease Control.
 
-citations: CDC Tuberuclosis 2013 Report - http://www.cdc.gov/mmwr/preview/mmwrhtml/mm6211a2.htm
-WHO Global Tuberculosis Report 2013 - http://www.who.int/tb/publications/global\_report/en/ \\
+\TODO{}citations: CDC Tuberuclosis 2013 Report - http://www.cdc.gov/mmwr/preview/mmwrhtml/mm6211a2.htm
+WHO Global Tuberculosis Report 2013 - http://www.who.int/tb/publications/global\_report/en/
 
@@
 Figure~\ref{fig:hillModelSchematic}. Each compartment represents a different
-possible health state with respect to TB for every US-born or foreign-born
-individual, and arrows between different compartments represent possible
-transitions between states.  Individuals also leave the model from all
-compartments due to natural death, which is left out of the figure for clarity.
+possible TB health state for every US-born or FB individual, and
+arrows between different compartments represent possible transitions between
+states. Individuals also leave the model from all compartments due to natural
+death, which is left out of the figure for clarity.
 
@@
 The majority of USB and FB individuals fall into the Susceptible (S) category,
-which includes everyone who is uninfected and has not been exposed to TB.  After
-exposure to an individual with TB, a person in the Susceptible compartment can
-develop Latent TB Infection (LTBI). Latently infected individuals are
-asymptomatic and non-infectious, but have some risk of developing active TB
-infection over time. To reflect the fact that real LTBI patients have a
-much higher risk of developing active TB within two years of exposure, the Hill
-Model splits the LTBI compartment into Acute LTBI (fast progressors) and Chronic
-LTBI (slow progressors). Accordingly, individuals in the Acute LTBI compartment
-have a higher risk of developing active TB than those in the Chronic LTBI
-compartment. Individuals in the Chronic LTBI compartment may also be
-exogenously re-infected and transition to the Acute LTBI compartment.
+which includes everyone who is uninfected and has not been exposed to TB, or
+those who have been successfully cured of the disease. After exposure to an
+individual with TB, a person in the Susceptible compartment can develop Latent
+TB Infection (LTBI). Latently infected individuals are asymptomatic and
+non-infectious, but have some risk of developing active TB infection over time.
+To reflect the fact that real LTBI patients have a much higher risk of
+developing active TB within two years of exposure, the Hill Model splits the
+LTBI compartment into Acute LTBI (fast progressors) and Chronic LTBI (slow
+progressors). Accordingly, individuals in the Acute LTBI compartment have a
+higher risk of developing active TB than those in the Chronic LTBI compartment.
+Individuals in the Chronic LTBI compartment may also be exogenously re-infected
+and transition to the Acute LTBI compartment.
 
@@
 which were solved via the $\texttt{lsoda}$ routine. The systems of differential
-equations used to capture basic disease dynamics in the Basic Hill Model are
-shown in Figure~\ref{fig:hillEquations}.  In the Extended Hill Model, each flow
-rate equation from the Basic Hill Model was separated into its component part
-and these were tracked separately. In other words, rather than tracking net flow
-into various compartments, the Extended Hill Model tracks flow between all pairs
-of compartments separately. Furthermore, these equations were each also supplemented to
-also estimate their corresponding US HCS costs.  These equations are detailed in
-the\\
-{\huge\color{red} Add extended Hill equations to the appendix.}\\
-appendix,
-section~\ref{sec:extendedHillEqs}.  Historical data from 2000-2008 was used to
-initialize the model, which was then run up to the year 2100.
+equations and relevant constants used to capture basic disease dynamics in the
+Basic Hill Model are shown in Figures~\ref{fig:hillEquations}
+and~\ref{fig:basicHillConstants}, though a full analysis of the model is better
+suited for \TODO{<+Cite Hill+>}. \TODO{Add equations for $\lambda$. I don't have
+a pdf of Hill, apparently, though, so I can't.}  In the Extended Hill Model,
+each flow rate equation from the Basic Hill Model was separated into the
+components that tracked specific population migrations (i.e., terms that dictate
+flow rates from one compartment to another) and these were tracked separately.
+In other words, rather than tracking net flow into various compartments, the
+Extended Hill Model tracks flow between all pairs of compartments separately.
+Furthermore, these equations were each also supplemented to estimate their
+corresponding US HCS costs. A relevant subset of the Extended Hill equations are
+detailed in the appendix, section~\ref{sec:extendedHillEqs}. Historical data
+from 2000-2008 was used to initialize the model, which was then run up to the
+year 2100.
 
 \begin{figure}
-  {\huge\color{red} Make this not a figure. This should definitely just be tex.}
-  \begin{center}
-    \includegraphics[scale=0.75]{figures/BasicHillEquations.pdf}
-  \end{center}
+  \begin{align*}
+    \dot{S}_0 &= \rho(N_0+N_1) + \sigma_0^FF_0 + \sigma^LL_0 
+                +\varphi_0(I_0+J_0) - \lambda_0 S_0 - \mu_0 S_0\\
+    \dot{F}_0 &= p\lambda_0S_0 + xp\lambda_0L_0 - (\mu_0+\nu^F+\sigma_0^F)F_0\\
+    \dot{L}_0 &= (1-p)\lambda_0S_0 - xp\lambda_0L_0 
+                -(\mu_0+\nu_0^L+\sigma^L)L_0\\
+    \dot{I}_0 &= q(\nu^FF_0 + \nu_0^LL_0) - (\mu_0+\mu^d+\varphi_0)I_0\\
+    \dot{J}_0 &= (1-q)(\nu^FF_0 + \nu_0^LL_0) - (\mu_0+\mu^d+\varphi_0)J_0\\
+    \dot{S}_1 &= (1-f)\alpha(N_0+N_1) + \sigma_1^FF_1 + \sigma^LL_1 
+                +\varphi_1(I_1+J_1) - \lambda_1S_1 - \mu_1S_1\\
+    \dot{F}_1 &= gpf\alpha(N_0+N_1) + p\lambda_1S_1 + xp\lambda_1L_1 
+                -(\mu_1+\nu^F+\sigma_1^F)F_1\\
+    \dot{L}_1 &= (1-gp)f\alpha(N_0+N_1) + (1-p)\lambda_1S_1 - xp\lambda_1L_1 
+                -(\mu_1+\nu_1^L+\sigma^L)L_1\\
+    \dot{I}_1 &= q(\nu^FF_1 + \nu_1^LL_1) - (\mu_1+\mu^d+\varphi_1)I_1\\
+    \dot{J}_1 &= (1-q)(\nu^FF_1 + \nu_1^LL_1) - (\mu_1+\mu^d+\varphi_1)J_1\\
+  \end{align*}
   \caption{System of Differential Equations given in the Hill Model.}
   \label{fig:hillEquations}
+\end{figure}
+\begin{figure}
+  \begin{align*}
+    \sigma^{L} &= 0.057   &&\text{(Treatment rate for chronic LTBI)}\\
+    v^{L}_{0}  &= 0.0014  &&\text{(Progression rate for reactivation in the USB
+                                   population)}\\
+    v^{L}_{1}  &= 0.0010  &&\text{(Progression rate for reactivation in the FB
+                                   population)}\\
+    f          &= 0.187   &&\text{(Fraction of FB arrivals with LTBI)}\\
+    p          &= 0.103   &&\text{(Fraction of new infections which are acute)}\\
+    ARI_{0}    &= 0.00030 &&\text{(2000 Annual Risk of Infection, USB)}\\
+    q          &= 0.708   &&\text{(Fraction of infections progressing to infectious
+                                   disease)}\\
+    g          &= 0.0047  &&\text{(Fraction of FB arrivals with LTBI who are fast
+                                   progressors)}\\
+    \sigma^{F} &= 0.461   &&\text{(Cumulative fraction of treatment for acute
+                                   infection)}\\
+    r_{0}      &= 0.667   &&\text{(Fraction of cases due to reactivation in USB
+                                   population)}\\
+    r_{1}      &= 0.780   &&\text{(Fraction of cases due to reactivation in FB
+                                   population)}\\
+    \mu^{d}    &= 0.115   &&\text{(Mortality rate due to TB)}\\
+    x          &= 0.111   &&\text{(Fraction of re-infected chronic LTBI moving to
+                                   acute infection)}\\
+    \phi       &= 0.897   &&\text{(Cumulative fraction self-cure and treatment of
+                                   active disease)}\\
+    e_{0}      &= 0.965   &&\text{(Fraction of preferred contacts within own
+                                   population for USB)}\\
+    e_{1}      &= 0.985   &&\text{(Fraction of preferred contacts within own
+                                  population for FB)}\\
+  \end{align*}
+  \caption{The relevant constants used in the Basic Hill Model.  }
+  \label{fig:basicHillConstants}
 \end{figure}
@@
 L_1, I_1, J_1$ contain the number of foreign-born individuals. $N_0$ and $N_1$
-are the total populations of US-born and foreign-born individuals.  The
-constants $\rho$ and $\alpha$ are birth rates, while $\mu_i$, and $\mu_d$ are
-death rates. A complete list and descriptions of all constants used in the model
-can be found in the Appendix, Section~\ref{subsec:hillConstants}.
+are the total populations of US-born and foreign-born individuals. 
+\TODO{Is the next bit needed? I think move the stuff below out and the stuff
+above back where we introduce the equations.}
+The constants $\rho$ and $\alpha$ are birth rates, while $\mu_i$, and $\mu_d$
+are death rates. A complete list and descriptions of all constants used in the
+model can be found in the Appendix, Section~\ref{subsec:hillConstants}.
 
@@
 differential equations used to describe TB spread were separated into their
-component parts and each section was tracked separately.
-These components were made into compartments, tracked by differential equations
-detailed in the appendix. Progressions into active TB due to activations of LTBI
-or exogenous infection were tracked, allowing for sourced incidence data to be
-generated. These equations allowed the model to track the sourced number of TB
-cases, TB deaths, and natural deaths. Furthermore, the model also tracks the
-sourced cost on the US HCS. The immigrating cases of LTBI (acute or chronic)
-were also tracked. In the case of intervention testing, the number of cured and
-untreated cases of entering LTBI were both tracked. Cured cases of LTBI
-entering, TB deaths, total TB cases, and total cost were also tracked discounted
-at 3\% annually. This discounting was converted to a continuous differential
-equation for use within the model. In general, incidence data is calculated in
-the same way in the Extended Hill Model as it was in the Basic Hill Model.
+component parts and each part was tracked separately. In effect, each flow rate
+between two compartments in the Basic Hill model was made into its own
+``virtua'' compartment, thereby enabling computation not only of expected TB
+incidence, but also of the source of that incidence. In particular, progressions
+into active TB due to activations of LTBI or exogenous infection were tracked,
+allowing for sourced incidence data to be generated. These equations allowed the
+model to track the sourced number of TB cases, TB deaths, and natural deaths.
+Furthermore, the model also tracks the sourced cost on the US HCS. The
+immigrating cases of LTBI (acute or chronic) were also tracked. In the case of
+intervention testing, the number of cured and untreated cases of entering LTBI
+were both tracked. Cured cases of LTBI entering, TB deaths, total TB cases, and
+total cost were also tracked discounted at 3\% annually. This discounting was
+converted to a continuous differential equation for use within the model. In
+general, incidence data is calculated in the same way in the Extended Hill Model
+as it was in the Basic Hill Model.
 
+\TODO{Where does this fit in? I'm not seeing why this is here? Maybe in the
+results, instead?}
 In addition, estimations of the basic reproductive number of FB or USB active,
@@
 term $1$. In this case, $N = 100$, and the ratios for FB infectious individuals
-and USB infectious individuals were obtained from <+RATIO CITATION COLIN+>
+and USB infectious individuals were obtained from 
+\TODO{<+RATIO CITATION COLIN+>.}
 \subsection{Economic Modeling}
-In order to track the US HCS economic load given the TB rates, we made the
-following treatment cost assumptions. A single case of active TB was assumed to
-yield a \$14,000 US HCS cost, charged immediately upon disease contraction. This
-cost is the weighted mean of the costs of cases requiring hospitalization
-(happening 49\% of the time) and cases not requiring hospitalization (51\%).
-These cost estimates were found in <+DYLAN COST STUDY CITATION+>. LTBI treatment
-costs were given by \$468.00 US HCS cost, charged immediately upon successful
-treatment. These estimates were calculated based on the cost of a successfull
-treatment, and the typical adherence and efficacy of said treatment <+DYLAN COST
-STUDY CITATION, ADHERENCE CITATION+>. It is important to note that the charging
-assumptions are different for treatment of active TB as opposed to treatment of
-latent TB. In particular, cases of active TB imply a cost immediately upon
-disease contraction, whereas latent TB costs are charged only upon successful
-treatment. The motivation for this distinction is that active TB treatment is
-mandated by the US for all known cases and, further, most treatment costs are
-incurred at the beginning of the treatment cycle. As such, charging for every
-known case, immediately at contraction is a well motivated assumption. On the
-other hand, latent TB is only rarely treated in discovered cases and the costs
-are more evenly distributed. Furthermore, the choice to charge only upon
-successful treatment yields a more conservative estimate of the success of any
-intervention analyzed.
+In order to track the US HCS TB cost, we made the following treatment cost
+assumptions. A single case of active TB was assumed to yield a \$14,000 US HCS
+cost, charged immediately upon disease contraction. This cost is the weighted
+mean of the costs of cases requiring hospitalization (49\%) and cases not
+requiring hospitalization (51\%).  These cost estimates were found in 
+\TODO{<+DYLAN COST STUDY CITATION+>.} LTBI treatment costs were assumed to be
+\$468.00, charged immediately upon successful treatment. These estimates were
+calculated based on the cost of a successful treatment, and the typical
+adherence and efficacy of said treatment 
+\TODO{<+DYLAN COST STUDY CITATION, ADHERENCE CITATION+>.}
+It is important to note that the charging assumptions are different for
+treatment of active TB as opposed to treatment of latent TB. In particular,
+cases of active TB imply a cost immediately upon disease contraction, whereas
+latent TB costs are charged only upon successful treatment. The motivation for
+this distinction is that active TB treatment is mandated by the US for all known
+cases and, further, most treatment costs are incurred at the beginning of the
+treatment cycle. As such, charging for every known case, immediately at
+contraction is a well motivated assumption. On the other hand, latent TB is only
+rarely treated in discovered cases and the costs are more evenly distributed.
+Furthermore, the choice to charge only upon successful treatment yields a more
+conservative estimate of the success of any intervention analyzed. Finally, it
+is worth noting that, though accurate, these estimates of US HCS treatment cost
+are not intended to be fixed parameters. The code for this model is freely
+available, and as new research amends the necessary costs and new methods of
+treatment are developed, these values can be modified and the model re-run to
+produce a revised prediction of the US HCS TB cost.
 
-Cost data were separately tracked due to incoming active TB costs stemming from
-activation of LTBI vs exogenous reinfection. These data were modelled as
-additional compartments and also solved by $\texttt{lsoda}$.  Given the
-uncertainty in measurments of LTBI treatment cost, extensive sensitivity
-analysis was performed on this parameter relative to final cost outcomes. In
-addition to US HCS cost, the system was implemented so as to also track
-projected intervention implementation cost, given user-inputted parameters
-relating to various possible intervention cost strategies. The extended Hill
-Model was used to track the effect of many interventions tested by the Hill
-Model. In particular, the intervention strategy of curing entering cases of LTBI
-proved very promising and elimination year, final cost, and cost per case
-averted were tracked for various levels of entering LTBI cure rate. The
-interventions were implemented so as to take effect during the year 2013 and run
-to 2100. The numerical DE solver $\texttt{lsoda}$ used was run with a time step
-of $0.8$. Sensitivity analysis was performed on this parameter and reducing the
-time step was shown to have minimal effect on final size or cost values.
+In addition to refining the model to produce sourced US TB incidence estimates,
+the additional cost modeling was also tracked in a way that preserved the source
+of the US HCS cost. In particular, active TB treatment cost was tracked
+separately for cases resulting from an activation of LTBI (modeled as a
+progression from the Chronic Latent category) and for cases resulting from a
+novel, exogenous infection (modeled as a progression from the Acute Latent
+category). All cost equations were also solved by $\texttt{lsoda}$.  Given the
+uncertainty in estimates of LTBI treatment cost, extensive sensitivity analysis
+was performed on this parameter relative to final cost outcomes. Furthermore,
+the US HCS cost caused by LTBI treatment (which was tracked) was often omitted
+from Cost Benefit intervention analyses, so as to provide the most conservative
+estimate of total US HCS cost given various TB interventions. In addition to US
+HCS cost, the system was implemented so as to also track projected intervention
+implementation cost, given user-inputted parameters relating to various possible
+intervention cost strategies. The extended Hill Model was used to track the
+effect of many interventions tested by the Hill Model. In particular, the
+intervention strategy of curing entering cases of LTBI proved very promising and
+elimination year, final cost, and cost per case averted were tracked for various
+levels of entering LTBI cure rate. The interventions were implemented so as to
+take effect during the year 2013 and run to 2100. The numerical DE solver
+$\texttt{lsoda}$ used was run with a time step of $0.8$. Sensitivity analysis
+was performed on this parameter and reducing the time step was shown to have
+minimal effect on final size or cost values.
 
 \subsection{Agent Based}
+\TODO{What's the story we are trying to tell here? I mean, we are following a
+  very standard format, but I think it would be better if we had a cohesive
+  message.}
 The population level agent based model was implemented in several ways. Early
 implementations were built in \texttt{Netlogo} and \texttt{Java}, but final
-implementations were constructed in $\texttt{C++}$. Probabilites of agent
+implementations were constructed in \texttt{C++}. Probabilities of agent
 progression between various health states were computed given rates in the hill
@@
 individual records for every individual with LTBI or active TB. Susceptible
-individuals were not modelled as agents; instead, a binomial distribution was used to
-probabilistically determine the number of new infections each time step.
-Similarlly, the number of new immigrants each time step was chosen from a
-probability distribution. We collected final population distribution data via
-<+NUMBER OF RUNS 2160+> runs with each agent in the model truly representing one
-infected individual and a time step of $0.01$.  These data were analyzed in $R$.
-This model was also made to track deaths, total TB cases, and infection sources,
-as well as economic data. These data were consistently normal and matched the
-deterministic model.
+individuals were not modeled as agents; instead, a binomial distribution was
+used to probabilistically determine the number of new infections each time step.
+Similarly, the number of new immigrants each time step was chosen from a
+probability distribution. As the model was stochastic, all final data is
+inherently merely a probabilistic sample; as such, many simulations are required
+to draw conclusions from the model. As such, we collected final population
+health statistics from approximately 2160 model simulations, with each agent in
+the model truly representing one infected individual, and a time step of $0.01$.
+These data were analyzed in $R$. The agent based model also tracks deaths, total
+TB cases, and infection sources, and can also easily track economic data. These
+data were consistently normal and matched the deterministic model. 
+\TODO{Does it track economic data yet?}
 
@@
 the basic Hill Model. Specifically, the acute latent compartment in the basic
-Hill Model is a vestigal necessity of compartmental modeling and not reflective
+Hill Model is a vestigial necessity of compartmental modeling and not reflective
 of the biology of tuberculosis. As such, an agent based model was implemented
@@
 necessity of LTBI treatment in any effective intervention strategy. 
+\TODO{Why does it agree? We aren't doing any data analysis here, which is a
+problem. We need to walk our readers through this.}
 \begin{figure}[h]
@@
 indications that this is the case. In every intervention we tested (see, for
-example, Intervention {\huge\color{red} TODO}<+ADD ME+> and <+ADD ME+> in section <+ADD ME+>) we
+example, Intervention \TODO{<+ADD ME+> and <+ADD ME+> in section <+ADD ME+>}) we
 observed a plateauing effect, where the incidence per million stabilized after
@@
 their best-fit values. A full listing of constants used in the original Hill
-Model can be found in <+CITATION HERE+>. \\
+Model can be found in \TODO{<+CITATION HERE+>} \TODO{Can we delete this
+section?}
+
 \textit{(USB = US born, FB = Foriegn born)}
@@
 
-{\huge \color{red} TODO: What equations should be put in here?}
+\TODO{What equations should be put in here?}
 

### 2014-07-18 in_progress/presentations/paper/draft.tex
Editted. Proceeding to form new outline.

@@
 of the biology of tuberculosis. As such, an agent based model was implemented
-that more closely respects the biology of tuberculosis. Results from this model
-were also normal and did not differ significantly from the strict Hill model.
+that only had one LTBI health state, and instead relied on time-dependent
+probabilities to ensure that individuals transferred within the first two years
+with higher probability. Results from this model were also normal and did not
+differ significantly from the strict Hill model. 
+\TODO{This does work, right? Like, that thing exists, right?}
 
@@
 number of cases infected will follow a geometric series.
-{\huge \color{red} TODO: formalize this with math. We can fit it here.}
-This analysis predicts
-that over 100 years, one USB infection will lead to $1.04$ subsequent infections,
-whereas one FB infection will lead to $.83$ subsequent infections. Experimentally, 
-these data were also analyzed, with results of $1.03$ and $.64$, respectively. 
-Full calculations are included in the Appendix.
+\TODO{Formalize this with math. We can fit it here.}
+This analysis predicts that over 100 years, one USB infection will lead to
+$1.04$ subsequent infections, whereas one FB infection will lead to $.83$
+subsequent infections. Experimentally, these data were also analyzed, with
+results of $1.03$ and $.64$, respectively.  Full calculations are included in
+the Appendix.  
+\TODO{Why are these different? Also, label and ref for Appendix, not hard coded}
 
@@
 reduction, respectively.
-{\huge \color{red} TODO: This section is a bit confusing. Also, a graph would
-make things much prettier.}
+\TODO{This section is a VERY confusing. Also, a graph would make things much
+prettier.}
 
@@
 \end{table}
+\TODO{Table headings are confusing. What do they mean?}
 
@@
 The results for these interventions, which were consistently less effective than
-curing entering LTBI cases, are given in the appendix. {\huge \color{red} TODO:
-Which section?}
+curing entering LTBI cases, are given in the appendix. 
+\TODO{Which section?}
 
@@
 the most influential parameters in the model, we used Latin Hypercube Sampling
-to analyze the deterministic model, implemented with the \texttt{lhs} package in
+to analyze the Extended Hill model, implemented with the \texttt{lhs} package in
 \texttt{R}.  We varied the 16 parameters from the original Hill model according
@@
 additional treatment cost parameters according to uniform distributions.
-{\huge\color{red} TODO: These distributions were chosen because\ldots}. All
-non-economic parameters analyzed reported statistically similar results to their
-analysis in the Basic Hill Model. For economic outcomes, we found the parameter
-$f$, the fraction of FB arrivals with LTBI, to be highly correlated with the
-projected overall cost burden of TB in the United States over the next 100
-years.  Another highly influential parameter in the model was $\sigma^{L}$, the
-treatment rate for chronic LTBI.  However, while increasing $\sigma^{L}$
+\TODO{These distributions were chosen because\ldots}. 
+All non-economic parameters analyzed reported statistically similar results to
+their analysis in the Basic Hill Model. For economic outcomes, we found the
+parameter $f$, the fraction of FB arrivals with LTBI, to be highly correlated
+with the projected overall cost burden of TB in the United States over the next
+100 years.
+\TODO{Positively or negatively?}
+Another highly influential parameter in the model was $\sigma^{L}$,
+the treatment rate for chronic LTBI.  However, while increasing $\sigma^{L}$
 significantly decreases the cost burden due to Active TB treatment, it increases
@@
 final population sizes were normal, with mean accurate to the deterministic
-model and standard deviations given in table {\huge\color{red} TODO: Add table
-\# and section \# here}, in the Appendix. Additionally,
-the agent-based model provided a computational framework to produce
-meaningful intervention results. On student lab gradet hardware, a statistically
-meaningful experiment could be run overnight, producing data in one day. This
-demonstrates that this modeling strategy is feasible in this general case.
-Furthermore, the agent-based model provides a greater extensibility to more
-specific and biologically reasonable scenarios, such as geographic dependency or
-greater population heterogenity.
+model and standard deviations given in table 
+\TODO{Add table \# and section \# here}
+, in the Appendix. Additionally, the agent-based model provided a computational
+framework to produce meaningful intervention results. On student lab gradet
+hardware, a statistically meaningful experiment could be run overnight,
+producing data in one day. This demonstrates that this modeling strategy is
+feasible in this general case.  Furthermore, the agent-based model provides a
+greater extensibility to more specific and biologically reasonable scenarios,
+such as geographic dependency or greater population heterogenity.
 
@@
 necessary step towards elimination and indicate that it is a cost effective
-option. \\
-{\huge \color{red} TODO: Where did we show it was cost effective relative to other
-interventions? Also, the section below (future work) might be better just
-directly included in the discussion. Also, if we want to make this claim here we
-need to include other interventions in the main body.}\\
+option.
+
+\TODO{Where did we show it was cost effective relative to other interventions?
+  Also, the section below (future work) might be better just directly included
+  in the discussion. Also, if we want to make this claim here we need to include
+  other interventions in the main body.
+}
 In addition, beyond demonstrating quantitatively that this intervention strategy
@@
 efficient. Additionally, our analysis shows that paying for the treatment of
-these individuals is extremely cost effective {\huge \color{red} TODO: Show
-this}.
+these individuals is extremely cost effective 
+\TODO{Show this}.
 \subsection{Future Work}
@@
 reported in the Hill model.  Probability distributions for $C_{A}$ and $C_{L}$
-were set to be Uniform, with range +/- 10\% of the estimated value.  All
+were set to be Uniform, with range $\pm10\%$ of the estimated value.  All
 probabilty distributions used to generate the Latin Hypercube are listed in

### 2014-07-18 in_progress/presentations/paper/draft.tex
added final outline

@@
 
+\textbf{Outline for Final Draft}
+
+\begin{description}
+  \item[Introduction] Introduce TB, quote WHO about prevelance, note US goals
+    for elimination. Recall typical structure of TB disease (Susc. -> LTBI ->
+    Active) and note that typical assumptions presumes active is the optimal
+    state of the intervention. Note recent work suggesting, in fact, that LTBI
+    intervention might also be necessary to acheive elimination goals. Introduce
+    possibility of answering that through modeling.
+
+    Recall compartmental models, and introduce Hill model and its findings.
+    Introduce our aim. We extended the hill model to provide sourced TB data, so
+    as to better analyze what causes US TB incidence. We also added sourced
+    economic tracking, so as to analyze US HCS costs due to TB and how various
+    intervention strategies affect the US TB load. Finally, we also implement an
+    agent based version of The Extended Hill, so as to test its statistical
+    accuracy and to establish a new, more extendible framework for modeling
+    diseases like TB.
+
+    Our results strongly indicate that the LTBI population and, in particular,
+    the immigration to this compartment from infected new arrivals to the US is
+    the driving force behind US TB incidence and cost. It also suggests that
+    curing incoming LTBI cases upon immigration would be a particularly cost
+    effective intervention, and would be necessary if elimination is desired.
+    These results are further validated by qualitative effects, such as the
+    plateuing effect observed across many interventions, in particular the
+    elimination of transmission, and sensitivity analysis.
+
+    The agent based model affirmed the statistical validity of the Hill Model
+    and proved to be a computationally realizable framework for disease study in
+    general. 
+  \item[The Basic Hill]
+    Go through the Hill Model in detail. List equations, compartments,
+    constants, and meaning. Discuss the fact that this is an approximation of a
+    stochastic phenonmena, and thus we cannot be sure it represents
+    statistically meaningful data, and discuss pros and cons to agent-based vs
+    compartmental models.
+
+    Recall their result about curing LTBI rate. 
+  \item[The Extended Hill]
+    Explain our strategies for extending the model (splitting equations and
+    tracking flows over compartments). Explain adding economic data. Link to
+    code github.
+
+    Discuss method of performing sensitivity analysis.
+
+    Explain the agent based hill copy, and the agent based non-hill. Explain
+    execution from a theoretical perspective, and in practice (performance,
+    language choice, extensibility, etc). 
+  \item[Results]
+    Document sourced US TB incidence and costs. Demonstrate effects of several
+    interventions, among them including eliminating transmission and curing
+    entering LTBI and one other. Highlight plateuing effect.
+
+    Discuss outcome of sensitivity analysis on the data, and how it compares to
+    results indicated above (e.g. agreement of importance of incoming LTBI cure
+    rate and cost).
+
+    Discuss statistical power of results via agent based models. Show
+    distributions and give statistics. 
+  \item[Discussion]
+    Discuss what results indicate about future of TB in US. Indicate that if we
+    do not target LTBI population, an endemic future well above elimination is
+    all but guaranteed. Discuss the cost effectiveness of curing, for free, all
+    incoming cases of LTBI relative to other metrics, such as searching for new
+    infected individuals after a case is discovered.
+
+    Discuss the feasibility of using agent based models as a general principle,
+    given the ease of use here. Discuss how relevant this will be as
+    drug-resistant disease becomes more and more prevalent, as that issue is one
+    that compartmental models are ill equipped to track.
+
+    Discuss possibility of extending model to handle drug resistance, HIV
+    comorbidity, regional dependence, urban vs rural targeted intervention, etc. 
+  \item[Conclusion]
+    Final recommendations: Most promising intervention, source of US TB and US
+    TB HCS costs, and statistical power of Hill Model (frame it as a nice, but
+    unnecessary verification, as this verification wasn't something anyone was
+    really asking for). 
+\end{description}
+
+\newpage
 {\huge \color{red} List of results}

### 2014-08-03 in_progress/presentations/paper/draft.tex
Added some scripts for the paper and worked on the paper

--- 2014-07-14 in_progress/presentations/paper/draft.tex
@@
 \usepackage{enumerate,placeins}
+\usepackage{standalone}
 \usepackage{color}
+\usepackage{hyperref}
+\usepackage{framed}
+\usepackage{tikz}
+\usetikzlibrary{positioning,arrows}
+\usetikzlibrary{calc}
 \graphicspath{{figures/}}
+\renewcommand{\(}{\left(}
+\renewcommand{\)}{\right)}
 
-\newcommand{\TODO}[1]{\hfill\\{\huge \color{red} TO DO:} #1 \hfill \\}
+\newcommand{\TODO}[1]{\begin{framed}{\huge \color{red} TO DO:}
+  #1 \end{framed}}
 
@@
 
-{\huge \color{red} List of results}
-Plan:
-\begin{enumerate}
-  \item Intervention Analysis: 
-    \begin{enumerate}
-      \item Reducing Entering LTBI
-      \item Cutting Transmission
-      \item Reducing Progression Rate
-    \end{enumerate}
-  \item Qualitative Strategy Conclusions:
-    \begin{enumerate}
-      \item Sourced Incidence \& Cost
-      \item Plateauing Effect
-      \item Extremal values for entering LTBI reduction
-      \item Linearity in Cost/Incidence for entering LTBI reduction
-      \item CPCA data
-    \end{enumerate}
-  \item Statistical Verification/Agent Based Feasibility
-    \begin{enumerate}
-      \item Normal Distributions
-      \item Basic Reproductive Numbers
-      \item Agent based running time \& Extendibility. 
-    \end{enumerate}
-\end{enumerate}
-Ideas:
-\begin{itemize}
-  \item Plateauing Effect
-  \item Intervention Analysis
-  \item Statistical Analysis of Hill Model
-  \item Agent-Based Feasibility
-  \item Theoretical/Experimental justification of basic reproduction number
-  \item Overall qualitative strategy conclusions. 
-\end{itemize}
+\TODO{Pick a journal. PLOS?}
+\TODO{Format to journal.}
+\TODO{Validate against 2000 - 2014, if absolutely necessary. This would require
+gathering data, re-running the model, re-performing sensitivity analysis, and
+potentially redoing interventions. It may not be necessary as we validated
+against the Hill model, but perhaps this should be more stressed.}
+\TODO{Change intervention start date to 2014, if absolutely necessary.}
+\TODO{Improve the final distributions figure. Is the fact that the deterministic
+  hill results are $2+$ standard deviations off the mean acceptable? Where is
+  the data for this? Where is the R script to generate these images?}
+\TODO{Clean up github.}
 
 \section{Abstract}
-An epidemiological and economic model for tuberculosis in the United States
- was developed, extending a model developed in 2012 by the Centers
-for Disease Control and Prevention. Sensitivity analysis of this model reveals
-that the percentage of foreign born immigrants with LTBI is a highly influential
-parameter. Various intervention strategies, particularly those that reduced LTBI
-among foreign-born arrivals, were evaluated, and cost per case averted estimates
-were found.  Additionally, a population-level, stochastic, agent-based model was
-built. This model demonstrated the feasibility of using agent-based modeling in
-the context of minimal population heterogeneity and provided statistical
-characterization of the results of the compartmental model. The distributions
-of the final population sizes and incidence rates projected by the stochastic model
-were found to be approximately normal, with means centered at the results of
-compartmental model.
+An epidemiological and economic model for the spread of tuberculosis in the
+United States was developed, extending a model developed in 2012 by the Centers
+for Disease Control and Prevention. Various intervention strategies,
+particularly those that reduced latent tuberculosis infection (LTBI) among
+foreign-born arrivals, were evaluated, and cost per case averted estimates were
+found. Curing cases of immigrating LTBI was found to be a highly effective and
+cost efficient intervention strategy. Additionally, a population-level,
+stochastic, agent-based model was built, which demonstrated the feasibility of
+using agent-based modeling in the context of minimal population heterogeneity
+and provided statistical characterization of the results of the compartmental
+model. The distributions of the final incidence rates projected by the
+stochastic model were found to be approximately normal, with means centered at
+the results of compartmental model.
 
 \section{Introduction}
-Epidemiological models allow public health professionals to predict and analyze
-disease dynamics and intervention effectiveness. The most common examples of
-such models are detereministic, compartmental, differential equation models. In
-these models, the population is split between several possible health states, or
-compartments, and a system of differential equations governs population flow
-between the various compartments. In 2012, Hill, Becerra, and Castro implemented
-a compartmental differential equaiton model of tuberculosis (TB) in the United
-States (US).  Their model characterized five health states across two
-subpopulations, US-born (USB) and foreign-born (FB), for a total of 10
-compartments. They used this model to evaluate several possible intervention
-strategies and ultimately concluded that though increasing LTBI treatment was an
-effective intervention strategy, the US was unlikely to meet their stated goal
-of elimination of TB in the US by 2100. Here, we present an extended Hill model
-with additional tracking capabilities, such that it can now report
-further granularity in the disease dynamics. Furthermore, this model also tracks
-economic data in order to project the US health care system (HCS) costs due to
-TB given our current policy, as well as in the context of various interventions.
+As a single infectious agent, tuberculosis (TB) is the second leading cause of
+death worldwide, and the World Health Organization (WHO) estimates that roughly
+one third of the global population has either active or latent TB
+\cite{_who_2013}. This high prevalence does not leave the US untouched; in 2013,
+9588 cases of TB were reported in the USA, which is an incidence rate of 30 new
+cases per million \cite{miramontes_trends_2013}. In this work, we analyze
+various TB intervention strategies aimed at reducing this incidence. In
+particular, we evaluate our interventions in the context of a particular goal:
+elimination of US TB by 2100. Here, we use elimination to mean that the yearly
+incidence of US TB would be lower than 1 new case per million. This goal is
+simultaneously ambitious given the prevalence of TB today and also potentially
+achievable, as it leaves over 80 years in which to focus on stopping TB.
 
-{\huge \color{red} Fix this paragraph. Its not the best. \textbackslash/}
+The majority of TB infections are caused by Mycobacterium tuberculosis, 
+an airborne pathogen which primarily affects the lungs and pulmonary system.  
+Individuals infected with this bacteria first develop a latent form of TB
+referred to as latent tuberculosis infection (LTBI).  These individuals are
+asymptomatic and not contagious, and thus, this infection is difficult to detect
+and can persist for many years. The latent tuberculosis infection may progress
+to active tuberculosis infection (active TB), at which point the patient becomes
+symptomatic and contagious. This progression is most likely within the first two
+years after contraction, but can happen throughout the rest of the lifespan of
+the individual.  Left untreated, individuals with LTBI have a lifelong
+probability of approximately 10\% to develop active TB.
+\TODO{in total? Or after they've progressed through the first two years? We need
+a new source for this, I think. It's not in the logical place of the WHO report.
+This also obviously needs to be cited. }
+The health risks for individuals with active TB are severe, and without medical
+interventions, the 10 year mortality rate for the disease is between 20\% and
+70\%, depending on the severity of the case and definition of a positive
+diagnosis.
+\cite{_who_2013}.
 
-Though compartmental, differential equation models are the most common strategy
-when modeling large-scale diseases at the population level, an alternative
-approach is to use an agent-based model. Agent
-based models provide a more nuanced view of disease spread as they provide a
-more biologically accurate modeling framework; however, they are often
-considered to be computationally infeasible at population level. In order to
-challenge this assumption of infeasibility and provide statistical verification
-of the results of the compartmental model, we implemented a stochastic,
-agent-based model of US TB dynamics at the population level.
+Effective drugs are available to cure almost all cases of LTBI and active TB,
+with the exception of drug resistant TB. However, the treatment methods for both
+LTBI and active TB are onerous, typically requiring a multi-month drug regiment
+of serious antibiotics with potentially harmful side effects, costing an average
+of \$14,000 per successful active TB treatment and \$468.00 per successful LTBI
+treatment. 
+\TODO{The LTBI number here seems off. If I just run
+  \href{https://github.com/mmcdermott/disease-modeling/blob/master/in_progress/models/costBenefitAnalysis/hillConstants.R}{\texttt{hillConstants.R}}
+  and look at the value of \texttt{Cl}, I get \$700 something. What's going on
+  here? Where does the \$468 number come from? What was this supposed to be?}
+\TODO{Cite Dylan's paper. Is it the one in zotero?}
+Given the high mortality rate for active TB, this treatment is deemed legally
+and medically necessary for cases of active TB. However, given the low
+progression rate from LTBI to active TB, and the high cost of treatment, this is
+often seen as unnecessary for LTBI patients. This becomes especially relevant
+when applied to the US immigration program. Before being admitted to the United
+States, all potential immigrants are required to take a TB test. If they have
+active TB, treatment is required before entry, but if they have LTBI, no
+treatment is mandated. As the global incidence for TB is so high, this
+contributes a sizable portion of the US LTBI population.
 
-\section{Background}
-\subsection{Tuberculosis} x 
-\TODO{Use TB instead of Tuberculosis maybe?}
-Tuberculosis is an infectious bacterial disease that primarily affects the lungs,
-with common symptoms including severe coughing, fevers, and chest pain.
-Tuberculosis is a major global health concern; The World Health Organization
-estimates that 8.6 million developed TB and 1.3 million people died from
-the disease in 2012. Tuberculosis is an airborne disease and is typically
-transmitted from person-to-person by coughing, sneezing, and the exchange of
-other respiratory fluids.  Infected individuals first enter a latent phase,
-during which the disease causing agent, \emph{Mycobacterium tuberculosis}, is
-present in their bodies, but the individuals remain asymptomatic and
-noncontagious. During this phase, individuals are said to have latent TB
-infection (LTBI). Eventually, some number of individuals with LTBI progress into
-what is known as the active phase of the disease, or active TB. Individuals with
-an active TB infection are symptomatic and contagious. The lifetime risk of
-progressing from Latent TB Infection (LTBI) to active TB is approximately
-5-10\%, although individuals with LTBI have the greatest chance of developing
-Active TB during the first two years immediately following infection, and if
-they have a suppressed immune system, such as in the case of a comorbid HIV
-infection. Cases of Active TB may be classified as pulmonary ($\sim$80\% of
-cases) or non-pulmonary ($\sim$20\% of cases), depending upon the biological
-location of infection. In the Hill model, pulmonary Active TB is treated as
-contagious and non-pulmonary Active TB is treated as non-contagious, which is an
-assumption we also use here.
+Given that LTBI patients are asymptomatic, many standard TB interventions omit
+focusing on LTBI treatment entirely, reasoning that a more aggressive focus on
+active TB would serve better in the long run.  However, as LTBI can persist over
+a lifetime, such disease control strategies often unintentionally create large
+pools of people with LTBI that may or may not eventually develop active TB. This
+is especially problematic in the U.S., where our high immigration rate leads to
+an even more inflated LTBI population. This leads some to question the
+effectiveness of these approaches; in particular, in 2012, Hill, Becerra, and
+Castro modeled the spread of TB in the USA and found that controlling the LTBI
+population and encouraging treatment of LTBI was essential to TB elimination.
+Unfortunately, they also found that reaching elimination was very unlikely, if
+not impossible, by 2100.
 
-In the United States, 9,951 new cases of TB were reported in 2012 by the Centers
-for Disease Control. The disease burden varied for different subpopulations in
-the U.S., and, in particular, the incidence rate of TB was 11.5 times higher for
-the FB population than the USB population.  For the
-past 20 years, the overall incidence of TB in the U.S. has declined each year,
-but in 2012 the annual incidence level of 32 new cases/million remains above the
-desired goal of the $<$1 new case/million, which is the target for disease
-elimination set by the Centers for Disease Control.
+% I commented out the below because I'm not sure we need it. Thoughts? 
+%Disease models like Hill, Becerra, and Castro's provide scientists and
+%policy makers some of their only tools when predicting intervention
+%effectiveness and cost, and are thus of prime importance when analyzing disease
+%spread and planning intervention strategies. However, forming such models and
+%extracting meaningful information about the underlying disease spread from their
+%results can often be very difficult. The choice of appropriate modeling
+%techniques is therefore essential in providing the most information possible
+%about a disease structure.
 
-\TODO{}citations: CDC Tuberuclosis 2013 Report - http://www.cdc.gov/mmwr/preview/mmwrhtml/mm6211a2.htm
-WHO Global Tuberculosis Report 2013 - http://www.who.int/tb/publications/global\_report/en/
+Hill, Becerra, and Castro's model (henceforth called the Hill model) is a
+compartmental model, meaning the model splits the population apart into disjoint
+``compartments,'' each of which represents a particular health state. The Hill
+model utilized a system of 10 compartments split across two sub-populations:
+US-born individuals (USB) and foreign born individuals (FB).  Each
+sub-population was split among five health states representing various subtypes
+of active or latent TB. The flow rates between these compartments were given by
+deterministic differential equations acting on a continuous population.
+Though this model is extremely effective at modeling TB behavior that agrees on
+average with real population data, it lacks tracking capabilities that
+would shed more light on the underlying cause of US TB incidence.
+Furthermore, it is also limited as it fails to provide any economic data
+regarding the cost to the US health care system due to TB (HCS cost) with our
+without various interventions. To address these shortcomings, we produced an
+extended version of the Hill model, which we refer to as the extended Hill
+model, which analyzes the same compartments as the Hill model, but also tracks
+the economic impact of TB and tracks the source of all infections and costs
+incurred, thus enabling much more detailed qualitative analysis of US TB
+dynamics.
 
-\subsection{The Hill Model}
-A flowchart representation of the Hill Model is shown in
-Figure~\ref{fig:hillModelSchematic}. Each compartment represents a different
-possible TB health state for every US-born or FB individual, and
-arrows between different compartments represent possible transitions between
-states. Individuals also leave the model from all compartments due to natural
-death, which is left out of the figure for clarity.
+Though deterministic compartmental models like the Hill model are well
+established in epidemiology, they also fail to capture the natural stochasticity
+of real world disease spread, and thus cannot provide any statistical
+characterization of their predicted outcomes. To understand these statistical
+factors for the extended Hill model, we also produced a stochastic, agent based,
+population level model of US TB dynamics that agreed with the Hill model on
+average, but provided meaningful statistical parameters regarding the final
+distributions of each of the various health states. In addition to providing
+statistical verification of the extended Hill results, this model also
+demonstrates that agent based modeling can be an effective strategy even in
+cases where the population size is very large, as the model ran quickly
+even on standard hardware.  This is especially promising as agent based models
+are much better equipped to model disease spread in highly heterogeneous
+populations, such as in cases of drug resistance or comorbidity, both of which
+are very relevant with TB and present excellent opportunities for model
+extension.
+
+Using both the extended Hill and the agent based model, we have demonstrated
+that LTBI treatment is essential in controlling US TB dynamics and reaching the
+2100 elimination goal, if that is possible at all. Furthermore, we have found
+that treating cases of immigrating LTBI in the US is critical to our overall TB
+control strategy and is cost effective compared to other interventions. In this
+paper, we first document the theoretical and implementation details of both the
+basic and extended Hill models, and then we provide significant results from
+these models. This work has practical implications for TB public health policy
+in the United States, and it also demonstrates the feasibility of using agent
+based models for large-scale applications in epidemiology.
+
+\section{The Hill Model}
+\label{sec:hillModel}
+A flowchart representation of the Hill model is shown in
+Figure~\ref{fig:hillModelSchematic}.
 
@@
   \begin{center}
-    \includegraphics[scale=0.25]{figures/HillModelFlowChart.png}
+    \includestandalone[width=\textwidth]{hillFlowChart}
+    %\includegraphics[scale=0.25]{figures/HillModelFlowChart.png}
   \end{center}
-  \caption{Schematic of the Hill Model.}
+  \caption{Schematic of the Hill model. Each compartment represents a different
+    possible TB health state for every US-born or FB individual, and arrows
+    between different compartments represent possible transitions between
+    states. Individuals also leave the model from all compartments due to
+    natural death, which is left out of the figure for clarity. Figure adapted
+    from \cite{hill_modelling_2012}}
   \label{fig:hillModelSchematic}
@@
 
-The majority of USB and FB individuals fall into the Susceptible (S) category,
+The majority of USB and FB individuals fall into the susceptible ($S$) category,
 which includes everyone who is uninfected and has not been exposed to TB, or
-those who have been successfully cured of the disease. After exposure to an
-individual with TB, a person in the Susceptible compartment can develop Latent
-TB Infection (LTBI). Latently infected individuals are asymptomatic and
-non-infectious, but have some risk of developing active TB infection over time.
-To reflect the fact that real LTBI patients have a much higher risk of
-developing active TB within two years of exposure, the Hill Model splits the
-LTBI compartment into Acute LTBI (fast progressors) and Chronic LTBI (slow
-progressors). Accordingly, individuals in the Acute LTBI compartment have a
-higher risk of developing active TB than those in the Chronic LTBI compartment.
-Individuals in the Chronic LTBI compartment may also be exogenously re-infected
-and transition to the Acute LTBI compartment.
+those who have been successfully cured of the disease. Individuals in the $S$
+category flow with some rate into an LTBI category, simulating exposure to TB.
+Because real LTBI patients have a higher risk of developing active TB within two
+years of exposure, the Hill model splits the LTBI population among two LTBI
+compartments: compartment $F$, or acute LTBI, representing those who progress
+within the first two years of catching the disease, and compartment $L$, or
+chronic LTBI, representing those who do not progress within the first two years.
+Both LTBI compartments feed into two active TB compartments, $I$ and $J$,
+representing infectious and non-infectious active TB, respectively. To respect
+the varying rates of LTBI activation, individuals in the Acute LTBI compartment
+have a much higher risk of developing active TB than those in the Chronic LTBI
+compartment. Individuals in the Chronic LTBI compartment may also be exogenously
+re-infected and transition to the Acute LTBI compartment
+\cite{hill_modelling_2012}.
 
-Latently infected individuals may progress to one of two active TB states: Infectious TB (I) or 
-Non-Infectious TB (J).  Individuals in both compartments have an increased risk of death from
-active TB infection, but only individuals in the Infectious TB compartment are contagious.  
-In addition, individuals in all of the infected compartments (F, L, I, J) may be treated or self-cure
-themselves of their respective TB health condition.  However, in the model, treatment or self-cure from TB
-does not grant immunity, and all healthy individuals are grouped in the Susceptible compartment
-and may be re-infected at a later time.\\
+Individuals in both active TB compartments have an increased risk of death from
+TB infection, but only individuals in the infectious TB compartment affect the
+infection flow rates. In addition, individuals in all of the infected
+compartments ($F$, $L$, $I$, $J$) may be treated or self-cure themselves of
+their respective TB health condition. However treatment or self-cure from TB
+does not grant immunity, and all healthy individuals are grouped in the
+susceptible compartment and may be re-infected at a later time
+\cite{hill_modelling_2012}.
 
-\section{Methods}
-\subsection{Basic Structure}
-Both the Hill Model (Basic Hill Model) and our extended Model (Extended Hill
-Model) were implemented in \texttt{R} as a system of differential equations,
-which were solved via the $\texttt{lsoda}$ routine. The systems of differential
-equations and relevant constants used to capture basic disease dynamics in the
-Basic Hill Model are shown in Figures~\ref{fig:hillEquations}
-and~\ref{fig:basicHillConstants}, though a full analysis of the model is better
-suited for \TODO{<+Cite Hill+>}. \TODO{Add equations for $\lambda$. I don't have
-a pdf of Hill, apparently, though, so I can't.}  In the Extended Hill Model,
-each flow rate equation from the Basic Hill Model was separated into the
-components that tracked specific population migrations (i.e., terms that dictate
-flow rates from one compartment to another) and these were tracked separately.
-In other words, rather than tracking net flow into various compartments, the
-Extended Hill Model tracks flow between all pairs of compartments separately.
-Furthermore, these equations were each also supplemented to estimate their
-corresponding US HCS costs. A relevant subset of the Extended Hill equations are
-detailed in the appendix, section~\ref{sec:extendedHillEqs}. Historical data
-from 2000-2008 was used to initialize the model, which was then run up to the
-year 2100.
+The rates that individuals move into and between compartments in the Hill model
+are determined by a system of deterministic differential equations. This system
+of equations, and the definitions of the constants used in the Hill model, are listed in
+Appendix~\ref{appendix:hillEqs} \cite{hill_modelling_2012}. These equations
+provide accurate estimations of the sizes of each compartment at any point in
+time, but can provide little insight into TB dynamics beyond that, as they offer
+no infection source information. Furthermore, it is important to note once again
+that though real-world disease dynamics are stochastic, the Hill model is a
+completely deterministic approximation and does not provide estimates for the
+distributions or standard errors of predicted disease rates. We addressed each
+of these issues with the extended Hill model and the agent based Hill model.
 
-\begin{figure}
+\section{The Extended Hill Model}
+\label{sec:extendHill}
+In order to refine the tracking capabilities of the Hill model, the original
+differential equations used to describe TB spread were separated into their
+component parts and each part was tracked separately. In effect, each flow rate
+between two compartments in the basic Hill model was made into its own
+``virtual'' compartment, which is tracked the same as a real compartment by the
+model but does not represent a particular health state. This enabled computation
+not only of expected TB cases and deaths, but also the source of those cases and
+deaths. A schematic for this model is shown in Figure~\ref{fig:extendedHill}.
+Immigrating cases of LTBI (acute or chronic) were also tracked. In the case of
+intervention testing, the number of cured and untreated cases of entering LTBI
+were both tracked.
+
+\begin{figure}[h]
+  \centering
+  \includestandalone[width=\textwidth]{extendedHillFlowChart}
+  \caption{A schematic of the extended Hill model. True compartments are
+    illustrated in red, with flow rates illustrated with black arrows and flow
+    tracking compartments illustrated in green with dashed edges.
+  }
+  \label{fig:extendedHill}
+\end{figure}
+
+The model was also extended to provide similarly sourced US health care system
+(HCS) TB costs. To do so, we made the following treatment cost assumptions. A
+single case of active TB was assumed to yield a \$14,000 US HCS cost, charged
+immediately upon disease contraction. This cost is the weighted mean of the
+costs of cases requiring hospitalization (49\%) and cases not requiring
+hospitalization (51\%).  These cost estimates were found in \TODO{<+DYLAN COST
+STUDY CITATION+>.} LTBI treatment costs were assumed to be \$468.00, charged
+immediately upon successful treatment. These estimates were calculated based on
+the cost of a successful treatment, and the typical adherence and efficacy of
+said treatment \TODO{<+DYLAN COST STUDY CITATION, ADHERENCE CITATION+>.} Note
+that active TB treatment costs are charged immediately upon disease contraction,
+whereas LTBI treatment costs are charged only upon successful treatment. The
+motivation for this distinction is that active TB treatment is mandated by the
+US for all known cases and, further, most treatment costs are incurred at the
+beginning of the treatment cycle. As such, charging for every known case,
+immediately at contraction is a well motivated simplification. On the other
+hand, latent TB is only rarely treated in discovered cases and the costs are
+more evenly distributed. Furthermore, the choice to charge only upon successful
+treatment yields a more conservative estimate of the success of any intervention
+analyzed, as it will always underestimate the total US HCS TB cost burden.
+Finally, it is worth noting that these estimates of US HCS treatment cost are
+not intended to be fixed parameters. The code for this model is freely
+available, and as new research amends the necessary costs and new methods of
+treatment are developed, these values can be modified and the model re-run to
+produce a revised prediction of the US HCS TB cost. In addition to US HCS cost,
+the system was implemented so as to also track projected intervention
+implementation cost, given user-inputted parameters relating to various possible
+intervention cost strategies.  Cured cases of LTBI entering, TB deaths, total TB
+cases, and total US HCS cost were also tracked discounted at 3\% annually for
+cost benefit analysis. This discounting was converted to a continuous
+differential equation for use within the model.
+
+The extended Hill model was implemented as a series of differential equations in
+\texttt{R}, and solved using the \texttt{lsoda} system with a timestep of $0.8$.
+Extensive sensitivity analysis was performed on this parameter and it was found
+that decreasing the timestep did not seriously affect the model outcomes.  A
+relevant subset of the extended Hill equations and a link to the full model code
+and documentation can be found in Appendix~\ref{appendix:hillEqs}. Historical
+data from 2000-2008 was used to initialize the model, which was then run up to
+the year 2100.
+
+In order to understand these results statistically, a stochastic, agent based
+model of TB spread in the US was implemented. This model was programmed in
+\texttt{C++}, and probabilities of agent transition between various health
+states were computed given rates in the hill model and a variety of integration
+approximations. The model maintained individual records for every individual
+with LTBI or active TB. Susceptible individuals were not modeled as agents;
+instead, a binomial distribution was used to probabilistically determine the
+number of new infections each time step. We ran the model with default parameter
+values for 2160 runs, with time step of $0.01$.  Final population health
+statistics were recorded for each run, and these data were analyzed in $R$. The
+agent based model also tracks deaths, total TB cases, and infection sources.
+These data were consistently normal and matched the deterministic model closely
+in mean, providing statistical validation of using the deterministic model
+results in intervention analysis and policy planning without more advanced
+statistical analysis.
+
+Further implementations of the agent based model were made that deviated from
+the basic Hill model. Specifically, the acute latent compartment in the basic
+Hill model is a vestigial necessity of compartmental modeling and is not
+reflective of the biology of tuberculosis. As such, an agent based model was
+implemented with one LTBI health state that relied on time-dependent
+probabilities to ensure that individuals transferred within the first two years
+with higher probability.  Results from this model were also normal and did not
+differ significantly from the strict Hill model. This also demonstrates the
+effectiveness of using agent based modeling at population level scale for
+general epidemiological studies. Agent based models are much better equipped to
+model population heterogeneity, drug resistance, or comorbidity, but are
+typically thought to be too computationally intensive to perform on large
+populations. These results show that with modern hardware, agent based modeling
+can be used even with a population of millions of agents.
+
+\section{Results}
+
+\subsection{Basic Population Breakdown}
+The additional tracking capabilities of the extended Hill model offered several
+key insights into US TB dynamics. Figure~\ref{fig:incPlotSourced} shows the
+yearly incidence of US TB, broken down by infection source. Recall that
+infections due to acute LTBI, in the Hill model, represent cases of a novel
+infection, whereas infections due to chronic LTBI represent the activation of a
+long standing latent infection.  Figure~\ref{fig:incPlotSourced} demonstrates
+that the majority of the US TB load is driven by activations of FB LTBI,
+followed by USB LTBI activations. Though contact investigation and aggressive TB
+treatment programs help prevent increasing the LTBI population, as active TB
+cases can also lead to long lasting LTBI cases, this suggests that a greater
+focus on LTBI treatment would potentially have a very large impact on US TB
+rates. 
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[scale=.5]{incPlotSourced}
+  \end{center}
+  \caption{Sourced yearly incidence data generated by the extended Hill model.}
+  \label{fig:incPlotSourced}
+\end{figure}
+
+Figure~\ref{fig:costPlotSourced} shows a similarly sourced plot, but analyzing the
+final US HCS costs due to active TB. One can see that in this plot, roughly half
+of the US TB HCS costs are due to activations of LTBI. Note that, again, in this
+figure it is appropriate to think of the costs due to acute LTBI as costs due to
+exogenous re-inection, whereas costs due to chronic LTBI are activations of long
+standing latent infections. 
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[scale=.35]{costPlotSourced}
+  \end{center}
+  \caption{Sourced US HCS economic TB load. Note that this data only illustrates
+    the load due to treating active TB, but illustrates where the infections
+    driving this cost come from.}
+  \label{fig:costPlotSourced}
+\end{figure}
+
+In fact, both of these plots underestimate the impact of LTBI on the spread of
+TB, as every chronic LTBI activation contributes not only to incidence and costs
+directly, but also indirectly by causing additional future cases, which is not
+captured in these graphs. Further, there are also US HCS costs due to LTBI
+treatment, which are not illustrated in these graphs due to the inherent
+uncertainty in estimating LTBI treatment costs. These omissions could only ever
+make the case for LTBI focus stronger, as they err on the side of
+underestimating its impact, not overestimating.
+\subsection{Intervention Analysis}
+Though the basic sourced data suggests that LTBI control may be key to US TB
+control, specific intervention analysis is necessary to come to a final
+conclusion, as active TB spread is potentially the driving force maintaining the
+endemic LTBI population. To examine this, we tested many different
+interventions, of which we will highlight two here that were particularly
+noteworthy. 
+\subsubsection{Curing entering LTBI cases}
+As mentioned in the Introduction, the US currently tests for LTBI upon
+immigration, but does not require treatment for those who test positive for LTBI
+prior to admitting them entry. Given the very high TB incidence rates in certain
+parts of the world, this means that the US has a very high yearly influx of LTBI
+infected patients.  Curing these patients of LTBI upon entry represents an
+excellent strategy of targeting the LTBI population because it is requires
+effectively no cost to find those infected with LTBI. As those with LTBI are
+asymptomatic, normally LTBI treatment is hindered by the fact that seeking out
+those with LTBI can be quite costly. However, here, the process of finding those
+with LTBI is already performed, so the question is only one of the benefits and
+costs of the treatment alone. To assess this intervention, we ran the model for
+various entering LTBI cure rates. Figure~\ref{fig:redEnLTBIInc} shows these
+results for $10\%$, $25\%$, $50\%$, and $100\%$ entering LTBI cure rate. 
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.8\textwidth]{figures/redEnLTBI}
+  \caption{The resulting incidence per million given various levels of entering
+    LTBI cure rates.}
+  \label{fig:redEnLTBIInc}
+\end{figure}
+
+Note that the Extended Hill model does not differentiate between documented and
+undocumented immigration, so these percentages of cases cured include curing
+cases of undocumented immigration, despite that the fact that they are not
+tested for LTBI in the first place, as a result of their unofficial channel of
+entry. Thus, achieving 100\% entering LTBI cure rates is practically impossible;
+however, it does illustrate a very important result.  Note that both other
+tested cure rates predict that eventually, incidence rates plateau, reaching a
+nearly steady state by 2075.  This plateau indicates that the system has reached
+an endemic state, where TB lives on in the population despite intervention
+efforts. Given the United States' already aggressive treatment of active TB, why
+does this plateau occur?  Our new model concretely demonstrates that this
+plateau occurs exactly because the US maintains a sizable influx into its LTBI
+population due to immigration, constantly maintaining the population at a large
+enough level to ensure consistent activations of active TB. If the LTBI
+population does not decay, then an endemic state will always be the final
+solution, as regardless of how aggressively active TB is treated, the
+asymptomatic LTBI population will always produce new cases. In our studies,
+every intervention observed had this plateauing effect, save reducing entering
+LTBI by 100\%. This establishes that it is precisely the constantly replenishing
+LTBI population that maintains US TB incidence. To demonstrate this more
+concretely, we consider another intervention, one which will isolate the effects
+of the LTBI driven TB dynamics versus the spread of active TB in all its forms.
+
+\subsubsection{Eliminating TB transmission}
+We also analyzed the intervention of eliminating all active TB transmission. In
+other words, after the start of the intervention, all TB spread is simply
+stopped; everyone infected with TB is noninfectious. This simply removes any
+real dependence on active TB spread, and instead highlights the incidence that
+stems from the self-replenishing LTBI population alone.
+Figure~\ref{fig:redTrans100} demonstrates this effect. 
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.8\textwidth,page=1]{figures/redTrans100Analysis}
+  \caption{This figure shows the yearly TB incidence per million given either no
+  intervention or eliminating active TB transmission.}
+  \label{fig:redTrans100}
+\end{figure}
+
+Figure~\ref{fig:redTrans100} demonstrates that eliminating active TB
+transmission is only moderately effective and still maintains the plateauing
+effect. Therefore, this endemic state is entirely due to the LTBI population. As
+it is substantially higher than the US goal for elimination, this demonstrates
+that LTBI treatment is essential to reach elimination by 2100. Among all LTBI
+treatment interventions tested, curing entering cases of LTBI was the most
+effective by far, for the reasons outlined above. Unfortunately, in order to
+obtain elimination by 2100, at least 95\% of entering LTBI cases had to
+be cured, which is realistically infeasible. Note that sensitivity analysis
+results also indicated that cure rates for entering LTBI cases and LTBI
+treatment rates were highly influential parameters, both in the US HCS costs and
+in the number of active infections.
+
+\subsubsection{Cost Effectiveness}
+\TODO{It also needs to talk about the cost effectiveness of reducing
+  transmission or something, to say that we're getting competitive numbers. We
+need a good source for cpca data for contact investigations, etc.}
+We also estimated the cost per case averted of curing entering cases of LTBI. To
+do so, we assumed that curing a single case of entering LTBI would cost \$800.
+This number is substantially higher than the assumed domestic LTBI treatment
+cost for a number of reasons; notably the cost of implementation as part of the
+immigration process would be very nontrivial. However, this inflation is also
+meant to be a conservative estimate, so as to underestimate the effectiveness of
+this intervention rather than overestimate. Given this treatment cost, we found
+that curing 25\% of entering cases of LTBI resulted in a net US HCS cost per
+case averted of \$67,654.07 at 2025, \$28,699.15 at 2050, and
+\$17,912.95 at 2100 (see Table \ref{tab:redEnLTBICosts} for the cost per case
+averted for other cure percentages). Given the variable nature of LTBI treatment
+cost, the model code is built so that a user can adjust these costs themselves
+to explore more specific methods of curing entering LTBI, especially as the
+treatment methods and associated costs evolve in future years. Curing
+immigrating cases of LTBI  also resulted in 11,900, 29,880, and 60,189 fewer
+cases of TB and 1,025, 2,573, and 5,185 fewer TB deaths for 10\%, 25\%, and 50\%
+cure rate, respectively.
+
+%We also found that the relationship between total incidence at 2100 and
+%percentage of incoming LTBI cases cured was linear. Given this, we estimated the
+%yearly average US HCS savings garnered by curing one case of entering LTBI per
+%year from 2000 to 2025, 2000 to 2050, and 2000 to 2100.  This value peaked
+%at \$1.283 billion at 2100 (25\% reduction). This illustrates that it
+%would be cost saving to cure cases of LTBI at the cost of \$1.283 billion
+%``2000'' dollars over the time period 2000-2100. 
+%These findings are illustrated in Table~\ref{tab:redEnLTBICosts}
+
+\begin{table}
+\centering
+\begin{tabular}{|r|cccc|} \hline
+      &5\% Reduction&10\% Reduction&25\% Reduction&50\% Reduction\\\hline
+  2025& \$67,908.81 & \$67,855.46 & \$67,654.07 & \$67,332.53 \\ 
+  2050& \$28,938.23 & \$28,878.70 & \$28,699.15 & \$28,404.13 \\ 
+  2075& \$21,044.88 & \$20,989.16 & \$20,820.53 & \$20,541.77 \\ 
+  2100& \$18,130.11 & \$18,076.11 & \$17,912.95 & \$17,642.64 \\ \hline
+\end{tabular}
+\caption{Cost Per Case Averted by Reducing Incoming LTBI by various percentages
+(in dollars per case)} 
+\label{tab:redEnLTBICosts}
+\end{table}
+
+\subsection{Agent Based Evaluation}
+Though the extended Hill model is validated against both the Hill model and real
+world data for the years 2000-2008, it still lacks the ability to describe the
+statistical parameters underlying its results. Real disease spread is
+stochastic, yet from the extended Hill model alone we do not know what
+distribution the final infection counts will take. The agent-based model allowed
+these statistical properties to be analyzed and thus gave us confidence in the
+statistical reliability of the extended Hill results. In particular, it
+illustrated that the deterministic Hill model provides a robust statistical
+measure of TB epidemic behavior in the US conditions, as we found that the
+distribution of incidence and final population sizes were approximately
+normal, with mean accurate to the deterministic model and very tight standard
+deviations. Figure~\ref{fig:finalDists} shows the final distributions for a run
+of approximately 2100 iterations of the agent based model. 
+\begin{figure}[h]
+  \centering
+  \begin{minipage}{0.45\textwidth}
+    \includegraphics[width=0.95\textwidth]{figures/IN0distOrig}
+  \end{minipage}
+  \begin{minipage}{0.45\textwidth}
+    \includegraphics[width=0.95\textwidth]{figures/IN1distOrig}
+  \end{minipage}
+  \caption{This figure shows the final distributions (at 2100) for the USB
+    incidence per million \textit{(left)} and FB incidence per million
+    \textit{(right)}. The data were approximately normal, with parameters given
+    by $\mu = 0.233$, $\sigma = 0.016534$, and $\mu = 98.6$, $\sigma = 0.525294$
+    for the USB and FB incidence levels, respectively. The hill model predicts
+    final incidence levels of $0.231$ and $96.36$, respectively, so these match
+    quite well given they come from different model frameworks.
+  }
+  \label{fig:finalDists}
+\end{figure}
+
+Additionally, the agent-based model provided a computational
+framework to produce meaningful intervention results. On student lab grade
+hardware, a statistically meaningful experiment could be run overnight,
+producing data in one day. This demonstrates that this modeling strategy is
+feasible in this general case.  Furthermore, the agent-based model provides a
+greater extensibility to more specific and biologically reasonable scenarios,
+such as geographic dependency or greater population heterogeneity.
+
+\section{Conclusion}
+These results suggest that  LTBI treatment is essential to
+controlling US TB dynamics. This is demonstrated through current US TB incidence
+sources as well as specific intervention analysis. 
+Furthermore, our model indicates that without an active effort to treat
+entering cases of LTBI, the US is likely to never reach its elimination goal, due to the plateauing
+effect. To attain elimination of TB in the US by 2100, we need to cure approximately
+95\% of entering LTBI cases per year, though this number may be reduced if
+combined with other, LTBI targeting interventions.
+
+In addition to immigrant LTBI treatment programs, the US government may consider
+investing in foreign TB control programs, to help bring TB incidence down
+globally so that our LTBI influx rate naturally slows. Further analysis
+incorporating immigration source (i.e. country of origin) and regional TB
+dynamics in the US would be able to determine which foreign TB programs would
+most warrant domestic aid. This would be a natural extension of this work,
+which could help guide US TB policy after implementing domestic interventions.
+
+The agent based model may also be extended to account for greater population
+heterogeneity, tracking more health parameters for each individual.
+Parameters such as HIV infection status, geographic location, and multi-drug
+resistant TB could be added to yield additional information about TB disease dynamics.
+For agent based models, simulation run times scale linearly with the number of health
+states, as opposed to exponentially for compartment based models. Therefore,
+these extensions could be made without significant increases in computational power.
+
+\section{Appendix} 
+\subsection{The Hill Model}
+\label{appendix:hillEqs}
+The differential equations governing the basic Hill model, which also govern the overall compartment flow
+in the extended Hill model, are shown in Figure~\ref{fig:hillEquations}, while
+the constants governing these equations are shown in
+Figure~\ref{fig:hillConstants}. In these equations, note that the variables
+$S_0, F_0, L_0, I_0, J_0$ contain the number of US-born individuals in the $S$,
+$F$, $L$, $I$, $J$ compartments respectively, whereas $S_1, F_1, L_1, I_1, J_1$
+contain the number of foreign-born individuals. $N_0$ and $N_1$ are the total
+populations of US-born and foreign-born individuals \cite{hill_modelling_2012}.
+\begin{figure}[h]
   \begin{align*}
@@
   \end{align*}
-  \caption{System of Differential Equations given in the Hill Model.}
+  \caption{System of Differential Equations given in the Hill model.}
   \label{fig:hillEquations}
 \end{figure}
-\begin{figure}
+\begin{figure}[h]
   \begin{align*}
+    \rho       &= 0.018   && \text{(US birth rate)}\\
+    \alpha     &= 0.005   && \text{(FB arrival rate)}\\
+    \mu_0      &= 1/78    && \text{(Natural USB mortality rate)}\\
+    \mu_1      &= 1/53    && \text{(FB mortality rate)}\\
     \sigma^{L} &= 0.057   &&\text{(Treatment rate for chronic LTBI)}\\
-    v^{L}_{0}  &= 0.0014  &&\text{(Progression rate for reactivation in the USB
+    \nu^{L}_{0}&= 0.0014  &&\text{(Progression rate for reactivation in the USB
                                    population)}\\
-    v^{L}_{1}  &= 0.0010  &&\text{(Progression rate for reactivation in the FB
+    \nu^{L}_{1}&= 0.0010  &&\text{(Progression rate for reactivation in the FB
                                    population)}\\
+    \nu^{F}    &= 1.5     &&\text{(Progression rate for acute LTBI)}\\
     f          &= 0.187   &&\text{(Fraction of FB arrivals with LTBI)}\\
@@
                                    infection)}\\
+    \sigma_0^{F} &= 1.296 &&\text{(Rate of treatment for USB acute infection)}\\
+    \sigma_1^{F} &= 1.301 &&\text{(Rate of treatment for FB acute infection (per
+                                   year))}\\
     r_{0}      &= 0.667   &&\text{(Fraction of cases due to reactivation in USB
@@
                                    active disease)}\\
-    e_{0}      &= 0.965   &&\text{(Fraction of preferred contacts within own
-                                   population for USB)}\\
-    e_{1}      &= 0.985   &&\text{(Fraction of preferred contacts within own
-                                  population for FB)}\\
+    \phi_0     &= 0.897   &&\text{(Cumulative rate of self-cure and treatment of
+                                   USB active disease)}\\
+    \phi_1     &= 0.897   &&\text{(Cumulative rate of self-cure and treatment of
+                                   FB active disease)}\\
   \end{align*}
-  \caption{The relevant constants used in the Basic Hill Model.  }
-  \label{fig:basicHillConstants}
+  \begin{align*}
+    e_{0}      &= 0.965   &&\text{(Fraction of intra-USB preferred contacts)}\\
+    e_{1}      &= 0.985   &&\text{(Fraction of intra-FB preferred contacts)}\\
+    \beta      &= 10.39   && \text{(Effective contact rate)}\\
+    \lambda_i  &= \beta\(c_i0\frac{I_0}{N_0} + c_{i1}\frac{I_1}{N_1}\)
+                          &&\text{(The force of infection)}\\
+    c_{ij}     &= e_i\delta_{ij} + (1-e_i)\frac{(1-e_j)N_j}
+                                               {(1-e_0)N_0 + (1-e_1)N_1}
+                          &&\text{(Contact proportion constants)}\\
+  \end{align*}
+  \caption{The relevant constants used in the basic Hill model. All rates are in
+           units of year$^{-1}$.}
+  \label{fig:hillConstants}
 \end{figure}
 
-The vector variables $S_0, F_0, L_0, I_0, J_0$ contain the number of US-born
-individuals in the S, F, L, I, J compartments respectively, whereas $S_1, F_1,
-L_1, I_1, J_1$ contain the number of foreign-born individuals. $N_0$ and $N_1$
-are the total populations of US-born and foreign-born individuals. 
-\TODO{Is the next bit needed? I think move the stuff below out and the stuff
-above back where we introduce the equations.}
-The constants $\rho$ and $\alpha$ are birth rates, while $\mu_i$, and $\mu_d$
-are death rates. A complete list and descriptions of all constants used in the
-model can be found in the Appendix, Section~\ref{subsec:hillConstants}.
+As mentioned above, the equations shown in Figure~\ref{fig:hillEquations} govern
+both the basic Hill model and the extended Hill model; the difference between
+the two is that in the extended Hill model, the equations were separated into
+their component parts so that each flow rate could be captured individually. For
+example, the equation
+\[\dot{I}_0 = q(\nu^FF_0 + \nu_0^LL_0) - (\mu_0+\mu^d+\varphi_0)I_0\]
+was separated into 
+\begin{align*}
+  \dot{{I_0}}_{F_0} &= q \nu^F F_0\\
+  \dot{{I_0}}_{L_0} &= q \nu_0^L L_0\\
+  \dot{{TBD}}_{I_0} &= \mu^dI_0 \\
+  \dot{{ND}}_{I_0}  &= \mu_0I_0 \\
+  \dot{{S}}_{I_0}   &= \varphi_0 I_0\\
+  \dot{I_0}         &= \dot{{I_0}_{F_0}} + \dot{{I_0}_{L_0}} +
+                       \dot{{TBD}_{I_0}} - \dot{{TBD}_{I_0}} -
+                       \dot{{ND}_{I_0}}  - \dot{S_{I_0}}
+\end{align*}
+where ${I_0}_{F_0}$ is the number of USB active, contagious infections (members
+of $I_0$) that arose due to new infections (activations from the USB acute LTBI
+compartment, $F_0$), ${I_0}_{L_0}$ is the number of USB active infections that
+arose from activations of longstanding LTBI infections (the USB chronic LTBI
+compartment, $L_0$), ${TBD}_{I_0}$ is the number of TB deaths from those in the
+infectious USB population, $I_0$, $ND_{I_0}$ is the number of natural deaths
+from those in the infectious USB population, and $S_{I_0}$ is the number of
+cases of active, infectious TB in the USB population that were cured.
 
-\subsection{Additional Tracking Capabilities}
-In order to refine the tracking capabilities of the Hill Model, the original
-differential equations used to describe TB spread were separated into their
-component parts and each part was tracked separately. In effect, each flow rate
-between two compartments in the Basic Hill model was made into its own
-``virtua'' compartment, thereby enabling computation not only of expected TB
-incidence, but also of the source of that incidence. In particular, progressions
-into active TB due to activations of LTBI or exogenous infection were tracked,
-allowing for sourced incidence data to be generated. These equations allowed the
-model to track the sourced number of TB cases, TB deaths, and natural deaths.
-Furthermore, the model also tracks the sourced cost on the US HCS. The
-immigrating cases of LTBI (acute or chronic) were also tracked. In the case of
-intervention testing, the number of cured and untreated cases of entering LTBI
-were both tracked. Cured cases of LTBI entering, TB deaths, total TB cases, and
-total cost were also tracked discounted at 3\% annually. This discounting was
-converted to a continuous differential equation for use within the model. In
-general, incidence data is calculated in the same way in the Extended Hill Model
-as it was in the Basic Hill Model.
+The extended Hill also added certain equations and constants to generate cost
+data. These equations are detailed in Figure~%\ref{fig:hillCosts}. 
+\TODO{Add figure hillCosts. We first need to determine what the correct LTBI
+cost parameters are. See the TODO above regarding that.}
+These parameters were derived via
+\TODO{Cite Dylan's cost study, adherence study, etc.}
 
-\TODO{Where does this fit in? I'm not seeing why this is here? Maybe in the
-results, instead?}
-In addition, estimations of the basic reproductive number of FB or USB active,
-infectious TB cases were made from a theoretical and an experimental
-perspective. Experimental data were calculated by reducing the initial
-FB or USB infectious TB populations by one and allowing the
-model to progress otherwise as normal. The decreased number of total TB cases
-seen details how many infections can be thought to be due to one infected
-individual in the given population. In the agent-based model, this \emph{one}
-was a true model agent whereas in the compartmental model, this decrease of
-\emph{one} was a proportional decrease based on the scaled population level.
+Finally, all the code for the extended hill and agent based model can be found
+on github, at \url{https://github.com/mmcdermott/disease-modeling}.
 
-From a theoretical perspective, the spread of TB was thought to be a geometric
-series. If one infectious individual infects $x$ people annually, over the
-course of $N$ years the total number of infections caused by this individual can
-be approximated by the geometric series of $N$ terms with rate $x$ and initial
-term $1$. In this case, $N = 100$, and the ratios for FB infectious individuals
-and USB infectious individuals were obtained from 
-\TODO{<+RATIO CITATION COLIN+>.}
-\subsection{Economic Modeling}
-In order to track the US HCS TB cost, we made the following treatment cost
-assumptions. A single case of active TB was assumed to yield a \$14,000 US HCS
-cost, charged immediately upon disease contraction. This cost is the weighted
-mean of the costs of cases requiring hospitalization (49\%) and cases not
-requiring hospitalization (51\%).  These cost estimates were found in 
-\TODO{<+DYLAN COST STUDY CITATION+>.} LTBI treatment costs were assumed to be
-\$468.00, charged immediately upon successful treatment. These estimates were
-calculated based on the cost of a successful treatment, and the typical
-adherence and efficacy of said treatment 
-\TODO{<+DYLAN COST STUDY CITATION, ADHERENCE CITATION+>.}
-It is important to note that the charging assumptions are different for
-treatment of active TB as opposed to treatment of latent TB. In particular,
-cases of active TB imply a cost immediately upon disease contraction, whereas
-latent TB costs are charged only upon successful treatment. The motivation for
-this distinction is that active TB treatment is mandated by the US for all known
-cases and, further, most treatment costs are incurred at the beginning of the
-treatment cycle. As such, charging for every known case, immediately at
-contraction is a well motivated assumption. On the other hand, latent TB is only
-rarely treated in discovered cases and the costs are more evenly distributed.
-Furthermore, the choice to charge only upon successful treatment yields a more
-conservative estimate of the success of any intervention analyzed. Finally, it
-is worth noting that, though accurate, these estimates of US HCS treatment cost
-are not intended to be fixed parameters. The code for this model is freely
-available, and as new research amends the necessary costs and new methods of
-treatment are developed, these values can be modified and the model re-run to
-produce a revised prediction of the US HCS TB cost.
-
-In addition to refining the model to produce sourced US TB incidence estimates,
-the additional cost modeling was also tracked in a way that preserved the source
-of the US HCS cost. In particular, active TB treatment cost was tracked
-separately for cases resulting from an activation of LTBI (modeled as a
-progression from the Chronic Latent category) and for cases resulting from a
-novel, exogenous infection (modeled as a progression from the Acute Latent
-category). All cost equations were also solved by $\texttt{lsoda}$.  Given the
-uncertainty in estimates of LTBI treatment cost, extensive sensitivity analysis
-was performed on this parameter relative to final cost outcomes. Furthermore,
-the US HCS cost caused by LTBI treatment (which was tracked) was often omitted
-from Cost Benefit intervention analyses, so as to provide the most conservative
-estimate of total US HCS cost given various TB interventions. In addition to US
-HCS cost, the system was implemented so as to also track projected intervention
-implementation cost, given user-inputted parameters relating to various possible
-intervention cost strategies. The extended Hill Model was used to track the
-effect of many interventions tested by the Hill Model. In particular, the
-intervention strategy of curing entering cases of LTBI proved very promising and
-elimination year, final cost, and cost per case averted were tracked for various
-levels of entering LTBI cure rate. The interventions were implemented so as to
-take effect during the year 2013 and run to 2100. The numerical DE solver
-$\texttt{lsoda}$ used was run with a time step of $0.8$. Sensitivity analysis
-was performed on this parameter and reducing the time step was shown to have
-minimal effect on final size or cost values.
-
-\subsection{Agent Based}
-\TODO{What's the story we are trying to tell here? I mean, we are following a
-  very standard format, but I think it would be better if we had a cohesive
-  message.}
-The population level agent based model was implemented in several ways. Early
-implementations were built in \texttt{Netlogo} and \texttt{Java}, but final
-implementations were constructed in \texttt{C++}. Probabilities of agent
-progression between various health states were computed given rates in the hill
-model and a variety of integration approximations. The model maintained
-individual records for every individual with LTBI or active TB. Susceptible
-individuals were not modeled as agents; instead, a binomial distribution was
-used to probabilistically determine the number of new infections each time step.
-Similarly, the number of new immigrants each time step was chosen from a
-probability distribution. As the model was stochastic, all final data is
-inherently merely a probabilistic sample; as such, many simulations are required
-to draw conclusions from the model. As such, we collected final population
-health statistics from approximately 2160 model simulations, with each agent in
-the model truly representing one infected individual, and a time step of $0.01$.
-These data were analyzed in $R$. The agent based model also tracks deaths, total
-TB cases, and infection sources, and can also easily track economic data. These
-data were consistently normal and matched the deterministic model. 
-\TODO{Does it track economic data yet?}
-
-Further implementations of the \texttt{C++} model were made that deviated from
-the basic Hill Model. Specifically, the acute latent compartment in the basic
-Hill Model is a vestigial necessity of compartmental modeling and not reflective
-of the biology of tuberculosis. As such, an agent based model was implemented
-that more closely respects the biology of tuberculosis. Results from this model
-were also normal and did not differ significantly from the strict Hill model.
-
-\section{Results}
-\subsection{Basic Population Breakdown}
-The additional tracking capabilities offered several key insights into US TB
-dynamics. Figure~\ref{fig:incPlotSourced} shows the yearly incidence of US TB, broken
-down into infection source. It can be seen that the majority of the US TB load
-is driven by activations of FB LTBI, followed by USB LTBI activations. This data
-further agrees with the conclusions drawn by Hill, Becerra, and Castro about the
-necessity of LTBI treatment in any effective intervention strategy. 
-\TODO{Why does it agree? We aren't doing any data analysis here, which is a
-problem. We need to walk our readers through this.}
-\begin{figure}[h]
-  \begin{center}
-    \includegraphics[scale=.5]{incPlotSourced}
-  \end{center}
-  \caption{Sourced yearly incidence data generated by the extended Hill Model.}
-  \label{fig:incPlotSourced}
-\end{figure}
-Further, figure~\ref{fig:costPlotSourced} shows a similarly sourced plot, but analyzing the
-final US HCS costs due to active TB. One can see that in this plot, roughly half
-of the US TB HCS costs are due to activations of LTBI. Note that in this data,
-it is appropriate to think of the costs due to acute LTBI as costs due to
-exogenous re-inection, whereas costs due to chronic LTBI are activations of long
-standing latent infections. 
-\begin{figure}[h]
-  \begin{center}
-    \includegraphics[scale=.35]{costPlotSourced}
-  \end{center}
-  \caption{Sourced US HCS economic TB load. Note that this data only illustrates
-    the load due to treating active TB, but illustrates where the infections
-    driving this cost come from.}
-  \label{fig:costPlotSourced}
-\end{figure}
-Note that both of these plots underestimate the impact of LTBI on the spread of
-TB, as every LTBI activation contributes not only
-to incidence and costs directly, but also indirectly by causing additional
-future cases, which is not captured in these graphs. Further, there are also US
-HCS costs due to LTBI treatment, which is not illustrated in these graphs. 
-\subsubsection{Basic Reproduction Number}
-The basic reproduction number of FB or USB cases of infectious TB was also
-estimated by this system. Using the best-fit values of parameters from the 
-Hill model, we found the average number of secondary infections arising from
-a single case of infectious TB to be 0.423 and 0.370 for USB and FB populations
-respectively.  These values differ because in the model, there are different
-estimates for death rates and the rate of TB treatment and self-cure in the USB and FB populations, 
-so the average infectious period differs between the two populations.
-Extrapolating these results, we can think of the
-total number of secondary infections over 100 years due to a FB or USB
-infectious TB case as describing a geometric series in a large population.
-Presuming there are no overlaps in infectious contacts, if a single case of
-infectious TB in either population infects $p_f, p_u$ new cases,
-respectively, then we can say that over the course of 100 years, the total
-number of cases infected will follow a geometric series.
-{\huge \color{red} TODO: formalize this with math. We can fit it here.}
-This analysis predicts
-that over 100 years, one USB infection will lead to $1.04$ subsequent infections,
-whereas one FB infection will lead to $.83$ subsequent infections. Experimentally, 
-these data were also analyzed, with results of $1.03$ and $.64$, respectively. 
-Full calculations are included in the Appendix.
-
-\subsection{Intervention Analysis}
-The primary interventions analyzed by the extended Hill were those that analyzed
-curing various percentages of entering LTBI cases. Four indicative percentages
-chosen were $5\%$, $10\%$, $25\%$, and $50\%$. Note that the Hill model does not
-distinguish between documented and undocumented immigration, so these
-percentages are over \emph{all} immigration into the United States, and can thus
-be thought to represent significantly higher percentages of documented
-immigration. It was seen that in this model as well as in the Basic Hill Model,
-no analyzed intervention predicted elimination by 2100. In order to obtain
-elimination by 2100, at least 95\% of entering LTBI cases had to be cured, which
-is infeasible in the real world. However, it was seen that curing entering cases of
-LTBI resulted in a net US HCS cost per case averted of \$67,654.07 at 2025, \$28,699.15 at 2050,
-and \$17,912.95 at 2100 (assuming 25\% reduction with each cure costing \$800; see Table
-\ref{tab:cpcaArt} for other percentages). Given the variable nature of LTBI
-treatment cost, the model code is extendible such that a user can adjust these
-costs themselves to explore more specific methods of curing entering LTBI,
-especially as the treatment methods and associated costs evolve in future years.
-Further, it was also found that the relationship between total incidence at 2100
-and percentage of incoming LTBI cases cured was linear, and from this estimates
-were made of the yearly average US HCS savings garnered by curing one case of
-entering LTBI over the time scale 2000 to 2025, 2000 to 2050, and 2000 to 2100.
-This value peaked at \$1.283 billion at 2100 (25\% reduction). This illustrates
-that it would be cost saving to cure cases of LTBI at the cost of \$1.283
-billion ``2000'' dollars over the time period 2000-2100. These intervention
-strategies also resulted in 11,900; 29,880; and 60,189 fewer cases of TB seen in
-the US, and 1,025; 2,573; and 5,185 fewer TB deaths, for 10\%, 25\%, and 50\%
-reduction, respectively.
-{\huge \color{red} TODO: This section is a bit confusing. Also, a graph would
-make things much prettier.}
-
-% latex table generated in R 3.0.1 by xtable 1.7-1 package
-% Mon Oct 14 00:36:15 2013
-\begin{table}
-\centering
-\begin{tabular}{|r|cccc|} \hline
-       & red5     & red10    & red25    & red50    \\ \hline
-  %2000 & ND       & ND       & ND       & ND       \\ 
-  2025 & 67908.81 & 67855.46 & 67654.07 & 67332.53 \\ 
-  2050 & 28938.23 & 28878.70 & 28699.15 & 28404.13 \\ 
-  2075 & 21044.88 & 20989.16 & 20820.53 & 20541.77 \\ 
-  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ \hline
-\end{tabular}
-\caption{Cost Per Case Averted by Reducing Incoming LTBI by X percent (in dollar per case)} 
-\label{tab:cpcaArt}
-\end{table}
-
-Several other intervention strategies analyzed by the Hill Model were also
-examined via the Extended Hill, and economic properties about each were tracked.
-The results for these interventions, which were consistently less effective than
-curing entering LTBI cases, are given in the appendix. {\huge \color{red} TODO:
-Which section?}
-
-\subsection{Sensitivity Analysis}
-To account for uncertainty of input parameter values and to gain insight about
-the most influential parameters in the model, we used Latin Hypercube Sampling
-to analyze the deterministic model, implemented with the \texttt{lhs} package in
-\texttt{R}.  We varied the 16 parameters from the original Hill model according
-to triangular distributions centered around their best-fit values, and two
-additional treatment cost parameters according to uniform distributions.
-{\huge\color{red} TODO: These distributions were chosen because\ldots}. All
-non-economic parameters analyzed reported statistically similar results to their
-analysis in the Basic Hill Model. For economic outcomes, we found the parameter
-$f$, the fraction of FB arrivals with LTBI, to be highly correlated with the
-projected overall cost burden of TB in the United States over the next 100
-years.  Another highly influential parameter in the model was $\sigma^{L}$, the
-treatment rate for chronic LTBI.  However, while increasing $\sigma^{L}$
-significantly decreases the cost burden due to Active TB treatment, it increases
-the cost burden due to Latent TB treatment by a greater amount, given the
-treatment cost estimates of \$700 and \$14,000 for LTBI and Active TB,
-respectively.  A full description of the Latin Hypercube Sampling analysis and
-tables of Partial Rank Correlation Coefficient (PRCC) results for all parameters
-are given in the appendix, in Section~\ref{subsec:lhs}.
-
-\subsection{Agent Based Evaluation}
-The agent-based model allowed the statistical properties of the system to be
-analyzed and verified. In particular, it illustrated that the deterministic
-Hill model provides a robust and consistent statistical measure of TB epidemic
-behavior in the US conditions. We found that the distribution of incidence and
-final population sizes were normal, with mean accurate to the deterministic
-model and standard deviations given in table {\huge\color{red} TODO: Add table
-\# and section \# here}, in the Appendix. Additionally,
-the agent-based model provided a computational framework to produce
-meaningful intervention results. On student lab gradet hardware, a statistically
-meaningful experiment could be run overnight, producing data in one day. This
-demonstrates that this modeling strategy is feasible in this general case.
-Furthermore, the agent-based model provides a greater extensibility to more
-specific and biologically reasonable scenarios, such as geographic dependency or
-greater population heterogenity.
-
-\section{Discussion}
-These results confirm the hypothesis that curing incoming LTBI rates is a
-necessary step towards elimination and indicate that it is a cost effective
-option. \\
-{\huge \color{red} TODO: Where did we show it was cost effective relative to other
-interventions? Also, the section below (future work) might be better just
-directly included in the discussion. Also, if we want to make this claim here we
-need to include other interventions in the main body.}\\
-In addition, beyond demonstrating quantitatively that this intervention strategy
-is a necessary step towards US elimination, we also obtained qualitative
-indications that this is the case. In every intervention we tested (see, for
-example, Intervention \TODO{<+ADD ME+> and <+ADD ME+> in section <+ADD ME+>}) we
-observed a plateauing effect, where the incidence per million stabilized after
-some time and resisted further change. In particular, even when transmission was
-reduced to $0\%$, we still observed this plateauing effect, which implies that
-something other than active transmission was generating enough incidence to
-sustain TB in an endemic state in the US population. However, when the FB LTBI
-immigration was cut, this effect vanished. These results therefore support the
-argument that the USB LTBI population is sufficiently large to sustain a
-sizable, endemic TB-disease state in the United States provided it is
-continually refueled via the entering LTBI immigrants. Thus, there is no
-intervention that can ignore the LTBI population that can hope to eliminate TB
-in the United States. Among those interventions that treat cases of LTBI,
-targeting the immigrating LTBI requires no additional US HCS dollars beyond what
-is spent now to identify the LTBI population and is therefore extremely
-efficient. Additionally, our analysis shows that paying for the treatment of
-these individuals is extremely cost effective {\huge \color{red} TODO: Show
-this}.
-\subsection{Future Work}
-This work could be extended by examining different classes of interventions or
-more accurately estimating intervention cost with the deterministic extended
-Hill. Further work could also be done with the agent-based Hill Model, by using
-it to examine the effect contact structure plays on US TB incidence levels or to
-examine the effects drug-resistant TB will have on US TB dynamics.
-
-\section{Appendix} 
-\subsection{Hill Constants}
-\label{subsec:hillConstants}
-Below, we detail some of the relevant constants in the Basic Hill Model, and
-their best-fit values. A full listing of constants used in the original Hill
-Model can be found in \TODO{<+CITATION HERE+>} \TODO{Can we delete this
-section?}
-
-\textit{(USB = US born, FB = Foriegn born)}
-\begin{align*}
-  \sigma^{L} &= 0.057   &&\text{(Treatment rate for chronic LTBI)}\\
-  v^{L}_{0}  &= 0.0014  &&\text{(Progression rate for reactivation in the USB
-                                 population)}\\
-  v^{L}_{1}  &= 0.0010  &&\text{(Progression rate for reactivation in the FB
-                                 population)}\\
-  f          &= 0.187   &&\text{(Fraction of FB arrivals with LTBI)}\\
-  p          &= 0.103   &&\text{(Fraction of new infections which are acute)}\\
-  ARI_{0}    &= 0.00030 &&\text{(2000 Annual Risk of Infection, USB)}\\
-  q          &= 0.708   &&\text{(Fraction of infections progressing to infectious
-                                 disease)}\\
-  g          &= 0.0047  &&\text{(Fraction of FB arrivals with LTBI who are fast
-                                 progressors)}\\
-  \sigma^{F} &= 0.461   &&\text{(Cumulative fraction of treatment for acute
-                                 infection)}\\
-  r_{0}      &= 0.667   &&\text{(Fraction of cases due to reactivation in USB
-                                 population)}\\
-  r_{1}      &= 0.780   &&\text{(Fraction of cases due to reactivation in FB
-                                 population)}\\
-  \mu^{d}    &= 0.115   &&\text{(Mortality rate due to TB)}\\
-  x          &= 0.111   &&\text{(Fraction of re-infected chronic LTBI moving to
-                                 acute infection)}\\
-  \phi       &= 0.897   &&\text{(Cumulative fraction self-cure and treatment of
-                                 active disease)}\\
-  e_{0}      &= 0.965   &&\text{(Fraction of preferred contacts within own
-                                 population for USB)}\\
-  e_{1}      &= 0.985   &&\text{(Fraction of preferred contacts within own
-                                population for FB)}\\
-\end{align*}
-\subsection{The Extended Hill Equations}
-\label{sec:extendedHillEqs}
-Below, we detail some of the relevant equations used in the extended hill model.
-In many cases, the equations of the Hill model were split into their component
-parts, which could then be tracked separately.
-
-\TODO{What equations should be put in here?}
-
-Here, a continuous discounting approximation is used to a discount rate of $3\%$
-yearly, found via $discV$. In many of the differential equations, a small $c$ is
-used to denote \emph{cost of}. 
-\FloatBarrier
-\subsection{Estimations for Infectious Rates of FB and USB}
-
-\subsection{Statistical Qualities of the Agent Based Model}
-
-\begin{figure}
-    \includegraphics[scale=0.4]{figures/qqnormUSBInc.pdf}
-    \includegraphics[scale=0.4]{figures/qqnormFBInc.pdf}
-    \includegraphics[scale=0.4]{figures/qqnormUSBPop.pdf}
-    \includegraphics[scale=0.4]{figures/qqnormFBPop.pdf}
-  \caption{Normal Q-Q Plots for 2103 runs of the Stochastic Model with population constant = 1.}
-  \label{fig:qqnormPlots}
-\end{figure}
-
-Results for USB Incidence, FB Incidence, USB Population, and FB Population in the year
-2100 shown, overlayed with linear (normal) fit are shown in
-figure~\ref{fig:qqnormPlots}. These plots demonstrate the normality of the
-Stochastic data. 
-\subsection{Finer Intervention Analysis}
-
-% latex table generated in R 3.0.1 by xtable 1.7-1 package
-% Mon Oct 14 00:36:15 2013
-\begin{table}
-\centering
-\begin{tabular}{|r|cccc|} \hline
-       & red5    & red10    & red25    & red50    \\ \hline
-  %2000 & 0.00    & 0.00     & 0.00     & 0.00     \\ 
-  2025 & 1115.12 & 2231.70  & 5592.43  & 11227.57 \\ 
-  2050 & 3406.41 & 6821.27  & 17117.18 & 34447.71 \\ 
-  2075 & 4976.77 & 9967.15  & 25021.33 & 50389.58 \\ 
-  2100 & 5942.02 & 11900.90 & 29880.03 & 60189.49 \\ 
-   \hline
-\end{tabular}
-\caption{Cases of TB Averted by Reducing Incoming LTBI by various percentages
-         (Cure=\$800)} 
-\label{tab:caRed}
-\end{table}
-
-% latex table generated in R 3.0.1 by xtable 1.7-1 package
-% Mon Oct 14 00:36:15 2013
-\begin{table}
-\centering
-\begin{tabular}{|r|cccc|} \hline
-       & red5     & red10    & red25    & red50    \\ \hline
-  %2000 & ND       & ND       & ND       & ND       \\ 
-  2025 & 67908.81 & 67855.46 & 67654.07 & 67332.53 \\ 
-  2050 & 28938.23 & 28878.70 & 28699.15 & 28404.13 \\ 
-  2075 & 21044.88 & 20989.16 & 20820.53 & 20541.77 \\ 
-  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ \hline
-\end{tabular}
-\caption{Cost Per Case Averted by Reducing Incoming LTBI by various percent (in
-dollars per case, Cure=\$800)} 
-\label{tab:cpcaRed}
-\end{table}
-
-\subsection{Latin H ypercube Sampling}
-\label{subsec:lhs}
-%The model parameters and variable names referred to in this analysis are listed
-%below, along with best-fit or estimated values. 
-Following the example of the
-Hill model, we generated a Latin Hypercube Sample varying 18 of the input
-parameters.  From these parameters, 16 are identical to the input parameters
-varied in the sensitivity analysis of the original Hill model, and the remaining
-two parameters, $C_{A}$ and $C_{L}$, detailed below, are variables for the average cost of
-Active and Latent TB treatment in the US.   Probability distributions for the
-original 16 parameters of the Hill model were all set to be Triangular, with
-mode at the best fit value and end points at the 2.5 and 97.5 percentile values
-reported in the Hill model.  Probability distributions for $C_{A}$ and $C_{L}$
-were set to be Uniform, with range +/- 10\% of the estimated value.  All
-probabilty distributions used to generate the Latin Hypercube are listed in
-Table 1.\\
-
-{\bf Additional Cost Parameters}
-\begin{align*}
-  C_{A} &= \$14,014.50 &&\text{(Cost per Active TB treatment)}\\
-  C_{L} &= \$700       &&\text{(Cost per Latent TB treatment)}
-\end{align*}
-\vspace{5mm}
-
-\begin{table}[h]
-\centering
-\begin{tabular}{l l}
-\hline\hline\\
-Parameter & Distribution\\ [0.5ex]
-\hline\\
-$\sigma_{L}$  & Tri(0.015,0.057,0.086) \\
-$v^{L}_{1}$   & Tri(0.0009,0.0010,0.0014) \\
-$f$                 & Tri(0.157,0.187,0.232) \\
-$p$                & Tri(0.053,0.103,0.137) \\
-$ARI_{0}$      & Tri(0.00021,0.00030,0.00030) \\
-$q$                & Tri(0.569,0.708,0.825) \\
-$g$                & Tri(0.0008,0.0047,0.0815)  \\
-$\sigma_{F}$ & Tri(0.419,0.461,0.574) \\
-$r_{1}$          & Tri(0.759,0.780,0.831) \\
-$r_{0}$          & Tri(0.623,0.667,0.694) \\
-$\mu^{d}$      & Tri(0.071,0.115,0.231) \\
-$x$                 & Tri(0.088,0.111,0.860) \\
-$v^{L}_{0}$   & Tri(0.0011,0.0014,0.0015) \\
-$\phi$            & Tri(0.861,0.897,0.938) \\
-$e_{0}$          & Tri(0.853,0.965,0.995) \\
-$e_{1}$          & Tri(0.877,0.985,0.999) \\
-$C_{A}$           & Uniform(12613,15416) \\
-$C_{L}$           & Uniform(630,770) \\ [1ex]
-\hline
-\end{tabular}\\[1ex]
-
-{\bf Table 1.} Probability distributions for model parameters, where Tri(x,y,z) denotes the 
-Triangular distribution with endpoints (x,z) and mode y.
-\end{table}
-
-With a random Latin Hypercube Sample of size n=100,000, we computed partial rank correlation coefficients (PRCC) for each of the initial parameters and treatment costs, according to four different outcomes: 1) projected annual incidence in 2100 in the overall population, 2) projected cumulative cost of Latent TB treatments by 2100, 3) projected cumulative cost of Active TB treatments by 2100, 4) projected cumulative total cost of TB treatments by 2100.
-For outcome 1, PRCC values are shown alongside PRCC values computed in the original Hill model for the same outcome in Table 2, showing the closeness of our findings to the sensitivity results of the original Hill model.
-PRCC values for the remaining outcomes are reported in Table 3.
-\\
-
-\begin{table}[h]
-\centering
-\begin{tabular}{l r r}
-\hline\hline\\
-Parameter & Extended Hill Model & Original Hill model \\ [0.5ex]
-\hline\\
-$\sigma^{L}$  & -0.9303 & -0.9381 \\
-$v^{L}_{1}$   & 0.7871  & 0.8309 \\
-$f$                 & 0.7050  & 0.8072 \\
-$p$                & 0.8369  & 0.6100 \\
-$ARI_{0}$      & 0.5950  & 0.4939 \\
-$q$                & 0.5797  & 0.4543 \\
-$g$                & 0.6122  & 0.4517 \\
-$\sigma^{F}$ & -0.4911 & -0.3772 \\
-$r_{1}$          & 0.0028  & -0.1109 \\
-$r_{0}$          & 0.0018  & 0.0760 \\
-$\mu^{d}$      & 0.0923 & 0.0513 \\
-$x$                 & 0.0999 & 0.0345 \\
-$v^{L}_{0}$    & 0.0133 & 0.0266 \\
-$\phi$             & 0.0082 & 0.0177 \\
-$e_{0}$          & 0.0178 & -0.0072 \\
-$e_{1}$          & 0.1154 & 0.0046 \\
-$C_{A}$          & -0.0023 & N/A \\
-$C_{L}$           & 0.0009 & N/A \\ [1ex]
-\hline
-\end{tabular}\\[1ex]
-
-{\bf Table 2.} PRCC values for projected annual incidence in 2100
- in the overall population, alongside corresponding values from the
-original Hill model.
-\end{table}
-
-From Table 2, we see that the PRCC values in the Extended Hill Model and the
-Original Hill Model match up reasonably well.  In both cases, $\sigma^{L}$ is
-the most influential parameter, with PRCC values around -0.93.  The cost
-parameters $C_{A}$ and $C_{L}$ have PRCC values close to zero, which is expected
-because varying the treatment costs should not affect the incidence rate of TB.
-Parameters in the original Hill model with small PRCC magnitudes (less than
-0.15) also have small PRCC values in the extended model, while parameters with
-larger PRCC magnitudes (greater than 0.35) similarly have large PRCC values in
-the extended model.  This validates the non-economic components of our model
-against the original Hill model.   \\
-
-\begin{table}[h]
-\centering
-\begin{tabular}{l r r r}
-\hline\hline\\
-Parameter & Latent Costs & Active Costs & Total Costs\\ [0.5ex]
-\hline\\
-$\sigma^{L}$ & 0.9612  & -0.9284 & 0.4169 \\
-$v^{L}_{1}$  & -0.4190 & 0.6470  & 0.3533 \\
-$f$          & 0.7467  & 0.5493  & 0.8083 \\
-$p$          & 0.3371  & 0.8810  & 0.8776 \\
-$ARI_{0}$    & 0.3920  & 0.6728  & 0.7337 \\
-$q$          & 0.3837  & 0.6573  & 0.7200 \\
-$g$          & 0.1120  & 0.5369  & 0.5182 \\
-$\sigma^{F}$ & -0.1138 & -0.5631 &-0.5435 \\
-$r_{1}$      & 0.1253  &  0.0658 & 0.1401 \\
-$r_{0}$      & 0.1325  & 0.0878  & 0.1658 \\
-$\mu_{d}$    & 0.0249  & 0.0560  & 0.0613 \\
-$x$          & 0.0214  & 0.1282  & 0.1253 \\
-$v^{L}_{0}$  & -0.3103 & 0.0502  &-0.1867 \\
-$\phi$       & -0.0023 & -0.0102 &-0.0107 \\
-$e_{0}$      & 0.0081  & 0.0253  & 0.0269 \\
-$e_{1}$      & 0.0804  & 0.1653  & 0.1926 \\
-$C_{A}$      & 0.0011  & 0.7024  & 0.6385 \\
-$C_{L}$      & 0.8515  & 0.0013  & 0.7598 \\ [1ex]
-\hline
-\end{tabular}\\[1ex]
-
-{\bf Table 3.} PRCC values for cumulative US Health Care system costs from 
-Latent TB treatment, Active TB treatment, and Total treatment costs
-\end{table}
-
-In Table 3, we see that the cost parameters $C_{A}$ and $C_{L}$ are highly
-correlated with Active treatment costs and Latent treatment costs respectively.
-These high PRCC values are expected because there is a linear relationship
-between $C_{A}$ and the cumulative Active treatment cost, and similarly for
-$C_{L}$ and the cumulative Latent treatment cost.  In addition, we note that
-both $C_{A}$ and $C_{L}$ are influential in the total overall cost, with PRCC
-values of 0.6385 and 0.7598 respectively.  Because the PRCC value for $C_{L}$ is
-greater here, despite the fact that $C_{A} > C_{L}$, we can infer that
-cumulative Latent TB treatment costs are projected to be greater than cumulative
-Active TB costs with these estimates for cost parameters, so $C_{L}$ is a more
-influential parameter for total cumulative treatment costs.
-
-Other variables with significant PRCC magnitudes (greater than 0.5) in Table 3
-include $\sigma^{L}$, $v^{L}_{1}$, $f$, $p$, $ARI_{0}$, $q$, $g$, and
-$\sigma^{F}$.  Two of these parameters, $\sigma^{L}$ and $v^{L}_{1}$, have
-relatively large PRCC magnitudes for both Latent and Active Costs, but smaller
-PRCC magnitudes for Total Costs.  Because their PRCC values for each of these
-two outcomes is different in sign, the net change to the total cost is partially
-cancelled out, so these parameters have a reduced influence on final US
-healthcare system costs.  On the other hand, parameters such as $f$ and $p$ have
-large positive PRCC values for both Latent Costs and Active Costs, and we
-observe large positive PRCC values for Total Costs as well.\\
-
-To gain insight about strategies to reduce the cost burden for TB in the US, we
-focus on the parameters with the greatest PRCC magnitudes for Total Cost aside
-from $C_{A}$ and $C_{L}$, namely $f$, $p$, $ARI_{0}$, and $q$.  All these
-parameters have PRCC magnitudes above 0.7, and are highly correlated with the
-total cost burden of TB borne by the US projected over the next 100 years.  Out
-of these, $ARI_{0}$ is based on a historical fixed value, the Annual Risk of
-Infection among the US born population in the year 2000, and therefore is
-unchangeable under any intervention strategy.  The parameters $p$ (the fraction
-of new infections which are acute) and $q$ (the fraction of infections
-progressing to infectious disease) are variables which depend on physiological
-disease dynamics, and may be altered with advances in medicine or mutations in
-the bacterial strains of TB.  The parameter $f$ is the fraction of FB arrivals
-with LTBI, which may vary depending on US immigration policies and medical
-practices.  These results suggest that treating cases of LTBI among new FB
-arrivals may be the most cost efficient intervention strategy to reduce the
-disease burden for TB in the US, under the assumptions of the Hill model.  \\
+\newpage
+\bibliographystyle{plain}
+\bibliography{draft}
 \end{document}

### 2014-08-03 in_progress/presentations/paper/extendedHillFlowChart.tex
Added some scripts for the paper and worked on the paper

% arara: pdflatex
\documentclass{standalone}
\usepackage{tikz}
\usepackage{standalone}
\usetikzlibrary{positioning,arrows}
\usetikzlibrary{calc}

\begin{document}
\begin{tikzpicture}
  \newdimen\dist
  \dist=1.2cm

  \tikzstyle{modelGate} = [
    % Just text!
    %% The shape:
    %rectangle, minimum height=1cm, minimum width = 3cm, rounded corners=0.5mm,
    %% The border:
    %very thick,
    %draw=blue!50!black!50,
    %% The filling:
    %top color=blue!50!black!20,
    %bottom color=blue!50!black!20,
  ];
  \tikzstyle{annotation} = [
    % Just text!
  ];
  \tikzstyle{compartment} = [
    % The shape:
    rectangle, minimum height=\dist, minimum width=3.5cm, rounded corners=0.5mm,
    % The border:
    very thick,
    draw=red!50!black!50,
    % The filling:
    top color=red!50!black!20,
    bottom color=red!50!black!20,
    % Font:
    font=\itshape
  ];
  \tikzstyle{virtualCompartment} = [
    % The shape:
    rectangle, minimum height=0.5*\dist, minimum width=2.5cm, rounded corners=0.5mm,
    % The border:
    very thick,
    draw=green!50!black!50,dashed,align=center,
    % The filling:
    top color=green!50!black!10,
    bottom color=green!50!black!10,
    % Font:
    font=\itshape
  ];
  \tikzstyle{flow} = [
    draw = black,
    very thick,
    ->
  ]
  \tikzstyle{joiningFlow} = [
    draw = black,
    very thick
  ];

  \node [modelGate] (birthAndImmigration) {};

  \node [compartment, below = \dist of birthAndImmigration] (S) {Susceptible};
  \node [compartment, below right = 2*\dist and 1.5*\dist of S] (L) {Chronic LTBI};
  \node [compartment, below left = 2*\dist and 1.5*\dist of S] (F) {Acute LTBI};

  \node [modelGate, above = 2.2*\dist of L] (FBChronicLTBIArrivals) {};
  \node [modelGate, above = 2.2*\dist of F] (FBAcuteLTBIArrivals) {};

  \node [compartment, below = 3*\dist of L] (I) {Infectious TB};
  \node [compartment, below = 3*\dist of F] (J) {Non-infectious TB};

  \node [modelGate, below = 8*\dist of S] (TBDeath) {};

  \path [flow] (birthAndImmigration) to node[virtualCompartment]
                                            {US Births and uninfected FB
                                             immigration} (S);
  \path [flow] (FBChronicLTBIArrivals) to node[virtualCompartment,pos=0.25]{FB chronic LTBI immigration} (L);
  \path [flow] (FBAcuteLTBIArrivals) to node[virtualCompartment,pos=0.25]{FB acute LTBI immigration} (F);
  \path [flow] (S) to node[virtualCompartment,pos=0.7]{Exogenous Infection} (L);
  \path [flow] (S) to node[virtualCompartment,pos=0.7]{Exogenous Infection} (F);
  \path [flow] (L) to node[virtualCompartment]{Exogenous Re-infection} (F);
  \path [flow] (L) to node[virtualCompartment]{Longstanding LTBI Activation} (I);
  \path [flow] (L) to node[virtualCompartment,pos=0.2]{Longstanding LTBI Activation} (J);
  \path [flow] (F) to node[virtualCompartment,pos=0.2]{Novel TB Activation} (I);
  \path [flow] (F) to node[virtualCompartment]{Novel TB Activation} (J);

  \newdimen\SYCoord
  \pgfextracty\SYCoord{\pgfpointanchor{S}{center}}
  \newdimen\ActiveYCoord
  \pgfextracty\ActiveYCoord{\pgfpointanchor{I}{center}}
  \newdimen\LTBIYCoord
  \pgfextracty\LTBIYCoord{\pgfpointanchor{L}{center}}

  \path [flow] (I.east) to ++(2*\dist,0) 
                        to node[virtualCompartment,pos=0.16]
                               {Active TB Treatment \\ \& \\self-cure}
                               ++(0,\SYCoord-\ActiveYCoord)
                        to (S.east);
  \path [joiningFlow] (L.east) to ++(0.6*\dist,0)
                               to node[virtualCompartment,pos=0.4]
                                      {LTBI Treatment \\ \& \\ self-cure}
                                      ++(0,\SYCoord-\LTBIYCoord);
  \path [flow] (J.west) to ++(-2*\dist,0) 
                        to node[virtualCompartment,pos=0.16]
                               {Active TB Treatment \\ \& \\ self-cure}
                               ++(0,\SYCoord-\ActiveYCoord)
                        to (S.west);
  \path [joiningFlow] (F.west) to ++(-0.6*\dist,0)
                               to node[virtualCompartment,pos=0.4]
                                      {LTBI Treatment \\ \& \\ self-cure}
                                      ++(0,\SYCoord-\LTBIYCoord);

  \path [flow] (I) to node[virtualCompartment]{TB Death} (TBDeath);
  \path [flow] (J) to node[virtualCompartment]{TB Death} (TBDeath);
\end{tikzpicture}

\end{document}

### 2014-08-03 in_progress/presentations/paper/hillFlowChart.tex
Added some scripts for the paper and worked on the paper

--- 2014-08-03 in_progress/presentations/paper/extendedHillFlowChart.tex
@@
   \newdimen\dist
-  \dist=1.2cm
+  \dist=0.7cm
 
@@
   ];
-  \tikzstyle{virtualCompartment} = [
-    % The shape:
-    rectangle, minimum height=0.5*\dist, minimum width=2.5cm, rounded corners=0.5mm,
-    % The border:
-    very thick,
-    draw=green!50!black!50,dashed,align=center,
-    % The filling:
-    top color=green!50!black!10,
-    bottom color=green!50!black!10,
-    % Font:
-    font=\itshape
-  ];
   \tikzstyle{flow} = [
@@
 
-  \node [modelGate] (birthAndImmigration) {};
+  \node [modelGate] (birthAndImmigration) {US Births and uninfected FB
+                                           immigration};
 
   \node [compartment, below = \dist of birthAndImmigration] (S) {Susceptible};
+  \node [annotation, below = 0.25*\dist of S] {New Infection};
   \node [compartment, below right = 2*\dist and 1.5*\dist of S] (L) {Chronic LTBI};
@@
 
-  \node [modelGate, above = 2.2*\dist of L] (FBChronicLTBIArrivals) {};
-  \node [modelGate, above = 2.2*\dist of F] (FBAcuteLTBIArrivals) {};
+  \node [modelGate, above = \dist of L] (FBChronicLTBIArrivals) {FB chronic LTBI immigration};
+  \node [modelGate, above = \dist of F] (FBAcuteLTBIArrivals) {FB acute LTBI immigration};
 
@@
 
-  \node [modelGate, below = 8*\dist of S] (TBDeath) {};
+  \node [modelGate, below = 8*\dist of S] (TBDeath) {TB Death};
 
-  \path [flow] (birthAndImmigration) to node[virtualCompartment]
-                                            {US Births and uninfected FB
-                                             immigration} (S);
-  \path [flow] (FBChronicLTBIArrivals) to node[virtualCompartment,pos=0.25]{FB chronic LTBI immigration} (L);
-  \path [flow] (FBAcuteLTBIArrivals) to node[virtualCompartment,pos=0.25]{FB acute LTBI immigration} (F);
-  \path [flow] (S) to node[virtualCompartment,pos=0.7]{Exogenous Infection} (L);
-  \path [flow] (S) to node[virtualCompartment,pos=0.7]{Exogenous Infection} (F);
-  \path [flow] (L) to node[virtualCompartment]{Exogenous Re-infection} (F);
-  \path [flow] (L) to node[virtualCompartment]{Longstanding LTBI Activation} (I);
-  \path [flow] (L) to node[virtualCompartment,pos=0.2]{Longstanding LTBI Activation} (J);
-  \path [flow] (F) to node[virtualCompartment,pos=0.2]{Novel TB Activation} (I);
-  \path [flow] (F) to node[virtualCompartment]{Novel TB Activation} (J);
+  \path [flow] (birthAndImmigration) to (S);
+  \path [flow] (FBChronicLTBIArrivals) to (L);
+  \path [flow] (FBAcuteLTBIArrivals) to (F);
+  \path [flow] (S) to (L);
+  \path [flow] (S) to (F);
+  \path [flow] (L) to node[auto,swap]{Exogenous Re-infection} (F);
+  \path [flow] (L) to node[auto,swap]{LTBI Activation} (I);
+  \path [flow] (L) to (J);
+  \path [flow] (F) to (I);
+  \path [flow] (F) to node[auto]{LTBI Activation} (J);
 
@@
   \pgfextracty\ActiveYCoord{\pgfpointanchor{I}{center}}
-  \newdimen\LTBIYCoord
-  \pgfextracty\LTBIYCoord{\pgfpointanchor{L}{center}}
 
   \path [flow] (I.east) to ++(2*\dist,0) 
-                        to node[virtualCompartment,pos=0.16]
-                               {Active TB Treatment \\ \& \\self-cure}
-                               ++(0,\SYCoord-\ActiveYCoord)
-                        to (S.east);
-  \path [joiningFlow] (L.east) to ++(0.6*\dist,0)
-                               to node[virtualCompartment,pos=0.4]
-                                      {LTBI Treatment \\ \& \\ self-cure}
-                                      ++(0,\SYCoord-\LTBIYCoord);
+                        to ++(0,\SYCoord-\ActiveYCoord)
+                        to node[auto,swap]{Treatment and self-cure} (S.east);
+  \path [joiningFlow] (L.east) to ++(2*\dist,0);
   \path [flow] (J.west) to ++(-2*\dist,0) 
-                        to node[virtualCompartment,pos=0.16]
-                               {Active TB Treatment \\ \& \\ self-cure}
-                               ++(0,\SYCoord-\ActiveYCoord)
-                        to (S.west);
-  \path [joiningFlow] (F.west) to ++(-0.6*\dist,0)
-                               to node[virtualCompartment,pos=0.4]
-                                      {LTBI Treatment \\ \& \\ self-cure}
-                                      ++(0,\SYCoord-\LTBIYCoord);
-
-  \path [flow] (I) to node[virtualCompartment]{TB Death} (TBDeath);
-  \path [flow] (J) to node[virtualCompartment]{TB Death} (TBDeath);
+                        to ++(0,\SYCoord-\ActiveYCoord)
+                        to node[auto]{Treatment and self-cure} (S.west);
+  \path [joiningFlow] (F.west) to ++(-2*\dist,0);
+  \path [flow] (I) to (TBDeath);
+  \path [flow] (J) to (TBDeath);
 \end{tikzpicture}

### 2014-08-03 deliverables/costBenefitAnalysis/hillFunctions.R

@@ -173,8 +173,10 @@ hill <- function(intervenCost,sigmaL,f,transmission=1,incLTBI=1,initial=cutoffT,
 }
 
 generateIncidence <- function(dataSet) {
+  with(as.list(c(parms)), {
     IN0   <- 1e6 * (vF*dataSet$F0 + vL0*dataSet$L0)/dataSet$N0
     IN1   <- 1e6 * (vF*dataSet$F1 + vL1*dataSet$L1)/dataSet$N1
     INall <- 1e6 * (vF*(dataSet$F0 + dataSet$F1) + vL0*dataSet$L0 + vL1*dataSet$L1)/(dataSet$N0 + dataSet$N1)
-	return(data.frame(IN0,IN1,INall))
+	  return(data.frame(IN0,IN1,INall))
+  })
 }

### 2014-08-03 deliverables/costBenefitAnalysis/interventionConfig.R

@@ -21,7 +21,7 @@ allInterventions <- c("redEnLTBI100","redEnLTBI75","redEnLTBI50","redTrans100",
                       "incLTBItrmt100&redEnLTBI100","incLTBItrmt100&redEnLTBI75",
                       "incLTBItrmt100&redEnLTBI50","incLTBItrmt300&redEnLTBI100",
                       "incLTBItrmt300&redEnLTBI75","incLTBItrmt300&redEnLTBI50")
-curInterventions <- allInterventions
+curInterventions <- c("redEnLTBI10","redEnLTBI25","redEnLTBI50","redEnLTBI100")
 
 interventionConfig <- function(interventionStr) {
   error    <- F
@@ -35,22 +35,10 @@ interventionConfig <- function(interventionStr) {
   interVector <- strsplit(interventionStr,'&')[[1]]
   for (intervention in interVector) {
     interventionType <- sub("\\d+","",intervention)#sub empty str for digits
-    interventionMag  <- sub("\\D+","",intervention)#sub empty str for non-digits
+    interventionMag  <- as.numeric(sub("\\D+","",intervention))#sub empty str for non-digits
     if (interventionType == "redEnLTBI") {
-      #TODO: Make this a function depending on magnitude for greater flexibility
-      # (minor)
-      if (interventionMag == 50) {
-        LTBIEn  <- LTBIEn + 700
-        incLTBI <- incLTBI*0.5
-      } else if (interventionMag == 75) {
-        LTBIEn  <- LTBIEn + 800
-        incLTBI <- incLTBI*0.25
-      } else if (interventionMag == 100) {
-        LTBIEn  <- LTBIEn + 1000
-        incLTBI <- 0
-      } else {
-        error = T
-      }
+      incLTBI <- incLTBI*(100-interventionMag)/100
+      LTBIEn  <- 800 #LTBIEn + 400 + 600*(interventionMag/100) + x*100
     } else if (interventionType == "redImm") {
       #No Costs!
       if (interventionMag == 75) {

### 2014-08-03 deliverables/costBenefitAnalysis/interventionPresenter.R

@@ -51,7 +51,7 @@ presentIntervention <- function(interventionName) {
              scale_y_log10(breaks=c(1,2,5,10,25,50,100,200),
                            labels=c("Elimination (1)",2,5,10,25,50,100,200),
                            limits=c(0.5,250)) + 
-             labs(x="Years", y="Incidence/million", color="Population", 
+             labs(x="Years", y="Incidence/Million", color="Population", 
                   linetype="Intervention Status") + 
              plotTitle("Incidence Levels for Intervention",interventionName) + 
              geom_line(aes(y=baseUSB, color=USB, linetype=noInt))  + 

### 2014-08-03 in_progress/models/costBenefitAnalysis/interventionConfig.R

@@ -35,8 +35,8 @@ split20RedEnLTBIInter <- c('redEnLTBI0','redEnLTBI5','redEnLTBI10',
                            'redEnLTBI75','redEnLTBI80','redEnLTBI85',
                            'redEnLTBI90','redEnLTBI95','redEnLTBI100')
 redEnLTBI_Interventions <- allInterventions[1:3]                 
-redEnLTBI_Interventions_specialMag <- c('redEnLTBI10','redEnLTBI25','redEnLTBI50')                 
-curInterventions <- redEnLTBI_Interventions
+redEnLTBI_Interventions_specialMag <- c('redEnLTBI10','redEnLTBI25','redEnLTBI50','redEnLTBI100')                 
+curInterventions <- redEnLTBI_Interventions_specialMag
 incLTBICost <- 0
 
 interventionConfig <- function(interventionStr, x=0) { #x is an integer refering to cost option, ranges 0 to 5

### 2014-08-03 in_progress/models/costBenefitAnalysis/scriptsForPaper/deSolConstants.R

@@ -1,0 +1,9 @@
+#Initial Values
+deltaT    <- 0.8    #The length of each time step (years).
+initialYr <- 2000
+finalYr   <- 2100
+cutoffYr  <- 2008
+totT      <- floor((finalYr-initialYr)/deltaT)  #Time steps
+cutoffT   <- floor((cutoffYr-initialYr)/deltaT) + 1
+years     <- seq(initialYr+deltaT,finalYr,deltaT)
+yearsPC   <- seq(cutoffYr,finalYr - deltaT,deltaT) #years post cutoff

### 2014-08-03 in_progress/models/costBenefitAnalysis/scriptsForPaper/hillConstants.R

@@ -1,0 +1,38 @@
+sigmaLBase  <- 0.057
+fBase       <- 0.187
+transBase   <- 1
+incLTBIBase <- 1
+
+parms <- c(
+mu0   = 1/78,      #Natural mortality rate USB per year
+mu1   = 1/53,      #Natural mortality rate FB per year
+ro    = 0.018,     #USB birth rate per year
+alpha = 0.005,     #FB arrival rate per year
+p     = 0.103,     #Fraction of new infections which are acute (fast progressors)
+vF    = 1.5,       #Progression rate of acute infection per year
+l0    = 0.015,     #Prevalence of LTBI in the USB population in 2000
+l1    = 0.211,     #Prevalence of LTBI in the FB population in 2000: 
+r0    = 0.667,     #Fraction of cases due to reactivation in the USB population
+r1    = 0.780,     #Fraction of cases due to reactivation in the FB population
+vL0   = 0.0014,    #Progression rate for reactivation (chronic LTBI) in the USB population per year
+vL1   = 0.0010,    #Progression rate for reactivation (chronic LTBI) in the FB population per year
+q     = 0.708,     #Fraction of infections progressing to infectious disease
+mud   = 0.115,     #Mortality rate due to TB per year
+x     = 0.111,     #Fraction of re-infected chronic LTBI moving to acute infection
+ARI0  = 0.030/100, #Annual risk of infection for USB in 2000
+beta  = 10.39,     #Effective contact rate per year
+e0    = 0.965,     #Fraction of preferred contacts with own population for USB
+e1    = 0.985,      #Fraction of preferred contacts with own population for FB
+g     = 0.0047,    #Fraction of FB arrivals with LTBI who are fast progressors
+phi0  = 1.114,     #Cumulative fraction self-cure and treatment of active disease for both populations pre year RATES (USB)
+phi1  = 1.167,     #Cumulative fraction self-cure and treatment of active disease for both populations pre year RATES (FB)
+sigmaF0 = 1.296,   #Cumulative fraction of treatment for acute infection for both populations per year RATES (USB)
+sigmaF1 = 1.301,   #Cumulative fraction of treatment for acute infection for both populations per year RATES (FB)
+sigmaLBase = sigmaLBase, #Treatment rate for chronic LTBI per year
+fBase = fBase,      #Fraction of FB arrivals with LTBI
+
+#2010 New Cases in Population i (millions)
[…]

### 2014-08-03 in_progress/models/costBenefitAnalysis/scriptsForPaper/hillFunctions.R

@@ -1,0 +1,182 @@
+library(deSolve) # for lsoda routine
+
+#Hill Constants
+source('hillConstants.R')
+
+#DE Solving Parameters + runge-kutta solver: 
+source('deSolConstants.R')
+
+#Initializations:
+# Compartments:
+S0<-S1<-F0<-F1<-L0<-L1<-I0<-I1<-J0<-J1<-N0<-N1<-rep(0,totT)
+# Compartment Costs:
+cL0<-cF0<-cI0<-cJ0<-cL1<-cF1<-cI1<-cJ1<-cN0<-cN1<-rep(0,totT)
+# Tracking Data:
+LTBIEn       <- rep(0,totT)                #LTBI arrivals
+LTBIEnD      <- rep(0,totT)                #Discounted LTBI arrivals
+curedLTBIEn  <- rep(0,totT)                #Cured LTBI arrivals
+curedLTBIEnD <- rep(0,totT)                #Discounted Cured LTBI arrivals
+natdeath0    <- natdeath1   <- rep(0,totT) #Natural Deaths
+tbdeath0     <- tbdeath1    <- rep(0,totT) #TB Deaths
+tbdeathD0    <- tbdeathD1   <- rep(0,totT) #Discounted TB Deaths
+progAcute0   <- progAcute1  <- rep(0,totT) #Acute LTBI Progressions
+progChron0   <- progChron1  <- rep(0,totT) #Chronic LTBI Progressions
+progTotalD0  <- progTotalD1 <- rep(0,totT) #Discounted Progressions
+exogenous0   <- exogenous1  <- rep(0,totT) #Exogenous re-Infections
+interventionCost <- rep(0,totT)            #Cumulative intervention cost
+
+#Intervention per time step cost array 
+# cost of new cases, total population, and LTBI cases entering
+P <- data.frame(S0,F0,L0,I0,J0,S1,F1,L1,I1,J1,N0,N1,cL0,cF0,cI0,cJ0,cL1,cF1,cI1,
+                cJ1,cN0,cN1,LTBIEn,LTBIEnD,curedLTBIEn,curedLTBIEnD,natdeath0,
+                natdeath1,tbdeath0,tbdeath1,tbdeathD0,tbdeathD1,progAcute0,
+                progChron0,progAcute1,progChron1,progTotalD0,progTotalD1, 
+                exogenous0,exogenous1,interventionCost)
+
[…]

### 2014-08-03 in_progress/models/costBenefitAnalysis/scriptsForPaper/interventionAnalyzer.R

@@ -1,0 +1,37 @@
+#Option Processing
+args <- commandArgs(trailingOnly = T)
+if (length(args) > 0) {
+  generateNewData <- as.logical(args[1])
+} else {
+  generateNewData <- F
+}
+
+#Which interventions to run:
+source('interventionConfig.R')
+
+#Hill Model:
+source('hillFunctions.R')
+
+#Base Data: 
+C <- c(newCases=0,totPop=0,LTBIEn=0) 
+if (!generateNewData) {
+  P               <- read.csv(baseFile)
+  generateNewData <- (length(P$X) != length(years))
+  P$X             <- NULL
+} 
+if (generateNewData) {
+  P <- hill(C,sigmaLBase,fBase,transBase,incLTBIBase,1,totT)
+  write.csv(P,baseFile)
+}
+baseInc <- generateIncidence(P)
+
+#Intervention Analyzing:
+#for (intervention in curInterventions) {
+#  intConfig <- interventionConfig(intervention)
+#  costs     <- intConfig$costs
+#  params    <- intConfig$params
+#  interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
+#                    params[["incLTBI"]])
+#  write.csv(interData, paste(c(intFilePrefix,intervention,intFileSuffix),
+#                             collapse=""))
+#}

### 2014-08-03 in_progress/models/costBenefitAnalysis/scriptsForPaper/interventionConfig.R

@@ -1,0 +1,84 @@
+source('hillConstants.R')
+
+directory     <- 'data/'
+baseFile      <- paste(c(directory,'baseData.csv'),collapse="")
+intFilePrefix <- directory
+intFileSuffix <- '.csv'
+#Intervention string details:
+# inc/red                   --> increase/reduce 
+# EnLTBI/Imm/LTBItrmt/Trans --> Entering LTBI, Immigration, LTBI Treatment, 
+#                               Transmission.
+# Magnitude (the numbers)   --> Interpert these by placing a 'by' prior to the 
+#                               number and adding a percent at the end. 
+# &                         --> 'and'. This chains interventions.
+#Ex: 
+# redImm25&incLTBItrmt100   --> reduce immigration by 25% and increase LTBI 
+#                               treatment by 100%
+allInterventions <- c("redEnLTBI100","redEnLTBI75","redEnLTBI50","redTrans100",
+                      "redImm75","redImm50","incLTBItrmt100","incLTBItrmt300",
+                      "redImm75&incLTBItrmt100","redImm50&incLTBItrmt100",
+                      "redImm75&incLTBItrmt100","redImm50&incLTBItrmt300",
+                      "incLTBItrmt100&redEnLTBI100","incLTBItrmt100&redEnLTBI75",
+                      "incLTBItrmt100&redEnLTBI50","incLTBItrmt300&redEnLTBI100",
+                      "incLTBItrmt300&redEnLTBI75","incLTBItrmt300&redEnLTBI50")
+paperRedEnLTBIInts <- c("redEnLTBI10","redEnLTBI25","redEnLTBI50","redEnLTBI100")
+paperRedTransInts <- c("redTrans100")
+curInterventions <- c("redEnLTBI10","redEnLTBI25","redEnLTBI50",
+                      "redEnLTBI100","redTrans100")
+
+interventionConfig <- function(interventionStr) {
+  error    <- F
+  sigmaL   <- sigmaLBase #define me
+  f        <- fBase
+  trans    <- transBase
+  incLTBI  <- incLTBIBase
+  newCases <- 0
+  totPop   <- 0
+  LTBIEn   <- 0
+  interVector <- strsplit(interventionStr,'&')[[1]]
+  for (intervention in interVector) {
+    interventionType <- sub("\\d+","",intervention)#sub empty str for digits
+    interventionMag  <- as.numeric(sub("\\D+","",intervention))#sub empty str for non-digits
[…]

### 2014-08-03 in_progress/models/costBenefitAnalysis/scriptsForPaper/interventionGroups.R

@@ -1,0 +1,44 @@
+source('interventionAnalyzer.R')
+#Group by type IMPORTANT: Reset all intervention costs to default values in interventionConfig.R before running
+#for(intervention in redEnLTBI_Interventions_specialMag) {
+#  intConfig <- interventionConfig(intervention)
+#  costs     <- intConfig$costs
+#  params    <- intConfig$params
+#  interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
+#                    params[["incLTBI"]])
+#  write.csv(interData, paste(c(intFilePrefix,intervention,intFileSuffix),
+#                             collapse=""))
+#}
+#
+#for(intervention in incLTBItrmt_Interventions) {
+#  intConfig <- interventionConfig(intervention)
+#  costs     <- intConfig$costs
+#  params    <- intConfig$params
+#  interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
+#                    params[["incLTBI"]])
+#  write.csv(interData, paste(c(intFilePrefix,intervention,intFileSuffix),
+#                             collapse=""))
+#}
+#
+#
+##Cost Vary
+#for(x in 0:9){
+#  for(intervention in redEnLTBI_Interventions_specialMag) {
+#    intConfig <- interventionConfig(intervention,x)
+#    costs     <- intConfig$costs
+#    params    <- intConfig$params
+#    interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
+#                    params[["incLTBI"]])
+#    write.csv(interData, paste(c(intFilePrefix,intervention,x,intFileSuffix),
+#                             collapse=""))
+#  }
+#  # for(intervention in incLTBItrmt_Interventions) {
+#    # intConfig <- interventionConfig(intervention,x)
+#    # costs     <- intConfig$costs
+#    # params    <- intConfig$params
+#    # interData <- hill(costs,params[["sigmaL"]],params[["f"]],params[["trans"]],
+#                    # params[["incLTBI"]])
+#    # write.csv(interData, paste(c(intFilePrefix,intervention,x,intFileSuffix),
+#                             # collapse=""))
+#  # }
+#}

### 2014-08-03 in_progress/models/costBenefitAnalysis/scriptsForPaper/interventionGroupsPresenter.R

@@ -1,0 +1,325 @@
+library(ggplot2)
+source('interventionGroups.R')
+source('deSolConstants.R')
+
+#Title Generation:
+plotTitle <- function(base,interventionName,final="") {
+  if (final != "") {
+    return(ggtitle(paste(c(base,interventionName,final),collapse=" ")))
+  } else {
+    return(ggtitle(paste(c(base,interventionName),collapse=" ")))
+  }
+}
+
+baseData <- read.csv(baseFile)
+#Base Incidence
+baseInc <- generateIncidence(baseData)
+#US Health Care System (HCS) TB costs due to base system
+baseHCSCost <- (baseData$cN0 + baseData$cN1)/1e9
+baseCasesD <- 1e6*(baseData$progTotalD0 + baseData$progTotalD1)
+
+#Data Labels
+USB             <- rep("USB",                 totT)
+FB              <- rep("FB",                  totT)
+all             <- rep("All",                 totT)
+noInt           <- rep("No Intervention",     totT)
+int             <- rep("Intervention",        totT)
+int10           <- rep("10% Cured",           totT)
+int25           <- rep("25% Cured",           totT)
+int50           <- rep("50% Cured",           totT)
+int100          <- rep("100% Cured",          totT)
+savings         <- rep("Savings",             totT)
+costs           <- rep("Implementation Cost", totT)
+totalCosts      <- rep("US HCS Cost",         totT)
+averted         <- rep("Cases Averted",       totT)
+TBdeathsAverted <- rep("TB Deaths Averted",   totT)
+redEnLTBI100L   <- rep("100% reduction",      totT)
+redEnLTBI75L    <- rep("75% reduction",       totT)
+redEnLTBI50L    <- rep("50% reduction",       totT)
+redEnLTBI25L    <- rep("25% reduction",       totT)
+redEnLTBI10L    <- rep("10% reduction",       totT)
+
+#Aesthetics
+USBC             <- 'blue'
+FBC              <- 'green'
+allC             <- 'red'
+noIntC           <- 'black'
+intC             <- 'blue'
+savingsC         <- '#24913C'
+costsC           <- '#9F0013'
+avertedC         <- '#24913C'
+TBdeathsAvertedC <- '#24913C'
+
+# Creating our data containers.
+rawData      <- as.list(paperRedEnLTBIInts)
+incidence    <- as.list(paperRedEnLTBIInts)
[…]

### 2014-08-03 in_progress/models/costBenefitAnalysis/scriptsForPaper/interventionPresenter.R

@@ -1,0 +1,249 @@
+library(ggplot2)
+source('deSolConstants.R')
+source('hillFunctions.R') #for generateIncidence
+source('interventionConfig.R')
+
+#Title Generation:
+plotTitle <- function(base,interventionName,final="") {
+  if (final != "") {
+    return(ggtitle(paste(c(base,interventionName,final),collapse=" ")))
+  } else {
+    return(ggtitle(paste(c(base,interventionName),collapse=" ")))
+  }
+}
+
+#Data Labels
+USB             <- rep("USB",             totT)
+FB              <- rep("FB",              totT)
+all             <- rep("All",             totT)
+noInt           <- rep("No Intervention", totT)
+int             <- rep("Intervention",    totT)
+savings         <- rep("Savings",         totT)
+costs           <- rep("Cost",            totT)
+averted         <- rep("Cases Averted",   totT)
+TBdeathsAverted <- rep("TB Deaths Averted",   totT)
+
+#Aesthetics
+USBC             <- 'blue'
+FBC              <- 'green'
+allC             <- 'red'
+noIntC           <- 'black'
+intC             <- 'blue'
+savingsC         <- '#24913C'
+costsC           <- '#9F0013'
+avertedC         <- '#24913C'
+TBdeathsAvertedC <- '#24913C'
+
+baseData         <- read.csv(baseFile)
+baseInc          <- generateIncidence(baseData)
+
+presentIntervention <- function(interventionName) {
+  interventionData <- read.csv(paste(c(intFilePrefix,interventionName,
+                                       intFileSuffix),collapse=""))
+  interventionInc  <- generateIncidence(interventionData)
+  
+  #Incidence Reports: Comparing Baseline Incidence against Intervention Incidence
+  incData <- data.frame(year = years, 
+                        baseUSB = baseInc$IN0,   intUSB = interventionInc$IN0, 
+                        baseFB  = baseInc$IN1,    intFB = interventionInc$IN1, 
+                        baseAll = baseInc$INall, intAll = interventionInc$INall)
+  incPlot <- ggplot(incData, aes(x=year)) + 
+             scale_y_log10(breaks=c(1,2,5,10,25,50,100,200),
+                           labels=c("Elimination (1)",2,5,10,25,50,100,200),
[…]

### 2014-08-03 in_progress/models/costBenefitAnalysis/scriptsForPaper/old.R

@@ -1,0 +1,55 @@
+
+y <- 1
+for (interventionName in paperRedEnLTBIInts) {
+  interventionData[[y]] <- read.csv(paste(c(intFilePrefix,interventionName,
+                                       intFileSuffix),collapse=""))
+  #HCS cost borne by intervention
+  interHCSCost[[y]] <- (interventionData[[y]]$cN0 + interventionData[[y]]$cN1)/1e9
+  #Implementation cost of intervention
+  costOfInter[[y]] <- (interventionData[[y]]$interventionCost)/1e9
+  #Savings from intervention
+  saveOfInter[[y]] <- baseHCSCost - interHCSCost[[y]]
+  print(interventionName)
+  print(saveOfInter[[y]])
+  #Total US HCS cost due to intervention
+  interTot[[y]] <- interHCSCost[[y]] + costOfInter[[y]]
+  #Total additional spent by US HCS due to intervention
+  totSpent[[y]]  <- interTot[[y]] - baseHCSCost 
+  
+  #Cost per cases averted
+  intCasesD         <- 1e6*(interventionData[[y]]$progTotalD0 + interventionData[[y]]$progTotalD1)
+  casesAvertedD     <- baseCasesD - intCasesD
+  cpcaDataD <- 1e9*totSpent[[y]]/casesAvertedD
+  
+  y <- y + 1
+}
+
+
+yrange <- round(seq(min(-1*saveOfInter[[1]])-0.5,max(costOfInter[[1]])+0.5,by=0.5),1)
+
+# Plot of cost averted (savings)
+# Only includes costs for Active TB treatment
+# No treatment implementation costs accounted for
+
+redEnLTBISavings <- data.frame(year = years, 
+                        redEnLTBI10_savings  = saveOfInter[[1]], 
+                        redEnLTBI25_savings  = saveOfInter[[2]], 
+                        redEnLTBI50_savings  = saveOfInter[[3]],
+                        redEnLTBI100_savings = saveOfInter[[4]])
+
+x <- ggplot(redEnLTBISavings,aes(x=year)) + 
+       labs(x="Years", y="Billions of USD", color="Economic Distinction", 
+            linetype="% Reduction") +
+       #scale_y_continuous(breaks=yrange) + 
+       plotTitle("Averted TB Costs for US HCS given 
+10%, 25%, and 50% LTBI reduction","") + 
+       geom_hline(aes(y=0),size=2) +
[…]

### 2014-08-03 in_progress/models/costBenefitAnalysis/scriptsForPaper/rightWay.R

@@ -1,0 +1,23 @@
+
+# Creating our data containers.
+rawData      <- data.frame(years=years,base=baseData)# as.list(paperRedEnLTBIInts)
+incidence    <- data.frame(years=years,baseUSB=baseInc$IN0,
+                                       baseFB =baseInc$IN1,
+                                       baseAll=baseInc$INall)# as.list(paperRedEnLTBIInts)
+HCSCost      <- data.frame(years=years)# as.list(paperRedEnLTBIInts)
+costOfInter  <- data.frame(years=years)# as.list(paperRedEnLTBIInts)  
+saveOfInter  <- data.frame(years=years)# as.list(paperRedEnLTBIInts)  
+interTot     <- data.frame(years=years)# as.list(paperRedEnLTBIInts)
+totSpent     <- data.frame(years=years)# as.list(paperRedEnLTBIInts) 
+cpca         <- data.frame(years=years)# as.list(paperRedEnLTBIInts)
+casesAverted <- data.frame(years=years)# as.list(paperRedEnLTBIInts)
+# Naming them for convenience.
+# names(interventionData) <- paperRedEnLTBIInts
+# names(interventionInc)  <- paperRedEnLTBIInts
+# names(interHCSCost)     <- paperRedEnLTBIInts
+# names(costOfInter)      <- paperRedEnLTBIInts
+# names(saveOfInter)      <- paperRedEnLTBIInts
+# names(interTot)         <- paperRedEnLTBIInts
+# names(totSpent)         <- paperRedEnLTBIInts
+# names(cpca)             <- paperRedEnLTBIInts
+# names(casesAverted)     <- paperRedEnLTBIInts

### 2014-08-03 in_progress/presentations/paper/draft.tex
Updated draft

@@
 the individual.  Left untreated, individuals with LTBI have a lifelong
-probability of approximately 10\% to develop active TB.
-\TODO{in total? Or after they've progressed through the first two years? We need
-a new source for this, I think. It's not in the logical place of the WHO report.
-This also obviously needs to be cited. }
-The health risks for individuals with active TB are severe, and without medical
-interventions, the 10 year mortality rate for the disease is between 20\% and
-70\%, depending on the severity of the case and definition of a positive
-diagnosis.
-\cite{_who_2013}.
+probability of approximately 10\% to develop active TB. The health risks for
+individuals with active TB are severe, and without medical interventions, the 10
+year mortality rate for the disease is between 20\% and 70\%, depending on the
+severity of the case and definition of a positive diagnosis
+\cite{_who_2013,tufariello_latent_2003}.
 
@@
 costs of cases requiring hospitalization (49\%) and cases not requiring
-hospitalization (51\%).  These cost estimates were found in \TODO{<+DYLAN COST
-STUDY CITATION+>.} LTBI treatment costs were assumed to be \$468.00, charged
-immediately upon successful treatment. These estimates were calculated based on
-the cost of a successful treatment, and the typical adherence and efficacy of
-said treatment \TODO{<+DYLAN COST STUDY CITATION, ADHERENCE CITATION+>.} Note
+hospitalization (51\%).  LTBI treatment costs were assumed to be \$468.00,
+charged immediately upon successful treatment. These estimates were calculated
+based on the cost of a successful treatment, and the typical adherence and
+efficacy of said treatment
+\cite{lobue_use_2003,page_kr_improved_2006,denholm_use_2010}.
+\TODO{<+DYLAN COST STUDY CITATION+>.} 
+Note
 that active TB treatment costs are charged immediately upon disease contraction,
@@
 \subsubsection{Cost Effectiveness}
-\TODO{It also needs to talk about the cost effectiveness of reducing
-  transmission or something, to say that we're getting competitive numbers. We
-need a good source for cpca data for contact investigations, etc.}
 We also estimated the cost per case averted of curing entering cases of LTBI. To
@@
 cases of TB and 1,025, 2,573, and 5,185 fewer TB deaths for 10\%, 25\%, and 50\%
-cure rate, respectively.
-
-%We also found that the relationship between total incidence at 2100 and
-%percentage of incoming LTBI cases cured was linear. Given this, we estimated the
-%yearly average US HCS savings garnered by curing one case of entering LTBI per
-%year from 2000 to 2025, 2000 to 2050, and 2000 to 2100.  This value peaked
-%at \$1.283 billion at 2100 (25\% reduction). This illustrates that it
-%would be cost saving to cure cases of LTBI at the cost of \$1.283 billion
-%``2000'' dollars over the time period 2000-2100. 
-%These findings are illustrated in Table~\ref{tab:redEnLTBICosts}
+cure rate, respectively. These costs compare favorably to certain styles of
+contact investigation, which is a widely practiced intervention. In particular,
+using the common concentric circle approach to contact investigation over the contact
+priority method (which is slightly less effective, but cheaper) has a cost per case
+averted of \$92,934 from one estimate, which is substantially more than the cost
+per case averted of treating entering LTBI found here \cite{pisu_targeted_2009}.
 
@@
 such as geographic dependency or greater population heterogeneity.
+
+\TODO{Improve Figure~\ref{fig:finalDists}. The labels need to be bigger, and it
+might be wise to illustrate via some marker where the hill model results live.}
 
@@
 The extended Hill also added certain equations and constants to generate cost
-data. These equations are detailed in Figure~%\ref{fig:hillCosts}. 
-\TODO{Add figure hillCosts. We first need to determine what the correct LTBI
-cost parameters are. See the TODO above regarding that.}
-These parameters were derived via
-\TODO{Cite Dylan's cost study, adherence study, etc.}
+data. These equations are detailed in Figure~\ref{fig:hillCosts}.
+\begin{figure}[h]
+  \centering
+  \TODO{Add this figure. We first need to determine what the correct LTBI
+  cost parameters are. See the TODO above regarding that. Also cite Dylan's
+paper here.}
+  \caption{The equations used to track the economic impact of US TB dynamics.
+  Parameters derived principally from
+  \cite{lobue_use_2003,page_kr_improved_2006,denholm_use_2010}}
+  \label{fig:hillCosts}
+\end{figure}
 
